### 2019-04-30 Draft.tex
first draft

\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[center]{caption}
\usepackage{hyperref}

\usepackage{apacite}

\definecolor{green}{rgb}{0,1,0}
\newcommand{\NS}[1] {{\textcolor{green}{#1}}}
\newcommand{\TM}[1] {{\textcolor{orange}{#1}}}
\newcommand{\AT}[1] {{\textcolor{blue}{#1}}}

\begin{document}
\title{ESRC SDAI Application}
\maketitle

Domestic abuse is a multifaceted phenomenon that affects people from all walks of life, and is increasingly recognised as a major public policy concern across the world, including the UK. While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men have reported to have experienced some form of domestic abuse since the age of 16 in England and Wales \cite{ONS}. The current legal definition of domestic abuse in the UK \cite{govuk} aims to capture its complex nature by recognising it as a pattern of behaviour encompassing a wide range of behaviours, including emotional, sexual, and physical abuse; threatening and intimidating behaviour, and coercive and controlling behaviour, which was introduced in 2015.

Mental health implications? The most extreme cases of domestic abuse domestic homicides resulting in the loss of 70 lives in England and Wales in the period between April, 2017 and March, 2018, of whom 90\% of were women \cite{homic}.

Taken these together, the estimated economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was £66 billion \cite{costs}.

Recognising the severity of this widespread societal problem has resulted in the UK government launching several awareness campaigns to both encourage reporting and

\bibliographystyle{apacite}
\bibliography{domesticabuse_refs}

\end{document}

### 2019-05-03 Draft.tex
Anna first draft

@@
 \title{ESRC SDAI Application}
+\date{}
 \maketitle
 
-Domestic abuse is a multifaceted phenomenon that affects people from all walks of life, and is increasingly recognised as a major public policy concern across the world, including the UK.
-While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men have reported to have experienced some form of domestic abuse since the age of 16 in England and Wales \cite{ONS}.
-The current legal definition of domestic abuse in the UK \cite{govuk} aims to capture its complex nature by recognising it as a pattern of behaviour encompassing a wide range of behaviours, including emotional, sexual, and physical abuse; threatening and intimidating behaviour, and coercive and controlling behaviour, which was introduced in 2015.
+\section{Intro}
 
-Mental health implications?
-The most extreme cases of domestic abuse domestic homicides resulting in the loss of 70 lives in England and Wales in the period between April, 2017 and March, 2018, of whom 90\% of were women \cite{homic}.
+Domestic abuse is a complex phenomenon affecting people from all walks of life.
+It is increasingly recognised as a major public policy concern in many countries, including the UK \cite{ep}.
+While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men in England and Wales reported to have experienced some form of domestic abuse since the age of 16 \cite{ONS}.
+The current legal definition in the UK \cite{govuk} aims to capture the multifaceted nature of domestic abuse, by recognising that domestic abuse encompasses a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour.
 
-Taken these together, the estimated economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was £66 billion \cite{costs}.
+Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, along with a significantly higher likelihood of reporting symptoms of anxiety and depression, compared to the general population \cite{ferrari}.
+In addition, witnessing domestic abuse at home can have severe developmental impacts on children, including an increased risk of experiencing mental and physical health problems and encountering difficulties in interpersonal relationships in later life, worse educational attainment, and increased likelihood of engaging in criminal behaviours \cite{callaghan}.
 
-Recognising the severity of this widespread societal problem has resulted in the UK government launching several awareness campaigns to both encourage reporting and
+In the most extreme cases, domestic abuse can culminate in domestic homicide.
+In the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, 90\% of the victims were women \cite{homic}.
+While the pervasive problem of underreporting poses a significant obstacle to deriving reliable estimates of the true extent of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be £66 billion \cite{costs}.
+The largest component of this cost is represented by the physical and emotional consequences of abuse, reflected in a reduced expected quality of life for survivors.
+In addition, lost economic output resulting from missed workdays and reduced productivity, and costs to the health care system also significantly contribute to the overall figure.
+
+Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020.
+The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
+
+\section{Data}
+
+Our datasets include the
+
+\section{Aims}
+
+\subsection{Victim-offender profiles - comparison of CSEW and WMPD}
+
+Aim 1: Who perpetrates?
+Who becomes a victim?
+- our police dataset allows us to explore what other types of criminal behaviours abusers are likely to engage in/be a victim of; same for victims with police and CSEW; victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
+Find out what kind of cases get reported.
+Break down the 17\% based on socioeconomic and incident characteristics.
+
+\subsection{Reporting behaviour}
+Aim 2: The timecourse of abuse.
+The decision to report.
+Breaking point theory - do we see a long string of abuse being reported after certain days (Xmas, Valentine’s day)?
+Hazard model?
+Tim knows the birthdays.
+Separation.
+
+\subsection{Association with other criminal behaviours}
+Aim 3: explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
+No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
+Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+
+\subsection{Protective factors - shouldn't this go into the victim-offender profiles?}
+Aim 4: Protective factors and interventions.
+various aspects of alcohol-involvement.
+Is it worse when alcohol is involved?
+{Outlawed: Coventry domestic abuse interventions?} Protective factors identified in CSEW data---e.g., having a job, car, no litter outside, living with other relatives,
 

### 2019-05-17 Draft.tex
update

@@
 The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
+\textit{Sentence about that while violent crime is decreasing, if repeat victims of domestic abuse is taken into account, domestic violence against women shows an increasing trend}
 
@@
 \subsection{Reporting behaviour}
+
 Aim 2: The timecourse of abuse.
@@
 \subsection{Association with other criminal behaviours}
+
 Aim 3: explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?

### 2019-05-17 Draft.tex
update

@@
 
-Aim 2: The timecourse of abuse.
-The decision to report.
-Breaking point theory - do we see a long string of abuse being reported after certain days (Xmas, Valentine’s day)?
+Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides.
+Our unique crime dataset will allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.
+
+We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
+Insights from this investigation can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+
+Separation is one of the biggest predictors of abuse resulting in serious injury.
+Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+
  Hazard model?
-Tim knows the birthdays.
-Separation.
 

### 2019-05-17 Draft.tex
Update Draft.tex

--- 2019-05-17 Draft.tex
@@
 
+It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
+It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes.
+We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse.
+The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.
+It also contains information about  multiple members of the household.
+This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime.
+By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
+
+The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years.
+We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
+Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk.
+In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes.
+It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.
+For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
+
+victim future behavs, risk factors, intervention possibility
+
 Aim 3: explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?

### 2019-05-17 Draft.tex
update

--- 2019-05-17 Draft.tex
@@
 
+We first explore the characteristics of offenders and victims, focusing on gender, age and ethnicity.
+
 Aim 1: Who perpetrates?
@@
 Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides.
-Our unique crime dataset will allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.
+We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police and identify groups who are the least likely to report.
+We can contrast and validate these findings using our crime dataset.
 
+Our unique crime dataset will further allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.
 We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
@@
 Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
-
- Hazard model?
 

### 2019-05-17 Draft.tex
update

@@
 \usepackage{apacite} 
+\usepackage{setspace}
+\doublespacing
 
@@
 The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
-\textit{Sentence about that while violent crime is decreasing, if repeat victims of domestic abuse is taken into account, domestic violence against women shows an increasing trend}
 
@@
 
-Our datasets include the
+Our crime dataset was provided by the West Midlands Police, and includes all recorded crimes and incidents from the period between January, 2010 and October, 2018.
+Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK, whereas domestic abuse incidents refer to cases that do not qualify as a crime.
+About 31\% of all crimes and incidents have a domestic abuse marker.
+For each record in this dataset, we have information about the exact location and time of the incident or crime, the gender, age and ethnicity of the offender and victim, and the severity of the injury sustained by the victim, if any.
+The first and last occurrence of the offence, as well as the exact time of reporting is also recorded.
+Each person in this dataset has a unique person identifier, allowing us to follow people over time.
+
+Talk about CSEW
 
@@
 
-Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides.
-We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police and identify groups who are the least likely to report.
+Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
+We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
 We can contrast and validate these findings using our crime dataset.

### 2019-05-18 Draft.tex
update

@@
 
-Talk about CSEW
+The Crime Survey for England and Wales (CSEW) is an annual, representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year (ref).
+The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular (ref).
+Given the vast levels of underreporting characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+
+The two datasets have different merits allowing us to gain a deeper insight into the phenomenon and derive policy implications.
+The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic and socio-economic information on the respondent (victim).
 

### 2019-05-18 Draft.tex
update

--- 2019-05-17 Draft.tex
@@
 The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
+\textit{I found an \href{https://www.researchcatalogue.esrc.ac.uk/grants/ES.K002899.1/read}{SDAI Grant}  from 2014 in which they show that if the CSEW does not use capping when it comes to the number of reported DA incidents, the prevalence of DA against women increases between 2008 and 2014 (following a long decline), contrary to the overall decline in violent crimes.
+Shall I make a reference to this?}
 
@@
 
-Our crime dataset was provided by the West Midlands Police, and includes all recorded crimes and incidents from the period between January, 2010 and October, 2018.
+\textit{My current approach is to describe the two datasets in two paragraphs, and then briefly discuss the range of research questions we can answer with them.}
+
+The first dataset is provided by the West Midlands Police, and includes all recorded crimes and incidents from the period between January, 2010 and October, 2018.
+The West Midlands Police is the third largest police force in England, serving a population of 2.9 million \textit{(ref)}.
 Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK, whereas domestic abuse incidents refer to cases that do not qualify as a crime.
@@
 Each person in this dataset has a unique person identifier, allowing us to follow people over time.
+\textit{Sentence about access to this dataset.}
 
-Talk about CSEW
+The second dataset is the Crime Survey for England and Wales (CSEW), which is an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \textit{(ref)}.
+The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular \textit{(ref)}.
+Given the serious problem of underreporting uniquely characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+
+The two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
+The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (victim).
+However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators.
+In contrast, the crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships and identify the predictors of escalation.
+Information on the exact timing of the abuse and the time of reporting will help us identify high-risk times of the year and understand the factors influencing the decision to report.
+Information on alcohol involvement is more likely to be accurate in the crime dataset than in the self-completion survey.
+Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender and victim.
+We do not intend to link the two datasets.
 
@@
 We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
-We can contrast and validate these findings using our crime dataset.
+We can contrast and validate these findings using the crime dataset.
 
-Our unique crime dataset will further allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.
+The crime dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time.
 We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
-Insights from this investigation can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
 
 Separation is one of the biggest predictors of abuse resulting in serious injury.
-Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+If not, we can still use info on location + breaches of non-molestation orders?}
 

### 2019-05-18 Draft.tex
update

@@
 The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
-\textit{I found an \href{https://www.researchcatalogue.esrc.ac.uk/grants/ES.K002899.1/read}{SDAI Grant}  from 2014 in which they show that if the CSEW does not use capping when it comes to the number of reported DA incidents, the prevalence of DA against women increases between 2008 and 2014 (following a long decline), contrary to the overall decline in violent crimes.
-Shall I make a reference to this?}
+These interventions are crucial in light of the fact that after a long decline, domestic violence against women has significantly increased between the period of 2008 and 2014 \textit{ref}.
 
@@
 
-We first explore the characteristics of offenders and victims, focusing on gender, age and ethnicity.
+We first explore the characteristics of offenders and victims. \textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
+
+While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the offenders.
+Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are
+
+The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
+We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
 
@@
 Who becomes a victim?
-- our police dataset allows us to explore what other types of criminal behaviours abusers are likely to engage in/be a victim of; same for victims with police and CSEW; victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
+victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
 Find out what kind of cases get reported.
@@
 
-\subsection{Reporting behaviour}
+\subsection{Reporting behaviour and temporal dynamics}
 
@@
 
+\newpage
+
 \bibliographystyle{apacite}

### 2019-06-07 Draft.tex
update

@@
 
-Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, along with a significantly higher likelihood of reporting symptoms of anxiety and depression, compared to the general population \cite{ferrari}.
-In addition, witnessing domestic abuse at home can have severe developmental impacts on children, including an increased risk of experiencing mental and physical health problems and encountering difficulties in interpersonal relationships in later life, worse educational attainment, and increased likelihood of engaging in criminal behaviours \cite{callaghan}.
+Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, and a significantly higher likelihood of reporting symptoms of anxiety and depression, compared to the general population \cite{ferrari}.
+The long lasting impacts of domestic abuse are not limited to the direct target of abuse.
+Witnessing domestic abuse at home can have severe developmental impacts on children, including an increased risk of experiencing mental and physical health problems and encountering difficulties in interpersonal relationships in later life, worse educational attainment, and increased likelihood of engaging in criminal behaviours \cite{callaghan}.
+
+As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature.
+Estimates show that on average, victims live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}.
+The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey including a self-completion module on domestic abuse.
+According to the CSEW, of those respondents who experienced domestic abuse between April 2017 and March 2018, only 17\% reported it to the police \cite{ONS}.
+This extremely high level of underreporting is another characteristic that is specific to domestic abuse.
 
 In the most extreme cases, domestic abuse can culminate in domestic homicide.
-In the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, 90\% of the victims were women \cite{homic}.
-While the pervasive problem of underreporting poses a significant obstacle to deriving reliable estimates of the true extent of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be £66 billion \cite{costs}.
+In the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, 90\% of these victims were women \cite{homic}, demonstrating that domestic abuse is a fundamentally gendered phenomenon.
+While the pervasive problem of underreporting poses a significant obstacle to deriving reliable estimates of the true extent of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
 The largest component of this cost is represented by the physical and emotional consequences of abuse, reflected in a reduced expected quality of life for survivors.
-In addition, lost economic output resulting from missed workdays and reduced productivity, and costs to the health care system also significantly contribute to the overall figure.
+In addition, lost economic output resulting from missed workdays and reduced productivity, as well as costs to the health care system also significantly contribute to the overall figure.
 
@@
 The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
-These interventions are crucial in light of the fact that after a long decline, domestic violence against women has significantly increased between the period of 2008 and 2014 \textit{ref}.
+
+%These interventions are crucial in light of the fact that after a long decline, domestic violence against women has significantly increased between the period of 2008 and 2014 \textit{ref}.
+
+\newpage
 
 \section{Data}
-
-\textit{My current approach is to describe the two datasets in two paragraphs, and then briefly discuss the range of research questions we can answer with them.}
 
@@
 
-Aim 3: explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
+ explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
 No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
@@
 
-\subsection{Protective factors - shouldn't this go into the victim-offender profiles?}
-Aim 4: Protective factors and interventions.
-various aspects of alcohol-involvement.
-Is it worse when alcohol is involved?
-{Outlawed: Coventry domestic abuse interventions?} Protective factors identified in CSEW data---e.g., having a job, car, no litter outside, living with other relatives,
+\subsection{Environmental factors}
+
+neighbourhood characteristics (deprivation), fixed odds betting terminals, alcohol outlets, events (football, festivals)
 

### 2019-06-07 Draft.tex
update

@@
 
+anything that affects propensity to drink/financial stress
+
 neighbourhood characteristics (deprivation), fixed odds betting terminals, alcohol outlets, events (football, festivals)
+
+\href{https://www.birminghammail.co.uk/news/midlands-news/universal-credit-rolled-out-across-14142901}{Universal credit roll-out in the West Midlands}
+
+\href{https://www.birminghammail.co.uk/black-country/universal-credit-claimants-black-country-15946831}{Universal credit roll-out in the Black Country}
+
+food bank dependence? data on housing e.g. evictions? homelessness.
 

### 2019-06-12 Draft.tex
Formatting
Reorganisation

@@
-\documentclass[12pt, letterpaper]{article}
+\documentclass[11pt, a4paper]{article}
+
+% Helvetica
+\usepackage[scaled]{helvet}
+\renewcommand\familydefault{\sfdefault} 
+\usepackage[T1]{fontenc}
+
+% 2cm margins
+\usepackage[margin=2cm]{geometry}
+
 \usepackage{graphicx}
@@
 \usepackage{apacite} 
-\usepackage{setspace}
-\doublespacing
+%\usepackage{setspace}
+%\doublespacing
 
@@
 The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (victim).
-However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators.
+However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators and has limited longitudinal information.
 In contrast, the crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships and identify the predictors of escalation.
@@
 
-\subsection{Victim-offender profiles - comparison of CSEW and WMPD}
-
-We first explore the characteristics of offenders and victims. \textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
-
-While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the offenders.
-Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are
-
-The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
-We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
-
-Aim 1: Who perpetrates?
-Who becomes a victim?
-victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
-Find out what kind of cases get reported.
-Break down the 17\% based on socioeconomic and incident characteristics.
-
-\subsection{Reporting behaviour and temporal dynamics}
-
-Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
-We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
-We can contrast and validate these findings using the crime dataset.
-
-The crime dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time.
-We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
-Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
-
-Separation is one of the biggest predictors of abuse resulting in serious injury.
-\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
-If not, we can still use info on location + breaches of non-molestation orders?}
+\subsection{A description of victims and perpetrators}
 
@@
 
- explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
-No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
-Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+?
+
+\subsection{Who does not report DA?}
+
+The WMP data are cases that have been reported to the police.
+The CSEW allows an estimate of the prevalence of domestic abuse.
+The discrepancy between the two datasets allows us to estimate the reporting gap.
+We first explore the characteristics of offenders and victims.
+\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
+
+While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators.
+Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are
+
+The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
+We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
+
+Aim 1: Who perpetrates?
+Who becomes a victim?
+victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
+Find out what kind of cases get reported.
+Break down the 17\% based on socioeconomic and incident characteristics.
+
+Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+
+Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
+We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
+We can contrast and validate these findings using the crime dataset.
+
+\subsection{Predicting serious harm}
+Separation is one of the biggest predictors of abuse resulting in serious injury.
+\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+If not, we can still use info on location + breaches of non-molestation orders?}
+
+\subsection{Collateral damage}
 
@@
 
+\subsection{The Temporal Course of Domestic Abuse OR Reporting behaviour and temporal dynamics}
+
+The crime dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time.
+We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
+Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+
+ explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
+No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
+Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+
 \newpage

### 2019-06-12 case_for_support.tex
X

--- 2019-06-12 Draft.tex
@@
 
-\subsection{A description of victims and perpetrators}
-
-\subsection{Association with other criminal behaviours}
-
-It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
-It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes.
-We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse.
-The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.
-It also contains information about  multiple members of the household.
-This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime.
-By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
-
-The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years.
-We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
-Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk.
-In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes.
-It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.
-For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
-
-victim future behavs, risk factors, intervention possibility
-
-?
-
 \subsection{Who does not report DA?}
@@
 We first explore the characteristics of offenders and victims.
-\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
 
@@
 
+Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+
 Aim 1: Who perpetrates?
@@
 
-Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+\subsubsection{A description of victims and perpetrators}
+
+victim future behavs, risk factors, intervention possibility
+
+\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
+
+\subsubsection{Association with other criminal behaviours}
+
+It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
+It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes.
+We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse.
+The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.
+
+The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years.
+We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
+Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk.
+In addition, we can measure the relationship between experiencing domestic abuse, and the likelihood of being recorded as a suspect in other crimes.
+It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.
 
@@
 \subsection{Predicting serious harm}
+
 Separation is one of the biggest predictors of abuse resulting in serious injury.
@@
 
+For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
+
 \subsection{Collateral damage}
+It also contains information about  multiple members of the household.
+This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime.
+By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
 
 \subsection{Environmental factors}
+
+Australia study on domestic abuse and proximity to fixed-odds betting terminals, and the one on offlicences.
 
@@
 
-\subsection{The Temporal Course of Domestic Abuse OR Reporting behaviour and temporal dynamics}
+\subsection{The Temporal Course and the Decision to Report}
 

### 2019-06-12 case_for_support.tex
Wednesday

@@
 
-\section{Aims}
+\section*{Research Programme}
 
-\subsection{Who does not report DA?}
+In outlining the research program we specify X core regression analyses, which we will preregister ahead of beigging research on the OSF.
+These will be complemented with the robustness checks and further exploratory regressions (see, Trendl Football, for an example of this approach).
 
+\subsection*{1. Who is abused and who reports abuse?}
+
+Aim: Who perpetrates?
+Who is a victim?
+victim/perpetrator characteristics (gender/ethnicity); Find out what kind of cases get reported.
+Break down the 17\% based on socioeconomic and incident characteristics.
+
+In our first programme we will answer the question ``Who doesn't report domestic abuse?''.
+Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
+We will also provide more broad demographic descriptions of the victims and the perpetrators of domestic abuse.
+
+We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
+We are able to do this because CSEW respondents indicated whether they reported the abuse to the police  and whether the police came to know of the abuse in another way (Question X).
+
+Regression 1: data --- subset of people who in CSEW responding that they have been abused
+
+	unreported abuse / reported abuse ~ 
+	[demographics] age + sex + marital status + earnings + ... 
+	other crime dummies + ...
+	[information about abuse] level of harm + ...
+	[geomatched stuff] socioeconomic status
+
+Respondents also answered questions indicating the level of harm that they have suffered, which will allow us to estimate how reporting and police awareness depend upon the level of harm.
+\NS{Anna: broaden this paragraph to be about all of the covariates}
+
+Linear probability model (and logit model?)
+
+We can contrast and validate these findings using the WMP dataset. 
 The WMP data are cases that have been reported to the police.
-The CSEW allows an estimate of the prevalence of domestic abuse.
+The CSEW data allow an estimate of the true underlying prevalence of domestic abuse.
 The discrepancy between the two datasets allows us to estimate the reporting gap.
-We first explore the characteristics of offenders and victims.
+That is, we can use the WMP dataset to provide a second estimate of the degree of underreporting, indpendent of the CSEW respondent's indications of report.
+Discrepancy between reporting prevelence estimated from CSEW and the number of cases in the WMP data give important information about the police's recording and categorisation of domestic abuse cases---do police flag all of the cases of domestic abuse?
+https://www.bbc.co.uk/news/uk-england-46867657
 
 While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators.
-Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are
+Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are.
 
-The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
-We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
+We will also extend the analysis to provide a more general description of the victims of abuse by considering
 
-Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+Domestic abuse doesn't discriminate---well we can estimate this by comparing the 7.7\% for females and 4.4\% for males in the past year with the size of the coefficients.
 
-Aim 1: Who perpetrates?
-Who becomes a victim?
-victim/perpetrator characteristics (gender/ethnicity); deprivation and domestic abuse?
-Find out what kind of cases get reported.
-Break down the 17\% based on socioeconomic and incident characteristics.
-
-\subsubsection{A description of victims and perpetrators}
-
-victim future behavs, risk factors, intervention possibility
-
-\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
-
-\subsubsection{Association with other criminal behaviours}
+Regression 2: 
+	no abuse / abuse ~ 	[demographics] age + sex + marital status + earnings + employment + ... other crime dummies
+		health + mental health +
 
@@
 The high level of detail in the CSEW allows us to examine the comorbidity of domestic abuse with other crimes during the previous year, and since the age of 16.
+
+Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+
+\subsection{The time course of abuse and the predicting serious harm}
+
+Aim:
+
+The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,
+
+Regression 3: type of abuse ~ 
+	visit hospital ~ 
+	mental health ~
+
+Separation is one of the biggest predictors of abuse resulting in serious injury.
+\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+If not, we can still use info on location + breaches of non-molestation orders?}
+
+But cross-sectional data present a particular problem for making casual claims: For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
 
@@
 
-Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
-We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
-We can contrast and validate these findings using the crime dataset.
+The WMP dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time. 
+In the WMP data we can follow X victim-perp pairs for X years, with each pair appearing X times on average in the data.
 
-\subsection{Predicting serious harm}
+We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
+Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
 
-Separation is one of the biggest predictors of abuse resulting in serious injury.
-\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
-If not, we can still use info on location + breaches of non-molestation orders?}
+Regression 4: offense classification[proxy for harm] ~ .
+	type of abuse ~ .
 
-For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
+Future victim behaviours. Future perpetrator behaviours
+
+serious event at t ~ stuff at t-1  + perpetrator previous crimes
+ and 	a model with pair fixed effects
+
+Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents.
+
+Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.
 
 \subsection{Collateral damage}
+
+Aim:
+
+CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
+Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below
+
 It also contains information about  multiple members of the household.
@@
 
+ explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
+No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
+Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+
+Match on name, location, and date of birth in WMP data to see effect on children
+
+WMP regression:
+
+take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse
+
+What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse
+
+Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.
+
 \subsection{Environmental factors}
+
+Aim:
+
+CSEW analysis
+
+Unit of analysis is large geographical area in a year 
+Time span 2005-
+
+DA or not ~
+
+Given DA: report or not ~
+
+Fixed effects for region and year
+
+WMP analysis
+
+Unit of analysis is LSOA (MSOA?) per month or per quarter
+Time span - 2010-2020
+
+Number of DA cases ~
+
+The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
+We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
+
+Extend regression model X to include region fixed effects?
+
+\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
 
@@
 
-\subsection{The Temporal Course and the Decision to Report}
-
-The crime dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time.
-We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
-Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
-
- explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
-No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
-Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+Mention we can construct some of these variables by access to "a very large UK bank" which whom we have a data sharing agreement.
+We cna build them from the row-per-transactino data for spending on current account and credit cards.
 

### 2019-06-12 case_for_support.tex
Wednesday

@@
 
+	abuse or not ~
+   	[demographics] age + sex + marital status + earnings + ...
+	other crime dummies + ...
+
 	unreported abuse / reported abuse ~ 
@@
 	[information about abuse] level of harm + ...
-	[geomatched stuff] socioeconomic status
 
@@
 
-Regression 2: 
-	no abuse / abuse ~ 	[demographics] age + sex + marital status + earnings + employment + ... other crime dummies
-		health + mental health +
+We can describe who is abused and their demographics in CSEW, CSEW who report, and in WMP.
+
+We can also compare those abused in WMP data with any other reference group in the WMP data. (e.g., burgled) and then use DA-burgled in CSEW vs WMP to back out stuff.
 
@@
 It is possible that some criminal behaviour is a precursor to experiencing domestic abuse whilst others follow it.
+
+Should you be identifying the couples most at risk of serious harm from time-invariant properties, or should you be following couples over time and using time-varying properties to spot when to intervene?
 
@@
 
+matched in socieoconomic
+
 WMP analysis

### 2019-06-17 case_for_support.tex
update

@@
 Given the serious problem of underreporting uniquely characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+since when?
 
@@
 
+\newpage
+
 \section*{Research Programme}
@@
 
-Aim: Who perpetrates?
-Who is a victim?
-victim/perpetrator characteristics (gender/ethnicity); Find out what kind of cases get reported.
-Break down the 17\% based on socioeconomic and incident characteristics.
+ \textcolor{red}{\textit{Short intro about aims.}}
+In our first research project, we will be using the CSEW and WMP datasets to answer two main research questions.
+First, we will identify the demographic and socio-economic characteristics of the victims of domestic abuse.
+Second, we will estimate the extent of underreporting, and explore the characteristics of victims who are least likely to report domestic abuse.
+Exploring the characteristics of groups vulnerable to domestic abuse, the true extent of the problem of underreporting and the factors affecting the likelihood of reporting is crucial for designing effective interventions and prevent potential cases of domestic homicide.
 
-In our first programme we will answer the question ``Who doesn't report domestic abuse?''.
-Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation that can potentially result in domestic homicide.
-We will also provide more broad demographic descriptions of the victims and the perpetrators of domestic abuse.
+\textcolor{red}{\textit{What we know so far}} from the \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{CSEW} : 7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders.
 
-We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
-We are able to do this because CSEW respondents indicated whether they reported the abuse to the police  and whether the police came to know of the abuse in another way (Question X).
+\textcolor{red}{\textit{Detailed plan, highlighting added value}}
 
-Regression 1: data --- subset of people who in CSEW responding that they have been abused
+\textbf{Aim 1.} First, using the CSEW data, we will conduct a statistical analysis to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation.
+We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, the decision to report, the type of abuse, and the level of harm suffered.
+The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
+\textit{Could we also use a e.g.
+a random forest classification algorithm and look at variable importance?} Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
+These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
 
-	abuse or not ~
-   	[demographics] age + sex + marital status + earnings + ...
-	other crime dummies + ...
+Second, we can validate some of these findings using the WMP data.
+This dataset contains information about the sex and age of victims.
+We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW\textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
+We will also use the WMP data on the offender's sex and age to characterise domestic abuse perpetrators.
 
-	unreported abuse / reported abuse ~ 
-	[demographics] age + sex + marital status + earnings + ... 
-	other crime dummies + ...
-	[information about abuse] level of harm + ...
+%As mentioned, domestic abuse is a complex phenomenon that encompasses a number of notifiable criminal offences that are usually repeat incidents in nature (e.g., violence against the person including physical or verbal abuse, sexual offences, criminal damage, stalking and harassment).
+However, the CSEW mainly focuses on
 
-Respondents also answered questions indicating the level of harm that they have suffered, which will allow us to estimate how reporting and police awareness depend upon the level of harm.
-\NS{Anna: broaden this paragraph to be about all of the covariates}
+\textbf{Aim 2.}  While the strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a victim of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
+First, because it does not collect information on repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases).
+Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, fraud, burglary, theft).
+Third, it does not collect information on whether different offences against the same victim were perpetrated by the same offender.
+In contrast, the WMP data allows us to tell if a reported case was domestic abuse related, regardless of the actual offence committed.
+We can estimate the co-morbidity of self-reported victimisation by crime type using the CSEW.
+We can contrast this with the estimated co-morbidity of reported victimisation from the police data.
+\textit{is this silly?
+then we can maybe estimate what percentage of true victimisation is domestic-abuse related?}
 
-Linear probability model (and logit model?)
-
-We can contrast and validate these findings using the WMP dataset. 
-The WMP data are cases that have been reported to the police.
-The CSEW data allow an estimate of the true underlying prevalence of domestic abuse.
-The discrepancy between the two datasets allows us to estimate the reporting gap.
-That is, we can use the WMP dataset to provide a second estimate of the degree of underreporting, indpendent of the CSEW respondent's indications of report.
-Discrepancy between reporting prevelence estimated from CSEW and the number of cases in the WMP data give important information about the police's recording and categorisation of domestic abuse cases---do police flag all of the cases of domestic abuse?
-https://www.bbc.co.uk/news/uk-england-46867657
-
-While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators.
-Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are.
-
-We will also extend the analysis to provide a more general description of the victims of abuse by considering
-
-Domestic abuse doesn't discriminate---well we can estimate this by comparing the 7.7\% for females and 4.4\% for males in the past year with the size of the coefficients.
-
-We can describe who is abused and their demographics in CSEW, CSEW who report, and in WMP.
-
-We can also compare those abused in WMP data with any other reference group in the WMP data. (e.g., burgled) and then use DA-burgled in CSEW vs WMP to back out stuff.
-
-It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
+%It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
 It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes.
@@
 
-Core outcomes: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+\textbf{Aim 3.} Police forces in England, including the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
+By contrasting the extrapolated estimates from the CSEW (which is representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
+
+%co-occurrence of other types of crimes - we can contrast results from the CSEW with results from our crime data - e.g., if we see that those reporting domestic abuse have also experienced criminal damage in the CSEW, we can check in the WMP data if criminal damage or home theft is usually a spillover effect from domestic abuse ; deliberate violence; account theft
+
+%We will use the CSEW to understand the demographic and socioeconomic predictors of the decision to report the abuse to the police, and identify specific groups who are less likely to report.
+We are able to do this because CSEW respondents indicated whether they reported the abuse to the police  and whether the police came to know of the abuse in another way (Question X).
+%
+%Regression 1: data --- subset of people who in CSEW responding that they have been abused
+%
+%	abuse or not ~
+%   	[demographics] age + sex + marital status + earnings + ...
+%	other crime dummies + ...
+%
+%
+%	unreported abuse / reported abuse ~ 
+%	[demographics] age + sex + marital status + earnings + ... 
+%	other crime dummies + ...
+%	[information about abuse] level of harm + ...
+
+%Respondents also answered questions indicating the level of harm that they have suffered, which will allow us to estimate how reporting and police awareness depend upon the level of harm.
+\NS{Anna: broaden this paragraph to be about all of the covariates}
+
+%Linear probability model (and logit model?)
+
+%We can contrast and validate these findings using the WMP dataset. 
+%The WMP data are cases that have been reported to the police.
+The CSEW data allow an estimate of the true underlying prevalence of domestic abuse.
+The discrepancy between the two datasets allows us to estimate the reporting gap.
+%That is, we can use the WMP dataset to provide a second estimate of the degree of underreporting, indpendent of the CSEW respondent's indications of report.
+Discrepancy between reporting prevelence estimated from CSEW and the number of cases in the WMP data give important information about the police's recording and categorisation of domestic abuse cases---do police flag all of the cases of domestic abuse?
+https://www.bbc.co.uk/news/uk-england-46867657
+
+%While the CSEW provides us with accurate information on the characteristics of victims, it does not contain information on the perpetrators.
+Combining the two datasets helps us find commonalities between the perpetrators of abuse cases that are.
+
+%We will also extend the analysis to provide a more general description of the victims of abuse by considering
+
+%Domestic abuse doesn't discriminate---well we can estimate this by comparing the 7.7\% for females and 4.4\% for males in the past year with the size of the coefficients.
+
+%We can describe who is abused and their demographics in CSEW, CSEW who report, and in WMP.
+
+%We can also compare those abused in WMP data with any other reference group in the WMP data. (e.g., burgled) and then use DA-burgled in CSEW vs WMP to back out stuff.
+
+\textit{Core outcomes}: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+
+\newpage
 
@@
 
+how the house looks within the neighbourhood/litter on the streets, own perception of litter, foot patrol
+
 Unit of analysis is large geographical area in a year 

### 2019-06-18 case_for_support.tex
Anna update

@@
 
-\subsection*{1. Who is abused and who reports abuse?}
+\subsection*{1. Understanding domestic abuse: victim characteristics, extent of domestic abuse and police mis-recording}
 
- \textcolor{red}{\textit{Short intro about aims.}}
-In our first research project, we will be using the CSEW and WMP datasets to answer two main research questions.
-First, we will identify the demographic and socio-economic characteristics of the victims of domestic abuse.
-Second, we will estimate the extent of underreporting, and explore the characteristics of victims who are least likely to report domestic abuse.
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+In our first research project, we will be using the CSEW and WMP datasets to investigate three main research questions.
+First, we will use the CSEW and WMP to identify the demographic and socio-economic characteristics of the victims of domestic abuse, and the WMP to characterise perpetrators of reported cases.
+In addition, we aim to explore the predictors of the decision to report and the level of harm suffered.
 Exploring the characteristics of groups vulnerable to domestic abuse, the true extent of the problem of underreporting and the factors affecting the likelihood of reporting is crucial for designing effective interventions and prevent potential cases of domestic homicide.
+Second, we will estimate the true extent of domestic abuse victimisation.
+Given the multifaceted nature of domestic abuse and the problem of underreporting, it is very hard to reliably estimate the extent of the problem and the societal costs of domestic abuse.
+We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse related).
+Finally, we will estimate the extent of police mis-recording domestic abuse.
+Improving the police's response to reported incidents is key in encouraging victims to report domestic abuse.
+By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.
 
-\textcolor{red}{\textit{What we know so far}} from the \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{CSEW} : 7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders.
+\textcolor{red}{\textit{What we know so far}}
 
-\textcolor{red}{\textit{Detailed plan, highlighting added value}}
+Aim 1.
+\href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{CSEW} : 7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders.
+
+Aim 2. The prevalence of DA is usually based on the CSEW, so I think the second analysis can add value.
+
+Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS}
+
+\textcolor{red}{\textit{Detailed plan}}
 
@@
 We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW\textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
-We will also use the WMP data on the offender's sex and age to characterise domestic abuse perpetrators.
+We will also use the WMP data on the offender's sex and age to provide a characterisation of domestic abuse perpetrators.
 
@@
 
-\textbf{Aim 2.}  While the strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a victim of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
-First, because it does not collect information on repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases).
-Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, fraud, burglary, theft).
-Third, it does not collect information on whether different offences against the same victim were perpetrated by the same offender.
+\textbf{Aim 2.}  While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a victim of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
+First, because it does not collect detailed information on repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases), but only on the number of incidents involving physical violence perpetrated by household members.
+In addition, victims who suffer frequent, ongoing abuse are less likely to accurately remember the exact number of incidents.
+Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, financial abuse, burglary).
+In addition, it does not collect information on whether different offences against the same victim were perpetrated by the same offender.
 In contrast, the WMP data allows us to tell if a reported case was domestic abuse related, regardless of the actual offence committed.
+In addition, it allows us to identify various incidents where the same victim-offender pair were involved.
 We can estimate the co-morbidity of self-reported victimisation by crime type using the CSEW.
@@
 \textit{is this silly?
-then we can maybe estimate what percentage of true victimisation is domestic-abuse related?}
+then we can maybe estimate what percentage of true victimisation is domestic-abuse related?
+the £66 billion cost estimate is based on the CSEW}
 
@@
 By contrasting the extrapolated estimates from the CSEW (which is representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
+Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time.
 
@@
 
-%We will also extend the analysis to provide a more general description of the victims of abuse by considering
-
 %Domestic abuse doesn't discriminate---well we can estimate this by comparing the 7.7\% for females and 4.4\% for males in the past year with the size of the coefficients.
@@
 
-\textit{Core outcomes}: A demographic description of victims, a demographic description of perpetrators, and an estimate of the reporting gap, and a demographic description of who does not report domestic abuse.
+\textcolor{red}{\textit{Core outcomes}} 
+A deeper understanding of the socio-economic predictors of domestic abuse victimisation, the decision to report and the level of harm suffered.
+The first estimation of the true extent of domestic abuse-related victimisation across all offence types.
+An estimation of the extent of police (WMP) mis-recording of domestic abuse over time.
 

### 2019-06-18 case_for_support.tex
Anna update

@@
 First, we will use the CSEW and WMP to identify the demographic and socio-economic characteristics of the victims of domestic abuse, and the WMP to characterise perpetrators of reported cases.
-In addition, we aim to explore the predictors of the decision to report and the level of harm suffered.
-Exploring the characteristics of groups vulnerable to domestic abuse, the true extent of the problem of underreporting and the factors affecting the likelihood of reporting is crucial for designing effective interventions and prevent potential cases of domestic homicide.
+Exploring the characteristics of groups vulnerable to domestic abuse, and the true extent of the problem of underreporting is crucial for designing effective interventions and prevent potential cases of domestic homicide.
 Second, we will estimate the true extent of domestic abuse victimisation.
@@
 \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{CSEW} : 7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders.
+single mothers and mothers with young children are more at risk
 
@@
 \textbf{Aim 1.} First, using the CSEW data, we will conduct a statistical analysis to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation.
-We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, the decision to report, the type of abuse, and the level of harm suffered.
-The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
+We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, and the type of abuse suffered (physical abuse, threats, sexual abuse).
+The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
 \textit{Could we also use a e.g.
-a random forest classification algorithm and look at variable importance?} Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
-These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
 
@@
 Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time.
+We can complement this investigation with analysing the self-reported outcome of incidents that have been reported to the police from the CSEW.
 
@@
 \textcolor{red}{\textit{Core outcomes}} 
-A deeper understanding of the socio-economic predictors of domestic abuse victimisation, the decision to report and the level of harm suffered.
+A deeper understanding of the socio-economic predictors of domestic abuse victimisation.
 The first estimation of the true extent of domestic abuse-related victimisation across all offence types.
@@
 
-\subsection{The time course of abuse and the predicting serious harm}
+\subsection*{2. Predicting serious harm and understanding the decision to report}
 
-Aim:
+\textcolor{red}{\textit{Detailed plan}}
 
-The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,
+Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
 
-Regression 3: type of abuse ~ 
-	visit hospital ~ 
-	mental health ~
+\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered depends on the individual-level characteristics of the victim (especially focusing on the issue of separation and divorce, as it has proven to be a significant risk factor predicting serious harm) and the co-morbidity with other types of victimisation (other offence types).
+The CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
+We also have information on the respondent's self-reported health, well-being, and alcohol and drug consumption, and we can also use these as outcome variables (although it is impossible to claim causality).
 
-Separation is one of the biggest predictors of abuse resulting in serious injury.
-\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
-If not, we can still use info on location + breaches of non-molestation orders?}
+Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.
 
-But cross-sectional data present a particular problem for making casual claims: For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
+We can predict incidents with serious harm, using the type of offence occurred previously.
+number of days elapsed.
+This will allow us to identify and commonalities in the pattern of domestic abuse cases that lead to escalation in the form of serious harm.
+We can also identify and characterise high-risk perpetrators who breach court orders designed to protect the victims from further harms.
 
-The scope of the WMP dataset across time lets us take these questions further, by looking at the order in which events occur and at patterns across many years.
-We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
+%We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
 Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk.
@@
 
-Should you be identifying the couples most at risk of serious harm from time-invariant properties, or should you be following couples over time and using time-varying properties to spot when to intervene?
+\textbf{Aim 2.} First, we will use the CSEW, and a logistic approach to understand how the decision to report to the police (or seeking any external help) depends on the individual-level characteristics of the victim (especially focusing on mental and physical health and financial independence) and the abuse suffered.
 
-The WMP dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time. 
-In the WMP data we can follow X victim-perp pairs for X years, with each pair appearing X times on average in the data.
-
-We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
+Second, using the WMP data, we will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
 Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
 
-Regression 4: offense classification[proxy for harm] ~ .
-	type of abuse ~ .
+%Aim:
 
-Future victim behaviours. Future perpetrator behaviours
+%The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,
 
-serious event at t ~ stuff at t-1  + perpetrator previous crimes
- and 	a model with pair fixed effects
+%Regression 3: type of abuse ~ 
+%	visit hospital ~ 
+%	mental health ~
 
-Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents.
+%Separation is one of the biggest predictors of abuse resulting in serious injury.
+\textit{Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.
+If not, we can still use info on location + breaches of non-molestation orders?}
 
-Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.
+%But cross-sectional data present a particular problem for making casual claims: For example, incidents involving drugs or alcohol intoxication: some individuals may end up in an abusive relationship because of an existing dependency, or a dependency may develop as a counterproductive strategy of coping with the abusive relationship.
 
-\subsection{Collateral damage}
+%Should you be identifying the couples most at risk of serious harm from time-invariant properties, or should you be following couples over time and using time-varying properties to spot when to intervene?
+
+%The WMP dataset will further allow us to follow victim-offender pairs over time, and explore how the severity and nature of reported abuse changes over time. 
+%In the WMP data we can follow X victim-perp pairs for X years, with each pair appearing X times on average in the data.
+
+%Regression 4: offense classification[proxy for harm] ~ .
+%	type of abuse ~ .
+%
+%Future victim behaviours. Future perpetrator behaviours
+%
+%serious event at t ~ stuff at t-1  + perpetrator previous crimes
+% and 	a model with pair fixed effects
+%
+%Murders are very rare, so we are adopting a ``near miss'' airline / nuclear industry strategy of predicting the more prevalent but less serious incidents. 
+%
+%Say pair fixed effects control for all non-time varying characteristics. With and without pair fixed effects let's use see how much state vs trait matters for prediction.
+
+\newpage
+
+\subsection*{Collateral damage}
 
@@
 
-\subsection{Environmental factors}
+\newpage
 
-Aim:
+\subsection*{Environmental factors}
 
-CSEW analysis
+\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+In our last research project, we will be using the CSEW and WMP datasets to investigate the environmental predictors of domestic abuse.
+First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data.
+Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these.
+Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
+Second, we will be looking at how time-varying factors affect domestic abuse.
 
-how the house looks within the neighbourhood/litter on the streets, own perception of litter, foot patrol
+\textcolor{red}{\textit{What we know so far}}  neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks;  however, in deprived neighbourhoods where IPV is accepted social interactions can increase IPV
 
-Unit of analysis is large geographical area in a year 
-Time span 2005-
+\textcolor{red}{\textit{Detailed plan}}
 
-DA or not ~
+\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant association between the prevalence of domestic abuse, and the willingness to report and the environmental characteristics of the neighbourhood they live in.
+Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse.
+Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases.
+\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level}.
 
-Given DA: report or not ~
+\textbf{Aim 2.} In this section we will be looking at time-varying environmental factors that we hypothesize to have an effect on domestic abuse.
+By identifying local events whilst controlling for weather, we can estimate at how an increase in alcohol consumption and people congregating in large numbers affects reported levels of domestic abuse (see the football).
+The recent roll-out of the universal credit had been criticised widely due to the temporal financial strain it imposes on the least financially resilient people.
+Many studies have identified financial problems as one contributing factor to domestic abuse.
+As part of a data sharing agreement with a very large UK bank, we will have access to the credit card and current account spending of x customers across the UK.
+\textit{I'm not sure about the specifics of this, would we combine this with the WMP or CSEW?
+I guess we won't know the card owner's address?}
 
-Fixed effects for region and year
+We will also test whether the proximity of fixed odds betting terminals affect the prevalence of domestic abuse.
 
-matched in socieoconomic
+\textcolor{red}{\textit{Core outcomes}}
+%Unit of analysis is large geographical area in a year 
+%Time span 2005-
+%
+%DA or not ~
+%
+%Given DA: report or not ~
+%
+%Fixed effects for region and year
+%
+%matched in socieoconomic
+%
+%
+%
+%WMP analysis
+%
+%Unit of analysis is LSOA (MSOA?) per month or per quarter
+%Time span - 2010-2020
+%
+%Number of DA cases ~
 
-WMP analysis
-
-Unit of analysis is LSOA (MSOA?) per month or per quarter
-Time span - 2010-2020
-
-Number of DA cases ~
-
-The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
+%The CSEW allows us to identify the demographic and socio-economic characteristics of victims who are the least likely to report, and therefore should be in the focus of support services.
 We can validate and contrast these findings with insights from a spatial regression analysis of the crime data, using low-level geographical area information from the census.
 
-Extend regression model X to include region fixed effects?
+%Extend regression model X to include region fixed effects?
+%
+%
+%\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
 
-\textit{A sentence about what earlier investigations have found about particular risk factors, including socio-economic deprivation.}
-
-Australia study on domestic abuse and proximity to fixed-odds betting terminals, and the one on offlicences.
-
-anything that affects propensity to drink/financial stress
-
-neighbourhood characteristics (deprivation), fixed odds betting terminals, alcohol outlets, events (football, festivals)
-
-\href{https://www.birminghammail.co.uk/news/midlands-news/universal-credit-rolled-out-across-14142901}{Universal credit roll-out in the West Midlands}
-
-\href{https://www.birminghammail.co.uk/black-country/universal-credit-claimants-black-country-15946831}{Universal credit roll-out in the Black Country}
-
-food bank dependence? data on housing e.g. evictions? homelessness.
-
-Mention we can construct some of these variables by access to "a very large UK bank" which whom we have a data sharing agreement.
+%deprivation is a risk factor for women
+%
+%Australia study on domestic abuse and proximity to fixed-odds betting terminals, and the one on offlicences.
+%
+%anything that affects propensity to drink/financial stress
+%
+%neighbourhood characteristics (deprivation), fixed odds betting terminals, alcohol outlets, events (football, festivals)
+%
+%\href{https://www.birminghammail.co.uk/news/midlands-news/universal-credit-rolled-out-across-14142901}{Universal credit roll-out in the West Midlands}
+%
+%\href{https://www.birminghammail.co.uk/black-country/universal-credit-claimants-black-country-15946831}{Universal credit roll-out in the Black Country}
+%
+%
+%food bank dependence? data on housing e.g. evictions? homelessness.
+%
+%Mention we can construct some of these variables by access to "a very large UK bank" which whom we have a data sharing agreement.
 We cna build them from the row-per-transactino data for spending on current account and credit cards.

### 2019-06-19 case_for_support.tex
Anna update

@@
 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In our last research project, we will be using the CSEW and WMP datasets to investigate the environmental predictors of domestic abuse.
-First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data.
+In this research project, we will be using the CSEW and WMP datasets to investigate some of the environmental predictors of domestic abuse.
+First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data.
 Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these.
@@
 
-\textcolor{red}{\textit{What we know so far}}  neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks;  however, in deprived neighbourhoods where IPV is accepted social interactions can increase IPV
+\textcolor{red}{\textit{What we know so far}} interestingly, there are no studies about this using UK data; neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV, especially financial independence;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks might foster community cohesion and reduces IPV;  however, in deprived neighbourhoods, where IPV is accepted social interactions can increase IPV
+
+\href{https://www.sciencedirect.com/science/article/abs/pii/S0277953616302891}{The relationship between electronic gaming machine accessibility and police-recorded domestic violence: A spatio-temporal analysis of 654 postcodes in Victoria, Australia, 2005–2014}
+
+\href{https://journals.sagepub.com/doi/abs/10.1177/1525107115623938}{Economic Stress and Domestic Violence: Examining the Impact of Mortgage Foreclosures on Incidents Reported to the Police }
+
+\href{https://journals.sagepub.com/doi/abs/10.1177/1524838013515758}{Neighborhood Environment and Intimate Partner Violence: A Systematic Review }
 

### 2019-06-19 case_for_support.tex
Anna update

@@
 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In this research project, we will be using the CSEW and WMP datasets to investigate some of the environmental predictors of domestic abuse.
-First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data.
-Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these.
+In this research project, we will be using the CSEW and WMP datasets, as well as external sources of data to investigate some of the environmental predictors of domestic abuse.
+First, using data from the CSEW and drawing on previous research on the topic, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report.
+We will complement this with an additional analysis on WMP and census data.
+We will be able to account for the dynamic nature of these neighbourhood characteristics, by using longitudinal and repeated cross-sectional datasets.
 Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
+
 Second, we will be looking at how time-varying factors affect domestic abuse.
@@
 
+\href{https://journals.sagepub.com/doi/abs/10.1177/1524838012445641?journalCode=tvaa}{
+The Impact of Neighborhoods on Intimate Partner Violence and Victimization
+}
+
+the type sof social tie matters: friendship ties reduce the risk of IPV, family ties have no effect
+
 \href{https://journals.sagepub.com/doi/abs/10.1177/1524838013515758}{Neighborhood Environment and Intimate Partner Violence: A Systematic Review }
@@
 
-\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant association between the prevalence of domestic abuse, and the willingness to report and the environmental characteristics of the neighbourhood they live in.
+\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in.
+Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these.
+For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse.
+
 Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse.

### 2019-06-19 case_for_support.tex
Anna update

@@
 a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+We are particularly interested in the association between experiences of domestic abuse and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
 
@@
 \textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in.
-Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these.
-For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse.
-
-Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection to the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse.
+Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, but the question has not been explored in a UK context yet.
+Our rich data allows us to determine the relative explanatory power of these.
+For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse through reduced collective efficacy.
+Another potential pathway is social norms, suggesting that acceptance and normalisation of violence within a community can encourage domestic abuse.
+Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse.
 Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases.
-\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level}.
+Using a spatial regression will account for the spatial dependency between our observations and improve the reliability of our estimates.
+\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?}.
 

### 2019-06-19 case_for_support.tex
Anna update

@@
 Another potential pathway is social norms, suggesting that acceptance and normalisation of violence within a community can encourage domestic abuse.
-Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation and trust in CJS reflected in the propensity to report abuse.
-Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics of the area to predict the number of reported abuse cases.
+Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation and trust in CJS, reflected in the propensity to report abuse.
+Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics (average income, education levels and benefit dependency) of the area to predict the number of reported abuse cases.
 Using a spatial regression will account for the spatial dependency between our observations and improve the reliability of our estimates.
-\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?}.
+\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?}
 
-\textbf{Aim 2.} In this section we will be looking at time-varying environmental factors that we hypothesize to have an effect on domestic abuse.
-By identifying local events whilst controlling for weather, we can estimate at how an increase in alcohol consumption and people congregating in large numbers affects reported levels of domestic abuse (see the football).
+\textbf{Aim 2.} In this section, we will be looking at time-varying environmental factors that may influence domestic abuse.
+This part of the project will benefit from a dataset containing credit card and current account spending of x customers across the UK, to which we will have access as part of a data sharing agreement with a very large UK bank.
+\textit{I'm not sure about the specifics of this, would we combine this with the WMP or CSEW?
+I guess we won't know the card owner's address?} First, by using the WMP and credit card data, we will identify time-specific changes in alcohol consumption in parts of the West Midlands by identifying externals events that may affect it (e.g., local festivals, weather, bank holidays, sport tournaments), and investigate their effect on alcohol-related domestic abuse.
+Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on propensity to be violent.
+
   The recent roll-out of the universal credit had been criticised widely due to the temporal financial strain it imposes on the least financially resilient people.
 Many studies have identified financial problems as one contributing factor to domestic abuse.
-As part of a data sharing agreement with a very large UK bank, we will have access to the credit card and current account spending of x customers across the UK.
-\textit{I'm not sure about the specifics of this, would we combine this with the WMP or CSEW?
-I guess we won't know the card owner's address?}
-
 We will also test whether the proximity of fixed odds betting terminals affect the prevalence of domestic abuse.

### 2019-06-19 case_for_support.tex
Anna update

@@
 Using a spatial regression will account for the spatial dependency between our observations and improve the reliability of our estimates.
-\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?}
+\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?} This analysis, contrasted with that outlined in project 1 about the individual-level predictors of domestic abuse, will provide us with the most comprehensive understanding on the risk factors of domestic abuse within the context of the UK.
 
@@
 I guess we won't know the card owner's address?} First, by using the WMP and credit card data, we will identify time-specific changes in alcohol consumption in parts of the West Midlands by identifying externals events that may affect it (e.g., local festivals, weather, bank holidays, sport tournaments), and investigate their effect on alcohol-related domestic abuse.
-Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on propensity to be violent.
+Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
 

### 2019-06-19 case_for_support.tex
Anna update

@@
 
-Second, we will be looking at how time-varying factors affect domestic abuse.
+Second, we will be looking at how time-varying, exogenous factors affect domestic abuse.
+We will first explore the effect of local events that increase alcohol-consumption, since our previous study have found a significant relationship between alcohol-related domestic abuse and football.
+Second, we will conduct two studies to understand the relationship between financial stress and the prevalence of domestic abuse.
+First, we will explore the association between gambling accessibility in the local area, and reported numbers of domestic abuse.
+Second, we will examine how the roll-out of the Universal Credit system affected levels of domestic abuse across the West Midlands.
+Apart from delivering important policy-relevant insights, these investigations will also aim to inform the local police about the optimal allocation of police resources.
 
@@
 
-  The recent roll-out of the universal credit had been criticised widely due to the temporal financial strain it imposes on the least financially resilient people.
-Many studies have identified financial problems as one contributing factor to domestic abuse.
-We will also test whether the proximity of fixed odds betting terminals affect the prevalence of domestic abuse.
+  The recent reforms of the UK benefit system, in the form of the introduction of the Universal Credit (UC) had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
+Drawing on previous findings about the link between financial stress and domestic abuse, we will explore what effect the roll-out of the UC across the West Midlands had on the reported number of domestic abuse cases.
+The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
+For this estimation, we will use data on the proportion of benefits claimants in each LSOA.
+\textit{I know we were talking about using the credit card data for this one, but I am not sure what was the exact plan}.
+Gambling is increasingly recognised as a serious health concern across the UK, and can have an adverse impact on family finances.
+To assess the link between gambling accessibility and the prevalence of domestic abuse, we will use data on the number of licensed betting shops in the West Midlands within a spatial regression approach.
 
-\textcolor{red}{\textit{Core outcomes}}
+\href{https://secure.gamblingcommission.gov.uk/PublicRegister}{List of licensed gambling businesses} We can also contact the local authorities, as they should have an up-to-date list
+
+\textcolor{red}{\textit{Core outcomes}} The first extensive analysis of the complex individual-- and neighbourhood level predictors of domestic abuse within the UK.
+An exploration of the exogenous, time-varying factors affecting levels of reported domestic abuse (mostly through alcohol).
+An examination of how gambling accessibility and temporal financial stress affect the reported number of domestic abuse cases in the West Midlands.
+
 %Unit of analysis is large geographical area in a year 

### 2019-06-19 case_for_support.tex
Anna update

@@
 
+Using data from the CSEW and well as population data of the West Midlands, we can estimate how many children and young people below 18 in each LSOA of the West Midlands are at risk of witnessing domestic abuse at home each year.
+
+\textit{The problem is that we don't know the address of the young offenders.
+Could we the location info on where they committed the offences as a proxy of the LSOA where they live?
+not sure if this is viable;
+defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it;
+I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse}
+
 Aim:

### 2019-06-19 case_for_support.tex
Anna update

@@
 not sure if this is viable;
-defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it;
-I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse}
+defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it, maybe we should just concentrate on criminal activities;
+I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse; however, the location id doesn't seem to specific to one place - one id can correspond to a road, dwelling, shop etc.}
+
+There's a children's questionnaire, and they ask about gang membership. However, the sample size is very low (3,100 for the whole country).
 

### 2019-06-20 case_for_support.tex
Anna update

--- 2019-06-19 case_for_support.tex
@@
 
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+
+\textcolor{red}{\textit{What we know so far}}
+
+\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} escalation often happens when the abuser feels like they are losing control (e.g., because the victim threatens to leave); separation is an important risk factors of serious harm;
+
+\href{http://www.safelives.org.uk/policy-evidence/about-domestic-abuse/how-long-do-people-live-domestic-abuse-and-when-do-they-get}{Reporting}
+
 \textcolor{red}{\textit{Detailed plan}}
+
+does the level of harm depend on the length of time spent in the relationship
 
@@
 The CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
-We also have information on the respondent's self-reported health, well-being, and alcohol and drug consumption, and we can also use these as outcome variables (although it is impossible to claim causality).
 
@@
 
+children's safety as a concern
+
 Second, using the WMP data, we will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
 Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+
+\textcolor{red}{\textit{Core outcomes}}
 
@@
 
-\subsection*{Collateral damage}
+\subsection*{3. The long-lasting effects of domestic abuse}
 
-Aim:
+it's impossible to establish causality
 
-CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
-Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+Domestic abuse has long-lasting adverse effects on victims and those close to them.
+In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household.
+Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design victim support programmes and quantify the societal harm caused by it.
 
-It also contains information about  multiple members of the household.
+\textcolor{red}{\textit{What we know so far}}
+\href{https://www.womensaid.org.uk/information-support/what-is-domestic-abuse/the-nature-and-impact-of-domestic-abuse/}{Women's aid, effect on victims} increased likelihood of mental health problems (isolation, low self-esteem), alcohol and drug dependency, financial consequences due to financial abuse or losing a job as a result of the abuse, fighting back?
+
+\href{https://uksaysnomore.org/effects-of-domestic-abuse-on-children/}{Effect on children I} witnessing violence is major predictor for PTSD and depressive symptoms in children; behavioural problems, bullying (either victims or perpetrators)
+
+\href{https://www.psychologytoday.com/gb/blog/progress-notes/201902/alarming-effects-childrens-exposure-domestic-violence}{Effect on children II} cognitive development is affected, learning difficulties are more common, difficulties in social relationships, withdrawal, antisocial behaviours, they are more likely to become both perpetrators and victims of domestic abuse; protective factors: literacy, intelligence, social competence, supportive relationship with at least one influential adult
+
+\textcolor{red}{\textit{Detailed plan}}
+
+\textbf{Aim 1.} First, using the CSEW, we will explore the long-lasting effects of experiencing domestic abuse.
+In the CSEW, in two separate questions, respondents are asked whether they have experienced any form of domestic abuse (use of violence, sexual abuse, threatening behaviour, stalking) since the age of 16 or in the last 12 months.
+This way we can identify respondents who have suffered specific forms of abuse in the past, but not in the last 12 months.
+Using propensity score matching, we can then compare their physical and mental health-related outcomes, and alcohol and drug consumption with those, who have never experienced any form of abuse, but otherwise have similar socio-economic characteristics.
+This will allow us to estimate the effect of past abuse on present outcomes whilst controlling for individual- and macro-level characteristics.
+
+\textbf{Aim 2.} Using data from the 10-15 year old questionnaire of the CSEW, which can be linked to the adult questionnaire, we can examine the effect of domestic abuse on children living in such households.
+The questionnaire records information on whether the child had been physically or verbally abused by someone (and if that person lives in the household), as well as their experiences with bullying, carrying knives and information on gang membership, school truancy and health.
+We can explore the effect of domestic and child abuse on these outcomes through propensity score matching.
+
+Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a victim of a domestic abuse offender. No control group.
+
+%Using data from the CSEW and well as population data of the West Midlands, we can estimate how many children and young people below 18 in each LSOA of the West Midlands are at risk of witnessing domestic abuse at home each year.
+
+%\textit{The problem is that we don't know the address of the young offenders.
+Could we the location info on where they committed the offences as a proxy of the LSOA where they live?
+not sure if this is viable; defining a gang member is problematic in the crime data - if something serious is committed probably only one of them will be charged with it, maybe we should just concentrate on criminal activities; I was trying to identify children who were victims of something happening at an address where DA happened and perpetrated by a DA offender - it's very narrow and excludes children who *just* witnessed abuse; however, the location id doesn't seem to specific to one place - one id can correspond to a road, dwelling, shop etc.}
+
+%We can use school exclusion data - unfortunately this data is only available on the local authority and school-type (state-funded primary, secondary, special) level...
+
+%There's a children's questionnaire, and they ask about gang membership. However, the sample size is very low (3,100 for the whole country).
+
+%of the 119,539 under 18s who were victims of crimes (domestic/child abuse, or other more serious physical/sexual violence) in the dataset, 11\% were later offenders with an average of 2 offences (mostly domestic abuse, physical violence, drug possession and theft) - these are only the kids we have evidence were traumatised at some point
+
+%of the 149,759 da offenders, 19\% have an incident against an under 18
+
+%Aim:
+%
+%CSEW regression: child gang membership ~ any domestic abuse or reported DA [2x2 table of abuse/no abuse by gang / no gang]
+%Also estimate, given gang membership what fraction are DA---which links ot WMP analysis below
+%
+%It also contains information about  multiple members of the household.
 This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime.
 By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.
-
- explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
+% 
+% explore the lasting effect of domestic abuse on the victims and their children (do we see kids having behavioural problems?
 No control group unfortunately)- CSEW question about gang membership - are those who report having a child gang member more likely to be victims of domestic abuse?
 Following people over time (Dynamic topic modelling for victims)- what’s the temporal order?
+%
+%Match on name, location, and date of birth in WMP data to see effect on children
+%
+%WMP regression:
+%
+%take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse
+%
+%What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse
+%
+%Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.
 
-Match on name, location, and date of birth in WMP data to see effect on children
-
-WMP regression:
-
-take every juvinile in a gang and try to match all to domestic abuse cases----estimates of what fraction of gang members have co-morbid domestic abuse
-
-What fraction of reported child abuse has comorbid DA; what fraction of DA has comorbid child abuse
-
-Using school census we can go futher and estimate frequencies in a 2x2 child abuse  by domestic abuse table---providing we can match children to mothers.
+\textcolor{red}{\textit{Core outcomes}}
 

### 2019-06-21 case_for_support.tex
Anna update

@@
  \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In our first research project, we will be using the CSEW and WMP datasets to investigate three main research questions.
-First, we will use the CSEW and WMP to identify the demographic and socio-economic characteristics of the victims of domestic abuse, and the WMP to characterise perpetrators of reported cases.
-Exploring the characteristics of groups vulnerable to domestic abuse, and the true extent of the problem of underreporting is crucial for designing effective interventions and prevent potential cases of domestic homicide.
+In our first research project, we will be investigating three main research questions.
+First, we will use the CSEW and WMP datasets to identify the demographic and socio-economic characteristics of victims of domestic abuse, and the WMP to characterise perpetrators of domestic abuse cases reported to the police.
 Second, we will estimate the true extent of domestic abuse victimisation.
-Given the multifaceted nature of domestic abuse and the problem of underreporting, it is very hard to reliably estimate the extent of the problem and the societal costs of domestic abuse.
-We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse related).
-Finally, we will estimate the extent of police mis-recording domestic abuse.
-Improving the police's response to reported incidents is key in encouraging victims to report domestic abuse.
+Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the extent of domestic abuse victimisation and the subsequent societal costs.
+We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related).
+Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide.
+Finally, we will estimate the extent of police mis-recording of domestic abuse.
+Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
 By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.
@@
 
-Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS}
+Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS about West Midlands mis-recording}
 
@@
 
-\textbf{Aim 1.} First, using the CSEW data, we will conduct a statistical analysis to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation.
-We will first use a logistic regression approach to explore the factors predicting individual-level domestic abuse victimisation, and the type of abuse suffered (physical abuse, threats, sexual abuse).
-The CSEW provides a wealth of information on the characteristics of the respondent including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, well-being, drug and alcohol use, and we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
+\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation.
+Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse suffered (physical abuse, threats, sexual abuse).
+The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, frequency of drug and alcohol use.
+Using this wide range of individual-level information, we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
 \textit{Could we also use a e.g.
@@
 We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW\textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
-We will also use the WMP data on the offender's sex and age to provide a characterisation of domestic abuse perpetrators.
+We can complement this analysis with data on the offender's sex  and age to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.
 
@@
 \textbf{Aim 3.} Police forces in England, including the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
-By contrasting the extrapolated estimates from the CSEW (which is representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
+By contrasting the extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
 Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time.
@@
 
-does the level of harm depend on the length of time spent in the relationship
+does the level of harm depend on the length of time spent in the relationship, separation,
 
@@
 
-\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered depends on the individual-level characteristics of the victim (especially focusing on the issue of separation and divorce, as it has proven to be a significant risk factor predicting serious harm) and the co-morbidity with other types of victimisation (other offence types).
-The CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
+\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the victim (especially focusing on the issue of separation and divorce, as evidence suggests it is a significant risk factor predicting serious harm).
+We will also explore whether non domestic abuse-related victimisation is predictive of serious harm.
+We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
 
@@
 
-We can predict incidents with serious harm, using the type of offence occurred previously.
+We can predict incidents with serious harm, using the type of offence occurred previously, criminal history of the offender.
 number of days elapsed.
@@
 
-\textbf{Aim 2.} First, we will use the CSEW, and a logistic approach to understand how the decision to report to the police (or seeking any external help) depends on the individual-level characteristics of the victim (especially focusing on mental and physical health and financial independence) and the abuse suffered.
+\textbf{Aim 2.} First, we will use the CSEW, and a logistic approach to understand how the decision to report to the police (or seeking any external help) depends on the individual-level characteristics of the victim (especially focusing on mental and physical health, financial independence and whether the victim has children) and the abuse suffered.
+We can complement this analysis with the WMP data,
 

### 2019-06-24 case_for_support.tex
Anna update

@@
 In our first research project, we will be investigating three main research questions.
-First, we will use the CSEW and WMP datasets to identify the demographic and socio-economic characteristics of victims of domestic abuse, and the WMP to characterise perpetrators of domestic abuse cases reported to the police.
+First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data.
 Second, we will estimate the true extent of domestic abuse victimisation.
@@
 
-\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors and their interactions in predicting domestic abuse victimisation.
-Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse suffered (physical abuse, threats, sexual abuse).
-The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, frequency of drug and alcohol use.
-Using this wide range of individual-level information, we will evaluate the importance of each of these variables and their interaction in predicting our outcome variables.
+\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
+Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse ever suffered (physical abuse, threats, sexual abuse).
+The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
+Using this wide range of individual-level information, we will evaluate the importance of each of these variables in predicting the likelihood of domestic abuse victimisation.
 \textit{Could we also use a e.g.
-a random forest classification algorithm and look at variable importance?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
-We are particularly interested in the association between experiences of domestic abuse and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
+a random forest classification algorithm and look at variable importance?
+this way we could also look at interactions?
+does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+We are particularly interested in the association between experiences of domestic abuse, number of children and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
 
-Second, we can validate some of these findings using the WMP data.
-This dataset contains information about the sex and age of victims.
-We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW\textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
-We can complement this analysis with data on the offender's sex  and age to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.
+Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the victim reported the domestic abuse to the police.
+The WMP contains information about the sex and age of victims.
+We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW \textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
+We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.
 

### 2019-06-24 case_for_support.tex
Anna update

@@
 As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature.
-Estimates show that on average, victims live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}.
+Estimates show that on average, survivors live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}.
 The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey including a self-completion module on domestic abuse.
@@
 
-Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020.
-The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase victim safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
+%Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020.
+The action plan focuses on a range of areas to reduce the prevalence of domestic abuse, including increasing awareness and willingness to report through education and information campaigns, introducing legal measures to increase survivor safety (e.g., Domestic Violence Protection Order, Domestic Violence Disclosure Scheme, intervention programmes), and improve the responses of support services and health care professionals \cite{vawag}.
 
@@
 The two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
-The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (victim).
+The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor).
 However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators and has limited longitudinal information.
@@
 
-\subsection*{1. Understanding domestic abuse: victim characteristics, extent of domestic abuse and police mis-recording}
+\subsection*{1. Understanding domestic abuse: survivor characteristics, extent of domestic abuse and police mis-recording}
 
@@
 First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data.
+Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
+
 Second, we will estimate the true extent of domestic abuse victimisation.
-Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the extent of domestic abuse victimisation and the subsequent societal costs.
+Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the prevalence of domestic abuse.
 We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related).
-Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide.
+Estimating the true prevalence of domestic abuse across various types of criminal offences will help us to obtain a better estimate of the societal cost associated with domestic abuse.
+
+%Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide.
+
 Finally, we will estimate the extent of police mis-recording of domestic abuse.
@@
 does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
-We are particularly interested in the association between experiences of domestic abuse, number of children and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
+We are particularly interested in the association between experiences of domestic abuse, number of children, and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
 
-Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the victim reported the domestic abuse to the police.
+Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police.
 The WMP contains information about the sex and age of victims.
 We can contrast the sex-age victimisation numbers from the WMP with corresponding population estimates to validate the findings of the CSEW \textit{(we were initially talking about using victims of burglary, but maybe this is better?)}.
-We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW.
+We can also complement this analysis with data on the offender's sex  and age, to estimate the prevalence of different forms of reported domestic abuse (child to parent violence, parent to child violence, intimate partner violence) and contrast it with estimates based on self-reported data from the CSEW, which distinguishes between family and intimate partner violence.
 
@@
 
-\textbf{Aim 2.}  While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a victim of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
-First, because it does not collect detailed information on repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases), but only on the number of incidents involving physical violence perpetrated by household members.
-In addition, victims who suffer frequent, ongoing abuse are less likely to accurately remember the exact number of incidents.
+\textbf{Aim 2.}  The CSEW is used to estimate the costs of domestic abuse in the UK.
+While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a survivor of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
+First, because it does not collect detailed information on various aspects of repeat domestic abuse victimisation (an inherent characteristic of domestic abuse cases), as it only records the number of incidents involving physical violence perpetrated by household members (and ignores repeated cases of non-physical violence).
+In addition, survivors who suffer frequent, ongoing abuse are less likely to accurately remember the exact number of incidents.
 Second, because it only focuses on certain sub-categories of domestic abuse (physical violence, sexual assault, stalking), while ignores others (criminal damage, verbal abuse, financial abuse, burglary).
-In addition, it does not collect information on whether different offences against the same victim were perpetrated by the same offender.
-In contrast, the WMP data allows us to tell if a reported case was domestic abuse related, regardless of the actual offence committed.
-In addition, it allows us to identify various incidents where the same victim-offender pair were involved.
-We can estimate the co-morbidity of self-reported victimisation by crime type using the CSEW.
-We can contrast this with the estimated co-morbidity of reported victimisation from the police data.
+In addition, it does not collect information on whether different offences against the same survivor were perpetrated by the same offender.
+In contrast, the WMP data allows us to tell if a reported case was domestic abuse related (as the police is required to record this information), regardless of the actual offence committed.
+In addition, it allows us to identify various incidents with the same victim-offender pair, providing us with reliable data on reported cases of repeat victimisation.
+We can estimate the co-morbidity of domestic abuse victimisation with other types of criminal victimisation using the CSEW.
+We can combine this with the estimated likelihood of domestic abuse victimisation by offence type to get a better estimate of the overall extent of domestic abuse victimisation (reported and unreported).
 \textit{is this silly?
@@
 
-%It is common that individuals are more likely to be a victim of crime if they have previously been a victim of crime, and if they have perpetrated crimes.
-It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the victim of crimes.
+%It is common that individuals are more likely to be a survivor of crime if they have previously been a survivor of crime, and if they have perpetrated crimes.
+It is also more likely that an individual will commit criminal activities if they have done so before, and if they have previously been the survivor of crimes.
 We will use our datasets to improve our understanding of the temporal patterns of victims and perpetrators, particularly around domestic abuse.
@@
 
-\textbf{Aim 3.} Police forces in England, including the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
-By contrasting the extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the true number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
+\textbf{Aim 3.} Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
+By contrasting extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the recorded number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
 Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time.
-We can complement this investigation with analysing the self-reported outcome of incidents that have been reported to the police from the CSEW.
+We can complement this investigation with analysing the self-reported outcome of incidents that have been reported to the police from the CSEW, and the survivor's perception of the CJS.
 
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we are interested in exploring the risk factors of serious harm and the factors determining the decision to report the abuse.
+First,...
+ Second,...
+ does the level of harm depend on the length of time spent in the relationship, separation,
+
+Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
+ Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
 
@@
 
-\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} escalation often happens when the abuser feels like they are losing control (e.g., because the victim threatens to leave); separation is an important risk factors of serious harm;
+\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} often happens when the abuser feels like they are losing control (e.g., because the survivor threatens to leave); separation is an important risk factors of serious harm; contact over children
 
@@
 
+decision to report: serious violence; friends, family, neighbours notice; happens in public, in front of people
+
 \textcolor{red}{\textit{Detailed plan}}
 
-does the level of harm depend on the length of time spent in the relationship, separation,
-
-Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
-
-\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the victim (especially focusing on the issue of separation and divorce, as evidence suggests it is a significant risk factor predicting serious harm).
+\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the survivor.
+We are especially interested in the co-morbidity of separation and divorce wand serious physical harm, as evidence suggests that the survivor's decision to end the relationship is a significant risk factor predicting serious harm.
 We will also explore whether non domestic abuse-related victimisation is predictive of serious harm.
@@
 
-Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.
+%Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.
+
+Second, we will use the WMP
 
@@
 
-%We can examine whether a recorded victim of domestic abuse was previously recorded as a victim in other crimes, and if they were subsequently a victim of other criminal behaviours.
+%We can examine whether a recorded survivor of domestic abuse was previously recorded as a survivor in other crimes, and if they were subsequently a survivor of other criminal behaviours.
 Identifying risk factors is crucial for police services who want to identify individuals at risk of being future victims, so that they can target interventions and give the best advice possible to reduce an individual's risk.
@@
 
-\textbf{Aim 2.} First, we will use the CSEW, and a logistic approach to understand how the decision to report to the police (or seeking any external help) depends on the individual-level characteristics of the victim (especially focusing on mental and physical health, financial independence and whether the victim has children) and the abuse suffered.
-We can complement this analysis with the WMP data,
+Serious harm can be the cause or the consequence of the decision to report.
 
-children's safety as a concern
+\textbf{Aim 2.} First, we will use the CSEW, and a logistic regression approach to understand how the decision to report to the police (or the decision to seek any form of external help) depends on the individual-level characteristics of the survivor (especially focusing on mental and physical health, financial independence and whether the survivor has children), and the severity and type of the abuse suffered.
+We are also interested in the link between the decision to report and survivor's general trust in the CJS.
 
-Second, using the WMP data, we will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse.
-Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+Second, we can use the WMP data to investigate drivers of the decision to report.
+For this analysis, we will focus on the subset of incidents (6\% of all incidents), where the victim reported a long history of abuse (at least 3 days between first and last reported occurrence).
+We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, Halloween, Easter, etc.), potentially reflecting cases where the abuse has suddenly escalated, or became known to outsiders.
 
@@
 %
-%Future victim behaviours. Future perpetrator behaviours
+%Future survivor behaviours. Future perpetrator behaviours
 %
@@
 In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household.
-Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design victim support programmes and quantify the societal harm caused by it.
+Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
 
@@
 
-Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a victim of a domestic abuse offender. No control group.
+Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a survivor of a domestic abuse offender. No control group.
 
@@
 %It also contains information about  multiple members of the household.
-This allows us to examine whether young individuals living in a household with a victim of domestic abuse are more likely to be victims or perpetrators of other types of crime.
+This allows us to examine whether young individuals living in a household with a survivor of domestic abuse are more likely to be victims or perpetrators of other types of crime.
 By using other questions in the CSEW, we can also measure whether these children are more likely to perpetrate crimes, and to be involved in gang related activities.

### 2019-06-26 case_for_support.tex
Typo

@@
 
-In outlining the research program we specify X core regression analyses, which we will preregister ahead of beigging research on the OSF.
+In outlining the research program we specify X core regression analyses, which we will preregister on OSF ahead of beginning research.
 These will be complemented with the robustness checks and further exploratory regressions (see, Trendl Football, for an example of this approach).
@@
 In addition, it does not collect information on whether different offences against the same survivor were perpetrated by the same offender.
-In contrast, the WMP data allows us to tell if a reported case was domestic abuse related (as the police is required to record this information), regardless of the actual offence committed.
+In contrast, the WMP data allows us to tell if a reported case was domestic abuse related (as the police are required to record this information), regardless of the actual offence committed.
 In addition, it allows us to identify various incidents with the same victim-offender pair, providing us with reliable data on reported cases of repeat victimisation.

### 2019-06-27 case_for_support.tex
Anna update

@@
 \usepackage{hyperref}
+\usepackage{booktabs}
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+\usepackage{threeparttable}
+%\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}
 
@@
 
-In outlining the research program we specify X core regression analyses, which we will preregister on OSF ahead of beginning research.
-These will be complemented with the robustness checks and further exploratory regressions (see, Trendl Football, for an example of this approach).
+Our research programme involves four research projects in the broader topic of domestic abuse.
+In outlining each of these research projects, for the sake of clarity, we will specify a set of core regression analyses we plan to conduct.
+We will preregister all of our analysis plans on the Open Science Framework (OSF) ahead of beginning research.
+We aim to complement all analyses with robustness checks and further exploratory regressions (see, \textit{Trendl Football}, for an example of this approach).
 
-\subsection*{1. Understanding domestic abuse: survivor characteristics, extent of domestic abuse and police mis-recording}
+\subsection*{1. Understanding domestic abuse: survivor characteristics and police mis-recording}
 
  \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In our first research project, we will be investigating three main research questions.
-First, we will use the CSEW dataset to identify the demographic and socio-economic predictors of domestic abuse victimisation, and validate the CSEW estimates using the WMP data.
+In our first research project, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
+We will also use the WMP data to explore the extent of police mis-recording of domestic abuse.
+Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
 
-Second, we will estimate the true extent of domestic abuse victimisation.
+%Second, we will estimate the true extent of domestic abuse victimisation.
 Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the prevalence of domestic abuse.
@@
 
-Finally, we will estimate the extent of police mis-recording of domestic abuse.
+%Finally, we will estimate the extent of police mis-recording of domestic abuse.
 Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
@@
 
-\textcolor{red}{\textit{What we know so far}}
+%\textcolor{red}{\textit{What we know so far}} 
+%
+%7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders; bisexual women are twice as more likely to experience DA compared to heterosexual women; mixed/multiple ethnicity; social housing; unemployment.
+%single mothers and mothers with young children are more at risk
+%
+%Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS about West Midlands mis-recording}
 
-Aim 1.
-\href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{CSEW} : 7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders.
-single mothers and mothers with young children are more at risk
+\textcolor{red}{\textit{Detailed plan}} First, using the CSEW data, we will extend our understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
+The CSEW provides and ever broader range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data.
+Building on what we know so far, we will explore the relative explanatory power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
+We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
 
-Aim 2. The prevalence of DA is usually based on the CSEW, so I think the second analysis can add value.
+ However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
+To uncover the structure of these interactions (without having to a priori specify them, as is required in a logistic regression model), we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
+Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
 
-Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS about West Midlands mis-recording}
+ Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
+\textit{Why don't we use the aggregate number of police-recorded domestic abuse cases for each police force to do this?
+But if we don't particularly rely on the WMP data is there a point in this?}
 
-\textcolor{red}{\textit{Detailed plan}}
+\begin{table}[!htbp]
+\caption{Information on Swiss nuclear power plants}
+  \begin{threeparttable}[t]
+  \centering
+       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+    \toprule
+     \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
+    \midrule
+    What are the characteristics of domestic abuse victims?
+& CSEW & Individual (respondent-level) & Domestic abuse victimisation; Victimisation by type (physical, sexual abuse, threats) & e & Logistic regression/random forest \\
+    What is the extent of police mis-recording of domestic abuse in the West Midlands? & CSEW & & & & \\
+%    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
+%    Mühleberg & 01.07.1971 & Boiling water reactor & 373   & 2019\\
+%    Gösgen & 02.02.1979 & Pressurised water reactor & 1010  & 2039 \\
+%    Leibstadt & 24.05.1984 & Boiling water reactor & 1220  & 2044 \\
+     \bottomrule
+  \end{tabular}
+%     \begin{tablenotes}
+%     \item[1] Assumption: life time of 60 years.
+%     \item[2] Official shut-down.
+%   \end{tablenotes}
+    \end{threeparttable}%
+  \label{tab:addlabel}%
+\end{table}%
 
-\textbf{Aim 1.} First, using the CSEW data, we will conduct a series of statistical analyses to provide a deeper understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
-Using a logistic regression approach, we will explore the factors predicting individual-level domestic abuse victimisation, depending on the type of abuse ever suffered (physical abuse, threats, sexual abuse).
-The CSEW provides a wealth of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
-Using this wide range of individual-level information, we will evaluate the importance of each of these variables in predicting the likelihood of domestic abuse victimisation.
-\textit{Could we also use a e.g.
-a random forest classification algorithm and look at variable importance?
-this way we could also look at interactions?
-does clustering make sense here to explore structure?}  These analyses will represent the first extensive quantitative investigation of the individual-level predictors of domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
-We are particularly interested in the association between experiences of domestic abuse, number of children, and financial resilience, as previous research has suggested that access to resources is an important factor in escaping the cycle of abuse, especially for women with children.
-
-Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police.
+%Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police.
 The WMP contains information about the sex and age of victims.
@@
 
-\textbf{Aim 2.}  The CSEW is used to estimate the costs of domestic abuse in the UK.
+%\textbf{Aim 2.}  The CSEW is used to estimate the costs of domestic abuse in the UK.
 While a unique strength of the CSEW is that it provides reliable estimates of the proportion of the population who have been a survivor of a certain crime, it cannot capture the true extent of domestic abuse victimisation for several reasons.
@@
 
-\textbf{Aim 3.} Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
-By contrasting extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the recorded number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
+%By contrasting extrapolated estimates from the CSEW (which is a representative sample) with WMP data on the recorded number of reported cases, we can estimate the true extent of the mis-recording of domestic abuse cases by the WMP.
 Given the repeated cross-sectional nature of the CSEW, and the longitudinal nature of the WMP, we can quantify the proportion of mis-recorded incidents over time.
@@
 \textcolor{red}{\textit{Core outcomes}}
-A deeper understanding of the socio-economic predictors of domestic abuse victimisation.
-The first estimation of the true extent of domestic abuse-related victimisation across all offence types.
-An estimation of the extent of police (WMP) mis-recording of domestic abuse over time.
+
+The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation.
 
@@
 Second, we will use the WMP
+
+\begin{table}[!htbp]
+\caption{Information on Swiss nuclear power plants}
+  \begin{threeparttable}[t]
+  \centering
+       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+    \toprule
+     \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
+    \midrule
+    What are the predictors of serious harm? & CSEW & Individual (respondent-level) & Injury suffered from domestic abuse victimisation & e & Logistic regression \\
+    What are the predictors of serious harm?
+& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & Age/sex of perpetrator and victim, previous recorded offences of perpetrator &  \\
+%    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
+%    Mühleberg & 01.07.1971 & Boiling water reactor & 373   & 2019\\
+%    Gösgen & 02.02.1979 & Pressurised water reactor & 1010  & 2039 \\
+%    Leibstadt & 24.05.1984 & Boiling water reactor & 1220  & 2044 \\
+     \bottomrule
+  \end{tabular}
+%     \begin{tablenotes}
+%     \item[1] Assumption: life time of 60 years.
+%     \item[2] Official shut-down.
+%   \end{tablenotes}
+    \end{threeparttable}%
+  \label{tab:addlabel}%
+\end{table}%
 

### 2019-06-27 case_for_support.tex
Psych Sci draft

@@
  Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
+%
+%\textcolor{red}{\textit{What we know so far}}
+%
+%\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} often happens when the abuser feels like they are losing control (e.g., because the survivor threatens to leave); separation is an important risk factors of serious harm; contact over children
+%
+%\href{http://www.safelives.org.uk/policy-evidence/about-domestic-abuse/how-long-do-people-live-domestic-abuse-and-when-do-they-get}{Reporting} 
+%
+%decision to report: serious violence; friends, family, neighbours notice; happens in public, in front of people
 
-\textcolor{red}{\textit{What we know so far}}
+\textcolor{red}{\textit{Detailed plan}} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the survivor.
+We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
+Drawing on the results of our investigation on the risk factors predicting domestic abuse, we will select 3-4 victim characteristics that have the highest explanatory power to understand how these predict serious harm.
+We are especially interested in the co-morbidity of separation and divorce wand serious physical harm, as evidence suggests that the survivor's decision to end the relationship is a significant risk factor predicting serious harm.
 
-\href{https://www.thehotline.org/2018/09/28/escalation/}{Escalation} often happens when the abuser feels like they are losing control (e.g., because the survivor threatens to leave); separation is an important risk factors of serious harm; contact over children
-
-\href{http://www.safelives.org.uk/policy-evidence/about-domestic-abuse/how-long-do-people-live-domestic-abuse-and-when-do-they-get}{Reporting}
-
-decision to report: serious violence; friends, family, neighbours notice; happens in public, in front of people
-
-\textcolor{red}{\textit{Detailed plan}}
-
-\textbf{Aim 1.} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the survivor.
-We are especially interested in the co-morbidity of separation and divorce wand serious physical harm, as evidence suggests that the survivor's decision to end the relationship is a significant risk factor predicting serious harm.
-We will also explore whether non domestic abuse-related victimisation is predictive of serious harm.
-We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
+In the WMP data, we have access to detailed information on the characteristics of each reported domestic abuse incident, such as whether the victim lives with the perpetrator, or whether they are or have been in an intimate partner relationship.
 

### 2019-06-28 case_for_support.tex
Anna update

@@
 
-Our research programme involves four research projects in the broader topic of domestic abuse.
+Our research programme involves four research projects exploring different aspects of domestic abuse.
 In outlining each of these research projects, for the sake of clarity, we will specify a set of core regression analyses we plan to conduct.
-We will preregister all of our analysis plans on the Open Science Framework (OSF) ahead of beginning research.
-We aim to complement all analyses with robustness checks and further exploratory regressions (see, \textit{Trendl Football}, for an example of this approach).
+We will preregister all of our analysis plans using the Open Science Framework (OSF) ahead of beginning research.
+We will also aim to complement all analyses with robustness checks and further exploratory regressions as the data allows (see, \textit{Trendl Football}, for an example of this approach).
 
@@
  \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In our first research project, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
+In this research project, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
@@
 \textcolor{red}{\textit{Detailed plan}} First, using the CSEW data, we will extend our understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
-The CSEW provides and ever broader range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
+The CSEW provides a broad range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
 Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data.
-Building on what we know so far, we will explore the relative explanatory power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
+Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
+Investigating the explanatory power of these characteristics within one statistical model will provide us with a deeper understanding of the importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
 We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
@@
  Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
-\textit{Why don't we use the aggregate number of police-recorded domestic abuse cases for each police force to do this?
-But if we don't particularly rely on the WMP data is there a point in this?}
+\textit{Why don't we use the aggregate number of \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/datasets/domesticabuseinenglandandwalesappendixtables}{police-recorded domestic abuse cases for each police force} to do this?
+But if we don't particularly rely on the WMP data is there a point in this?
+They use \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/bulletins/domesticabuseinenglandandwales/yearendingmarch2018}{CSEW and police data} in this report, but they don't seem to compare the two}
 
 \begin{table}[!htbp]
-\caption{Information on Swiss nuclear power plants}
+\caption{Understanding domestic abuse: survivor characteristics and police mis-recording, regressions}
   \begin{threeparttable}[t]
@@
     What are the characteristics of domestic abuse victims?
-& CSEW & Individual (respondent-level) & Domestic abuse victimisation; Victimisation by type (physical, sexual abuse, threats) & e & Logistic regression/random forest \\
-    What is the extent of police mis-recording of domestic abuse in the West Midlands? & CSEW & & & & \\
+& CSEW & Individual (respondent-level) & Domestic abuse victimisation; Victimisation by type (physical, sexual abuse, threats) & demographic and socio-economic characteristics & Logistic regression/random forest \\
+        \midrule
+    What is the extent of police mis-recording of domestic abuse? & ONS data & & & & \\
 %    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we are interested in exploring the risk factors of serious harm and the factors determining the decision to report the abuse.
-First,...
- Second,...
- does the level of harm depend on the length of time spent in the relationship, separation,
-
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will explore the victim and offender characteristics that are predict serious harm and the factors determining the decision to report the abuse.
+Identifying high-risk victim-offender pairs is key in preventing serious harm.
 Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
@@
 
-\textcolor{red}{\textit{Detailed plan}} First, we will use the CSEW, and a multinomial logistic approach to understand how the level of harm suffered (threats, minor or serious injury) depends on the individual-level characteristics of the survivor.
+\textcolor{red}{\textit{Detailed plan}} Drawing on the relative strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
+Previous studies investigating this question mostly relied on police data and focused on identifying high-risk offenders.
+We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
+Specifically, using a multinomial logistic approach, we will explore to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (not going out, living alone or with the perpetrator), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
 We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
-Drawing on the results of our investigation on the risk factors predicting domestic abuse, we will select 3-4 victim characteristics that have the highest explanatory power to understand how these predict serious harm.
-We are especially interested in the co-morbidity of separation and divorce wand serious physical harm, as evidence suggests that the survivor's decision to end the relationship is a significant risk factor predicting serious harm.
 
-In the WMP data, we have access to detailed information on the characteristics of each reported domestic abuse incident, such as whether the victim lives with the perpetrator, or whether they are or have been in an intimate partner relationship.
+Using the WMP data, we will also explore the risk factors associated with the perpetrator, using each perpetrator-victim pair as a unit of analysis.
+The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
+Our detailed crime dataset will allow to investigate the extent to which previous recorded self-harm and suicide attempts, previous violent and drug offences, breaching court orders and separation will predict causing serious harm.
+From the detailed description of the incident, we will know if the perpetrator and the victim live together.
+We will explore this question using a multinomial logistic regression analysis with perpetrator-victim fixed effects.
 
@@
 
-Second, we will use the WMP
-
 \begin{table}[!htbp]
-\caption{Information on Swiss nuclear power plants}
+\caption{Predicting serious harm and understanding the decision to report, regressions}
   \begin{threeparttable}[t]
@@
     \midrule
-    What are the predictors of serious harm? & CSEW & Individual (respondent-level) & Injury suffered from domestic abuse victimisation & e & Logistic regression \\
-    What are the predictors of serious harm?
-& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & Age/sex of perpetrator and victim, previous recorded offences of perpetrator &  \\
+    What victim characteristics predict serious harm?
+& CSEW & Individual (respondent-level) & Level of harm resulting from domestic abuse victimisation (no physical harm, minor, serious) & financial resources, mental health, dependence, social isolation, separation, feeling scared & Multinomial logistic regression \\
+        \midrule
+     What perpetrator characteristics predict serious harm?
+& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, previous violent and drug offences, breaching court orders, separation & Multinomial logistic regression with perpetrator-victim fixed effects \\
 %    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
@@
 
-We can predict incidents with serious harm, using the type of offence occurred previously, criminal history of the offender.
-number of days elapsed.
-This will allow us to identify and commonalities in the pattern of domestic abuse cases that lead to escalation in the form of serious harm.
-We can also identify and characterise high-risk perpetrators who breach court orders designed to protect the victims from further harms.
-
 %We can examine whether a recorded survivor of domestic abuse was previously recorded as a survivor in other crimes, and if they were subsequently a survivor of other criminal behaviours.
@@
 
-Serious harm can be the cause or the consequence of the decision to report.
-
-\textbf{Aim 2.} First, we will use the CSEW, and a logistic regression approach to understand how the decision to report to the police (or the decision to seek any form of external help) depends on the individual-level characteristics of the survivor (especially focusing on mental and physical health, financial independence and whether the survivor has children), and the severity and type of the abuse suffered.
-We are also interested in the link between the decision to report and survivor's general trust in the CJS.
+We will also use both datasets to explore the predictors of the decision to report the abuse.
+Using the CSEW, we will investigate the factors predicting the decision to report using a logistic regression approach to understand how the decision to report to the police (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
+We are especially interested in the effect of trust in the Criminal Justice System (CJS), social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
 

### 2019-06-28 case_for_support.tex
Anna update

@@
 We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
-Specifically, using a multinomial logistic approach, we will explore to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (not going out, living alone or with the perpetrator), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
+Specifically, using a multinomial logistic approach, we will explore to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (not going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
 We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
@@
 We will explore this question using a multinomial logistic regression analysis with perpetrator-victim fixed effects.
+Using this statistical framework will allow us to disentangle the relative importance of our explanatory variables and perpetrator-victim specific factors in predicting serious harm.
 
@@
 & WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, previous violent and drug offences, breaching court orders, separation & Multinomial logistic regression with perpetrator-victim fixed effects \\
-%    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
-%    Mühleberg & 01.07.1971 & Boiling water reactor & 373   & 2019\\
-%    Gösgen & 02.02.1979 & Pressurised water reactor & 1010  & 2039 \\
-%    Leibstadt & 24.05.1984 & Boiling water reactor & 1220  & 2044 \\
+                \midrule
+     What time-invariant (victim) characteristics predict the decision to report?
+& CSEW & Individual (respondent-level) & Reported abuse to the police & severity/type of abuse, trust in CJS, social ties, financial status, children, mental health, dependencies & Logistic regression \\
+       \midrule
+          What time-varying characteristics predict the decision to leave?
+& WMP & Perpetrator-victim pairs & Reported ongoing abuse to the police & time of year, specific holidays, length of abuse, severity of last occurrence & Logistic regression \\
      \bottomrule
   \end{tabular}
-%     \begin{tablenotes}
-%     \item[1] Assumption: life time of 60 years.
-%     \item[2] Official shut-down.
-%   \end{tablenotes}
     \end{threeparttable}%
@@
 
-We will also use both datasets to explore the predictors of the decision to report the abuse.
-Using the CSEW, we will investigate the factors predicting the decision to report using a logistic regression approach to understand how the decision to report to the police (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
-We are especially interested in the effect of trust in the Criminal Justice System (CJS), social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
-
-Second, we can use the WMP data to investigate drivers of the decision to report.
-For this analysis, we will focus on the subset of incidents (6\% of all incidents), where the victim reported a long history of abuse (at least 3 days between first and last reported occurrence).
+We will also use both datasets to explore the predictors of the decision to report and escape the abuse.
+Using the CSEW and logistic regression approach, we will investigate how the decision to report (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
+We are especially interested in exploring how trust in the Criminal Justice System (CJS), social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency affect the decision to report.
+Using the WMP data, we will explore time-varying factors affecting the decision to leave the abuser.
+Due to the high levels of underreporting, it is hard to distinguish between time periods when the number of domestic abuse incidents increase and when the victims have a higher propensity to finally report the ongoing abuse.
+Here we are mainly interested in the latter, therefore we will focus on the subset of incidents, where the victim for the first time reported a long history of abuse.
 We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, Halloween, Easter, etc.), potentially reflecting cases where the abuse has suddenly escalated, or became known to outsiders.
@@
 \textcolor{red}{\textit{Core outcomes}}
+
+A deeper understanding of the victim and perpetrator characteristics that predict serious harm, and the time-invariant and time-varying factors affecting the decision to report the abuse to the police.
 

### 2019-07-01 case_for_support.tex
Anna update

@@
 Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender and victim.
-We do not intend to link the two datasets.
+In all the analysis plans outlined below, we will not link the individuals in these datasets.
 
@@
 Our research programme involves four research projects exploring different aspects of domestic abuse.
+Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP, we aim to complement, extend and deepen our understanding of domestic abuse.
 In outlining each of these research projects, for the sake of clarity, we will specify a set of core regression analyses we plan to conduct.
@@
 The CSEW provides a broad range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
-Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{descriptive statistics} derived from the CSEW data.
 Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
@@
  However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
-To uncover the structure of these interactions (without having to a priori specify them, as is required in a logistic regression model), we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
+To uncover the structure of these interactions without having to a priori specify them, as is required in a logistic regression model, we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
 Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will explore the victim and offender characteristics that are predict serious harm and the factors determining the decision to report the abuse.
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will explore the victim and offender characteristics that predict serious harm and the factors determining the decision to report the abuse.
 Identifying high-risk victim-offender pairs is key in preventing serious harm.
-Understanding what affects the decision to report is particularly important since underreporting represents the biggest obstacle to effectively tackling domestic abuse.
+Understanding what affects the decision to report is particularly important, as underreporting represents the biggest obstacle to effectively tackling domestic abuse.
 Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
@@
 \textcolor{red}{\textit{Detailed plan}} Drawing on the relative strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
-Previous studies investigating this question mostly relied on police data and focused on identifying high-risk offenders.
+Previous studies investigating this question mostly relied on police data and focused on \href{https://link.springer.com/article/10.1007/s41887-017-0011-1}{identifying high-risk offenders}.
 We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
-Specifically, using a multinomial logistic approach, we will explore to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (not going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
+Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
 We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
+Given the cross-sectional nature of the CSEW data, this analysis will be exploratory rather than causal.
 
@@
 The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
-Our detailed crime dataset will allow to investigate the extent to which previous recorded self-harm and suicide attempts, previous violent and drug offences, breaching court orders and separation will predict causing serious harm.
+Our detailed crime dataset will allow to investigate the extent to which the perpetrator's previous recorded self-harm and suicide attempts, previous violent and drug offences, breaches of court orders and separation from the victim will predict causing serious harm.
 From the detailed description of the incident, we will know if the perpetrator and the victim live together.
-We will explore this question using a multinomial logistic regression analysis with perpetrator-victim fixed effects.
-Using this statistical framework will allow us to disentangle the relative importance of our explanatory variables and perpetrator-victim specific factors in predicting serious harm.
+We will explore this question using a multinomial logistic regression analysis with perpetrator-victim fixed effects, where we will use previously known information about the perpetrator to predict serious harm.
+Using a fixed-effects regression approach will allow us to disentangle the relative importance of our explanatory variables and perpetrator-victim specific factors in predicting serious harm.
 
@@
 We will also use both datasets to explore the predictors of the decision to report and escape the abuse.
+We are not aware of previous research exploring this question.
 Using the CSEW and logistic regression approach, we will investigate how the decision to report (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
@@
 Using the WMP data, we will explore time-varying factors affecting the decision to leave the abuser.
-Due to the high levels of underreporting, it is hard to distinguish between time periods when the number of domestic abuse incidents increase and when the victims have a higher propensity to finally report the ongoing abuse.
-Here we are mainly interested in the latter, therefore we will focus on the subset of incidents, where the victim for the first time reported a long history of abuse.
+Due to the high levels of underreporting, it is hard to distinguish between time periods when the number of domestic abuse incidents increase, and when the victims have a higher propensity to finally report the ongoing abuse.
+Here we are mainly interested in the latter case (and will explore the first case in more detail in the last research project), therefore we will focus on the subset of incidents where the victim for the first time reported a long history of abuse.
 We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, Halloween, Easter, etc.), potentially reflecting cases where the abuse has suddenly escalated, or became known to outsiders.
@@
 
-\newpage
-
 \subsection*{3. The long-lasting effects of domestic abuse}
-
-it's impossible to establish causality
 
@@
 
-\textcolor{red}{\textit{What we know so far}}
-\href{https://www.womensaid.org.uk/information-support/what-is-domestic-abuse/the-nature-and-impact-of-domestic-abuse/}{Women's aid, effect on victims} increased likelihood of mental health problems (isolation, low self-esteem), alcohol and drug dependency, financial consequences due to financial abuse or losing a job as a result of the abuse, fighting back?
+%\textcolor{red}{\textit{What we know so far}}
+%\href{https://www.womensaid.org.uk/information-support/what-is-domestic-abuse/the-nature-and-impact-of-domestic-abuse/}{Women's aid, effect on victims} increased likelihood of mental health problems (isolation, low self-esteem), alcohol and drug dependency, financial consequences due to financial abuse or losing a job as a result of the abuse, fighting back?
+%
+%\href{https://uksaysnomore.org/effects-of-domestic-abuse-on-children/}{Effect on children I} witnessing violence is major predictor for PTSD and depressive symptoms in children; behavioural problems, bullying (either victims or perpetrators)
+%
+%\href{https://www.psychologytoday.com/gb/blog/progress-notes/201902/alarming-effects-childrens-exposure-domestic-violence}{Effect on children II} cognitive development is affected, learning difficulties are more common, difficulties in social relationships, withdrawal, antisocial behaviours, they are more likely to become both perpetrators and victims of domestic abuse; protective factors: literacy, intelligence, social competence, supportive relationship with at least one influential adult
 
-\href{https://uksaysnomore.org/effects-of-domestic-abuse-on-children/}{Effect on children I} witnessing violence is major predictor for PTSD and depressive symptoms in children; behavioural problems, bullying (either victims or perpetrators)
+\textcolor{red}{\textit{Detailed plan}} First, we will explore the causal effect of past experiences of domestic and child abuse on present socio-economic outcomes.
+First, using the CSEW, we will explore how experiencing abuse in childhood affects educational, employment and health outcomes in adulthood.
+The 2016 CSEW included a module asking respondents about whether they experienced abuse as a child or witnessed domestic abuse.
+\href{https://www.ons.gov.uk/releases/abuseduringchildhoodfindingsfromtheyearendingmarch2016crimesurveyforenglandandwales}{Descriptive statistics} of this dataset revealed that those who reported to have experienced abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household.
+However, due to the possibility of various confounders (e.g., those growing up in economically deprived areas are more likely to experience abuse, but economic deprivation also affects educational outcomes), these statistics do not tell us the causal effect of childhood abuse on socio-economic outcomes in adulthood.
+To overcome this difficulty in establishing causal relationships, we will use propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of childhood abuse on educational, employment, and mental and physical health outcomes, and the probability of experiencing domestic abuse in adulthood.
+In a similar vein, using propensity score matching, we will explore how past experiences of domestic abuse affect current health outcomes, by comparing people who have experienced domestic abuse in the past, but not in the last 12 months, with people who have never experienced domestic abuse, but otherwise have similar socio-economic characteristics.
 
-\href{https://www.psychologytoday.com/gb/blog/progress-notes/201902/alarming-effects-childrens-exposure-domestic-violence}{Effect on children II} cognitive development is affected, learning difficulties are more common, difficulties in social relationships, withdrawal, antisocial behaviours, they are more likely to become both perpetrators and victims of domestic abuse; protective factors: literacy, intelligence, social competence, supportive relationship with at least one influential adult
+Second, using both the CSEW and WMP, we will explore how children's behavioural problems are affected by witnessing or experiencing domestic abuse at home.
+Using data from the 10-15 year old questionnaire of the CSEW, which can be linked to the adult questionnaire, we can examine the effect of domestic and child abuse on children living in such households.
+The children's questionnaire records information on whether the child had been physically or verbally abused by someone (and if that person lives in the household), as well as their experiences with bullying, carrying knives, and information on gang membership, school truancy, learning difficulties and health, including drug use and drinking behaviour.
+This allows us to explore the causal effect of past and present domestic abuse in the household and child abuse on these outcomes through propensity score matching.
+\textit{Estimating the effect of indirect exposure to domestic abuse through a previously abused parent?}
 
-\textcolor{red}{\textit{Detailed plan}}
+We will complement this analysis using the WMP, by estimating how living in a household with domestic and child abuse affects the likelihood of engaging in various types of criminal behaviours (property-related vs violent crime).
+We will do so by identifying what percentage of young offenders are victims of child abuse, and have a home address that is associated with domestic abuse incidents.
+Given the problem of underreporting, this will give us a lower bound for the estimate of the proportion of children with behavioural problems who live in abusive households.
+\textit{Am I missing something here?}
 
-\textbf{Aim 1.} First, using the CSEW, we will explore the long-lasting effects of experiencing domestic abuse.
-In the CSEW, in two separate questions, respondents are asked whether they have experienced any form of domestic abuse (use of violence, sexual abuse, threatening behaviour, stalking) since the age of 16 or in the last 12 months.
-This way we can identify respondents who have suffered specific forms of abuse in the past, but not in the last 12 months.
-Using propensity score matching, we can then compare their physical and mental health-related outcomes, and alcohol and drug consumption with those, who have never experienced any form of abuse, but otherwise have similar socio-economic characteristics.
-This will allow us to estimate the effect of past abuse on present outcomes whilst controlling for individual- and macro-level characteristics.
-
-\textbf{Aim 2.} Using data from the 10-15 year old questionnaire of the CSEW, which can be linked to the adult questionnaire, we can examine the effect of domestic abuse on children living in such households.
-The questionnaire records information on whether the child had been physically or verbally abused by someone (and if that person lives in the household), as well as their experiences with bullying, carrying knives and information on gang membership, school truancy and health.
-We can explore the effect of domestic and child abuse on these outcomes through propensity score matching.
-
-Domestic abuse often co-occurs with child abuse. We can use the WMP data to estimate this co-morbidity, and identify under 18s who had been a survivor of a domestic abuse offender. No control group.
+\begin{table}[!htbp]
+\caption{The long-lasting effects of domestic abuse, regressions}
+  \begin{threeparttable}[t]
+  \centering
+       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+    \toprule
+     \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
+    \midrule
+    How does past childhood abuse affect socio-economic outcomes in adulthood?
+& CSEW & Individual (respondent-level) & Educational attainment, employment status and health-related outcomes, including domestic abuse victimisation & Degree and type of childhood abuse suffered & Propensity score matching \\
+                \midrule
+                   How does experiences of past (but not recent) domestic abuse affect socio-economic outcomes in adulthood?
+& CSEW & Individual (respondent-level) & Current health and employment outcomes & Degree and type of domestic abuse suffered & Propensity score matching \\
+                \midrule
+     How does experiences of domestic abuse at home and experiences of child abuse affect behavioural outcomes in childhood?
+& CSEW & Individual (respondent-level) & Bullying, involvement with gangs, school truancy, carrying knives, drugs and alcohol usage, learning difficulties, health & Degree and type of domestic abuse witnessed/child abuse suffered & Propensity score matching \\
+                \midrule
+          What proportion of young offenders come from abusive households? & WMP & Young offenders &  &  &  \\
+     \bottomrule
+  \end{tabular}
+    \end{threeparttable}%
+  \label{tab:addlabel}%
+\end{table}%
 
@@
 \textcolor{red}{\textit{Core outcomes}}
-
-\newpage
+ The first UK-based quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
 
@@
 In this research project, we will be using the CSEW and WMP datasets, as well as external sources of data to investigate some of the environmental predictors of domestic abuse.
-First, using data from the CSEW and drawing on previous research on the topic, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report.
-We will complement this with an additional analysis on WMP and census data.
-We will be able to account for the dynamic nature of these neighbourhood characteristics, by using longitudinal and repeated cross-sectional datasets.
+We will first explore how neighbourhood-level characteristics affect domestic abuse victimisation and the willingness to report.
 Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
 
-Second, we will be looking at how time-varying, exogenous factors affect domestic abuse.
+We will also explore how time-varying, exogenous factors affect domestic abuse.
 We will first explore the effect of local events that increase alcohol-consumption, since our previous study have found a significant relationship between alcohol-related domestic abuse and football.
-Second, we will conduct two studies to understand the relationship between financial stress and the prevalence of domestic abuse.
+Second, we will explore the relationship between financial stress and the prevalence of domestic abuse.
 First, we will explore the association between gambling accessibility in the local area, and reported numbers of domestic abuse.
@@
 
-\textcolor{red}{\textit{What we know so far}} interestingly, there are no studies about this using UK data; neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV, especially financial independence;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks might foster community cohesion and reduces IPV;  however, in deprived neighbourhoods, where IPV is accepted social interactions can increase IPV
+%\textcolor{red}{\textit{What we know so far}} interestingly, there are no studies about this using UK data; neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV, especially financial independence;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks might foster community cohesion and reduces IPV;  however, in deprived neighbourhoods, where IPV is accepted social interactions can increase IPV
+%
+%\href{https://www.sciencedirect.com/science/article/abs/pii/S0277953616302891}{The relationship between electronic gaming machine accessibility and police-recorded domestic violence: A spatio-temporal analysis of 654 postcodes in Victoria, Australia, 2005–2014}
+%
+%\href{https://journals.sagepub.com/doi/abs/10.1177/1525107115623938}{Economic Stress and Domestic Violence: Examining the Impact of Mortgage Foreclosures on Incidents Reported to the Police }
+%
+%\href{https://journals.sagepub.com/doi/abs/10.1177/1524838012445641?journalCode=tvaa}{
+%The Impact of Neighborhoods on Intimate Partner Violence and Victimization
+%}
+%
+%the type sof social tie matters: friendship ties reduce the risk of IPV, family ties have no effect
+%
+%\href{https://journals.sagepub.com/doi/abs/10.1177/1524838013515758}{Neighborhood Environment and Intimate Partner Violence: A Systematic Review }
 
-\href{https://www.sciencedirect.com/science/article/abs/pii/S0277953616302891}{The relationship between electronic gaming machine accessibility and police-recorded domestic violence: A spatio-temporal analysis of 654 postcodes in Victoria, Australia, 2005–2014}
+\textcolor{red}{\textit{Detailed plan}} Using the CSEW, we will first explore the association between the environmental characteristics of the neighbourhood, the prevalence of domestic abuse and willingness to report.
+Previous literature has suggested various pathways, including reduced collective efficacy of neighbourhood, and normalisation and acceptance of violence through social norms to explain the link between neighbourhood characteristics and domestic abuse, but the question has not been explored in a UK context yet.
+Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, member of Neighbourhood Watch) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
+In investigating this question further, we will explore how deprivation in a neighbourhood (LSOA level, measured by the \href{https://data.gov.uk/dataset/8f601edb-6974-417e-9c9d-85832dd2bbf2/english-indices-of-deprivation-2015-lsoa-level}{Multiple Indices of Deprivation}) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
+Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
+These analyses will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first project to provide a comprehensive exploration of the factors affecting domestic abuse victimisation and willingness to report.
 
-\href{https://journals.sagepub.com/doi/abs/10.1177/1525107115623938}{Economic Stress and Domestic Violence: Examining the Impact of Mortgage Foreclosures on Incidents Reported to the Police }
-
-\href{https://journals.sagepub.com/doi/abs/10.1177/1524838012445641?journalCode=tvaa}{
-The Impact of Neighborhoods on Intimate Partner Violence and Victimization
-}
-
-the type sof social tie matters: friendship ties reduce the risk of IPV, family ties have no effect
-
-\href{https://journals.sagepub.com/doi/abs/10.1177/1524838013515758}{Neighborhood Environment and Intimate Partner Violence: A Systematic Review }
-
-\textcolor{red}{\textit{Detailed plan}}
-
-\textbf{Aim 1.} First, we will use the CSEW to investigate if there are significant associations between the prevalence of domestic abuse, the willingness to report, and the environmental characteristics of the neighbourhood they live in.
-Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, but the question has not been explored in a UK context yet.
-Our rich data allows us to determine the relative explanatory power of these.
-For example, social disorganization theory posits that neighbourhood disadvantage is associated with an increased risk of domestic abuse through reduced collective efficacy.
-Another potential pathway is social norms, suggesting that acceptance and normalisation of violence within a community can encourage domestic abuse.
-Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, \textit{member of Neighbourhood Watch?}) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation and trust in CJS, reflected in the propensity to report abuse.
-Second, using the WMP and the census, we can compliment this with an LSOA-level spatial regression, where we use the socio-economic characteristics (average income, education levels and benefit dependency) of the area to predict the number of reported abuse cases.
-Using a spatial regression will account for the spatial dependency between our observations and improve the reliability of our estimates.
-\textit{Not sure whether we can do the same with the CSEW, probably not on the LSOA level, but maybe on the MSOA level?} This analysis, contrasted with that outlined in project 1 about the individual-level predictors of domestic abuse, will provide us with the most comprehensive understanding on the risk factors of domestic abuse within the context of the UK.
-
-\textbf{Aim 2.} In this section, we will be looking at time-varying environmental factors that may influence domestic abuse.
-This part of the project will benefit from a dataset containing credit card and current account spending of x customers across the UK, to which we will have access as part of a data sharing agreement with a very large UK bank.
-\textit{I'm not sure about the specifics of this, would we combine this with the WMP or CSEW?
-I guess we won't know the card owner's address?} First, by using the WMP and credit card data, we will identify time-specific changes in alcohol consumption in parts of the West Midlands by identifying externals events that may affect it (e.g., local festivals, weather, bank holidays, sport tournaments), and investigate their effect on alcohol-related domestic abuse.
+We are also interested in exploring how time-varying external factors, including alcohol consumption, and financial stress (measured by gambling expenditure and benefit dependency) affect the propensity to engage in abusive behaviours.
+In investigating this question, we will benefit from a dataset containing credit card and current account spending of x customers across the UK, to which we will have access as part of a data sharing agreement with a very large UK bank.
+This dataset will allow us to quantify spending on alcohol over time by LSOA.
+By using the WMP and credit card data, we will identify time-specific changes in alcohol consumption in parts of the West Midlands by identifying externals events that may affect it (e.g., local festivals, weather, bank holidays, sport tournaments), and investigate their effect on reported alcohol-related domestic abuse (from the WMP).
 Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
@@
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
-For this estimation, we will use data on the proportion of benefits claimants in each LSOA.
-\textit{I know we were talking about using the credit card data for this one, but I am not sure what was the exact plan}.
+To further explore the effect of financial shocks on the propensity for violence, we focus on gambling.
 Gambling is increasingly recognised as a serious health concern across the UK, and can have an adverse impact on family finances.
-To assess the link between gambling accessibility and the prevalence of domestic abuse, we will use data on the number of licensed betting shops in the West Midlands within a spatial regression approach.
+We will use our credit card and WMP datasets to assess the link between changes in spending on gambling and domestic abuse.
 
-\href{https://secure.gamblingcommission.gov.uk/PublicRegister}{List of licensed gambling businesses} We can also contact the local authorities, as they should have an up-to-date list
+%\href{https://secure.gamblingcommission.gov.uk/PublicRegister}{List of licensed gambling businesses} We can also contact the local authorities, as they should have an up-to-date list
 
-\textcolor{red}{\textit{Core outcomes}} The first extensive analysis of the complex individual-- and neighbourhood level predictors of domestic abuse within the UK.
-An exploration of the exogenous, time-varying factors affecting levels of reported domestic abuse (mostly through alcohol).
-An examination of how gambling accessibility and temporal financial stress affect the reported number of domestic abuse cases in the West Midlands.
+\begin{table}[!htbp]
+\caption{Environmental factors affecting domestic abuse, regressions}
+  \begin{threeparttable}[t]
+  \centering
+       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+    \toprule
+     \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
+    \midrule
+    How do environmental characteristics of the neighbourhood predict domestic abuse?
+& CSEW & Individual (respondent-level) & domestic abuse victimisation/willingness to report & Perception of neighbourhood, socio-economic characteristics & Logistic regression \\
+         \midrule
+          How does neighbourhood deprivation predict domestic abuse?
+& IMD, CSEW & LSOA-level & domestic abuse victimisation/willingness to report (proportion of overall population) & Various measures of deprivation & Spatial Logistic regression \\
+         \midrule
+    How do temporal changes in alcohol consumption and income affect domestic abuse?
+& WMP, Credit card data & LSOA, day/week-level & Number of reported domestic abuse cases & Spending on alcohol and gambling, changes in benefit receipts & Poisson/Negative binomial regression \\
+
+     \bottomrule
+  \end{tabular}
+    \end{threeparttable}%
+  \label{tab:addlabel}%
+\end{table}%
+
+\textcolor{red}{\textit{Core outcomes}} The first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
+An exploration of the exogenous, time-varying factors, including alcohol consumption and financial stress (gambling, universal credit) affecting the reported number of domestic abuse cases in the West Midlands.
 

### 2019-07-03 case_for_support.tex
Anna update

@@
 The first dataset is provided by the West Midlands Police, and includes all recorded crimes and incidents from the period between January, 2010 and October, 2018.
-The West Midlands Police is the third largest police force in England, serving a population of 2.9 million \textit{(ref)}.
+The West Midlands Police is the third largest police force in England, serving a population of 2.9 million \cite{Homeoffice}.
 Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK, whereas domestic abuse incidents refer to cases that do not qualify as a crime.
@@
 
-The second dataset is the Crime Survey for England and Wales (CSEW), which is an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \textit{(ref)}.
-The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular \textit{(ref)}.
+The second dataset is the Crime Survey for England and Wales (CSEW), which is an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}.
+The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.
 Given the serious problem of underreporting uniquely characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
-since when?
 
@@
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
-We will also use the WMP data to explore the extent of police mis-recording of domestic abuse.
+We will also use the CSEW and WMP data to explore the police's response to reported cases of domestic abuse.
 Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
@@
 The CSEW provides a broad range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
-Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/articles/domesticabusefindingsfromthecrimesurveyforenglandandwales/yearendingmarch2018}{descriptive statistics} derived from the CSEW data.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data \cite{ONS}.
 Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
@@
 
- Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
+ Her Majesty's Inspectorate of Constabulary and Fires \& Rescue Services (HMICFRS) oversees police forces in England Wales, and regularly inspects their responses to reported crime, including cases of domestic abuse.
+Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
+These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of domestic abuse cases reported to the police, a majority of which would have qualified as a crime.
+To explore some of the reasons underlying this phenomenon as well as understanding its implications with regards to victims' trust in the CJS, we will limit our sample to those who have reported a specific type of domestic abuse incident (sexual, physical violence, harassment and stalking) in the past 12 months, according to the CSEW.
+First, we will run a multinomial logistic regression model with police force fixed effects, aiming to explain how the police action taken depend on the socio-economic characteristics of the victim.
+\textit{For example, it is possible that police forces are less likely to record a case if the victim has a substance dependency.
+Too speculative?} To complement this analysis and explore potential interactions, we will also investigate this question with a mixed effects random forest with police force clustering.
+Second, we will also investigate how victim's satisfaction with the police, and their perception of their personal security depends on the police action taken, and their socio-economic characteristics, using a logistic and a random forest statistical framework.
+
+% Using the CSEW, we are interested in understanding how for each offence type (sexual, physical with injury, stalking and harassment), the police's response depend on the victim's socio-economic characteristics
+% 
+% From the CSEW, we can estimate what percentage of reported cases that ended in warning, arrest, charge, or no action, a well as the victim's satisfaction with the police handling the case and their perception of their own security as a result of the outcome.
+% 
+%https://www.justiceinspectorates.gov.uk/hmicfrs/our-work/article/crime-data-integrity/reports-rolling-programme-crime-data-integrity/
+
+% Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
 \textit{Why don't we use the aggregate number of \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/datasets/domesticabuseinenglandandwalesappendixtables}{police-recorded domestic abuse cases for each police force} to do this?
@@
         \midrule
-    What is the extent of police mis-recording of domestic abuse? & ONS data & & & & \\
+    How does the police response depend on victim characteristics?
+& CSEW (reported domestic abuse, by type of offence) & Individual (respondent-level) & Police action taken (no action, warning, arrest, charge) & demographic and socio-economic characteristics of the victim & Multinomial logistic regression with  fixed effects/ mixed effects random forest \\
+     \midrule
+    How do victims of domestic abuse who reported perceive the police?
+& CSEW (reported domestic abuse, by type of offence) & Individual (respondent-level)& Satisfaction with police action, perception of security after reporting & police action taken, demographic and socio-economic characteristics of the victim & Multinomial logistic regression with fixed effects/ mixed effects random forest \\
 %    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
@@
 The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation.
-
-\newpage
+An exploration of how police response to reported cases, victim satisfaction with the police and perception of security after reporting domestic abuse depend on victim characteristics.
 
@@
 \textcolor{red}{\textit{Detailed plan}} Drawing on the relative strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
-Previous studies investigating this question mostly relied on police data and focused on \href{https://link.springer.com/article/10.1007/s41887-017-0011-1}{identifying high-risk offenders}.
+Previous studies investigating this question mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
 We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
@@
 Given the problem of underreporting, this will give us a lower bound for the estimate of the proportion of children with behavioural problems who live in abusive households.
-\textit{Am I missing something here?}
+\textit{?}
 
@@
     \midrule
-    How does past childhood abuse affect socio-economic outcomes in adulthood?
-& CSEW & Individual (respondent-level) & Educational attainment, employment status and health-related outcomes, including domestic abuse victimisation & Degree and type of childhood abuse suffered & Propensity score matching \\
+    How does witnessing domestic abuse as a child affect socio-economic outcomes in adulthood?
+& CSEW & Individual (respondent-level) & Educational attainment, employment status and health-related outcomes, including domestic abuse victimisation & Witnessing domestic abuse & Propensity score matching \\
                 \midrule
@@
                 \midrule
-     How does experiences of domestic abuse at home and experiences of child abuse affect behavioural outcomes in childhood?
-& CSEW & Individual (respondent-level) & Bullying, involvement with gangs, school truancy, carrying knives, drugs and alcohol usage, learning difficulties, health & Degree and type of domestic abuse witnessed/child abuse suffered & Propensity score matching \\
+     How does living a household with domestic abuse affect behavioural outcomes in childhood?
+& CSEW & Individual (respondent-level) & Bullying, involvement with gangs, school truancy, carrying knives, drugs and alcohol usage, learning difficulties, health & Degree and type of domestic abuse in household & Propensity score matching \\
                 \midrule
-          What proportion of young offenders come from abusive households? & WMP & Young offenders &  &  &  \\
+          Are young offenders from abusive households more violent?
+& WMP & Young offenders (individual) & Type of offence (property-related, public order offence, violent) & Household LSOA socio-economic characteristics, abusive household or not & Multinomial logistic regression \\
      \bottomrule

### 2019-07-03 case_for_support.tex
Anna update

@@
 \usepackage{hyperref}
+\usepackage{placeins}
 \usepackage{booktabs}
@@
 \begin{table}[!htbp]
-\caption{Understanding domestic abuse: survivor characteristics and police mis-recording, regressions}
+\caption{Understanding domestic abuse: survivor characteristics and police mis-recording, analysis plan}
   \begin{threeparttable}[t]
@@
 \end{table}%
-
+\FloatBarrier
 %Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police.
@@
 
+\newpage
+
 \subsection*{2. Predicting serious harm and understanding the decision to report}
@@
 We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
-Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury) \textit{causality issue?}.
+Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury).
 We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
@@
 \begin{table}[!htbp]
-\caption{Predicting serious harm and understanding the decision to report, regressions}
+\caption{Predicting serious harm and understanding the decision to report, analysis plan}
   \begin{threeparttable}[t]
@@
 %Aim:
-
+\FloatBarrier
 %The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,
@@
 
-\textcolor{red}{\textit{Detailed plan}} First, we will explore the causal effect of past experiences of domestic and child abuse on present socio-economic outcomes.
-First, using the CSEW, we will explore how experiencing abuse in childhood affects educational, employment and health outcomes in adulthood.
-The 2016 CSEW included a module asking respondents about whether they experienced abuse as a child or witnessed domestic abuse.
-\href{https://www.ons.gov.uk/releases/abuseduringchildhoodfindingsfromtheyearendingmarch2016crimesurveyforenglandandwales}{Descriptive statistics} of this dataset revealed that those who reported to have experienced abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household.
-However, due to the possibility of various confounders (e.g., those growing up in economically deprived areas are more likely to experience abuse, but economic deprivation also affects educational outcomes), these statistics do not tell us the causal effect of childhood abuse on socio-economic outcomes in adulthood.
-To overcome this difficulty in establishing causal relationships, we will use propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of childhood abuse on educational, employment, and mental and physical health outcomes, and the probability of experiencing domestic abuse in adulthood.
-In a similar vein, using propensity score matching, we will explore how past experiences of domestic abuse affect current health outcomes, by comparing people who have experienced domestic abuse in the past, but not in the last 12 months, with people who have never experienced domestic abuse, but otherwise have similar socio-economic characteristics.
+\textcolor{red}{\textit{Detailed plan}} First, we will explore the causal effect of past experiences of domestic abuse on present socio-economic outcomes.
+First, using the CSEW, we will explore how witnessing abuse at home in childhood affects educational, employment and health outcomes in adulthood.
+The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
+Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
+However, due to the possibility of various confounders (e.g., those growing up in economically deprived areas are more likely to witnessing abuse, but economic deprivation also affects educational outcomes), these descriptive statistics do not reveal the causal effect of witnessing abuse as a child on socio-economic outcomes in adulthood.
+To overcome this difficulty in quantifying this causal relationship, we will use propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse on educational, employment, and mental and physical health outcomes, and the probability of experiencing domestic abuse in adulthood.
+In a similar vein, using propensity score matching and the CSEW, we will explore how past experiences of domestic abuse affect current health outcomes, by comparing people who have experienced domestic abuse in the past, but not in the last 12 months, with people who have never experienced domestic abuse, but otherwise have similar socio-economic characteristics.
 
-Second, using both the CSEW and WMP, we will explore how children's behavioural problems are affected by witnessing or experiencing domestic abuse at home.
-Using data from the 10-15 year old questionnaire of the CSEW, which can be linked to the adult questionnaire, we can examine the effect of domestic and child abuse on children living in such households.
-The children's questionnaire records information on whether the child had been physically or verbally abused by someone (and if that person lives in the household), as well as their experiences with bullying, carrying knives, and information on gang membership, school truancy, learning difficulties and health, including drug use and drinking behaviour.
-This allows us to explore the causal effect of past and present domestic abuse in the household and child abuse on these outcomes through propensity score matching.
-\textit{Estimating the effect of indirect exposure to domestic abuse through a previously abused parent?}
+Second, using both the CSEW and WMP, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
+Using data from the 10-15 year old questionnaire of the CSEW (which can be linked to the adult questionnaire), we can examine the effect of domestic abuse on children living in such households.
+The children's questionnaire records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
+Using this dataset and a propensity score matching approach, we will explore the causal effect of living in an abusive household on childhood behavioural outcomes.
 
-We will complement this analysis using the WMP, by estimating how living in a household with domestic and child abuse affects the likelihood of engaging in various types of criminal behaviours (property-related vs violent crime).
-We will do so by identifying what percentage of young offenders are victims of child abuse, and have a home address that is associated with domestic abuse incidents.
-Given the problem of underreporting, this will give us a lower bound for the estimate of the proportion of children with behavioural problems who live in abusive households.
-\textit{?}
+We will complement this analysis using data on young offenders from the WMP.
+We will identify if young offenders' home addresses can be linked with a domestic abuse incident which will allow us to explore whether the type of domestic abuse in the household (if any) predict the type of crime they will engage in (property-related, public order offence, violent), controlling for the socio-economic characteristics of the neighbourhood (from the Indices of Multiple Deprivation; IMD).
 
 \begin{table}[!htbp]
-\caption{The long-lasting effects of domestic abuse, regressions}
+\caption{The long-lasting effects of domestic abuse, analysis plan}
   \begin{threeparttable}[t]
@@
           Are young offenders from abusive households more violent?
-& WMP & Young offenders (individual) & Type of offence (property-related, public order offence, violent) & Household LSOA socio-economic characteristics, abusive household or not & Multinomial logistic regression \\
+& WMP, IMD & Young offenders (individual) & Type of offence (property-related, public order offence, violent) & Household LSOA socio-economic characteristics, abusive household or not & Multinomial logistic regression \\
      \bottomrule
@@
  The first UK-based quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
-
+\FloatBarrier
 \subsection*{Environmental factors}
@@
 Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, member of Neighbourhood Watch) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
-In investigating this question further, we will explore how deprivation in a neighbourhood (LSOA level, measured by the \href{https://data.gov.uk/dataset/8f601edb-6974-417e-9c9d-85832dd2bbf2/english-indices-of-deprivation-2015-lsoa-level}{Multiple Indices of Deprivation}) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
+In investigating this question further, we will explore how deprivation in a neighbourhood (LSOA level, measured by the Multiple Indices of Deprivation; \citeNP{IMD}) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
 Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
@@
 \begin{table}[!htbp]
-\caption{Environmental factors affecting domestic abuse, regressions}
+\caption{Environmental factors affecting domestic abuse, analysis plan}
   \begin{threeparttable}[t]

### 2019-07-04 case_for_support.tex
Anna update

@@
 \begin{document}
-\title{ESRC SDAI Application}
+\title{ESRC SDAI Application - Understanding domestic abuse using Big Data}
 \date{}
@@
 
-\section{Intro}
+\section{Introduction}
 
@@
 While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men in England and Wales reported to have experienced some form of domestic abuse since the age of 16 \cite{ONS}.
-The current legal definition in the UK \cite{govuk} aims to capture the multifaceted nature of domestic abuse, by recognising that domestic abuse encompasses a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour.
+The current legal definition in the UK aims to capture the multifaceted nature of domestic abuse, by recognising that domestic abuse encompasses a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour \cite{govuk}.
 
-Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, and a significantly higher likelihood of reporting symptoms of anxiety and depression, compared to the general population \cite{ferrari}.
+Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, and are significantly more likely to report symptoms of anxiety and depression compared to the general population \cite{ferrari}.
 The long lasting impacts of domestic abuse are not limited to the direct target of abuse.
-Witnessing domestic abuse at home can have severe developmental impacts on children, including an increased risk of experiencing mental and physical health problems and encountering difficulties in interpersonal relationships in later life, worse educational attainment, and increased likelihood of engaging in criminal behaviours \cite{callaghan}.
+Witnessing domestic abuse at home can have severe developmental impacts on children, including an increased risk of mental and physical health problems, difficulties in interpersonal relationships in later life, worse educational attainment, and a higher likelihood of engaging in criminal behaviours \cite{callaghan}.
 
 As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature.
-Estimates show that on average, survivors live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse before getting effective help \cite{SafeLives2015}.
-The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey including a self-completion module on domestic abuse.
-According to the CSEW, of those respondents who experienced domestic abuse between April 2017 and March 2018, only 17\% reported it to the police \cite{ONS}.
-This extremely high level of underreporting is another characteristic that is specific to domestic abuse.
+Estimates show that before getting effective help, on average, survivors live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse \cite{SafeLives2015}.
+The most reliable statistics on domestic abuse in the UK is the Crime Survey for England and Wales (CSEW; \citeNP{ONS}), a victimisation survey, which includes a self-completion module on domestic abuse.
+According to the CSEW, of those respondents who experienced any form of domestic abuse between April 2017 and March 2018, only 17\% reported it to the police \cite{ONS}.
+This extremely high level of underreporting is another characteristic that is specific to domestic abuse compared to other types of crimes.
 
@@
 
+This research programme consists of four research projects aiming to deliver useful, policy-relevant insights about domestic abuse.
+First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, the reasons behind police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
+Second, we will investigate the factors predicting suffering serious injury and the decision to report.
+Third, we will examine the long-lasting effects of being a victim of domestic abuse or witnessing domestic abuse at home as a child.
+Finally, we explore the association between exogenous, time-varying factors, such as changes in alcohol consumption and financial resources, and the prevalence of domestic abuse.
+
 %Recognising the severity of this widespread societal problem led the UK government to develop a strategic plan to tackle domestic abuse with a funding of £100m for the period between 2016 and 2020.
@@
 
-\newpage
+%\newpage
 
-\section{Data}
+\section{Data sources}
 
-The first dataset is provided by the West Midlands Police, and includes all recorded crimes and incidents from the period between January, 2010 and October, 2018.
-The West Midlands Police is the third largest police force in England, serving a population of 2.9 million \cite{Homeoffice}.
+The research projects detailed below draw on various data sources.
+All of the projects rely on the CSEW, an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}.
+The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.
+Given the serious problem of underreporting, one of the unique characteristic of domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+
+Some of the projects also benefit from a crime dataset provided by the West Midlands Police (WMP), which includes all crimes and incidents recorded by the police force in the period between January, 2010 and October, 2018.
+The WMP is the third largest police force in England, serving a population of 2.9 million \cite{Homeoffice}.
 Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK, whereas domestic abuse incidents refer to cases that do not qualify as a crime.
 About 31\% of all crimes and incidents have a domestic abuse marker.
-For each record in this dataset, we have information about the exact location and time of the incident or crime, the gender, age and ethnicity of the offender and victim, and the severity of the injury sustained by the victim, if any.
+For each record in this dataset, we have rich information about the circumstances of the case, including exact location and time of the incident or crime, the gender, age and ethnicity of the offender and victim, \textbf{their address}, and the severity of the injury sustained by the victim, if any.
 The first and last occurrence of the offence, as well as the exact time of reporting is also recorded.
 Each person in this dataset has a unique person identifier, allowing us to follow people over time.
-\textit{Sentence about access to this dataset.}
+\textbf{\emph{\textit{Sentence about access to this dataset.}}}
 
-The second dataset is the Crime Survey for England and Wales (CSEW), which is an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}.
-The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.
-Given the serious problem of underreporting uniquely characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+These two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
+A unique benefit of the CSEW is that it provides information on a control group (those who have not suffered domestic abuse),  allowing us to investigate the causal effect of domestic abuse.
+In addition, the CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor).
+However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators, and has limited longitudinal information (respondents are asked about whether they suffered domestic abuse in the past 12 months, but the dates of those incidents are not specified).
+In contrast, the WMP crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships, and identify the predictors of escalation.
+Information on the exact timing of the abuse and the time of reporting will help us identify high-risk times of the year and understand the factors influencing the decision to report.
+Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender.
+In all the analysis plans outlined below, we will not link the individuals in these datasets.
 
-The two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
-The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor).
-However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators and has limited longitudinal information.
-In contrast, the crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships and identify the predictors of escalation.
-Information on the exact timing of the abuse and the time of reporting will help us identify high-risk times of the year and understand the factors influencing the decision to report.
-Information on alcohol involvement is more likely to be accurate in the crime dataset than in the self-completion survey.
-Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender and victim.
-In all the analysis plans outlined below, we will not link the individuals in these datasets.
+Our last proposed project will also rely on a transaction per row dataset containing credit card and current account spending of 20 million customers across the UK.
+We have access to this data as part of a data sharing agreement with a very large UK bank.
+As we know which neighbourhood (LSOA) the card owners live in, this data will allow us to construct a neighbourhood-level measure of spending on alcohol, gambling, and benefit payments throughout time.
+We will not use individual-level data or match people in this dataset with people in the WMP dataset.
+
+In addition, in analyses that rely on neighbourhood-level characteristics, we will use the Incides of Multiple Deprivation (IMD; \citeNP{IMD}).
+The IMD ranks all 32,844 LSOAs in the UK based on their relative deprivation on various domains, including income, employment, education, health, crime, housing and living environment, providing us with a complex descriptor of the socio-economic characteristics of each neighbourhood in the country.
 
@@
 
-Our research programme involves four research projects exploring different aspects of domestic abuse.
+This research programme involves four research projects exploring different aspects of domestic abuse.
 Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP, we aim to complement, extend and deepen our understanding of domestic abuse.
-In outlining each of these research projects, for the sake of clarity, we will specify a set of core regression analyses we plan to conduct.
+In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct for the sake of clarity (including dataset, unit of analysis, outcome and explanatory variables, and statistical method).
 We will preregister all of our analysis plans using the Open Science Framework (OSF) ahead of beginning research.
-We will also aim to complement all analyses with robustness checks and further exploratory regressions as the data allows (see, \textit{Trendl Football}, for an example of this approach).
+We will aim to complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach).
 
@@
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
-We will also use the CSEW and WMP data to explore the police's response to reported cases of domestic abuse.
+We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
 Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
@@
 
+ %When a crime is not recorded the force may have recorded details of the report on a different record, such as an incident log.
+It is these records that HMICFRS can audit to establish the extent to which reported crime is being recorded.
+In some cases an officer will have responded to the report.
+
  Her Majesty's Inspectorate of Constabulary and Fires \& Rescue Services (HMICFRS) oversees police forces in England Wales, and regularly inspects their responses to reported crime, including cases of domestic abuse.
 Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of domestic abuse cases reported to the police, a majority of which would have qualified as a crime.
-To explore some of the reasons underlying this phenomenon as well as understanding its implications with regards to victims' trust in the CJS, we will limit our sample to those who have reported a specific type of domestic abuse incident (sexual, physical violence, harassment and stalking) in the past 12 months, according to the CSEW.
-First, we will run a multinomial logistic regression model with police force fixed effects, aiming to explain how the police action taken depend on the socio-economic characteristics of the victim.
+These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of domestic abuse-related  cases reported to the police, a majority of which would have qualified as a crime.
+
+  To explore , as well as understanding its implications with regards to victims' trust in the CJS, we will limit our sample to those who have reported a specific type of domestic abuse incident (sexual, physical violence, harassment and stalking) in the past 12 months, according to the CSEW.
+First, we will run a multinomial logistic regression model with police force fixed effects, aiming to explain how the police action taken (no action, warning, arrest, charge) depend on the socio-economic characteristics of the victim.
 \textit{For example, it is possible that police forces are less likely to record a case if the victim has a substance dependency.
@@
      \midrule
-    How do victims of domestic abuse who reported perceive the police?
+    What predicts victims' trust in the police?
 & CSEW (reported domestic abuse, by type of offence) & Individual (respondent-level)& Satisfaction with police action, perception of security after reporting & police action taken, demographic and socio-economic characteristics of the victim & Multinomial logistic regression with fixed effects/ mixed effects random forest \\

### 2019-07-05 case_for_support.tex
Anna update

@@
 Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of domestic abuse-related  cases reported to the police, a majority of which would have qualified as a crime.
+These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of reported crimes that were domestic abuse-related.
 
-  To explore , as well as understanding its implications with regards to victims' trust in the CJS, we will limit our sample to those who have reported a specific type of domestic abuse incident (sexual, physical violence, harassment and stalking) in the past 12 months, according to the CSEW.
-First, we will run a multinomial logistic regression model with police force fixed effects, aiming to explain how the police action taken (no action, warning, arrest, charge) depend on the socio-economic characteristics of the victim.
-\textit{For example, it is possible that police forces are less likely to record a case if the victim has a substance dependency.
-Too speculative?} To complement this analysis and explore potential interactions, we will also investigate this question with a mixed effects random forest with police force clustering.
-Second, we will also investigate how victim's satisfaction with the police, and their perception of their personal security depends on the police action taken, and their socio-economic characteristics, using a logistic and a random forest statistical framework.
+ We will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties might be less likely to be recorded as a crime by the police).
+Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
+We will run a multinomial regression with police force fixed effects for each broad crime type (sexual, physical violence, harassment and stalking), predicting whether the police's response (no action, warning, arrest, charge) depends on the socio-economic characteristics of the victim.
+Using a fixed effects approach will tell us the relative importance of police force and victim characteristics in crime mis-recording.
+To complement this analysis and explore potential interactions between our explanatory variables, we will also investigate this question with a mixed effects random forest with police force clustering.
+Second, using the same statistical model for each type of crime, we will also investigate how victim's satisfaction with the police, and their perception of their personal security after reporting a crime depends on the police action taken, and their socio-economic characteristics.
 
@@
 The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation.
-An exploration of how police response to reported cases, victim satisfaction with the police and perception of security after reporting domestic abuse depend on victim characteristics.
+A deeper understanding of the characteristics of police mis-recording and its effect on victim's trust in the CJS.
 

### 2019-07-05 case_for_support.tex
Anna update

@@
 Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data \cite{ONS}.
-Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics in statistical model, using a logistic regression approach.
-Investigating the explanatory power of these characteristics within one statistical model will provide us with a deeper understanding of the importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
+Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics, using a logistic regression approach.
+Investigating the explanatory power of these characteristics within one statistical model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
 We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
@@
  However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
-To uncover the structure of these interactions without having to a priori specify them, as is required in a logistic regression model, we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
+To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
 Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
@@
 We will run a multinomial regression with police force fixed effects for each broad crime type (sexual, physical violence, harassment and stalking), predicting whether the police's response (no action, warning, arrest, charge) depends on the socio-economic characteristics of the victim.
-Using a fixed effects approach will tell us the relative importance of police force and victim characteristics in crime mis-recording.
+Using a fixed effects approach will help us tell the relative importance of police force and victim characteristics in crime mis-recording.
 To complement this analysis and explore potential interactions between our explanatory variables, we will also investigate this question with a mixed effects random forest with police force clustering.
@@
 
-\textcolor{red}{\textit{Detailed plan}} Drawing on the relative strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
+\textcolor{red}{\textit{Detailed plan}} Drawing on the different strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
 Previous studies investigating this question mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
-We will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injuries using the CSEW.
-Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury).
+Using the CSEW, we will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injury.
+Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury).
 We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
-Given the cross-sectional nature of the CSEW data, this analysis will be exploratory rather than causal.
+While we cannot investigate causal relationships due to the cross-sectional nature of the CSEW, this analysis will nevertheless provide us with important insights about the characteristics of groups most vulnerable to domestic abuse.
 
-Using the WMP data, we will also explore the risk factors associated with the perpetrator, using each perpetrator-victim pair as a unit of analysis.
+Using the WMP data, we will also explore the risk factors associated with the perpetrator.
 The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
-Our detailed crime dataset will allow to investigate the extent to which the perpetrator's previous recorded self-harm and suicide attempts, previous violent and drug offences, breaches of court orders and separation from the victim will predict causing serious harm.
+Our detailed crime dataset will allow to investigate the extent to which the perpetrator's previous recorded self-harm and suicide attempts, previous violent and drug offences, breaches of court orders and separation from the victim will predict causing serious harm, using each perpetrator-victim pair as a unit of analysis.
 From the detailed description of the incident, we will know if the perpetrator and the victim live together.
@@
 We will complement this analysis using data on young offenders from the WMP.
-We will identify if young offenders' home addresses can be linked with a domestic abuse incident which will allow us to explore whether the type of domestic abuse in the household (if any) predict the type of crime they will engage in (property-related, public order offence, violent), controlling for the socio-economic characteristics of the neighbourhood (from the Indices of Multiple Deprivation; IMD).
+We will identify if young offenders' home addresses can be linked with a domestic abuse incident in the recent past, allowing us to explore whether living in a household with a domestic abuse problem predict the type of crime they will engage in (property-related, public order offence, violent), controlling for the socio-economic characteristics of the neighbourhood (using the IMD).
+We are especially interested if living in an abusive environment is predictive of knife crime-related offences.
 
@@
 \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In this research project, we will be using the CSEW and WMP datasets, as well as external sources of data to investigate some of the environmental predictors of domestic abuse.
-We will first explore how neighbourhood-level characteristics affect domestic abuse victimisation and the willingness to report.
+In this research project, we will investigate some of the environmental predictors of domestic abuse.
+While individual-level characteristics are likely to be the main predictors of domestic abuse victimisation, the environment around the victim can play a key role in either exacerbating or alleviating domestic abuse.
 Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
-
-We will also explore how time-varying, exogenous factors affect domestic abuse.
-We will first explore the effect of local events that increase alcohol-consumption, since our previous study have found a significant relationship between alcohol-related domestic abuse and football.
-Second, we will explore the relationship between financial stress and the prevalence of domestic abuse.
-First, we will explore the association between gambling accessibility in the local area, and reported numbers of domestic abuse.
-Second, we will examine how the roll-out of the Universal Credit system affected levels of domestic abuse across the West Midlands.
-Apart from delivering important policy-relevant insights, these investigations will also aim to inform the local police about the optimal allocation of police resources.
+We will also explore how time-varying, exogenous factors related to alcohol consumption and financial stability affect domestic abuse.
 
@@
 
-\textcolor{red}{\textit{Detailed plan}} Using the CSEW, we will first explore the association between the environmental characteristics of the neighbourhood, the prevalence of domestic abuse and willingness to report.
-Previous literature has suggested various pathways, including reduced collective efficacy of neighbourhood, and normalisation and acceptance of violence through social norms to explain the link between neighbourhood characteristics and domestic abuse, but the question has not been explored in a UK context yet.
-Using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, member of Neighbourhood Watch) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
-In investigating this question further, we will explore how deprivation in a neighbourhood (LSOA level, measured by the Multiple Indices of Deprivation; \citeNP{IMD}) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
+\textcolor{red}{\textit{Detailed plan}} Using the CSEW, we will first explore whether neighbourhood characteristics are predictive of the prevalence of domestic abuse and the willingness to report.
+Previous literature has suggested various pathways, including reduced collective efficacy of neighbourhood, and normalisation and acceptance of violence through social norms, to explain the link between neighbourhood characteristics and domestic abuse, but the question has not been explored in a UK context yet.
+Fisrt, using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, member of Neighbourhood Watch) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
+Second, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
 Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
@@
 We are also interested in exploring how time-varying external factors, including alcohol consumption, and financial stress (measured by gambling expenditure and benefit dependency) affect the propensity to engage in abusive behaviours.
-In investigating this question, we will benefit from a dataset containing credit card and current account spending of x customers across the UK, to which we will have access as part of a data sharing agreement with a very large UK bank.
-This dataset will allow us to quantify spending on alcohol over time by LSOA.
-By using the WMP and credit card data, we will identify time-specific changes in alcohol consumption in parts of the West Midlands by identifying externals events that may affect it (e.g., local festivals, weather, bank holidays, sport tournaments), and investigate their effect on reported alcohol-related domestic abuse (from the WMP).
+In investigating this question, we will use the transaction dataset described earlier, which allows us to estimate a spending profile for each LSOA over time.
+This will allow us to identify time-specific changes in alcohol consumption, gambling expenses and benefit receipts in parts of the West Midlands, and investigate their effect on the number of reported domestic abuse cases in the area (from the WMP), using a spatial Poisson regression approach.
+
+To explore the effect of alcohol consumption on domestic abuse, we will identify externals events that may affect alcohol consumption (e.g., local festivals, weather, bank holidays, sport tournaments) measured by spending on alcohol in an LSOA in a given time period, and investigate whether it affects the number of reported domestic abuse incidents in that area.
 Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
 
+To explore the effect of financial shocks on domestic abuse, we will be using the same estimation approach, but we will focusing on gambling and benefit payments.
+Gambling is increasingly recognised as a serious health concern across the UK, and can have a profoundly adverse impact on family finances.
+We will use our transaction data and WMP dataset to assess the link between changes in spending on gambling in a given LSOA and the prevalence of domestic abuse in that area.
 The recent reforms of the UK benefit system, in the form of the introduction of the Universal Credit (UC) had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
@@
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
-To further explore the effect of financial shocks on the propensity for violence, we focus on gambling.
-Gambling is increasingly recognised as a serious health concern across the UK, and can have an adverse impact on family finances.
-We will use our credit card and WMP datasets to assess the link between changes in spending on gambling and domestic abuse.
-
-%\href{https://secure.gamblingcommission.gov.uk/PublicRegister}{List of licensed gambling businesses} We can also contact the local authorities, as they should have an up-to-date list
 
@@
     How do temporal changes in alcohol consumption and income affect domestic abuse?
-& WMP, Credit card data & LSOA, day/week-level & Number of reported domestic abuse cases & Spending on alcohol and gambling, changes in benefit receipts & Poisson/Negative binomial regression \\
+& WMP, Credit card data & LSOA, day/week-level & Number of reported domestic abuse cases & Spending on alcohol and gambling, changes in benefit receipts & Poisson/Negative binomial regression with spatial effects \\
 

### 2019-07-08 case_for_support.tex
Anna update

@@
 These two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
-A unique benefit of the CSEW is that it provides information on a control group (those who have not suffered domestic abuse),  allowing us to investigate the causal effect of domestic abuse.
+A unique benefit of the CSEW is that it allows us to investigate the causal effect of domestic abuse by providing information on a control group (those who have not suffered domestic abuse).
 In addition, the CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor).
@@
 
-\subsection*{1. Understanding domestic abuse: survivor characteristics and police mis-recording}
+\subsection*{1. Exploring the characteristics of survivors, and understanding the police response to reported cases}
 
@@
 \begin{table}[!htbp]
-\caption{Understanding domestic abuse: survivor characteristics and police mis-recording, analysis plan}
+\caption{Exploring the characteristics of survivors, and understanding the police response to reported cases, analysis plan}
   \begin{threeparttable}[t]

### 2019-07-08 case_for_support.tex
Anna update

@@
 We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
-Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
+Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
 
@@
 Using the CSEW and logistic regression approach, we will investigate how the decision to report (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
-We are especially interested in exploring how trust in the Criminal Justice System (CJS), social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency affect the decision to report.
+We are especially interested in exploring how trust in the CJS, social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency affect the decision to report.
 Using the WMP data, we will explore time-varying factors affecting the decision to leave the abuser.
@@
 We will identify if young offenders' home addresses can be linked with a domestic abuse incident in the recent past, allowing us to explore whether living in a household with a domestic abuse problem predict the type of crime they will engage in (property-related, public order offence, violent), controlling for the socio-economic characteristics of the neighbourhood (using the IMD).
-We are especially interested if living in an abusive environment is predictive of knife crime-related offences.
+We are especially interested in exploring whether living in an abusive environment is predictive of knife crime-related offences.
 
@@
 \FloatBarrier
-\subsection*{Environmental factors}
+\subsection*{4. Environmental factors influencing the prevalence of domestic abuse}
 
@@
 In this research project, we will investigate some of the environmental predictors of domestic abuse.
-While individual-level characteristics are likely to be the main predictors of domestic abuse victimisation, the environment around the victim can play a key role in either exacerbating or alleviating domestic abuse.
-Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
+While individual-level characteristics are likely to be the most important predictors of domestic abuse victimisation, the environment around the victim can play a key role in either exacerbating, or alleviating domestic abuse.
+Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and the willingness to report is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
 We will also explore how time-varying, exogenous factors related to alcohol consumption and financial stability affect domestic abuse.
@@
 Previous literature has suggested various pathways, including reduced collective efficacy of neighbourhood, and normalisation and acceptance of violence through social norms, to explain the link between neighbourhood characteristics and domestic abuse, but the question has not been explored in a UK context yet.
-Fisrt, using a logistic regression, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, and the general condition of houses, member of Neighbourhood Watch) as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
-Second, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report, using a spatial regression framework.
+First, using a logistic regression approach, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses, Neighbourhood Watch), as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
+Second, using a spatial regression framework, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report.
 Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
@@
 In investigating this question, we will use the transaction dataset described earlier, which allows us to estimate a spending profile for each LSOA over time.
-This will allow us to identify time-specific changes in alcohol consumption, gambling expenses and benefit receipts in parts of the West Midlands, and investigate their effect on the number of reported domestic abuse cases in the area (from the WMP), using a spatial Poisson regression approach.
+This way we can identify time-specific changes in alcohol consumption, gambling expenses and benefit receipts in parts of the West Midlands, and investigate their effect on the number of reported domestic abuse cases in the area (from the WMP), using a spatial Poisson regression approach.
 
@@
 Gambling is increasingly recognised as a serious health concern across the UK, and can have a profoundly adverse impact on family finances.
-We will use our transaction data and WMP dataset to assess the link between changes in spending on gambling in a given LSOA and the prevalence of domestic abuse in that area.
+We will use our transaction data and WMP dataset to assess the link between changes in spending on gambling in a given LSOA, and the prevalence of domestic abuse in that area.
 The recent reforms of the UK benefit system, in the form of the introduction of the Universal Credit (UC) had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
@@
 \begin{table}[!htbp]
-\caption{Environmental factors affecting domestic abuse, analysis plan}
+\caption{Environmental factors influencing the prevalence of domestic abuse, analysis plan}
   \begin{threeparttable}[t]

### 2019-07-09 case_for_support.tex
Tim changes comments intro

@@
 
-This research programme consists of four research projects aiming to deliver useful, policy-relevant insights about domestic abuse.
-First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, the reasons behind police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
+This research programme consists of four research projects that will deliver useable, policy-relevant insights about domestic abuse.
+First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
 Second, we will investigate the factors predicting suffering serious injury and the decision to report.
@@
 The WMP is the third largest police force in England, serving a population of 2.9 million \cite{Homeoffice}.
-Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK, whereas domestic abuse incidents refer to cases that do not qualify as a crime.
+Crimes that have a domestic abuse marker indicate cases of domestic abuse that meet the criteria for notifiable offences in the UK (e.g.
+assault, or GBH), whereas domestic abuse incidents refer to cases that do not qualify as a crime.
 About 31\% of all crimes and incidents have a domestic abuse marker.
@@
 Each person in this dataset has a unique person identifier, allowing us to follow people over time.
-\textbf{\emph{\textit{Sentence about access to this dataset.}}}
+\textbf{\emph{\textit{Sentence about access to this dataset.}}} \TM{Access to this dataset is highly sensitive and strictly controlled.
+All researchers on this project have already been vetted by WMP and have been granted access to the required data fields.
+The PI, as data controller for the project is vetted to level 3, and the CoI's to level 2.}
 
@@
 This research programme involves four research projects exploring different aspects of domestic abuse.
-Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP, we aim to complement, extend and deepen our understanding of domestic abuse.
-In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct for the sake of clarity (including dataset, unit of analysis, outcome and explanatory variables, and statistical method).
-We will preregister all of our analysis plans using the Open Science Framework (OSF) ahead of beginning research.
-We will aim to complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach).
+Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP, this research complements, extends and deepens our understanding of domestic abuse.
+In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct.
+We will preregister all of our analysis plans using the Open Science Framework (OSF) \TM{I favour not specifying OSF, as it is a steaming pile of excrement and there are better pre-registration alternatives out there.}.
+We will complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach).
 
@@
  However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
-To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
+To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm \TM{Do we know enough about random forest classification to be confident about it's appropriateness?
+Could an expert reviewer find a reason to complain about it or criticize it's use?
+I ask because I don't know it well at all.}, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
 Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.

### 2019-07-09 justification_of_resources.tex
Justifcation of resources for edit

Justification of Resources

Staff, Directly Incurred Posts

PDRA Mullett. We request 100\% support for PDRA Mullett. A postdoctoral appointment is
essential here, as the level of technical skill required to run and analyse eye movement data is
high. As outlined in Staff Duties, Mullett will design the studies with the PI and lead on the
writing of the majority. Mullett will program the eye movement system and implement the
statistical analysis designed with the PI using the R and Matlab programming languages.
Mullett will also take a secondary role in the impact programme, and lead on the supermarket
collaboration.

PDRA at Caltech. We seek 100\% support for a 1-year PDRA at Caltech. The experimental
games eye tracking from Series 1, 3, 5, and 6 will be conducted at Caltech, together with a
subset of cross-lab replications.

RA. We request 25\% support for an RA. BSc or MSc level training in Psychology or
Behavioural Science will be sufficient. As outlined in Staff Duties, testing of participants one-
by-one, and testing 100 people is about 3 weeks of full time work. RA support will free
PDRA time for the more skilled writing and analysis.

Staff, Directly Allocated Posts

PI Stewart. We request 30\% support for Stewart. 15\%, half of this support, will be spent on
the laboratory programme, designing experiments and analysing data with the PDRA.
Stewart has developed a new statistical analysis for eye movement data (see two papers
forthcoming in Journal of Behavioural Decision Making) and this work will continue here.
The other 15\% is required for the ambitious impact work, which requires professorial level
and extensive liaison with the three current industry partners to negotiate access to data and
field trials, to set up access to three new partners, and to disseminate results back into
industry.

CI Chris Starmer. We will seek 10\% support for significant input from Experimental
Economist Prof. Starmer. Because of the interdisciplinary nature of the research, this
contribution is important for maximising the academic impact of the work beyond
Psychology.

Other Directly Incurred Costs

Computer resources. The computations required to estimate drift diffusion models and assess
model flexibility (e.g., with parameter space partitioning, Mullett & Stewart, 2015; Pitt,
Woojae, Navarro, & Myung, 2006) require serial search of model parameter spaces.
Compared to typical regressions which take fractions of a second, these methods take of the
order of days or weeks on, for example, a typical Intel 8-core i7-4770 CPU. We request
£2,000 for this dedicated computer machine.

Travel and Subsistence

We seek the costs of day visits to impact partners, all London based. We anticipate 6 visits per year x 2 people x 3 years. We will attend the SJDM conferences in 2016 and 2017. 2
people x 2 years (Vancouver and New Orleans) and the SPUDM conference (European city)
in 2017. These conferences are the most significant in the domain, giving coverage of
America and Europe. We seek the cost of a postdoc exchange with Prof. Colin Camerer at
Caltech. Caltech is the home of Camerer and Rangel labs, leaders in eye tracking economics.

### 2019-07-09 pathways_to_impact.tex
Pathways to impacy

\section{Old Accumulating to Choose Pathways to Impact}

Pathways to Impact
We will target those in industry and public policy with interest in economic decision making.
While the focus of this programme is on informing micro-level theory of economic choice,
we will develop the implications for regulation and for the competitiveness of UK financial
industry. Our strategy will be to translate the laboratory work detailed in the Case for Support
into the field with a series of randomised control trials, detailed below. To deliver significant
impact it is essential for us to bridge the divide from the laboratory by working on live
problems for the regulator and industry using real consumers making real decisions.
Since their inception in 2012 the Financial Conduct Authority (the UK regulator for all
financial products, like savings accounts, pensions, mortgages, credit cards, and insurance)
have placed significant emphasis on behavioural regulation. This includes “...getting a better
understanding of why consumers act in the way they do, so we can adapt our regulation to
their [consumers’] common behavioural traits” (Martin Wheatley, outgoing Chief Executive,
FCA). Indeed, the first publication from the FCA made the case for using behavioural
economics in regulation (Erta, Hunt, Iscenko, Brambley, 2013). Recently Stewart has worked
closely with the new Behavioural Economics and Data Science Team at the FCA, led by Dr
Stefan Hunt, on the psychology of structured deposits (Hunt, Stewart, \& Zaliauskas, 2015).
The FCA are at the beginning of a project on the complexity of financial products. The
pathway to impact within the FCA will be via regular meetings between members of the FCA
Behavioural and Data Science Team, and Stewart and Mullett (most recently in August 2015).
Ultimately, as the data will drive public policy change regarding presentation and advertising
of financial products, with the creation of regulations grounded in behavioural science. The
outcome of this engagement will be the design of randomised control trials in collaboration
with the FCA and a customer-facing financial services provider using real consumers making
real decisions. Dissemination via the FCA working paper series will have more significant
reach than academic publication alone. Please see the letter of support from the Financial
Conduct Authority.
Warwick has a formal collaboration with the consumer group Which?, and Stewart has
worked closely with Alex Chesterfield, Head of Behavioural Insights, and team members
Sam Himmelweit, Harriet Patterson, and Phillida Cheetham. The formal collaboration covers
data sharing, exploitation, and publication rights, etc., and we have several existing and
completed projects (e.g., on credit card repayment behaviour and expectant mums’ birth
choices). Early insights from this work will feed into Which?’s project on the complexity of
financial products. They key route will be the monthly joint meetings between Warwick and
Which? Please see the letter of support from Which? Again, we would seek to implement
insight from these grants in a practical financial decision domain as part of Which?’s
consumer testing programme, and thus we will identify a practical application of the drift
diffusion model to a consumer choice of value to which and implement a field trial. Likely
candidates are: (a) the development of product information sheets for mortgages, savings
accounts, pensions, etc., within the context of providing behavioural nudges, and (b)
information provision for telecoms choices.
The UK Cards Association is the industry body for all credit card providers in the UK.
Stewart (and Gathergood, Economist, Nottingham) have a significant existing collaboration,
with the sharing of millions of credit card statements between about 10 of the largest card
companies and Warwick and Nottingham Universities. Contacts are Paul McCarron, Head of
Cards and Fraud Control, and Richard Koch, Head of Policy. Stewart contributed evidence to
the 2009 White Paper reviewing of the credit industry. Of key interest is (a) consumers’

decisions around credit card repayments, and their integration of information from monthly
statements and (b) consumers choice of card during switching and how cards are evaluated.
The former fits well with the evaluation work; the latter fits well with the choice work.
Dissemination of research findings will be via presentation to the Current Affairs working
group, with representatives from every UK card provider.
We will also work closely with the Economic and Social Research Institute, an independent
research institute funded mainly by the Irish Government. Our key contact is Dr Peter Lunn,
who has expertise in the application of decision making and consumer psychology research to
policy and regulation.
These routes to impact are time consuming. They would be led by the PI, with significant
involvement from the CI to distribute the load. We anticipate that 15% (i.e., half) of PI time
will be spent pursuing impact. These contacts will also add value for the PDRA and CI as
they can be taken to build research collaborations beyond the grant, independently of the PI.
We have requested funding to develop the field trials over the course of the grant, and in
previous experience the ability to make modest commitment to a larger programme of
randomised control trials enhances engagement.
Beyond these three existing routes to impact, during the course of the grant we will seek to
extend our contacts and influence to (a) one major UK supermarket, (b) one major UK
insurance company, and (c) one major bank.
Table 1. Translational field studies.
Translational Field Study

Anticipated Design

1. Financial Conduct
Authority

A representative sample of 2,000 investors in structured
deposits, payday loans, or other complicated financial
products.

2. Which?

Presenting multi-attribute choice options to 2,000
consumers switching broadband and or expectant mums.

3. UK Cards

A representative sample of 2,000 cardholders making (a)
direct debit setup decisions or (b) monthly repayment
decisions.

Finally, the opportunity to work with real consumers making real decisions with non-trivial
economic consequences (maybe tens of pounds with broadband, hundreds of pounds with
credit cards, and thousands of pounds with structured deposits of mortgages, and hours of
pain with expectant mums) is of significant academic value. The issue of incentivized choice
is critical in Experimental Economics (though less so in Psychology), and this impact work
extends the lab work into high stakes choice.

\section{Old Perfect Cop Pathways to Impact}

1

Pathways to Impact
This research is likely to deliver impact in recruitment of new officers, identifying outcomes
associated with the best management, reductions in the rates of sickness, reductions in
complaints and better responses to complaints, and matching officers to roles. In particular,
matching responses from our Online Lab to the police data adds value to those data. For
example, if, as we suspect, conscientiousness does indeed correlate with rates of sickness
and complaints, this would allow forces to understand sickness and complaints as, at least in
part, a function of individual differences in personality interacting with the local context in
which officers and staff are placed. And if well-being is associated with the quality of
management, this is a first step in developing mechanisms for improving the well-being of
officers and staff. Below we detail the pathways to these potential impacts.
The police support this research and have provided their data and access to officers and
staff without imposing constraints on the academic research programme. We have met with
and discussed the project with all of the officers and staff named here (and see meeting
dates on p. 2 of the Case for Support). At the MPS, this research project reports to the Total
Professionalism Board, which is chaired by our force lead Assistant Commissioner Helen
King. The Board is responsible workforce development and recruitment strategy. We have
already made presentations to the Board (April 2015, March 2016) and received their
backing. By integrating this project with the Board’s remit, we have official and long-term
support for the project. At Nottinghamshire the project reports to Chief Constable Sue Fish.
At States of Jersey the project reports to Chief Officer Mike Bowron.
The findings of this study have relevance to both metropolitan and county forces throughout
England, Wales and Northern Ireland (whom all operate under a common Doctrine and
Professional Standard). At the local level we will give at least six monthly feedback. For each
force, each Chief Constable and Police and Crime Commissioner pairing has independent
authority over their area (or MPS Commissioner / London Mayor pairing), and we will use
these meeting to develop interventions and analysis around the five themes below. At the
national level, the MPS is the largest police force in the UK and is a leader in practice. The
route to national-level impact is the National Police Chiefs’ Council (business area lead is
Chief Constable Giles York; Chief Constable Sue Fish is our NPCC sponsor) and through
the College of Policing who inform the National Approved Professional Practice (Rachel
Tuffin, Director, Knowledge, Research, and Education). At the international level, the high
regard of British policing provides a reference point for international standards. We have
already made links with the Chicago Citizens’ Police Data Project, Harvard Sociology, and
Chicago Police Department, and with New York Police Department via Warwick’s Institute for
Sustainable Cities. National and international level feedback will be via Warwick’s Centre for
Operational Policing Research, co-directed by PI Stewart with CI Hodgson.
Feedback to forces will be structured against the following themes, which have been
highlighted in discussions with senior officers, who will lead the implementation within their
forces. Feedback points are every six months, as agreed with the officers and staff named
below.
Public Desire. The research will deliver a list of psychological indicators of good
performance, reduced complaints and misconduct, and reduced physical and mental ill
health. These measures will inform the recruitment process and the selection of officers and
staff for specialist roles in the MPS. But changing recruitment processes represent a shift
from the implicit objective of police in the image of the public they serve. For example, “We
can’t have a police force representative of a London which has an ethnic minority population
of 55% when only 10% of its officers are from an ethnic minority” (Lammey, 13 January
2014; the 55% is probably a little too high here). Many forces use positive recruitment of
BME officers, and the MPS used residence requirements in 2013/14. How have recent
changes in recruitment changes the psychological attributes selected for? There is certainly
a political imperative for this directive, but little empirical evidence that the public wish this as

2
a determining factor for officer or staff recruitment. To this end, we will complement the
behavioural science evidence base with a survey of the public to measure the properties of
officers they desire (with Chief Constable Sue Fish, Nottinghamshire; Assistant
Commissioner Martin Hewitt, MPS; and the (London) Mayor’s Office for Police And Crime).
We will use a market research company to measure, from a representative sample of the UK
population, their views on the age, sex, race, ethnicity, religious affiliation, psychological
traits. Our objective is to start and develop a public dialogue.
Management. What is the impact of performance development review gradings on both
individual behaviours and those of their subordinates (Deputy Commissioner Craig Mackey
and Chief Superintendent Robert Jones). That is, what outcomes in are associated with
better line managers? We have already found that the highest scoring line managers have
subordinates with a 20% reduction in the incidence of sickness. We have also identified
significant variability across the Met within the sickness and complaints measures, with
some boroughs having half the rates of sickness and complaints of others, and some
boroughs having large changes within the 5-year period of the data. The mechanism for
impact within the MPS is the HR change programmes (Robin Wilkinson, HR Director).
Absenteeism and complaints. Using the data we already have, we see a very strong
association between sickness and complaints. Among officers who have no complaint in the
5-year period, 63% of officers have one or more episode of sickness. But among officers
who have a complaint, 84% have one of more sickness. Further, econometric panel data
analysis shows that there is almost no association between previous complaints and current
sickness or vice versa: Complaints do not appear to cause sickness, and sickness does not
put officers at greater risk of a complaint. The logical conclusion from this work is that there
are strong individual difference predictors of these measures—and we have
conscientiousness and agreeableness from the online lab as prime candidates. So key
questions are why are complaints and sickness associated (Chief Constable Sue Fish,
Nottinghamshire)? Which individual differences predict complaints and sickness (Chief
Superintendent Robert Jones)?
Right for the role? Do certain types of behavioural attributes (personality, risk attitudes)
coalesce in specific police functions, such as specialist operations or investigations (Chief
Officer Mike Bowron, States of Jersey Police)?
Bad cops or bad circumstances? Are there career hotspots for misconduct or serious
substantiated complaints (Deputy Commissioner Craig Mackey). Can we provide early
intervention warnings for officers at greatest risk of misconduct? The mechanism for impact
is through Professional Standards (Deputy Assistant Commissioner Fiona Taylor), to help
design career paths that avoid potentially potent placements or role succession that
materially increase the risk of misconduct.
We will also offer a series of four 1-day Behaviour Masterclasses to Senior Officers'
departments in the final year of the project. Classes will be advertised via the College of
Policing, the National Police Chief’s Council, and Warwick’s Centre for Operational Policing
Research. We will target the chief officers responsible for policy and implementation within
their force, and members of their teams. Classes will be co-led by Stewart or Ritchie, and an
officer. We will use feedback to shape the further development of the research.

### 2019-07-09 case_for_support_TM_hacked.tex

--- 2019-07-09 case_for_support.tex
@@
 Given the serious problem of underreporting, one of the unique characteristic of domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+We have access via the UK Data Service.
 
@@
 A unique benefit of the CSEW is that it allows us to investigate the causal effect of domestic abuse by providing information on a control group (those who have not suffered domestic abuse).
-In addition, the CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic (LSOA level) information on the respondent (survivor).
-However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators, and has limited longitudinal information (respondents are asked about whether they suffered domestic abuse in the past 12 months, but the dates of those incidents are not specified).
+In addition, the CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic, socio-economic and geographic information on the respondent (survivor).
+However, owing to the fact that it is a victimisation survey, it does not contain any information on the perpetrators, and has limited longitudinal information.
 In contrast, the WMP crime dataset has information (age, gender, ethnicity) on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to conduct a quantitative analysis of the dynamics of abusive relationships, and identify the predictors of escalation.
@@
 Furthermore, the crime dataset provides us with information on other criminal behaviours of the offender.
-In all the analysis plans outlined below, we will not link the individuals in these datasets.
+We will not link the individuals in these datasets at any time.
 
-Our last proposed project will also rely on a transaction per row dataset containing credit card and current account spending of 20 million customers across the UK.
-We have access to this data as part of a data sharing agreement with a very large UK bank.
+One proposed project relies on a dataset containing credit card and current account spending of 20 million customers across the UK.
+We have access to this data as part of a data sharing agreement with one of the "big 4" UK banks.
 As we know which neighbourhood (LSOA) the card owners live in, this data will allow us to construct a neighbourhood-level measure of spending on alcohol, gambling, and benefit payments throughout time.
-We will not use individual-level data or match people in this dataset with people in the WMP dataset.
+At no point will individual data be used, only geographic, LSAO level, aggregates.
 
-In addition, in analyses that rely on neighbourhood-level characteristics, we will use the Incides of Multiple Deprivation (IMD; \citeNP{IMD}).
+Finally, in analyses that rely on neighbourhood-level characteristics, we will use the Indices of Multiple Deprivation (IMD; \citeNP{IMD}).
 The IMD ranks all 32,844 LSOAs in the UK based on their relative deprivation on various domains, including income, employment, education, health, crime, housing and living environment, providing us with a complex descriptor of the socio-economic characteristics of each neighbourhood in the country.
@@
 
-This research programme involves four research projects exploring different aspects of domestic abuse.
-Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP, this research complements, extends and deepens our understanding of domestic abuse.
+This research programme addresses four overarching topics, exploring different aspects of domestic abuse.
+Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP data, this research complements, extends and deepens our understanding of domestic abuse.
 In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct.
 We will preregister all of our analysis plans using the Open Science Framework (OSF) \TM{I favour not specifying OSF, as it is a steaming pile of excrement and there are better pre-registration alternatives out there.}.
-We will complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach).
+We will complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach in some of our prior work on domestic abuse).
 
 \subsection*{1. Exploring the characteristics of survivors, and understanding the police response to reported cases}
+
+\NS{Add note at the end of each section on publication plan, suggesting specific journal titles, (e.g., PNAS, Nature Human Behaviour, Psychological Science, some domain specific journals.}
 
@@
 
-%Second, we will estimate the true extent of domestic abuse victimisation.
-Given the multifaceted nature of domestic abuse, and the pervasive problem of underreporting, it is very hard to reliably estimate the prevalence of domestic abuse.
-We wish to do so by combining the strengths of the two datasets (that is, the CSEW provides a more reliable measure of the true rate of victimisation across different offence types, while the WMP provides unique information on whether various types of offences were domestic abuse-related).
-Estimating the true prevalence of domestic abuse across various types of criminal offences will help us to obtain a better estimate of the societal cost associated with domestic abuse.
-
-%Exploring the risk factors in domestic abuse victimisation, and the true extent of the problem of underreporting is crucial for designing effective interventions to reduce the risk of escalation that may culminate in domestic homicide.
-
-%Finally, we will estimate the extent of police mis-recording of domestic abuse.
-Increasing victim's trust in the police through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
-By contrasting estimated levels from reported incidents within the West Midlands from the two datasets, we can identify any reporting gaps between the two sources of data that might arise from police mis-recording.
-
-%\textcolor{red}{\textit{What we know so far}} 
-%
-%7.9\% women and 4.2\% men reported to have experienced domestic abuse in the past year; women between 20-24 are most likely to have experienced domestic abuse; for men, age doesn't represent a significant risk factor;  divorced or separated status are significant risk factors across both sexes; long-term illness or disability is a significant predictor across both sexes; single parent households are the most vulnerable; women in the lowest household income bracket are the most likely to have experienced domestic abuse, the same is true for men but the pattern is less pronounced; only 17\% of people who have experienced domestic abuse in the past year have reported to the police, there is no significant difference in this proportion across genders; bisexual women are twice as more likely to experience DA compared to heterosexual women; mixed/multiple ethnicity; social housing; unemployment.
-%single mothers and mothers with young children are more at risk
-%
-%Aim 3. \href{https://www.justiceinspectorates.gov.uk/hmicfrs/news/news-feed/little-evidence-of-improvements-in-crime-recording-at-west-midlands-police/}{HMICFRS about West Midlands mis-recording}
-
 \textcolor{red}{\textit{Detailed plan}} First, using the CSEW data, we will extend our understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
@@
 Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data \cite{ONS}.
-Building on what we know so far, we will explore the predictive power of a broader range of victim characteristics, using a logistic regression approach.
+Building on this prior work, we will explore the predictive power of a broader range of victim characteristics.
 Investigating the explanatory power of these characteristics within one statistical model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
@@
 
- However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
+Given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
 To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm \TM{Do we know enough about random forest classification to be confident about it's appropriateness?
@@
 
- %When a crime is not recorded the force may have recorded details of the report on a different record, such as an incident log.
-It is these records that HMICFRS can audit to establish the extent to which reported crime is being recorded.
-In some cases an officer will have responded to the report.
-
- Her Majesty's Inspectorate of Constabulary and Fires \& Rescue Services (HMICFRS) oversees police forces in England Wales, and regularly inspects their responses to reported crime, including cases of domestic abuse.
-Their latest crime data integrity inspection of 32 police forces have found that 20 forces require significant improvements in their crime recording practices \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-These concerns are especially pertinent in the context of domestic abuse, for example, the latest report found that the WMP have failed to record 25\% of reported crimes that were domestic abuse-related.
-
- We will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties might be less likely to be recorded as a crime by the police).
+ A recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
+Thus, we will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties).
 Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
-We will run a multinomial regression with police force fixed effects for each broad crime type (sexual, physical violence, harassment and stalking), predicting whether the police's response (no action, warning, arrest, charge) depends on the socio-economic characteristics of the victim.
-Using a fixed effects approach will help us tell the relative importance of police force and victim characteristics in crime mis-recording.
-To complement this analysis and explore potential interactions between our explanatory variables, we will also investigate this question with a mixed effects random forest with police force clustering.
-Second, using the same statistical model for each type of crime, we will also investigate how victim's satisfaction with the police, and their perception of their personal security after reporting a crime depends on the police action taken, and their socio-economic characteristics.
+Multi-nomial regression allows us to examine the extent to which police mis-reporting is different accross broad crime types (sexual, physical violence, harassment and stalking) and depends upon the socio-economic characteristics of the victim.
+Complementing this with mixed effects random forrest also reveals the roles of interactions between individual and police force characteristics.
+Lastly these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
 

### 2019-07-10 case_for_support_TM_hacked.tex
TM comments and hack

@@
 Identifying high-risk victim-offender pairs is key in preventing serious harm.
-Understanding what affects the decision to report is particularly important, as underreporting represents the biggest obstacle to effectively tackling domestic abuse.
 Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.
@@
 
-\textcolor{red}{\textit{Detailed plan}} Drawing on the different strengths of the CSEW and the WMP datasets, we will explore the relative importance of the risk factors predicting serious harm.
-Previous studies investigating this question mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
-Using the CSEW, we will complement and extend this research by simultaneously considering the victim characteristics that are predictive of suffering serious injury.
-Specifically, using a multinomial logistic approach, we will explore the extent to which financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared) are predictors of various levels of harm (threats, minor or serious injury).
-We will know the level of harm suffered, because the CSEW asks whether the respondent needed to see a doctor, nurse or other health worker, or needed to take time off work because of the abuse.
-While we cannot investigate causal relationships due to the cross-sectional nature of the CSEW, this analysis will nevertheless provide us with important insights about the characteristics of groups most vulnerable to domestic abuse.
+\textcolor{red}{\textit{Detailed plan}} Previous studies investigating risk factors for serious harm mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
+Using a multinomial logistic approach, the CSEW data allows us to investigate the effects of financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
+In the CSEW the level of harm is identified by victims indicating that they required medical attention, or time off work.
+\TM{maybe delete: "While we cannot investigate causal relationships due to the cross-sectional nature of the CSEW, this analysis will nevertheless provide us with important insights about the characteristics of groups most vulnerable to domestic abuse."}
 
@@
 The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
-Our detailed crime dataset will allow to investigate the extent to which the perpetrator's previous recorded self-harm and suicide attempts, previous violent and drug offences, breaches of court orders and separation from the victim will predict causing serious harm, using each perpetrator-victim pair as a unit of analysis.
-From the detailed description of the incident, we will know if the perpetrator and the victim live together.
-We will explore this question using a multinomial logistic regression analysis with perpetrator-victim fixed effects, where we will use previously known information about the perpetrator to predict serious harm.
-Using a fixed-effects regression approach will allow us to disentangle the relative importance of our explanatory variables and perpetrator-victim specific factors in predicting serious harm.
+We will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with and separation from the victim.
 
@@
 
+\TM{This feels out of place.
+Should the mis-recording and underreporting be in the same section?
+Maybe it would make more sense having analyses 3&4 from this section actual put in section 1?
+If not, then we need to make it clearer what is the distinction.}
+
 We will also use both datasets to explore the predictors of the decision to report and escape the abuse.
-We are not aware of previous research exploring this question.
-Using the CSEW and logistic regression approach, we will investigate how the decision to report (or the decision to seek any form of external help) depends on the individual-level, time-invariant characteristics of the survivor, controlling for the severity and type of the abuse suffered.
-We are especially interested in exploring how trust in the CJS, social ties (living with family, going out, length of living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency affect the decision to report.
-Using the WMP data, we will explore time-varying factors affecting the decision to leave the abuser.
-Due to the high levels of underreporting, it is hard to distinguish between time periods when the number of domestic abuse incidents increase, and when the victims have a higher propensity to finally report the ongoing abuse.
-Here we are mainly interested in the latter case (and will explore the first case in more detail in the last research project), therefore we will focus on the subset of incidents where the victim for the first time reported a long history of abuse.
-We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, Halloween, Easter, etc.), potentially reflecting cases where the abuse has suddenly escalated, or became known to outsiders.
+We are not aware of previous research exploring this question in depth.
+Using the CSEW and logistic regression approach, we will investigate how the decision to report (or seek external help) depends on the individual-level, time-invariant characteristics of the survivor.
+Potential factors are trust in the justice system, social ties (living with family, time living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
+The WMP data complements this with time-varying factors.
+We will use this to examine what are the potential characteristics and triggers that enable a victim to report ongoing, long-term abuse.
+We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentines etc.).
+This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to encourage reporting.
 
@@
 In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household.
-Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
+ %Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
 
@@
 
-\textcolor{red}{\textit{Detailed plan}} First, we will explore the causal effect of past experiences of domestic abuse on present socio-economic outcomes.
-First, using the CSEW, we will explore how witnessing abuse at home in childhood affects educational, employment and health outcomes in adulthood.
+\textcolor{red}{\textit{Detailed plan}} First, we will consolidate and extend research on the effect of witnessing domestic abuse during childhood.
 The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
 Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
-However, due to the possibility of various confounders (e.g., those growing up in economically deprived areas are more likely to witnessing abuse, but economic deprivation also affects educational outcomes), these descriptive statistics do not reveal the causal effect of witnessing abuse as a child on socio-economic outcomes in adulthood.
-To overcome this difficulty in quantifying this causal relationship, we will use propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse on educational, employment, and mental and physical health outcomes, and the probability of experiencing domestic abuse in adulthood.
-In a similar vein, using propensity score matching and the CSEW, we will explore how past experiences of domestic abuse affect current health outcomes, by comparing people who have experienced domestic abuse in the past, but not in the last 12 months, with people who have never experienced domestic abuse, but otherwise have similar socio-economic characteristics.
+We will extend this using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse whilst also controlling for a range of confounds, such as economic deprivation.
+\TM{Do we have any info on economic deprivation of where they grew up, or just where they live now?}
 
-Second, using both the CSEW and WMP, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
-Using data from the 10-15 year old questionnaire of the CSEW (which can be linked to the adult questionnaire), we can examine the effect of domestic abuse on children living in such households.
-The children's questionnaire records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
-Using this dataset and a propensity score matching approach, we will explore the causal effect of living in an abusive household on childhood behavioural outcomes.
+Second, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
+The CSEW questionnaire for 10-15 year olds records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
+By applying propensity score matching, we will explore the causal effect of living in an abusive household.
 
 We will complement this analysis using data on young offenders from the WMP.
-We will identify if young offenders' home addresses can be linked with a domestic abuse incident in the recent past, allowing us to explore whether living in a household with a domestic abuse problem predict the type of crime they will engage in (property-related, public order offence, violent), controlling for the socio-economic characteristics of the neighbourhood (using the IMD).
-We are especially interested in exploring whether living in an abusive environment is predictive of knife crime-related offences.
+We will identify young offenders whose home addresses has been linked with a domestic abuse incident in the recent past.
+It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether the type of crime they engage in.
+For example, whether, after controlling for controlling for the socio-economic characteristics of the neighborhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
 
@@
 While individual-level characteristics are likely to be the most important predictors of domestic abuse victimisation, the environment around the victim can play a key role in either exacerbating, or alleviating domestic abuse.
-Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and the willingness to report is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns.
-We will also explore how time-varying, exogenous factors related to alcohol consumption and financial stability affect domestic abuse.
 
@@
 
-\textcolor{red}{\textit{Detailed plan}} Using the CSEW, we will first explore whether neighbourhood characteristics are predictive of the prevalence of domestic abuse and the willingness to report.
-Previous literature has suggested various pathways, including reduced collective efficacy of neighbourhood, and normalisation and acceptance of violence through social norms, to explain the link between neighbourhood characteristics and domestic abuse, but the question has not been explored in a UK context yet.
-First, using a logistic regression approach, we will explore how the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses, Neighbourhood Watch), as well as the respondent's connection and attitude towards the neighbourhood (length of time living in the local area, noisy neighbours, rubbish lying around, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, speeding traffic, police presence in the area, worries about crime levels) predict domestic abuse victimisation, after controlling for the socio-economic characteristics of the respondent.
-Second, using a spatial regression framework, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse (estimated from the CSEW), and the willingness to report.
+\textcolor{red}{\textit{Detailed plan}} The CSEW includes rich information about the individual's environment, including the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), as well as the respondent's connection and attitude towards the neighbourhood (time living in the local area, noisy neighbours, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, police presence in the area etc.).
+These properties of the environment can be used to predict domestic abuse victimisation, whilst controlling for the socio-economic characteristics of the respondent.
+Additionally, using a spatial regression framework, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse and the willingness to report.
 Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
@@
 
-We are also interested in exploring how time-varying external factors, including alcohol consumption, and financial stress (measured by gambling expenditure and benefit dependency) affect the propensity to engage in abusive behaviours.
+We are also interested in exploring the effect of factors including average alcohol consumption, and levels of financial stress at the community level, rather than the individual (measured by gambling expenditure and benefit dependency).
 In investigating this question, we will use the transaction dataset described earlier, which allows us to estimate a spending profile for each LSOA over time.
 This way we can identify time-specific changes in alcohol consumption, gambling expenses and benefit receipts in parts of the West Midlands, and investigate their effect on the number of reported domestic abuse cases in the area (from the WMP), using a spatial Poisson regression approach.
+\TM{Can we not do this for the whole country using the CSEW?
+I know the timecourse isn't great, but we have the data from individual years.}
 
-To explore the effect of alcohol consumption on domestic abuse, we will identify externals events that may affect alcohol consumption (e.g., local festivals, weather, bank holidays, sport tournaments) measured by spending on alcohol in an LSOA in a given time period, and investigate whether it affects the number of reported domestic abuse incidents in that area.
-Previously, we have found a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
+We shall complement this analysis by identifying external events that may affect alcohol consumption (e.g., festivals, weather, bank holidays, sport tournaments) measured by spending on alcohol in an LSOA in a given time period, and investigate whether it affects the number of reported domestic abuse incidents in that area.
+Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
 

### 2019-07-10 JeS_fields.tex
Anna update

\documentclass[11pt, a4paper]{article}

% Helvetica
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

% 2cm margins
\usepackage[margin=2cm]{geometry}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[center]{caption}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\usepackage{threeparttable}
%\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}

\usepackage{apacite} 
%\usepackage{setspace}
%\doublespacing

\definecolor{green}{rgb}{0,1,0}
\newcommand{\NS}[1] {{\textcolor{green}{#1}}}
\newcommand{\TM}[1] {{\textcolor{orange}{#1}}}
\newcommand{\AT}[1] {{\textcolor{blue}{#1}}}

\begin{document}
\title{ESRC SDAI Application - Understanding domestic abuse using Big Data}
\date{}
\maketitle
\section{Objectives}
\textit{List the main objectives of the proposed research [up to 4000 chars]}
\section{Summary}

\textit{Describe the proposed research in simple terms in a way that could be publicised to a general audience [up to 4000 chars]}

\textit{Not sure what the right angle is, my current approach is to 1) demonstrate the extent of the problem 2) highlight the gaps in our current knowledge and 3) very briefly explain how are we contributing}

Domestic abuse is a complex, multifaceted phenomenon, that has a profound impact on the lives of those affected. Anyone can become a victim, regardless of socio-economic status. The official definition of domestic abuse in the UK aims a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour \cite{govuk}.

Domestic abuse is increasingly recognised as a serious public health concern in many countries, including the UK. In the year ending 2018 March, an estimated 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}. Besides being more likely to experience any form of domestic abuse, compared to men, women are also significantly more likely to endure severe, often lethal violence at home: 41\% of femicides, and 0.6\% of homicides committed in the year ending 2018 March were domestic abuse-related \cite{homic}. The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse. Taking into account the emotional and physical consequences of the abuse suffered, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.

Despite the vast economic costs associated with it, there is relatively little academic research focusing on domestic abuse in the context of the UK. This is most likely due to the scarcity of data sources relating to this topic. Owing to the fact that it occurs in private settings, domestic abuse is a vastly underreported crime: it is estimated that only 17\% of victims who experienced any form of domestic abuse between April 2017 and March 2018 reported it to the police \cite{ONS}, which means that studies exclusively drawing on police data to understand various aspects of domestic abuse (e.g. \citeNP{Bland2015}) have limited ability to derive useful insights about this phenomenon. Another methodological approach is to conduct interviews with survivors (e.g. \citeNP{callaghan}), which, while are tremendously helpful in illuminating the contexts in which domestic abuse can occur, are unfortunately limited in the generalisability of their findings.

In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative victimisation survey across England and Wales, collecting data from 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}. The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.  While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature. In spite of the rich information provided by this survey, a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.

 By recognising its potential, we will rely on the CSEW and combine in with other external datasets to examine various aspects on domestic abuse in England and Wales, and provide a better understanding of this phenomenon. We will explore the individual- and environmental-level risk factors of domestic abuse, including the demographic and socio-economic predictors of victimisation, as well as the neighbourhood characteristics affecting it. Drawing on previous reports on police mis-recording of domestic abuse across England, we will explore whether this affects specific victim groups disproportionately, and its consequences regarding victim's trust in the Criminal Justice System. By combining the rich information in the CSEW with a police crime dataset provided by the West Midlands Police, we will explore the victim- and perpetrator-specific predictors of domestic abuse resulting serious harm and the time-varying and time-invariant predictors of reporting the abuse. The CSEW will also allow us to estimate the causal effect of direct and indirect domestic abuse victimisation on socio-economic and health-related outcomes in adulthood and the likelihood of engaging in violent criminal behaviours in childhood. In addition, we will explore how time-varying external factors, such as changes in alcohol consumption and financial health affect the reported number of domestic abuse incidents. Our previous investigation have revealed that the reported number of alcohol-related domestic abuse increases by 61\% following the victory of the England national football team, highlighting the profound effect external events can have on perpetrators' propensity to engage in violence.

\section{Academic Beneficiaries}

\textit{Describe who will benefit from the research [up to 4000 chars].}

\section{Staff Duties}

\textit{Summarise the roles and responsibilities of each post for which funding is sought [up to 2000 characters]}

\section{Impact Summary }

\textit{(please refer to the help for guidance on what to consider when completing this section) [up to 4000 chars]}

\section{Ethical Information}

\textit{Please explain what, if any, ethical issues you believe are relevant to the proposed research project, and which ethical approvals have been obtained, or will be sought if the project is funded? If you believe that an ethics review is not necessary, please explain your view (available: 4000 characters)}

\section{Attachments}

\href{https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm}{Instructions for attachments}

* Case for support (6 page limit, 11 points, A4, 1" margins)

* References

* Pathways to Impact (2 sides of A4)

* Justification of Resources (2 sides of A4)

* Letter of support from WMP

* Data management plan (modify from \href{https://github.com/neil-stewart/data_management_plan}{lab plan}

* Accumulating to choose progress report

* NIBS2 progress report

\newpage

\bibliographystyle{apacite}
\bibliography{domesticabuse_refs}

\end{document}

### 2019-07-10 JeS_fields.tex
Anna's really shitty summary

@@
 \textit{List the main objectives of the proposed research [up to 4000 chars]}
+
+1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation.
+Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
+While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.
+
+2) To translate our research into impact by delivering applicable insights for the relevant agencies.
+Police (improving recording practices, understanding domestic abuse reporting demand characteristics over time for a better allocation of resources), government (temporal/geographical planning of targeted campaigns, intervention programmes), shelters (temporal/geographical allocation of resources), academia (publications)
+
 \section{Summary}
@@
 
-\textit{Not sure what the right angle is, my current approach is to 1) demonstrate the extent of the problem 2) highlight the gaps in our current knowledge and 3) very briefly explain how are we contributing}
+\textit{I'm really bad at this. I don't really understand what should go in here}
 
-Domestic abuse is a complex, multifaceted phenomenon, that has a profound impact on the lives of those affected.
-Anyone can become a victim, regardless of socio-economic status.
-The official definition of domestic abuse in the UK aims a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour \cite{govuk}.
+Who are the people most vulnerable to becoming victims of domestic abuse?
+To what extent do neighbourhood characteristics predict the prevalence of domestic abuse?
+How can we prevent serious harm and what affects victims' decision to finally report the abuse?
+What is the quantifiable, long-term impact of domestic abuse victimisation, or witnessing domestic abuse as a child on socio-economic outcomes in later life?
+How do changes in alcohol consumption and financial stability affect the prevalence of domestic abuse?
+
+Addressing these questions are fundamental for a deeper understanding of the constellation of individual and environmental factors perpetuating domestic abuse, and the long-term consequences it can have on the lives of those affected.
+Designing effective policy interventions to protect victims can only be based on a sound understanding of the type of environments where domestic abuse is likely to occur.
+In this research programme, we combine various data sources to provide a comprehensive answer to these questions in the context of the UK.
 
 Domestic abuse is increasingly recognised as a serious public health concern in many countries, including the UK.
+It is estimated that in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}.
+Escalation of domestic abuse can result in homicide, and the risk of lethal violence is especially high in the case of female victims: 41\% of femicides, and 0.6\% of homicides committed in the year ending 2018 March were domestic abuse-related in England and Wales \cite{homic}.
+The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse.
+Taking into account the emotional and physical consequences of the abuse suffered, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
+
+Despite the vast economic costs associated with it, there is relatively little academic research focusing on domestic abuse in the context of the UK.
+Studies using police-recorded domestic abuse data have limited ability to derive useful insights about this phenomenon due to the vast levels of underreporting.
+In contrast, studies using qualitative methods have limited ability to derive useful insights about this phenomenon.
+
+%Domestic abuse is a complex, multifaceted phenomenon, that has a profound impact on the lives of those affected.
+It is increasingly recognised as a serious public health concern in many countries, including the UK.
 In the year ending 2018 March, an estimated 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}.
@@
 
-Despite the vast economic costs associated with it, there is relatively little academic research focusing on domestic abuse in the context of the UK.
+%Despite the vast economic costs associated with it, there is relatively little academic research focusing on domestic abuse in the context of the UK.
 This is most likely due to the scarcity of data sources relating to this topic.
@@
 Another methodological approach is to conduct interviews with survivors (e.g.
-\citeNP{callaghan}), which, while are tremendously helpful in illuminating the contexts in which domestic abuse can occur, are unfortunately limited in the generalisability of their findings.
+\citeNP{callaghan}), which, while are tremendously helpful in illuminating the contexts in which domestic abuse can occur, c.
 
@@
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.
+In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.
 
@@
 Our previous investigation have revealed that the reported number of alcohol-related domestic abuse increases by 61\% following the victory of the England national football team, highlighting the profound effect external events can have on perpetrators' propensity to engage in violence.
+
+para on implications
 

### 2019-07-10 case_for_support_TM_hacked.tex
Anna halfway through TM hacked

@@
 \usepackage{booktabs}
+\usepackage{titling}
+\usepackage{titlesec}
+\setlength{\droptitle}{-7em}  
 \usepackage{array}
@@
 
+\posttitle{\par\end{center}\vskip 0.1em}
+\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
+
 \begin{document}
@@
 While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men in England and Wales reported to have experienced some form of domestic abuse since the age of 16 \cite{ONS}.
-The current legal definition in the UK aims to capture the multifaceted nature of domestic abuse, by recognising that domestic abuse encompasses a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour \cite{govuk}.
+In the most extreme cases, domestic abuse can culminate in domestic homicide: in the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, and 90\% of these victims were women \cite{homic}.
+Domestic abuse has substantial mental health implications not only for the direct target of abuse \cite{ferrari}, but also for children witnessing it \cite{callaghan}.
+The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, taking into account various components including missed workdays, health care costs, and reduced quality fo life for survivors \cite{costs}.
 
-Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, and are significantly more likely to report symptoms of anxiety and depression compared to the general population \cite{ferrari}.
+%The current legal definition in the UK aims to capture the multifaceted nature of domestic abuse, by recognising that domestic abuse encompasses a wide range of behaviours, including emotional, sexual, and physical abuse, threatening, intimidating, coercive and controlling behaviour \cite{govuk}.
+
+%Domestic abuse has substantial mental health implications, with an estimated three-quarter of survivors experiencing posttraumatic stress disorder symptoms, and are significantly more likely to report symptoms of anxiety and depression compared to the general population \cite{ferrari}.
 The long lasting impacts of domestic abuse are not limited to the direct target of abuse.
@@
 
-As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature.
+%As the legal definition reflects, one characteristic of domestic abuse that differentiates it from other violent crimes is its repeated nature.
 Estimates show that before getting effective help, on average, survivors live in the abusive relationship for 2.7 years, experiencing an estimated 50 cases of abuse \cite{SafeLives2015}.
@@
 
-In the most extreme cases, domestic abuse can culminate in domestic homicide.
+%In the most extreme cases, domestic abuse can culminate in domestic homicide.
 In the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, 90\% of these victims were women \cite{homic}, demonstrating that domestic abuse is a fundamentally gendered phenomenon.
@@
 
-This research programme consists of four research projects that will deliver useable, policy-relevant insights about domestic abuse.
-First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
-Second, we will investigate the factors predicting suffering serious injury and the decision to report.
+This research programme consists of four research projects that will deliver applicable, policy-relevant insights about domestic abuse.
+First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, and the predictors of suffering serious harm.
+Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
 Third, we will examine the long-lasting effects of being a victim of domestic abuse or witnessing domestic abuse at home as a child.
@@
 Given the serious problem of underreporting, one of the unique characteristic of domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
-We have access via the UK Data Service.
+We have access to this dataset via the UK Data Service.
 
-Some of the projects also benefit from a crime dataset provided by the West Midlands Police (WMP), which includes all crimes and incidents recorded by the police force in the period between January, 2010 and October, 2018.
+%Some of the projects also benefit from a crime dataset provided by the West Midlands Police (WMP; the third largest police force in England, serving a population of 2.9 million; \citeNP{Homeoffice}), which includes all crimes and incidents recorded by the police force in the period between January, 2010 and October, 2018.
 The WMP is the third largest police force in England, serving a population of 2.9 million \cite{Homeoffice}.
@@
 About 31\% of all crimes and incidents have a domestic abuse marker.
-For each record in this dataset, we have rich information about the circumstances of the case, including exact location and time of the incident or crime, the gender, age and ethnicity of the offender and victim, \textbf{their address}, and the severity of the injury sustained by the victim, if any.
+For each record in this dataset, we have rich information about the circumstances of the case, including exact location and time of the incident or crime, the gender, age and ethnicity of the offender and victim, their address, and the severity of the injury sustained by the victim, if any.
 The first and last occurrence of the offence, as well as the exact time of reporting is also recorded.
 Each person in this dataset has a unique person identifier, allowing us to follow people over time.
-\textbf{\emph{\textit{Sentence about access to this dataset.}}} \TM{Access to this dataset is highly sensitive and strictly controlled.
+Access to this dataset is highly sensitive and strictly controlled.
 All researchers on this project have already been vetted by WMP and have been granted access to the required data fields.
-The PI, as data controller for the project is vetted to level 3, and the CoI's to level 2.}
+The PI, as data controller for the project is vetted to level 3, and the CoI's to level 2.
 
-These two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
+Some of the projects also benefit from an anonymised crime dataset provided by the West Midlands Police (WMP; the third largest police force in England, serving a population of 2.9 million; \citeNP{Homeoffice}), which includes all crimes and incidents recorded by the police force between 2010 and 2018, of which about 31\% are domestic abuse-related.
+For each record in this dataset, we know the exact location, time, the gender, age, ethnicity and address of those involved, and the severity of the injury.
+Each person has a person identifier, allowing us to follow people over time.
+Access to this dataset is highly sensitive and strictly controlled.
+All researchers on this project have already been vetted by WMP and have been granted access to the required data fields.
+The PI, as data controller for the project is vetted to level 3, and the CoI's to level 2.
+
+These two datasets have different merits.
+The CSEW provides us with rich demographic and socio-economic information on the respondent, and we can construct a control group from those individuals who have not experienced domestic abuse.
+However, it does not contain any information on the perpetrators, and has limited longitudinal information.
+In contrast, the WMP dataset has information on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to analyse temporal patterns, and identify high-risk times of the year.
+We will not link the individuals in these datasets at any time.
+
+%These two datasets have different merits, and combining them allows us to gain a deeper understanding the characteristics and dynamics of domestic abuse, and deliver policy-relevant insights.
 A unique benefit of the CSEW is that it allows us to investigate the causal effect of domestic abuse by providing information on a control group (those who have not suffered domestic abuse).
@@
 One proposed project relies on a dataset containing credit card and current account spending of 20 million customers across the UK.
-We have access to this data as part of a data sharing agreement with one of the "big 4" UK banks.
+We have access to this data as part of a data sharing agreement with one of the ``Big 4''  UK banks.
 As we know which neighbourhood (LSOA) the card owners live in, this data will allow us to construct a neighbourhood-level measure of spending on alcohol, gambling, and benefit payments throughout time.
-At no point will individual data be used, only geographic, LSAO level, aggregates.
-
+At no point will individual data be used, only geographic, LSOA level, aggregates.
 Finally, in analyses that rely on neighbourhood-level characteristics, we will use the Indices of Multiple Deprivation (IMD; \citeNP{IMD}).
@@
 
-\newpage
-
-\section*{Research Programme}
+\section{Research Programme}
 
@@
 In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct.
-We will preregister all of our analysis plans using the Open Science Framework (OSF) \TM{I favour not specifying OSF, as it is a steaming pile of excrement and there are better pre-registration alternatives out there.}.
-We will complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach in some of our prior work on domestic abuse).
+We will preregister all of our analysis plans and complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach in some of our prior work on domestic abuse).
 
-\subsection*{1. Exploring the characteristics of survivors, and understanding the police response to reported cases}
+\subsection*{1. Exploring the characteristics of survivors and the predictors of serious harm}
 
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
+% \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
 In this research project, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
-We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
-Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data \cite{ONS}.
+However, the CSEW provides a much broader range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
 
-\textcolor{red}{\textit{Detailed plan}} First, using the CSEW data, we will extend our understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
+Investigating the explanatory power of this rich set of victim characteristics within one statistical model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
+We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
+
+However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (e.g., we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
+To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
+Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+
+\TM{Do we know enough about random forest classification to be confident about it's appropriateness?
+Could an expert reviewer find a reason to complain about it or criticize it's use?
+I ask because I don't know it well at all.}
+
+%\textcolor{red}{\textit{Detailed plan}} First, using the CSEW data, we will extend our understanding of the demographic and socio-economic factors predicting domestic abuse victimisation.
 The CSEW provides a broad range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
@@
 
-Given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (for example, we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
-To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm \TM{Do we know enough about random forest classification to be confident about it's appropriateness?
-Could an expert reviewer find a reason to complain about it or criticize it's use?
-I ask because I don't know it well at all.}, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
-Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+ We will also explore the victim and offender characteristics that predict serious harm.
+Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
+Previous studies investigating risk factors for serious harm mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
 
- A recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-Thus, we will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties).
-Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
-Multi-nomial regression allows us to examine the extent to which police mis-reporting is different accross broad crime types (sexual, physical violence, harassment and stalking) and depends upon the socio-economic characteristics of the victim.
-Complementing this with mixed effects random forrest also reveals the roles of interactions between individual and police force characteristics.
-Lastly these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
+ Using a multinomial logistic approach, the CSEW data allows us to investigate the effects of financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
+In the CSEW, the level of harm is identified by victims indicating that they required medical attention, or time off work.
+
+ Using the WMP data, we will also explore the risk factors associated with the perpetrator.
+The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
+Using a logistic regression approach with perpetrator-victim fixed effects (FE), we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
 
@@
 
-% Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
+%Police forces in England, and particularly the West Midlands Police, have previously been criticised for mis-recording violent cases of violent crime, including \href{https://www.bbc.co.uk/news/uk-england-468676578}{domestic abuse.} Mis-recording these already heavily underreported crimes decrease victim's trust in the Criminal Justice System and their willingness to report subsequent incidents.
 \textit{Why don't we use the aggregate number of \href{https://www.ons.gov.uk/peoplepopulationandcommunity/crimeandjustice/datasets/domesticabuseinenglandandwalesappendixtables}{police-recorded domestic abuse cases for each police force} to do this?
@@
 
-\begin{table}[!htbp]
+\begin{table*}
 \caption{Exploring the characteristics of survivors, and understanding the police response to reported cases, analysis plan}
@@
   \centering
-       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+       \begin{tabular}{ L{2.4cm}  C{1.4cm}  C{1.5cm}  C{3.6cm}  C{3.1cm}  C{2.6cm} }
     \toprule
@@
     What are the characteristics of domestic abuse victims?
-& CSEW & Individual (respondent-level) & Domestic abuse victimisation; Victimisation by type (physical, sexual abuse, threats) & demographic and socio-economic characteristics & Logistic regression/random forest \\
+& CSEW & Individual  & Domestic abuse victimisation; Victimisation by type (physical, sexual abuse, threats) & demographic and socio-economic characteristics & Logistic regression/random forest \\
            \midrule
-    How does the police response depend on victim characteristics?
-& CSEW (reported domestic abuse, by type of offence) & Individual (respondent-level) & Police action taken (no action, warning, arrest, charge) & demographic and socio-economic characteristics of the victim & Multinomial logistic regression with  fixed effects/ mixed effects random forest \\
+    What victim characteristics predict serious harm?
+& CSEW & Individual (respondent-level) & Level of harm resulting from domestic abuse victimisation (no physical harm, minor, serious) & financial resources, mental health, dependence, social isolation, separation, feeling scared & Multinomial logistic regression \\
                 \midrule
-    What predicts victims' trust in the police?
-& CSEW (reported domestic abuse, by type of offence) & Individual (respondent-level)& Satisfaction with police action, perception of security after reporting & police action taken, demographic and socio-economic characteristics of the victim & Multinomial logistic regression with fixed effects/ mixed effects random forest \\
+                    What perpetrator characteristics predict serious harm?
+& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, violent and drug offences, breach of court orders, separation &  Logistic regression with perpetrator-victim FE \\
 %    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
@@
   \label{tab:addlabel}%
-\end{table}%
-\FloatBarrier
+\end{table*}%
+
 %Second, we can validate some of these findings using the WMP data, since the CSEW contains information on whether the survivor reported the domestic abuse to the police.
@@
 
-\textcolor{red}{\textit{Core outcomes}}
+%\textcolor{red}{\textit{Core outcomes}}
 
-The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation.
+%The first extensive investigation of the demographic and socio-economic predictors of domestic abuse victimisation.
 A deeper understanding of the characteristics of police mis-recording and its effect on victim's trust in the CJS.
 
-\newpage
+\subsection*{2. Understanding the decision to report and police mis-recording of domestic abuse}
 
-\subsection*{2. Predicting serious harm and understanding the decision to report}
+ \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will first explore victims reporting behaviour.
+We will also use both the CSEW and the WMP dataset to explore the predictors of the decision to report and escape the abuse.
+We are not aware of previous research exploring this question in depth.
+Using the CSEW and logistic regression approach, we will investigate how the decision to report (or seek external help) depends on the individual-level, time-invariant characteristics of the survivor.
+Potential factors are trust in the justice system, social ties (living with family, time living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
+The WMP data complements this with time-varying factors.
+We will use this to examine what are the potential characteristics and triggers that enable a victim to report ongoing, long-term abuse.
+We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentines etc.).
+This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to encourage reporting.
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will explore the victim and offender characteristics that predict serious harm and the factors determining the decision to report the abuse.
+%  the victim and offender characteristics that predict serious harm.
 Identifying high-risk victim-offender pairs is key in preventing serious harm.
@@
 
-\textcolor{red}{\textit{Detailed plan}} Previous studies investigating risk factors for serious harm mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
-Using a multinomial logistic approach, the CSEW data allows us to investigate the effects of financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
-In the CSEW the level of harm is identified by victims indicating that they required medical attention, or time off work.
-\TM{maybe delete: "While we cannot investigate causal relationships due to the cross-sectional nature of the CSEW, this analysis will nevertheless provide us with important insights about the characteristics of groups most vulnerable to domestic abuse."}
+We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
+Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
+A recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
+In this project, we will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties).
+Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
+A multinomial regression approach with police force FE allows us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), police forces, and depends upon the socio-economic characteristics of the victim.
+Complementing this analysis with a mixed effects (ME) random forest approach also reveals the roles of interactions between individual and police force characteristics.
+Lastly, these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
 
-Using the WMP data, we will also explore the risk factors associated with the perpetrator.
-The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
-We will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with and separation from the victim.
-
+\textcolor{red}{\textit{Detailed plan}} 
 %Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.
@@
   \centering
-       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+       \begin{tabular}{ L{2.8cm}  C{1.2cm}  C{1.5cm}  C{3.4cm}  C{3.1cm}  C{2.6cm} }
     \toprule
      \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
+
                      \midrule
-    What victim characteristics predict serious harm?
-& CSEW & Individual (respondent-level) & Level of harm resulting from domestic abuse victimisation (no physical harm, minor, serious) & financial resources, mental health, dependence, social isolation, separation, feeling scared & Multinomial logistic regression \\
+    How does the police response depend on victim characteristics?
+& CSEW  & Individual & Police action (no action, warning, arrest, charge) & demographic and socio-economic characteristics of the victim & Multinomial logistic regression with FE/ ME random forest \\
      \midrule
-                    What perpetrator characteristics predict serious harm?
-& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, previous violent and drug offences, breaching court orders, separation & Multinomial logistic regression with perpetrator-victim fixed effects \\
+    What predicts victims' trust in the police?
+& CSEW  & Individual & Satisfaction with police action, perception of security after reporting & police action, demographic and socio-economic characteristics of the victim & Multinomial logistic regression with FE/ ME random forest \\
                 \midrule
      What time-invariant (victim) characteristics predict the decision to report?
-& CSEW & Individual (respondent-level) & Reported abuse to the police & severity/type of abuse, trust in CJS, social ties, financial status, children, mental health, dependencies & Logistic regression \\
+& CSEW & Individual  & Reported abuse to the police & severity/type of abuse, trust in CJS, social ties, financial status, children, mental health, dependencies & Logistic regression \\
        \midrule
@@
 
-\TM{This feels out of place.
+%nd the factors determining the decision to report the abuse
+
+%\TM{This feels out of place.
 Should the mis-recording and underreporting be in the same section?
-Maybe it would make more sense having analyses 3&4 from this section actual put in section 1?
+Maybe it would make more sense having analyses 3\&4 from this section actual put in section 1?
 If not, then we need to make it clearer what is the distinction.}
-
-We will also use both datasets to explore the predictors of the decision to report and escape the abuse.
-We are not aware of previous research exploring this question in depth.
-Using the CSEW and logistic regression approach, we will investigate how the decision to report (or seek external help) depends on the individual-level, time-invariant characteristics of the survivor.
-Potential factors are trust in the justice system, social ties (living with family, time living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
-The WMP data complements this with time-varying factors.
-We will use this to examine what are the potential characteristics and triggers that enable a victim to report ongoing, long-term abuse.
-We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentines etc.).
-This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to encourage reporting.
 
@@
 
+\newpage
+
 %Unit of analysis is large geographical area in a year
@@
 
-\newpage
+\clearpage
 

### 2019-07-11 case_for_support_TM_hacked.tex
Anna case for support reduced to 6 pages

@@
 
-\NS{Add note at the end of each section on publication plan, suggesting specific journal titles, (e.g., PNAS, Nature Human Behaviour, Psychological Science, some domain specific journals.}
+%\NS{Add note at the end of each section on publication plan, suggesting specific journal titles, (e.g., PNAS, Nature Human Behaviour, Psychological Science, some domain specific journals.}
 
@@
 Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
-Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household and earning in the lowest income bracket), based on descriptive statistics derived from the CSEW data \cite{ONS}.
-However, the CSEW provides a much broader range of information on the characteristics of the respondent, including age, sex, marital status, number of children, ethnicity, education, employment, income, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household, earning in the lowest income bracket, having a long-term disability), based on descriptive statistics derived from the CSEW data \cite{ONS}.
+However, the CSEW provides a much broader range of information on the characteristics of the respondent, including number of children, ethnicity, education, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
 
-Investigating the explanatory power of this rich set of victim characteristics within one statistical model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
+Investigating the explanatory power of a broader set of victim characteristics within one regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
 We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
 
-However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (e.g., we would expect that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
-To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables, allowing us to identify particularly vulnerable subgroups of the population.
-Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England, using a national-level, large representative sample like the CSEW.
+However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (e.g., it is possible that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
+To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables in predicting categorical outcomes (e.g., domestic abuse victimisation), allowing us to identify particularly vulnerable subgroups of the population \cite{rforest}.
+Insights from both methods will provide us with the first extensive characterisation of the risk factors predicting domestic abuse victimisation in England and Wales, using a national-level, large representative sample like the CSEW.
 
@@
  We will also explore the victim and offender characteristics that predict serious harm.
-Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
 Previous studies investigating risk factors for serious harm mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
+Using a multinomial logistic approach, we will use the CSEW to investigate how victim characteristics predict the level of harm suffered, including financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
 
- Using a multinomial logistic approach, the CSEW data allows us to investigate the effects of financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
-In the CSEW, the level of harm is identified by victims indicating that they required medical attention, or time off work.
-
- Using the WMP data, we will also explore the risk factors associated with the perpetrator.
+ Using the WMP data, we will also explore the risk factors of serious harm associated with the perpetrator.
 The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
 Using a logistic regression approach with perpetrator-victim fixed effects (FE), we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
+
+ Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims. \AT{publication plan.}
 
@@
     What victim characteristics predict serious harm?
-& CSEW & Individual (respondent-level) & Level of harm resulting from domestic abuse victimisation (no physical harm, minor, serious) & financial resources, mental health, dependence, social isolation, separation, feeling scared & Multinomial logistic regression \\
+& CSEW & Individual  & Level of harm resulting from domestic abuse victimisation (no physical harm, minor, serious) & financial resources, mental health, dependence, social isolation, separation, feeling scared & Multinomial logistic regression \\
                 \midrule
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}} In this project, we will first explore victims reporting behaviour.
-We will also use both the CSEW and the WMP dataset to explore the predictors of the decision to report and escape the abuse.
-We are not aware of previous research exploring this question in depth.
-Using the CSEW and logistic regression approach, we will investigate how the decision to report (or seek external help) depends on the individual-level, time-invariant characteristics of the survivor.
-Potential factors are trust in the justice system, social ties (living with family, time living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
-The WMP data complements this with time-varying factors.
-We will use this to examine what are the potential characteristics and triggers that enable a victim to report ongoing, long-term abuse.
-We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentines etc.).
+In this project, we will first explore the factors influencing victim's decision to report the abuse.
+Even though improving willingness to report is key to effectively tackle domestic abuse, we are not aware of previous research exploring this question in depth.
+Using the CSEW and logistic regression approach, we will investigate how the decision to report (or seek external help) depends on the individual-level, time-invariant characteristics of the survivor, including trust in the justice system, social ties (living with family, time living in the area, member of Neighbourhood Watch), financial independence (own income, employment status, car ownership), number of children, mental health, and alcohol and drug dependency.
+
+We will complement this analysis with the exploration of time-varying factors affecting the decision to report ongoing abuse using the WMP.
+We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentine's Day etc.).
 This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to encourage reporting.
@@
 We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
-Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in encouraging victims to report domestic abuse and prevent further harm.
-A recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-In this project, we will explore whether the extent of crime mis-recording depends on victim characteristics (e.g., a crime reported by a victim with a mental illness, substance dependency or language difficulties).
-Using the CSEW, we will be able to tell whether the domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
-A multinomial regression approach with police force FE allows us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), police forces, and depends upon the socio-economic characteristics of the victim.
-Complementing this analysis with a mixed effects (ME) random forest approach also reveals the roles of interactions between individual and police force characteristics.
+Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in improving willingness to report.
+Mis-recording of domestic abuse is a serious problem across police forces, for example, a recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
+In this project, we will explore whether the extent of crime mis-recording depends on victim characteristics.
+Using the CSEW, we will be able to tell whether the type of domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
+A multinomial regression approach allows us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), and depends upon the socio-economic characteristics of the victim and the police forces (e.g., funding per police officer, deprivation).
+Complementing this analysis with a random forest approach will reveal the role of interactions between individual and police force characteristics.
 Lastly, these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
+\AT{publication plan.}
 
-\textcolor{red}{\textit{Detailed plan}} 
 %Second, using the WMP data, we can analyse the temporal patterns of reported domestic abuse incidents by following  23\% of the 182,646 victim-offender pairs over an eight-year-long period.
@@
 \begin{table}[!htbp]
-\caption{Predicting serious harm and understanding the decision to report, analysis plan}
+\caption{Understanding the decision to report and police mis-recording of domestic abuse, analysis plan}
   \begin{threeparttable}[t]
   \centering
-       \begin{tabular}{ L{2.8cm}  C{1.2cm}  C{1.5cm}  C{3.4cm}  C{3.1cm}  C{2.6cm} }
+       \begin{tabular}{ L{3cm}  C{1.1cm}  C{1.5cm}  C{3cm}  C{3.3cm}  C{2.8cm} }
     \toprule
      \textbf{Research question} & \textbf{Dataset}    & \textbf{Unit of analysis} & \textbf{Outcome variables} & \textbf{Explanatory variables} & \textbf{Model} \\
-
+                \midrule
+     What victim characteristics predict the decision to report?
+& CSEW & Individual  & Reported abuse to the police & type of abuse, trust in CJS, social ties, financial status, children, health, dependencies & Logistic regression \\
+       \midrule
+          What time-varying factors predict the decision to report?
+& WMP & Perpetrator-victim pairs & Reported ongoing abuse to the police & time of year, holidays, length of abuse, severity of last occurrence & Logistic regression \\
                      \midrule
     How does the police response depend on victim characteristics?
-& CSEW  & Individual & Police action (no action, warning, arrest, charge) & demographic and socio-economic characteristics of the victim & Multinomial logistic regression with FE/ ME random forest \\
+& CSEW  & Individual & Police action (no action, warning, arrest, charge) &  socio-economic characteristics of victim and police force  & Multinomial logistic regression/ random forest \\
      \midrule
     What predicts victims' trust in the police?
-& CSEW  & Individual & Satisfaction with police action, perception of security after reporting & police action, demographic and socio-economic characteristics of the victim & Multinomial logistic regression with FE/ ME random forest \\
-                \midrule
-     What time-invariant (victim) characteristics predict the decision to report?
-& CSEW & Individual  & Reported abuse to the police & severity/type of abuse, trust in CJS, social ties, financial status, children, mental health, dependencies & Logistic regression \\
-       \midrule
-          What time-varying characteristics predict the decision to leave?
-& WMP & Perpetrator-victim pairs & Reported ongoing abuse to the police & time of year, specific holidays, length of abuse, severity of last occurrence & Logistic regression \\
+& CSEW  & Individual & Satisfaction with police action, perception of security & police action,  socio-economic characteristics of victim and police force & Multinomial logistic regression/ random forest \\
      \bottomrule
@@
 
-\textcolor{red}{\textit{Core outcomes}}
-
-A deeper understanding of the victim and perpetrator characteristics that predict serious harm, and the time-invariant and time-varying factors affecting the decision to report the abuse to the police.
-
 %Aim:
-\FloatBarrier
 %The CSEW respondents indicated the level of harm, and we can use the CSEW to estimate the cross-sectional association between the most serious harm and other comorbid factors like alcohol, other crimes,
@@
 
- \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
- Domestic abuse has long-lasting adverse effects on victims and those close to them.
-In this research project, our is aim to explore some of these consequences on the direct victims of domestic abuse and the children who live in the same household.
+ Domestic abuse has long-lasting adverse effects on victims and children witnessing the abuse.
+In this research project, our is aim to explore some of these consequences.
+The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
+Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
+We will consolidate and extend these findings using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse whilst also controlling for a range of confounds, such as economic deprivation.
  %Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
@@
 
-\textcolor{red}{\textit{Detailed plan}} First, we will consolidate and extend research on the effect of witnessing domestic abuse during childhood.
-The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
-Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
-We will extend this using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse whilst also controlling for a range of confounds, such as economic deprivation.
-\TM{Do we have any info on economic deprivation of where they grew up, or just where they live now?}
+Second, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
+The CSEW questionnaire for 10-15 year old's records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
+By applying propensity score matching, we will explore the causal effect of living in an abusive household on these outcomes.
 
-Second, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
-The CSEW questionnaire for 10-15 year olds records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
-By applying propensity score matching, we will explore the causal effect of living in an abusive household.
+We will complement this analysis using WMP, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
+It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crime they engage in.
+For example, whether, after controlling for the socio-economic characteristics of the neighbourhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
 
-We will complement this analysis using data on young offenders from the WMP.
-We will identify young offenders whose home addresses has been linked with a domestic abuse incident in the recent past.
-It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether the type of crime they engage in.
-For example, whether, after controlling for controlling for the socio-economic characteristics of the neighborhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
+ These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes. \AT{publication plan.}
 
@@
   \centering
-       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+       \begin{tabular}{ L{3.9cm}  C{1cm}  C{1.9cm}  C{3.2cm}  C{2.8cm}  C{1.6cm} }
     \toprule
@@
     How does witnessing domestic abuse as a child affect socio-economic outcomes in adulthood?
-& CSEW & Individual (respondent-level) & Educational attainment, employment status and health-related outcomes, including domestic abuse victimisation & Witnessing domestic abuse & Propensity score matching \\
+& CSEW & Individual & Education, employment, health, domestic abuse victimisation & Witnessing domestic abuse & Propensity score matching \\
                 \midrule
-                   How does experiences of past (but not recent) domestic abuse affect socio-economic outcomes in adulthood?
-& CSEW & Individual (respondent-level) & Current health and employment outcomes & Degree and type of domestic abuse suffered & Propensity score matching \\
+                   How does experiences of past domestic abuse affect socio-economic outcomes in adulthood?
+& CSEW & Individual & Employment, health & Degree and type of domestic abuse suffered & Propensity score matching \\
                 \midrule
      How does living a household with domestic abuse affect behavioural outcomes in childhood?
-& CSEW & Individual (respondent-level) & Bullying, involvement with gangs, school truancy, carrying knives, drugs and alcohol usage, learning difficulties, health & Degree and type of domestic abuse in household & Propensity score matching \\
+& CSEW & Individual & Bullying, gangs, school truancy, carrying knives, drugs and alcohol, learning difficulties, health & Degree and type of domestic abuse in household & Propensity score matching \\
                 \midrule
           Are young offenders from abusive households more violent?
-& WMP, IMD & Young offenders (individual) & Type of offence (property-related, public order offence, violent) & Household LSOA socio-economic characteristics, abusive household or not & Multinomial logistic regression \\
+& WMP, IMD & Young offenders & Type of offence (property-related, public order offence, violent) & Neighbourhood socio-economic characteristics, abusive household & Multinomial logistic regression \\
      \bottomrule
@@
   \label{tab:addlabel}%
+%  \setlength\belowcaptionskip{-20pt}
 \end{table}%
-
+%\raggedbottom
 %Using data from the CSEW and well as population data of the West Midlands, we can estimate how many children and young people below 18 in each LSOA of the West Midlands are at risk of witnessing domestic abuse at home each year.
@@
 
-\textcolor{red}{\textit{Core outcomes}}
- The first UK-based quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
-\FloatBarrier
 \subsection*{4. Environmental factors influencing the prevalence of domestic abuse}
 
-\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
 In this research project, we will investigate some of the environmental predictors of domestic abuse.
-While individual-level characteristics are likely to be the most important predictors of domestic abuse victimisation, the environment around the victim can play a key role in either exacerbating, or alleviating domestic abuse.
+First, using the CSEW and a logistic regression approach, we will explore the neighbourhood predictors of domestic abuse victimisation and willingness to report, using information on the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), whilst controlling for the socio-economic characteristics of the respondent.
+
+Additionally, we will investigate how neighbourhood (LSOA) deprivation (measured by the IMD) affects the prevalence of domestic abuse and willingness to report, using a spatial regression framework.
+Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
 
@@
 
-\textcolor{red}{\textit{Detailed plan}} The CSEW includes rich information about the individual's environment, including the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), as well as the respondent's connection and attitude towards the neighbourhood (time living in the local area, noisy neighbours, teenagers hanging around, vandalism, drunken and anti-social behaviour, drug trafficking, abandoned cars, police presence in the area etc.).
-These properties of the environment can be used to predict domestic abuse victimisation, whilst controlling for the socio-economic characteristics of the respondent.
-Additionally, using a spatial regression framework, we will explore how deprivation in a neighbourhood (LSOA level, measured by the IMD) affects the prevalence of domestic abuse and the willingness to report.
-Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
+Using the CSEW and the transaction dataset, we will also explore how neighbourhood-level spending on alcohol and gambling predict the prevalence of domestic abuse in the area, whilst controlling for the deprivation of the neighbourhood.
+We will do so by estimating a spending profile on alcohol and gambling for each LSOA in a year.
 These analyses will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first project to provide a comprehensive exploration of the factors affecting domestic abuse victimisation and willingness to report.
 
-We are also interested in exploring the effect of factors including average alcohol consumption, and levels of financial stress at the community level, rather than the individual (measured by gambling expenditure and benefit dependency).
-In investigating this question, we will use the transaction dataset described earlier, which allows us to estimate a spending profile for each LSOA over time.
-This way we can identify time-specific changes in alcohol consumption, gambling expenses and benefit receipts in parts of the West Midlands, and investigate their effect on the number of reported domestic abuse cases in the area (from the WMP), using a spatial Poisson regression approach.
-\TM{Can we not do this for the whole country using the CSEW?
-I know the timecourse isn't great, but we have the data from individual years.}
-
-We shall complement this analysis by identifying external events that may affect alcohol consumption (e.g., festivals, weather, bank holidays, sport tournaments) measured by spending on alcohol in an LSOA in a given time period, and investigate whether it affects the number of reported domestic abuse incidents in that area.
-Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won, highlighting the profound effect exogenous events can have on the propensity for violence.
-
-To explore the effect of financial shocks on domestic abuse, we will be using the same estimation approach, but we will focusing on gambling and benefit payments.
-Gambling is increasingly recognised as a serious health concern across the UK, and can have a profoundly adverse impact on family finances.
-We will use our transaction data and WMP dataset to assess the link between changes in spending on gambling in a given LSOA, and the prevalence of domestic abuse in that area.
-The recent reforms of the UK benefit system, in the form of the introduction of the Universal Credit (UC) had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
-Drawing on previous findings about the link between financial stress and domestic abuse, we will explore what effect the roll-out of the UC across the West Midlands had on the reported number of domestic abuse cases.
+Finally, we will explore the extent to which changes in alcohol consumption and financial stability on the community level predicts the prevalence of domestic abuse.
+We can identify external events that may affect these (e.g., festivals, weather, bank holidays, sport tournaments), and investigate whether it affects the number of reported domestic abuse incidents in that area in a given time period.
+Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.
+Second, drawing on previous findings about the link between financial stress and domestic abuse, we we will explore what effect the roll-out of the Universal Credit (UC) across the West Midlands had on the reported number of domestic abuse cases.
+These reforms had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
@@
   \centering
-       \begin{tabular}{ L{2.8cm}  C{1.8cm}  C{1.8cm}  C{3.2cm}  C{2.8cm}  C{2cm} }
+       \begin{tabular}{ L{4cm}  C{1.2cm}  C{1.6cm}  C{3cm}  C{2.8cm}  C{1.8cm} }
     \toprule
@@
     \midrule
-    How do environmental characteristics of the neighbourhood predict domestic abuse?
-& CSEW & Individual (respondent-level) & domestic abuse victimisation/willingness to report & Perception of neighbourhood, socio-economic characteristics & Logistic regression \\
+    How do neighbourhood characteristics predict domestic abuse?
+& CSEW & Individual & domestic abuse victimisation/willingness to report & Perception of neighbourhood, socio-economic characteristics & Logistic regression \\
          \midrule
           How does neighbourhood deprivation predict domestic abuse?
-& IMD, CSEW & LSOA-level & domestic abuse victimisation/willingness to report (proportion of overall population) & Various measures of deprivation & Spatial Logistic regression \\
+& IMD, CSEW & LSOA-level & domestic abuse victimisation/willingness to report & Various measures of deprivation & Spatial Logistic regression \\
          \midrule
-    How do temporal changes in alcohol consumption and income affect domestic abuse?
-& WMP, Credit card data & LSOA, day/week-level & Number of reported domestic abuse cases & Spending on alcohol and gambling, changes in benefit receipts & Poisson/Negative binomial regression with spatial effects \\
+          How do community-level spending on alcohol and gambling affect domestic abuse?
+& CSEW, Transaction data, IMD & LSOA-level & domestic abuse victimisation & Spending on alcohol and gambling, deprivation & Spatial Poisson regression \\
+         \midrule
+    How do community-level temporal changes in alcohol consumption and income affect domestic abuse?
+& WMP, Transaction data & LSOA, day-, week-, month-level & Number of reported domestic abuse cases & Alcohol, gambling spending, benefits & Spatial Poisson regression \\
 
@@
 
-\textcolor{red}{\textit{Core outcomes}} The first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
-An exploration of the exogenous, time-varying factors, including alcohol consumption and financial stress (gambling, universal credit) affecting the reported number of domestic abuse cases in the West Midlands.
+These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. \AT{publication plan.}
 

### 2019-07-11 JeS_fields.tex
Anna crappy summary

@@
 To what extent do neighbourhood characteristics predict the prevalence of domestic abuse?
-How can we prevent serious harm and what affects victims' decision to finally report the abuse?
+What predicts serious harm and victims' decision to finally report the abuse?
 What is the quantifiable, long-term impact of domestic abuse victimisation, or witnessing domestic abuse as a child on socio-economic outcomes in later life?
@@
 
-Addressing these questions are fundamental for a deeper understanding of the constellation of individual and environmental factors perpetuating domestic abuse, and the long-term consequences it can have on the lives of those affected.
-Designing effective policy interventions to protect victims can only be based on a sound understanding of the type of environments where domestic abuse is likely to occur.
-In this research programme, we combine various data sources to provide a comprehensive answer to these questions in the context of the UK.
+Addressing these questions is fundamental for a deeper understanding of the far-reaching consequences of domestic abuse victimisation and the individual and environmental factors precipitating it.
+This knowledge can in turn form the basis of effective policy interventions aiming to encourage willingness to report and safeguarding groups vulnerable to domestic abuse.
+In this research programme, we aim to provide a comprehensive answer to these (and other) questions related to domestic abuse, with a series of quantitative analyses drawing on various data sources.
 
-Domestic abuse is increasingly recognised as a serious public health concern in many countries, including the UK.
 It is estimated that in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}.
-Escalation of domestic abuse can result in homicide, and the risk of lethal violence is especially high in the case of female victims: 41\% of femicides, and 0.6\% of homicides committed in the year ending 2018 March were domestic abuse-related in England and Wales \cite{homic}.
+Domestic abuse can result in homicide, and the risk of lethal violence is especially high in the case of female victims: 41\% of femicides, and 0.6\% of homicides committed in the year ending 2018 March were domestic abuse-related \cite{homic}.
 The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse.
-Taking into account the emotional and physical consequences of the abuse suffered, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
+The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
 
-Despite the vast economic costs associated with it, there is relatively little academic research focusing on domestic abuse in the context of the UK.
-Studies using police-recorded domestic abuse data have limited ability to derive useful insights about this phenomenon due to the vast levels of underreporting.
-In contrast, studies using qualitative methods have limited ability to derive useful insights about this phenomenon.
+Despite the extent of the problem, there is relatively little academic research focusing on domestic abuse in the context of the UK, perhaps due to the lack of data sources.
+Using police data is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
+In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
+While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
+In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.
 
@@
 
-In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative victimisation survey across England and Wales, collecting data from 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}.
-The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.
-While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.
+Our project takes advantage of the rich information contained in the CSEW, and draws on other data sources to characterise domestic abuse in England and Wales.
+We will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
+We will also explore whether there is any evidence that the police's response depend on the individual victim characteristics.
+We will quantify the causal effect of domestic abuse on the behavioural outcomes of child and the socio-economic outcomes of adult victims.
+Finally, we will explore how alcohol consumption, spending on gambling, and changes in benefit receipts affect the prevalence of domestic abuse.
 
- By recognising its potential, we will rely on the CSEW and combine in with other external datasets to examine various aspects on domestic abuse in England and Wales, and provide a better understanding of this phenomenon.
-We will explore the individual- and environmental-level risk factors of domestic abuse, including the demographic and socio-economic predictors of victimisation, as well as the neighbourhood characteristics affecting it.
-Drawing on previous reports on police mis-recording of domestic abuse across England, we will explore whether this affects specific victim groups disproportionately, and its consequences regarding victim's trust in the Criminal Justice System.
-By combining the rich information in the CSEW with a police crime dataset provided by the West Midlands Police, we will explore the victim- and perpetrator-specific predictors of domestic abuse resulting serious harm and the time-varying and time-invariant predictors of reporting the abuse.
-The CSEW will also allow us to estimate the causal effect of direct and indirect domestic abuse victimisation on socio-economic and health-related outcomes in adulthood and the likelihood of engaging in violent criminal behaviours in childhood.
-In addition, we will explore how time-varying external factors, such as changes in alcohol consumption and financial health affect the reported number of domestic abuse incidents.
-Our previous investigation have revealed that the reported number of alcohol-related domestic abuse increases by 61\% following the victory of the England national football team, highlighting the profound effect external events can have on perpetrators' propensity to engage in violence.
-
-para on implications
+para on implications (500 chars)
 

### 2019-07-17 JeS_fields.tex
Update JeS_fields.tex
General plan suggestion for summary
Anna update

@@
 
+Concern about domestic abuse is widespread, and it is rightly identified as a serious issue.
+However, the true severity is still often underestimated, and hard to comprehend: Of all women murdered in the UK, 41% die as a direct result of domestic abuse.
+
 Who are the people most vulnerable to becoming victims of domestic abuse?
@@
 para on implications (500 chars)
+Our work will have implications for the police and policy-makers.
+The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious cases, and times of the year when the number of reported cases is likely to be higher.
+Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, and better understand its far-reaching societal implications (effect on socio-economic characteristics, knife crime).
 

### 2019-07-17 pathways_to_impact.tex
Neil initial attempt

@@
+See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.
+
+We will work with researchers at the College of Policing, the Behavioural Insights Team at West Midlands Police,
+
+Our day-to-day contact at West Midlands Police is Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning).
+Our day-to-day contact at the West Midlands Police and Crime Commissioner's Office is Alison Spence.
+
+At the level of the National Police Chiefs' Council we will work with Deputy Chief Constable Louisa Rolfe who is the lead for domestic abuse.
+
+In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
+We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
+The summit will be a 50/50 academic / practitioner mix.
+We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+
+We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior managment team: 1.
+The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse.
+2.
+The programme on the  ``decision to report'' can link with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting.
+3.
+The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands,
+
+At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015.
+(https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
+(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf) We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
+
+Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability.
+Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
+Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship.
+Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.
+We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.
+
+Events:
+
+Impact summit (1 day at the Shard)
+Visits to key charities
+Visits to West Midlands Police
+Presentation to NPCC
+Data sprint session with WMP Behavioural Insights Team?
+
+In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts.
+We will submit these reports to the College of Police What Works database and log them on the Research Map (https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx)
+
+Although a high-profile ``launch'' event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.
+
+PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme.
+Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority.
+CI Stewart will also spend half of his time of the project on the impact activity.
+Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association.
+Postdoc Trendl will be fully involved in the impact programme, and this is also an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.
+Trendl will spend one third of her time on the programme on the impact activities.
+
+We will apply to the Warwick ESRC Impact Acceleration Fund and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.
+
 \section{Old Accumulating to Choose Pathways to Impact}

### 2019-07-17 JeS_fields.tex

--- 2019-07-11 JeS_fields.tex
@@
 
-Who are the people most vulnerable to becoming victims of domestic abuse?
+Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue.
+However, the true severity is still often underestimated, and hard to comprehend: in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
+The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse.
+The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
+
+%Who are the people most vulnerable to becoming victims of domestic abuse?
 To what extent do neighbourhood characteristics predict the prevalence of domestic abuse?
@@
 
-Addressing these questions is fundamental for a deeper understanding of the far-reaching consequences of domestic abuse victimisation and the individual and environmental factors precipitating it.
+%Addressing these questions is fundamental for a deeper understanding of the far-reaching consequences of domestic abuse victimisation and the individual and environmental factors precipitating it.
 This knowledge can in turn form the basis of effective policy interventions aiming to encourage willingness to report and safeguarding groups vulnerable to domestic abuse.
@@
 
-It is estimated that in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}.
+%It is estimated that in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}.
 Domestic abuse can result in homicide, and the risk of lethal violence is especially high in the case of female victims: 41\% of femicides, and 0.6\% of homicides committed in the year ending 2018 March were domestic abuse-related \cite{homic}.
-The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse.
-The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
 
@@
 para on implications (500 chars)
+Our work will have implications for the police and policy-makers.
+The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious cases, and times of the year when the number of reported cases is likely to be higher.
+Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood and  socio-economic outcomes in later life.
 

### 2019-07-17 JeS_fields.tex
Anna update

@@
 
-1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation.
+1) To utilise the detailed, rich information contained in the CSEW and
+
+2) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation.
 Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
@@
 
-2) To translate our research into impact by delivering applicable insights for the relevant agencies.
+3) To translate our research into impact by delivering applicable insights for the relevant agencies.
 Police (improving recording practices, understanding domestic abuse reporting demand characteristics over time for a better allocation of resources), government (temporal/geographical planning of targeted campaigns, intervention programmes), shelters (temporal/geographical allocation of resources), academia (publications)
@@
 
-\textit{I'm really bad at this. I don't really understand what should go in here}
-
-Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue.
-However, the true severity is still often underestimated, and hard to comprehend: in the year ending 2018 March, 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) have experienced some form of domestic abuse \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
-The long-lasting effect of domestic abuse are not limited to the direct target of abuse, as it can have severe developmental impacts on children witnessing the abuse.
-The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion \cite{costs}.
+Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue disproportionately affecting women.
+However, the true severity is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
+But the long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, it also has serious developmental implications for children witnessing the abuse.
+Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, reflecting the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
 
@@
 
-Despite the extent of the problem, there is relatively little academic research focusing on domestic abuse in the context of the UK, perhaps due to the lack of data sources.
-Using police data is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
-In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
+Despite the extent and severity of the problem, there is relatively little academic research focusing on domestic abuse in the context of the UK, perhaps due to the lack of reliable data sources.
+Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
+In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to understand domestic abuse.
+In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to explore the predictors of domestic abuse victimisation in England and Wales.
 
@@
 
-Our project takes advantage of the rich information contained in the CSEW, and draws on other data sources to characterise domestic abuse in England and Wales.
+Our project aims to fill this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
 We will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
-We will also explore whether there is any evidence that the police's response depend on the individual victim characteristics.
-We will quantify the causal effect of domestic abuse on the behavioural outcomes of child and the socio-economic outcomes of adult victims.
+We will also explore whether police mis-recording of domestic abuse-related crimes \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}  disproportionately affects certain victim groups.
+We will also quantify the short- and long-term causal effects of witnessing domestic abuse on behavioural outcomes in young adulthood (with particular focus on the propensity to engage in violent criminal behaviours) and socio-economic outcomes (educational attainment, income, mental and physical health and substance dependency) later in life.
 Finally, we will explore how alcohol consumption, spending on gambling, and changes in benefit receipts affect the prevalence of domestic abuse.
 
-para on implications (500 chars)
 Our work will have implications for the police and policy-makers.
-The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious cases, and times of the year when the number of reported cases is likely to be higher.
+The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious violence, and times of the year when the number of reported cases is likely to be higher.
 Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood and  socio-economic outcomes in later life.

### 2019-07-18 JeS_fields.tex
Anna update

@@
 \section{Objectives}
+
+%Objectives
+%
+%The objectives of the proposed project should be listed in order of priority and should be those that the Investigators would wish the Council to use as the basis for evaluation of work upon completion of any grant awarded.
+%
+%This field must be completed using:
+%
+%    No more than 4000 characters, including spaces, tabs and character returns (2 characters).
+%    Only the standard Je-S character set should be used.
+%    No specialist characters and symbols (e.g. mathematical symbols) because these may not transfer successfully to other computer systems.
+%    Please note that typing into a text box is not detectable by the system and is regarded as system inactivity. Please remember to save text regularly.
+%
+
 \textit{List the main objectives of the proposed research [up to 4000 chars]}
 
-1) To utilise the detailed, rich information contained in the CSEW and
-
-2) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation.
-Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
-While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.
-
-3) To translate our research into impact by delivering applicable insights for the relevant agencies.
-Police (improving recording practices, understanding domestic abuse reporting demand characteristics over time for a better allocation of resources), government (temporal/geographical planning of targeted campaigns, intervention programmes), shelters (temporal/geographical allocation of resources), academia (publications)
-
-\section{Summary}
-
-\textit{Describe the proposed research in simple terms in a way that could be publicised to a general audience [up to 4000 chars]}
-
-Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue disproportionately affecting women.
-However, the true severity is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
-But the long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, it also has serious developmental implications for children witnessing the abuse.
-Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, reflecting the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
-
-%Who are the people most vulnerable to becoming victims of domestic abuse?
+Who are the people most vulnerable to becoming victims of domestic abuse?
 To what extent do neighbourhood characteristics predict the prevalence of domestic abuse?
@@
 How do changes in alcohol consumption and financial stability affect the prevalence of domestic abuse?
+
+We have 3 core objectives.
+
+1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales as well as its consequences.
+Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
+While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.
+
+2) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
+Our results will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices.
+These insights will also help the government to design more effective intervention campaigns.
+
+3) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation.
+In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.
+
+\section{Summary}
+
+%Summary
+%
+%Note: This Summary will be published on publicly available sites should the project be funded. Please ensure confidential information is not included in this Summary.
+%
+%The Summary text box must be completed:
+%
+%    Maximum of 4000 characters (including spaces and returns).
+%
+%    Only the standard Je-S character set should be used.
+%
+%    No specialist characters and symbols (e.g. mathematical symbols) because these may not transfer successfully to other computer systems.
+%
+%The Summary is used for:
+%
+%    Sending to potential Peer reviewers to determine whether the proposal is within their field of expertise
+%
+%    To publicise the Councils research programmes to a variety of readers eg Opinion-formers and policy makers, the general public and the wider research community.
+%
+% Explain in plain English:
+%
+%    The context of the research.
+%
+%    Its aims and objectives.
+%
+%    Its potential applications and benefits.
+%
+%Please note that typing into a text box is not detectable by the system and is regarded as system inactivity. Please remember to save text regularly.
+
+\textit{Describe the proposed research in simple terms in a way that could be publicised to a general audience [up to 4000 chars]}
+
+Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue affecting the lives of people from all walks of life.
+However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
+But the long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, it also has serious developmental implications for children witnessing the abuse.
+Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, reflecting the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
 
@@
 Our project aims to fill this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
-We will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
+Using a wide range of statistical models (e.g., regression, random forest, propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
 We will also explore whether police mis-recording of domestic abuse-related crimes \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}  disproportionately affects certain victim groups.
-We will also quantify the short- and long-term causal effects of witnessing domestic abuse on behavioural outcomes in young adulthood (with particular focus on the propensity to engage in violent criminal behaviours) and socio-economic outcomes (educational attainment, income, mental and physical health and substance dependency) later in life.
+Furthermore, we will quantify the short- and long-term causal effects of witnessing domestic abuse on behavioural outcomes in young adulthood (with particular focus on the propensity to engage in violent criminal behaviours) and socio-economic and health-related outcomes in later life.
 Finally, we will explore how alcohol consumption, spending on gambling, and changes in benefit receipts affect the prevalence of domestic abuse.
 
-Our work will have implications for the police and policy-makers.
-The police will benefit from insights regarding the individual- and neighbourhood-level characteristics of particularly vulnerable victim groups (in terms of domestic abuse victimisation, reporting behaviour, and mis-recording of reported crimes), predictors of serious violence, and times of the year when the number of reported cases is likely to be higher.
-Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood and  socio-economic outcomes in later life.
+Our work will primarily have implications for the police and policy-makers.
+For example, insights about the predictors of serious harm can inform the police protocol aiming to prevent domestic homicides, while understanding the extent to which crime mis-recording depends on victim characteristics will help the police understanding the causes of mis-recording and improve their practices.
+Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, reporting behaviour, the extent to which gambling and alcohol spending affects it, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood and  socio-economic outcomes in later life.
 
@@
 
+Academic Beneficiaries
+
+%Please summarise how your proposed research will contribute to knowledge, both within the UK and globally.
+%
+%Academic Beneficiaries (4000 characters max) should address the following questions
+%
+%    how the research will benefit other researchers in the field
+%
+%    identify whether there are any academic beneficiaries in other disciplines and, if so, how they will benefit and what will be done to ensure that they benefit
+%
+%What other researchers, both within the UK and elsewhere are likely to be interested in or to benefit from the proposed research.
+%
+%Please look broadly beyond narrow research field.
+UKRI recognises that in generating new knowledge, a cross-disciplinary or single-disciplinary approach may be the most appropriate.
+Applicants are asked to clearly state their chosen approach and provide justification for that choice.
+%
+%List any academic beneficiaries from the research and give details of how they will benefit and how the results of the proposed research will be disseminated. Specific beneficiaries might be:
+%
+%    researchers in the investigator’s immediate professional circle, carrying out similar or related research
+%
+%    researchers in other disciplines
+%
+%    researchers in other academic institutions (in the UK and/or international)
+%
+%Also describe the relevance of the research to beneficiaries:
+%
+%    identify the potential academic impact of the proposed work
+%
+%    show how the research will benefit other researchers (this might include methodological or theoretical advances)
+%
+%    identify whether the research will produce data or materials of benefit to other researchers, and explain how these will be stored, maintained and made available
+%
+%    explain any collaboration with other researchers and their role in the project
+%
+%Note: The Academic Beneficiaries section may be published to demonstrate the impact of Research Council funded research.  Please ensure confidential information is not included in this section.
+
 \textit{Describe who will benefit from the research [up to 4000 chars].}
+
+Our results will benefit psychologists exploring the risk factors of domestic abuse victimisation by validating previous findings from qualitative investigations.
+
+health outcomes - consequences
+
+Understanding what affects reporting behaviour - behavioural scientists?
+
+economists - establishing the causal effect of domestic abuse victimisation/witnessing domestic abuse on well-being and other socio-economic outcomes
 
@@
 \section{Impact Summary }
+
+%Impact Summary
+%
+%Note: If the proposed research is funded the Impact Summary will be published on publicly available sites to demonstrate potential impact of Research Council funded research.
+Please ensure confidential information is not included in this Summary.
+%
+%The Summary text box must be completed:
+%
+%    · Maximum of 4000 characters (including spaces and returns)
+%
+%    · Only the standard Je-S character set should be used. See https://jes.rcuk.ac.uk/Handbook/pages/Generaldocumentactions/JeSstandardCharacterSet.htm.
+%
+%    · No specialist characters and symbols (e.g. mathematical symbols) because these may not transfer successfully to other computer systems.
+%
+%The Impact Summary should answer the two questions:
+%
+%    ·  Who might benefit from this research?
+%
+%    ·  How might they benefit from this research?
 

### 2019-07-18 JeS_fields.tex
Anna update

@@
 
-1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales as well as its consequences.
+1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales.
 Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
@@
 
-2) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
+2) To improve our understanding of the costs of domestic abuse, by investigating the causal effect of victimisation on a variety of socio-economic outcomes.
+Current cost estimates by the government do not take into account how educational attainment, income and employment status of victims are affected by victimisation and witnessing abuse as a child \cite{costs}.
+
+3) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
 Our results will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices.
@@
 
-3) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation.
+4) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation.
 In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.
@@
 
-health outcomes - consequences
-
 Understanding what affects reporting behaviour - behavioural scientists?
@@
 economists - establishing the causal effect of domestic abuse victimisation/witnessing domestic abuse on well-being and other socio-economic outcomes
+health outcomes - consequences
 
@@
 \textit{(please refer to the help for guidance on what to consider when completing this section) [up to 4000 chars]}
+
+1) characteristics of victims and understanding predictors of serious harm - police can use insights to prevent serious harm, characteristics of victims - expand on previous qualitative research (academics) and help policy-makers better target campaigns
+
+2) reporting behaviour and police mis-recording - police can improve recording practices, understanding reporting behaviour can benefit behavioural scientists who work for the government
+
+3) consequences - helps the government and academics by advancing our knowledge on the consequences of domestic abuse victimisation by improving the methodology of
 

### 2019-07-22 case_for_support_TM_hacked.tex
Anna update

@@
 In the most extreme cases, domestic abuse can culminate in domestic homicide: in the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, and 90\% of these victims were women \cite{homic}.
-Domestic abuse has substantial mental health implications not only for the direct target of abuse \cite{ferrari}, but also for children witnessing it \cite{callaghan}.
-The economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, taking into account various components including missed workdays, health care costs, and reduced quality fo life for survivors \cite{costs}.
+Domestic abuse has substantial mental health implications, which are not limited to the the direct target of abuse \cite{ferrari}, but can have a profound effect on the lives of children witnessing domestic abuse at home \cite{callaghan}.
+Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays, health care costs, and the reduced quality fo life for survivors \cite{costs}.
 
@@
 Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
-Third, we will examine the long-lasting effects of being a victim of domestic abuse or witnessing domestic abuse at home as a child.
-Finally, we explore the association between exogenous, time-varying factors, such as changes in alcohol consumption and financial resources, and the prevalence of domestic abuse.
+Third, we will attempt to quantify the long-term effects of being a victim of domestic abuse, and witnessing domestic abuse at home as a child.
+Finally, we explore the association between exogenous, time-varying factors, such as changes in alcohol consumption and financial resilience, and the prevalence of domestic abuse.
 
@@
 These two datasets have different merits.
-The CSEW provides us with rich demographic and socio-economic information on the respondent, and we can construct a control group from those individuals who have not experienced domestic abuse.
+The CSEW provides us with rich demographic and socio-economic information on the respondent, and to investigate the casual effects of domestic abuse victimisation, we can construct a control group from those individuals who have not experienced domestic abuse.
 However, it does not contain any information on the perpetrators, and has limited longitudinal information.
@@
 At no point will individual data be used, only geographic, LSOA level, aggregates.
-Finally, in analyses that rely on neighbourhood-level characteristics, we will use the Indices of Multiple Deprivation (IMD; \citeNP{IMD}).
+In addition, for analyses that rely on neighbourhood-level characteristics, we will use the Indices of Multiple Deprivation (IMD; \citeNP{IMD}).
 The IMD ranks all 32,844 LSOAs in the UK based on their relative deprivation on various domains, including income, employment, education, health, crime, housing and living environment, providing us with a complex descriptor of the socio-economic characteristics of each neighbourhood in the country.
@@
 Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household, earning in the lowest income bracket, having a long-term disability), based on descriptive statistics derived from the CSEW data \cite{ONS}.
-However, the CSEW provides a much broader range of information on the characteristics of the respondent, including number of children, ethnicity, education, benefit history, physical and mental health, frequency of going out, house and car ownership, self-reported well-being, and frequency of drug and alcohol use.
+However, the CSEW provides a much broader range of information on the characteristics of the respondent, including number of children, ethnicity, education, benefit history, physical and mental health, house and car ownership, self-reported well-being, substance abuse, and frequency of going out.
 
@@
 
-\TM{Do we know enough about random forest classification to be confident about it's appropriateness?
+%\TM{Do we know enough about random forest classification to be confident about it's appropriateness?
 Could an expert reviewer find a reason to complain about it or criticize it's use?
@@
 
- Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims. \AT{publication plan.}
+ Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
+\AT{publication plan.
+Journal of Interpersonal Violence.
+Trauma, Violence, \& Abuse.
+American Journal of Public Health.}
 
@@
 Lastly, these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
-\AT{publication plan.}
+\AT{publication plan. behavioural \& public policy journals?}
 
@@
 
- These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes. \AT{publication plan.}
+ These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
+\AT{publication plan.
+The Lancet Public Health.
+Annual Review of Public Health.
+American Journal of Public Health.}
 
@@
 Additionally, we will investigate how neighbourhood (LSOA) deprivation (measured by the IMD) affects the prevalence of domestic abuse and willingness to report, using a spatial regression framework.
-Using this statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
+This statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
 
@@
 Finally, we will explore the extent to which changes in alcohol consumption and financial stability on the community level predicts the prevalence of domestic abuse.
-We can identify external events that may affect these (e.g., festivals, weather, bank holidays, sport tournaments), and investigate whether it affects the number of reported domestic abuse incidents in that area in a given time period.
+We can identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and investigate how these affect the reported number of domestic abuse incidents in that area in a given time period.
 Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.
@@
 
-These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. \AT{publication plan.}
+These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
+\AT{publication plan.
+fancy behav journals?
+Nature Human Behaviour, PNAS}
 

### 2019-07-22 JeS_fields.tex
Anna update

@@
 How do changes in alcohol consumption and financial stability affect the prevalence of domestic abuse?
+In this research project, we will use a wide range of quantitative approaches, and various data sources to answer these questions.
 
@@
 1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales.
-Rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, providing a deeper understanding of the environments perpetuating domestic abuse.
-While we will only use UK data, these findings will likely to be relevant for researchers outside the UK.
+Through the rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales.
+While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.
 
-2) To improve our understanding of the costs of domestic abuse, by investigating the causal effect of victimisation on a variety of socio-economic outcomes.
+2) To improve our understanding of the costs of domestic abuse, by quantifying the causal effect of victimisation on a variety of socio-economic outcomes.
 Current cost estimates by the government do not take into account how educational attainment, income and employment status of victims are affected by victimisation and witnessing abuse as a child \cite{costs}.
+We will improve the precision of this calculation with the first, comprehensive UK-based exploration of the long-term effects of domestic abuse victimisation.
 
 3) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
-Our results will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices.
-These insights will also help the government to design more effective intervention campaigns.
+Our research will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices.
+In addition, these insights will also help the government to design more effective intervention campaigns, and will be of interest to a wide range of academics.
 
-4) To utilise the rich information contained in the CSEW to explore the predictors and consequences of domestic abuse victimisation.
+4) To utilise the rich information contained in the Crime Survey for England and Wales (CSEW) to explore the predictors and consequences of domestic abuse victimisation.
 In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.
+We aim to take full advantage of the wealth of information in the CSEW in understanding domestic abuse.
 
@@
 However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
-But the long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, it also has serious developmental implications for children witnessing the abuse.
-Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be \pounds 66 billion, reflecting the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
+The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse.
+Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which primarily reflects the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
 
@@
 Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
-In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
+In the UK, the most reliable source of data on domestic abuse is the CSEW, an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW (e.g., \citeNP{Khalifeh2013a}) to explore the predictors of domestic abuse victimisation in England and Wales.
+In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
 
@@
 
+%64 characters over the limit
+
 \section{Academic Beneficiaries}
-
-Academic Beneficiaries
 
@@
 
-Our results will benefit psychologists exploring the risk factors of domestic abuse victimisation by validating previous findings from qualitative investigations.
+Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, and health economics.
 
-Understanding what affects reporting behaviour - behavioural scientists?
+Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the  first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation.
+Previous investigations focusing on domestic abuse in the context of the UK have either used police records or relied on a small-sample, qualitative approach.
 
-economists - establishing the causal effect of domestic abuse victimisation/witnessing domestic abuse on well-being and other socio-economic outcomes
-health outcomes - consequences
+Behavioural researchers will benefit from our work exploring how exogenous, time-varying factors affect the willingness to report, and the causal effect of alcohol consumption and financial shocks on the prevalence of domestic abuse.
+These insights will be particularly important for behavioural researchers working for the UK government, owing to their policy-relevant nature.
+
+Health economists will be interested in our work on how direct or indirect domestic abuse victimisation affects socio-economic outcomes and physical and mental well-being in later life.
+These estimates will help us improve the precision of the estimated cost of domestic abuse in the UK.
 

### 2019-07-23 JeS_fields.tex
Staff Duties

@@
 Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
-In the UK, the most reliable source of data on domestic abuse is the CSEW, an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
+In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
@@
 
-Our project aims to fill this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
-Using a wide range of statistical models (e.g., regression, random forest, propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
+Our project fills this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
+Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
 We will also explore whether police mis-recording of domestic abuse-related crimes \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}  disproportionately affects certain victim groups.
@@
 
-%64 characters over the limit
+%64 characters over the limit - it will be different now (TM)
 
@@
 Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, and health economics.
+\TM{Do we want to mention criminologists as well or are we trying to avoid having them as reviewers?}
 
 Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation.
-Previous investigations focusing on domestic abuse in the context of the UK have either used police records or relied on a small-sample, qualitative approach.
+Previous investigations focusing on domestic abuse in the context of the UK have either used police records \TM{Aren't we relying on police records?
+Can we make it clearer why we have a particular strength over those previous approaches?} or relied on a small-sample, qualitative approach.
 
 Behavioural researchers will benefit from our work exploring how exogenous, time-varying factors affect the willingness to report, and the causal effect of alcohol consumption and financial shocks on the prevalence of domestic abuse.
-These insights will be particularly important for behavioural researchers working for the UK government, owing to their policy-relevant nature.
+These insights will be particularly important for behavioural researchers working for Behavioural Insights Teams and the UK government, owing to their policy-relevant nature.
 
@@
 \section{Staff Duties}
+
+As PI, Mullett will be responsible for coordinating the research.
+He will also act as the data controller for this project.
+Mullett has attained level three vetting with West Midlands Police, allowing him more comprehensive access to original police records, and he has the appropriate experience coordinating large datasets within projects.
+He will act as supervisor to the early career researcher Anna Trendl, ensuring that she can continue to build upon the impressive research capabilities she has already developed during her PhD.
+As a member of the Centre for Operational Policing Research (COPR), he will, in tandem with Prof Neil Stewart, liaise with West Midlands Police to ensure that the results are communicated back in the most effective and interpretable manner.
+This will maximise the impact that this research produces.
+
+As Co-I, Stewart's responsibilities will be to aid in coordinating the research program.
+He will also meet regularly with the early career researcher Anna Trendl, providing insights and support.
+A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities.
+This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research.
+
+As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers.
 

### 2019-07-23 JeS_fields.tex
Ethics

@@
 As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers.
+The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.
 
@@
 
+The primary ethical concerns in this project centre around data privacy and data security.
+In particular the data held in the West Midlands Police dataset is highly sensitive, and if it were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers.
+For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research.
+We will never link individuals across datasets, and our lab data plan is fully compliant with GDPR.
+
+As this research only involves secondary data analysis, concerns about possible harms during data collection are not relevant.
+However, in presenting the results, care will be taken to respect individuals who have been victims.
+
+One potential concern is the possibility of consuming police resources that are needed elsewhere.
+This is an ever present consideration within the Centre for Operational Policing Research.
+WMP have already outputted their data, and we have applied data cleaning to it ourselves.
+Therefore, we will make very minimal requests on police resources.
+Our primary cost upon staff time will be during feeding back our results to influence policy.
+There are structuers within the police force specifically designed for this, so by presenting our findings to those, we will actually increase WMP efficiency.
+
+Approval for this secondary data analysis will be attained from the University of Warwick's Humanities and Social Science Research Ethics Committee (HSSREC), as it has been for our previous work using WMP and other large datasets.
+
 \textit{Please explain what, if any, ethical issues you believe are relevant to the proposed research project, and which ethical approvals have been obtained, or will be sought if the project is funded?

### 2019-07-23 pathways_to_impact.tex
Pathways tinkering

@@
 
-We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior managment team: 1.
+We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior management team: 1.
 The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse.
 2.
-The programme on the  ``decision to report'' can link with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting.
+The programme on the  ``decision to report'' links with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting.
 3.
@@
 Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
-Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship.
+Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship and being able to make the decision to report an abuser.
 Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.
@@
 
-Impact summit (1 day at the Shard)
+Impact summit (1 day at the Shard) \TM{We haven't budgetted anything for this...}
 Visits to key charities
@@
 PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme.
-Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority.
+Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority, and in his research on predicting alcohol related crime or health crises.
 CI Stewart will also spend half of his time of the project on the impact activity.

### 2019-07-23 JeS_fields.tex
Pathways tinkering

@@
 
-Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, and health economics.
-\TM{Do we want to mention criminologists as well or are we trying to avoid having them as reviewers?}
+Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, criminology and health economics.
 
 Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation.
-Previous investigations focusing on domestic abuse in the context of the UK have either used police records \TM{Aren't we relying on police records?
-Can we make it clearer why we have a particular strength over those previous approaches?} or relied on a small-sample, qualitative approach.
+Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach.
+By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights.
 
@@
 These insights will be particularly important for behavioural researchers working for Behavioural Insights Teams and the UK government, owing to their policy-relevant nature.
+
+Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups.
 
@@
 As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers.
+She will also be deeply involved with impact related activity.
+As an early career researcher, it is crucial that she be given the opportunity to expand her network, and attain these new skills.
 The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.

### 2019-07-23 case_for_support_TM_hacked.tex

@@
  Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
-\AT{publication plan.
-Journal of Interpersonal Violence.
-Trauma, Violence, \& Abuse.
-American Journal of Public Health.}
+
+ \section{Publication Plan}
+
+ The insights from this section of work will result in a high impact journal paper focussing upon the social and interpersonal relationship patterns as well as demographic risk factors in domestic abuse.
+The target journals for this work are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquancy, and Personality and Social Psychology Bulletin.
+
+ \AT{publication plan. Journal of Interpersonal Violence. Trauma, Violence, \& Abuse. American Journal of Public Health.}
+
+ \TM{Social psychology or gender issues journals}
 
@@
 Lastly, these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
+
+\section{Publication Plan}
+
+We envisage two journal articles as a result of this work.
+One will focus upon the existing academic literature on decision making, and behaviour change, as this research will give unique insight into the process and factors that lead an individual to report.
+The target journals will be Nature Human Behaviour, and Psychological Science.
+The other paper will be more specifically focussed on the implications for policing, and this will be targetted towards the Journal of Research in Crime, and Criminology.
+
 \AT{publication plan. behavioural \& public policy journals?}
@@
  These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
-\AT{publication plan.
-The Lancet Public Health.
-Annual Review of Public Health.
-American Journal of Public Health.}
+
+ \section{Publication Plan}
+
+ \TM{Developmental Psychology Journals?}
+ \AT{publication plan. The Lancet Public Health. Annual Review of Public Health. American Journal of Public Health.}
 

### 2019-07-23 case_for_support_TM_hacked.tex
Anna update

--- 2019-07-22 case_for_support_TM_hacked.tex
@@
 Using a logistic regression approach with perpetrator-victim fixed effects (FE), we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
+Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
 
- Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
-\AT{publication plan.
-Journal of Interpersonal Violence.
-Trauma, Violence, \& Abuse.
-American Journal of Public Health.}
+ The findings from this work will result in a high impact journal paper focussing upon the social and interpersonal relationship patterns as well as socio-economic risk factors of domestic abuse victimisation.
+The target journals for this work are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquency, and Personality and Social Psychology Bulletin.
+\AT{most social psychology journals seem a bit too experimental for this}
+
+% \AT{publication plan. Journal of Interpersonal Violence. Trauma, Violence, \& Abuse. American Journal of Public Health.}
+
+% \TM{Social psychology or gender issues journals}
 
@@
 Lastly, these analyses can also be applied to examine the effect upon victim satisfaction with the police, and their perception of their personal security after reporting a crime.
-\AT{publication plan. behavioural \& public policy journals?}
+
+We envisage two journal articles as a result of this work.
+One will focus upon the existing academic literature on decision making, and behaviour change, as this research will give unique insight into the process and factors that lead an individual to report.
+The target journals will be Nature Human Behaviour, and Psychological Science.
+The other paper will be more specifically focussed on the implications for policing, and this will be targeted towards the Journal of Research in Crime and Delinquency, and Criminology.
+
+%\AT{publication plan. behavioural \& public policy journals?}
 

### 2019-07-23 case_for_support_TM_hacked.tex

@@
 \begin{document}
-\title{ESRC SDAI Application - Understanding domestic abuse using Big Data}
+\title{Understanding domestic abuse}
 \date{}
@@
 
+ \section{Publication Plan}
  These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
-
- \section{Publication Plan}
+The resulting paper will be targetted at The Lancet Public Health, and Social Science and Medicine.
 
@@
 
+\section{Publication Plan}
+
 These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
-\AT{publication plan.
-fancy behav journals?
-Nature Human Behaviour, PNAS}
+We envisage two articles.
+One will be focussed upon general behavioural theory and the effect of the environment.
+This will be targetted towards Nature Human Behaviour, and PNAS.
+THe other article will focus upon the impications for criminology and policing.
+The target journal will be Criminology.
+
+ \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}
 

### 2019-07-23 JeS_fields.tex

@@
 
-Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, criminology and health economics.
+Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural science, criminology and health economics.
 
-Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation.
+Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first comprehensive, quantitative UK-based investigation of the individual and environmental predictors of domestic abuse victimisation.
 Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach.

### 2019-07-23 case_for_support_TM_hacked.tex
Anna update

--- 2019-07-23 case_for_support_TM_hacked.tex
@@
 
- The findings from this work will result in a high impact journal paper focussing upon the social and interpersonal relationship patterns as well as socio-economic risk factors of domestic abuse victimisation.
-The target journals for this work are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquency, and Personality and Social Psychology Bulletin.
-\AT{most social psychology journals seem a bit too experimental for this}
+ The findings from this work will result in high impact journal papers focussing upon the socio-economic risk factors of domestic abuse victimisation and the social and interpersonal relationship patterns predicting serious harm.
+The target journals for these works are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquency, and Personality and Social Psychology Bulletin.
 
@@
  These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
+The resulting paper will be targeted at The Lancet Public Health, and Social Science and Medicine.
 
- \section{Publication Plan}
-
- \TM{Developmental Psychology Journals?}
- \AT{publication plan. The Lancet Public Health. Annual Review of Public Health. American Journal of Public Health.}
+% \TM{Developmental Psychology Journals?}
+% \AT{publication plan. The Lancet Public Health. Annual Review of Public Health. American Journal of Public Health.}
 
@@
 These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
-\AT{publication plan.
-fancy behav journals?
-Nature Human Behaviour, PNAS}
+We envisage two articles.
+One will be focussed upon general behavioural theory and the effect of the environment.
+This will be targeted towards Nature Human Behaviour, and Proceedings of the National Acedemy of Sciences.
+The other article will focus upon the implications for criminology and policing.
+The target journal will be Criminology.
+
+% \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}
 

### 2019-07-23 JeS_fields.tex
wmp summary and minor edits

@@
 
-We have 3 core objectives.
+We have 4 core objectives.
 
 1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales.
-Through the rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales.
+Through the rigorous validation of insights from existing, mostly quantitative investigations using a UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales.
 While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.

### 2019-07-23 WMP_Summary.tex
wmp summary and minor edits

This project will use existing datasets from West Midlands Police (WMP), and the Crime Survey for England and Wales (CSEW) to investigate a number of aspects of domestic abuse.

Despite the extent and severity of resultant suffering, there is relatively little academic research focusing on domestic abuse in the context of the UK. Perhaps due to the lack of reliable data sources. Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise. In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.  While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature. In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).

Our project fills this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, the breadth and longevity of the WMP data, and supplementary metrics provided by a large UK bank. Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, and propensity score matching), allows us to provide insights in 4 main areas:
1) Exploring the characteristics of survivors and the predictors of serious harm: Improving our understanding of risk factors for victims, and victims likely to be in most serious danger.
2) Understanding the decision to report and police mis-recording of domestic abuse: Improving our understanding of what events and properties of the victim’s profile/environment encourage the decision to report ongoing abuse. In addition, impriving our understanding of the types of victims or cases, which are at risk of being misidentified, or not given appropriate resources after a report has been made.
3) The long-lasting effects of domestic abuse: Understanding what are the long term effects on children who witness domestic abuse. What effect does this have on their long term outcomes, and propensity to commit crime as adults.
4) Environmental factors influencing the prevalence of domestic abuse: What properties of the local environment and community predict the prevalence for different forms of domestic abuse. Here we will make use of data from a large UK bank to build a geographical measure for the levels of spending on gambling and alcohol in a given area (LSOA). We will also use this to build a measure for financial distress, specifically looking at the effect of changes in benefits such as the rollout of universal credit

### 2019-07-23 JeS_fields.tex
Anna update

--- 2019-07-23 JeS_fields.tex
@@
 What predicts serious harm and victims' decision to finally report the abuse?
-What is the quantifiable, long-term impact of domestic abuse victimisation, or witnessing domestic abuse as a child on socio-economic outcomes in later life?
+What is the quantifiable, long-term impact of domestic abuse victimisation, or witnessing domestic abuse as a child on socio-economic and health outcomes in later life?
 How do changes in alcohol consumption and financial stability affect the prevalence of domestic abuse?
-In this research project, we will use a wide range of quantitative approaches, and various data sources to answer these questions.
+In this research project, we will address these questions using a wide range of quantitative approaches and various data sources.
 
@@
 1) To conduct the first large-scale, quantitative exploration of the individual- and neighbourhood-level risk factors of domestic abuse victimisation in England and Wales.
-Through the rigorous validation of insights from existing, mostly quantitative investigations using an UK-wide dataset, we will provide a deeper understanding of the environments perpetuating domestic abuse in England and Wales.
+By validating insights from previous, mostly qualitative investigations, we will provide a deeper understanding of the socio-economic factors and their interactions in perpetuating domestic abuse in England and Wales.
 While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.

### 2019-07-23 JeS_fields.tex
Minor typos in summary

@@
 
-We have 3 core objectives.
+We have 4 core objectives.
 
@@
 Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue affecting the lives of people from all walks of life.
-However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
-The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse.
+However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported experiencing some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
+The long-lasting, damaging effects of domestic abuse are not limited to the direct victim of abuse, but also has serious developmental implications for children witnessing the abuse.
 Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which primarily reflects the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.

### 2019-07-23 JeS_fields.tex
Anna update

--- 2019-07-23 JeS_fields.tex
@@
 Concern about domestic abuse is widespread, and it is rightly identified as a serious societal issue affecting the lives of people from all walks of life.
-However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in the same period were victims of domestic homicide.
+However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in this period were victims of domestic homicide.
 The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse.
-Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which primarily reflects the cost of missed work days, health costs, and the reduced quality of life for survivors \cite{costs}.
+Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion \cite{costs}.
 
@@
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
+Despite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
 
@@
 Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
-We will also explore whether police mis-recording of domestic abuse-related crimes \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}  disproportionately affects certain victim groups.
+We will also explore whether police mis-recording of domestic abuse-related crimes disproportionately affects certain victim groups.
 Furthermore, we will quantify the short- and long-term causal effects of witnessing domestic abuse on behavioural outcomes in young adulthood (with particular focus on the propensity to engage in violent criminal behaviours) and socio-economic and health-related outcomes in later life.

### 2019-07-23 WMP_Summary.tex

@@
-This project will use existing datasets from West Midlands Police (WMP), and the Crime Survey for England and Wales (CSEW) to investigate a number of aspects of domestic abuse.
+This project will use existing datasets from West Midlands Police (WMP) and the Crime Survey for England and Wales (CSEW) to investigate a number of aspects of domestic abuse.
 
-Despite the extent and severity of resultant suffering, there is relatively little academic research focusing on domestic abuse in the context of the UK.
-Perhaps due to the lack of reliable data sources.
+Despite the extent and severity of resultant suffering, there is relatively little academic research focusing on domestic abuse in the context of the UK, perhaps due to the lack of reliable data sources.
 Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
-In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse \cite{OfficeforNationalStatistics2019}.
+In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse.
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-In spite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
+Despite the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales.
 
 Our project fills this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, the breadth and longevity of the WMP data, and supplementary metrics provided by a large UK bank.
-Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, and propensity score matching), allows us to provide insights in 4 main areas:
-1) Exploring the characteristics of survivors and the predictors of serious harm: Improving our understanding of risk factors for victims, and victims likely to be in most serious danger.
-2) Understanding the decision to report and police mis-recording of domestic abuse: Improving our understanding of what events and properties of the victim’s profile/environment encourage the decision to report ongoing abuse.
-In addition, impriving our understanding of the types of victims or cases, which are at risk of being misidentified, or not given appropriate resources after a report has been made.
-3) The long-lasting effects of domestic abuse: Understanding what are the long term effects on children who witness domestic abuse.
-What effect does this have on their long term outcomes, and propensity to commit crime as adults.
+Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, and propensity score matching), allows us to provide insights in four main areas:
+
+1) Exploring the characteristics of survivors and the predictors of serious harm: We will improve our understanding of risk factors for victims, and victims likely to be in most serious danger.
+
+2) Understanding the decision to report and police mis-recording of domestic abuse: We will improve our understanding of which events and properties of the victim’s profile/environment encourage the decision to report ongoing abuse.
+In addition, we will improve our understanding of the types of victims or cases which are at risk of being misidentified, or not given appropriate resources after a report has been made.
+
+3) The long-lasting effects of domestic abuse: We will quantify the long term effects on children who witness domestic abuse.
+For example, what effect does witnessing abuse have on the children's long term outcomes, and propensity to commit crime as adults.
+
 4) Environmental factors influencing the prevalence of domestic abuse: What properties of the local environment and community predict the prevalence for different forms of domestic abuse.
 Here we will make use of data from a large UK bank to build a geographical measure for the levels of spending on gambling and alcohol in a given area (LSOA).
-We will also use this to build a measure for financial distress, specifically looking at the effect of changes in benefits such as the rollout of universal credit
+We will also use this to build a measure for financial distress, specifically looking at the effect of changes in benefits such as the roll out of Universal Credit.

### 2019-07-23 briefing_for_WMP.tex

--- 2019-07-23 WMP_Summary.tex
@@
+\documentclass[11pt, a4paper]{article}
+
+% Helvetica
+\usepackage[scaled]{helvet}
+\renewcommand\familydefault{\sfdefault}
+\usepackage[T1]{fontenc}
+
+% 2cm margins
+\usepackage[margin=2cm]{geometry}
+\usepackage[parfill]{parskip}
+
+\begin{document}
+\title{Understanding domestic abuse\\Briefing for WMP}
+\author{Tim Mullett, Anna Trendl, Neil Stewart}
+\date{}
+\maketitle
+
 This project will use existing datasets from West Midlands Police (WMP) and the Crime Survey for England and Wales (CSEW) to investigate a number of aspects of domestic abuse.
@@
 Despite the extent and severity of resultant suffering, there is relatively little academic research focusing on domestic abuse in the context of the UK, perhaps due to the lack of reliable data sources.
-Using police data to understand domestic abuse is problematic due to the vast levels of underreporting, while insights from qualitative approaches are hard to generalise.
+Using police data to understand domestic abuse is problematic due to the high levels of underreporting, while insights from qualitative approaches are hard to generalise.
 In the UK, the most reliable source of data on domestic abuse is the Crime Survey for England and Wales (CSEW), an annual, cross-sectional representative survey collecting information on socio-economic characteristics as well as experiences of domestic abuse.
@@
 
-2) Understanding the decision to report and police mis-recording of domestic abuse: We will improve our understanding of which events and properties of the victim’s profile/environment encourage the decision to report ongoing abuse.
+2) Understanding the decision to report and police mis-recording of domestic abuse: We will improve our understanding of which events and properties of the victim's profile/environment encourage the decision to report ongoing abuse.
 In addition, we will improve our understanding of the types of victims or cases which are at risk of being misidentified, or not given appropriate resources after a report has been made.
@@
 3) The long-lasting effects of domestic abuse: We will quantify the long term effects on children who witness domestic abuse.
-For example, what effect does witnessing abuse have on the children's long term outcomes, and propensity to commit crime as adults.
+For example, what effect does witnessing abuse have on the children's long term outcomes, and propensity to commit crime as adults?
 
-4) Environmental factors influencing the prevalence of domestic abuse: What properties of the local environment and community predict the prevalence for different forms of domestic abuse.
+4) Environmental factors influencing the prevalence of domestic abuse: What properties of the local environment and community predict the  different forms of domestic abuse.
 Here we will make use of data from a large UK bank to build a geographical measure for the levels of spending on gambling and alcohol in a given area (LSOA).
-We will also use this to build a measure for financial distress, specifically looking at the effect of changes in benefits such as the roll out of Universal Credit.
+We will also build a measure for financial distress, specifically looking at the effect of changes in benefits such as the roll out of Universal Credit.
+
+\end{document}

### 2019-07-23 pathways_to_impact.tex

@@
-See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.
+\documentclass[11pt, a4paper]{article}
+
+% Helvetica
+\usepackage[scaled]{helvet}
+\renewcommand\familydefault{\sfdefault} 
+\usepackage[T1]{fontenc}
+
+% 2cm margins
+\usepackage[margin=2cm]{geometry}
+
+\usepackage{graphicx}
+\usepackage{xcolor}
+\usepackage[center]{caption}
+\usepackage{hyperref}
+\usepackage{placeins}
+\usepackage{booktabs}
+\usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+\usepackage{threeparttable}
+%\newcolumntype{L}{>{\centering\arraybackslash}m{3cm}}
+
+\usepackage{apacite} 
+%\usepackage{setspace}
+%\doublespacing
+
+\definecolor{green}{rgb}{0,1,0}
+\newcommand{\NS}[1] {{\textcolor{green}{#1}}}
+\newcommand{\TM}[1] {{\textcolor{orange}{#1}}}
+\newcommand{\AT}[1] {{\textcolor{blue}{#1}}}
+
+\begin{document}
+\title{Understanding domestic abuse}
+\date{}
+\maketitle
+
+%See the section https://je-s.rcuk.ac.uk/Handbook/Index.htm#pages/GuidanceonCompletingaStandardG/CaseforSupportandAttachments/ESRCSpecificRequirements.htm on Pathways to Impact for ESRC.
 
@@
 
-At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015.
-(https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
-(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf) We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
+At the College of Policing (situated just a few miles from Warwick campus) we will work within the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
+(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{framework of the Authorised Professional Practice on domestic abuse}, released in 2015.
+We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
 
@@
 officer. We will use feedback to shape the further development of the research.
+\newpage
+
+\bibliographystyle{apacite}
+\bibliography{domesticabuse_refs}
+
+\end{document}

### 2019-07-23 JeS_fields.tex
jesp fields to look at: academic benef,impact sum

@@
 
+\textit{Summarise the roles and responsibilities of each post for which funding is sought [up to 2000 characters]}
+
 As PI, Mullett will be responsible for coordinating the research.
@@
 Mullett has attained level three vetting with West Midlands Police, allowing him more comprehensive access to original police records, and he has the appropriate experience coordinating large datasets within projects.
-He will act as supervisor to the early career researcher Anna Trendl, ensuring that she can continue to build upon the impressive research capabilities she has already developed during her PhD.
+He will act as supervisor to the early career researcher Anna Trendl, ensuring that she can continue to build upon the research capabilities she has already developed during her PhD.
 As a member of the Centre for Operational Policing Research (COPR), he will, in tandem with Prof Neil Stewart, liaise with West Midlands Police to ensure that the results are communicated back in the most effective and interpretable manner.
@@
 The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.
-
-\textit{Summarise the roles and responsibilities of each post for which funding is sought [up to 2000 characters]}
 
@@
 
+\textit{Please explain what, if any, ethical issues you believe are relevant to the proposed research project, and which ethical approvals have been obtained, or will be sought if the project is funded?
+If you believe that an ethics review is not necessary, please explain your view (available: 4000 characters)}
+
 The primary ethical concerns in this project centre around data privacy and data security.
@@
 Approval for this secondary data analysis will be attained from the University of Warwick's Humanities and Social Science Research Ethics Committee (HSSREC), as it has been for our previous work using WMP and other large datasets.
-
-\textit{Please explain what, if any, ethical issues you believe are relevant to the proposed research project, and which ethical approvals have been obtained, or will be sought if the project is funded?
-If you believe that an ethics review is not necessary, please explain your view (available: 4000 characters)}
 

### 2019-07-23 JeS_fields.tex
Impact summary update

@@
 
+Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety.
+We aim to do so by working together other stakeholders, including the police, charities, and the government.
+
+Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase trust, and willingness to report future incidents.
+
+victims of domestic abuse more liekly to report and less likely to be seriously harmed, children, police, policymaker - evidence base, charity
+
 1) characteristics of victims and understanding predictors of serious harm - police can use insights to prevent serious harm, characteristics of victims - expand on previous qualitative research (academics) and help policy-makers better target campaigns

### 2019-07-23 JeS_fields.tex
Impact summary update

@@
 
-Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase trust, and willingness to report future incidents.
+For charities and the government, insights from our research (risk factors of ) will provide useful information for the most effective targeting (geographical and temporal) of domestic abuse awareness campaigns.
+
+ will benefit from a comprehensive investigation of a wide range of risk factors of domestic abuse victimisation.
+
+Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase their trust, and willingness to report future incidents.
+The police will also benefit from a deeper understanding of the factors governing reporting behaviour, its temporal characteristics throughout the year, and this knowledge will allow for an improved allocation of scarce police resources.
+Our research on the predictors of serious harm will help design better interventions.
 

### 2019-07-23 pathways_to_impact.tex
Pathways to Impact TM

--- 2019-07-17 pathways_to_impact.tex
@@
 
-We will work with researchers at the College of Policing, the Behavioural Insights Team at West Midlands Police,
+Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP) , and the college of policing.
+These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.
 
-Our day-to-day contact at West Midlands Police is Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning).
-Our day-to-day contact at the West Midlands Police and Crime Commissioner's Office is Alison Spence.
+The research proposed here has been developed with direct input from officers and experts within WMP.
+This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accellerate the dissemination of findings, and changes in policy.
+To facilitate this, we have a day-to-day contact at West Midlands Police: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office: Alison Spence.
+As aresult of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.
 
-At the level of the National Police Chiefs' Council we will work with Deputy Chief Constable Louisa Rolfe who is the lead for domestic abuse.
+These relationships will enable us to work with West Midlands Police to import the insight from the research into their senior management team and also their day-to-day processes.
+This will be possible for each of the objectives and topics within our proposal:
 
-In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
-We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
-The summit will be a 50/50 academic / practitioner mix.
-We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+1.
+The programme on ``predictors of serious harm'' will inform refinement of the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, prevention and intervention) risk assessment model used for assessing calls and reports of domestic abuse.
+It will also provide a more general evidence base to help police develop policy.
 
-We will work with West Midlands Police to import the insight from the research into their day-to-day processes and also to their senior managment team: 1.
-The programme on ``predictors of serious harm'' into the THRIVE+ (threat, harm, risk, investigation, vulnerability, engagement, pervention and intervention) risk assessment model used for assessing calls and reports of domestic abuse.
 2.
-The programme on the  ``decision to report'' can link with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse) and ``police mis-recording of abuse'', which is of direct interest to their data quality and reporting.
+The programme on the  ``decision to report'' links with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse).
+It will also help the police to develop more efficient and targetted intervention and awareness campaigns.
+
 3.
-The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands,
+The programme on ``police mis-recording of abuse'', is of direct interest to their data quality and reporting, as well as identifying any potential shortcomings in the way they deal with reports from particular types of victims.
 
+4.
+The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands.
+It can also give clues as to likely triggering events, such as economic shocks, or changes to benefits, and large events such as sports championships.
+
+In addition to workign with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact accross all forces.
 At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015.
@@
 
-Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability.
-Warwick already has a relation with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
-Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship.
-Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.
-We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.
+We will meet regularly with our contacts at WMP and the college of policing througout the grant.
+This will enable us to adapt to current questions that arise during the period of the proposal.
+It also allows us to react quickly to any unaticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes.
+It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.
 
-Events:
-
-Impact summit (1 day at the Shard)
-Visits to key charities
-Visits to West Midlands Police
-Presentation to NPCC
-Data sprint session with WMP Behavioural Insights Team?
+In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
+This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Accelleration Account.
+We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
+The summit will be a 50/50 academic / practitioner mix.
+We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
 
@@
 
+Within Lloyds Bank, we will work with Martin King, Head of Customer Vulnerability.
+Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
+Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship and being able to make the decision to report an abuser.
+Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.
+We will present the findings from all four programmes to the Lloyds Vulnerability Team in six-monthly briefings, and work to integrate insight from the research into the Lloyds environment.
+
+%Events:
+
+%Impact summit (1 day at the Shard) \TM{We haven't budgetted anything for this...}
+%Visits to key charities
+%Visits to West Midlands Police
+%Presentation to NPCC
+%Data sprint session with WMP Behavioural Insights Team?
+
 PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme.
@@
 Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association.
-Postdoc Trendl will be fully involved in the impact programme, and this is also an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.
-Trendl will spend one third of her time on the programme on the impact activities.
+Postdoc Trendl will be fully involved in the impact programme.
+This is an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.
 
-We will apply to the Warwick ESRC Impact Acceleration Fund and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.
+We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.
 

### 2019-07-23 justification_of_resources.tex

@@
 Caltech. Caltech is the home of Camerer and Rangel labs, leaders in eye tracking economics.
+
+From machine learned personality grant:
+
+Justification of Resources
+Staff, Directly Incurred Posts
+Personality Psychology PDRA Skatova.
+We request 100% 36 months support for PDRA Skatova.
+A postdoctoral appointment is essential because the position requires high level of technical skills with psychometric approaches, as well as an advanced knowledge of the personality literature.
+The project is on the intersection of psychology and computer science, and thus experience across economics, computer science, and psychology that Skatova has will be essential.
+Further, experience translating output to industry, and experience of working with industry partners is essential.
+As outlined in Staff Duties, Skatova will design analyses with the investigators, and lead on the writing of publications.
+Skatova will implement the statistical analysis using the R programming language.
+Skatova will lead on contacts with industry partners (particularly Boots, Tesco and Barclays) and public policy collaborators (particularly the BIT and Which?).
+PDRA Computer Scientist.
+We request 100% 36 months support for a PDRA in the domains of data science, computer science, or machine learning.
+Postdoctoral experience of advanced algorithms and management of very large data sets is essential.
+The PDRA will lead on the writing of publications.
+The PDRA will supervise the management of data.
+The PDRA will develop the ML Personality Toolbox.
+Both PDRAs will be involved in the Pathways to Impact demonstrators and workshops.
+Lab manager.
+We request 10% 36 months support for a lab manager to support communication between the project team and project partners, implementing Data Management Plan as well as organization of Pathway to Impacts events including the workshops, MOOC and other public dissemination.
+Staff, Directly Allocated Posts
+PI Stewart.
+We request 20% 36 months support for psychologist Stewart.
+10%, half of this support, will be spent on the scientific programme, designing analyses of the data with the PDRA.
+Stewart has significant experience working with very large data sets, including financial transactions and police records.
+The other 10% is required for the ambitious impact work, which requires professorial level standing and extensive liaisons with the collaborators.
+Stewart will lead on contacts with the credit card industry and UBS.
+Stewart will oversee the second and third impact demonstrator.
+CI Goulding.
+We request 15% 36 months support for Goulding.
+10% of this support will be spent integrating personality concepts with the development of machine learning algorithms for very sparse transaction data.
+The other 5% support is required for the impact work.
+Goulding will oversee the first impact demonstrator.
+CI Chater.
+We request 10% 36 months support for Chater.
+Chater has extensive experience in mathematical psychology and the application to broad, domain-general principles of cognition.
+Chater also has significant experience in applying behavioural science to consumer behaviour as a director of Decision Technology.
+Finally Chater has led the “Mind is Flat” MOOC, one of Europe’s largest online courses, now in its fifth year and will supervise setting the MOOC for this project (see Pathways to Impact).
+Other Directly Incurred Costs
+Computer resources.
+We request support for (University non-standard) PCs.
+These require encrypted 6 TB HDDs to store the retail data, and enough RAM (64 GB) to run analyses without swapping to the HDD.
+The OS will be hosted on modest SSDs.
+Only typical desktop CPUs are required (e.g., Intel 8-core i7-4770), with only standard graphics.
+A non-standard PC is required for Psychology PDRA at £1,600; and a specialist PC is required for CS PDRA at £2,484 with a larger SSD and a second processor to deliver enough threads for the machine learning algorithms.
+Since the project requires coordinating collaborators and project partners in various places across the country and well as geographically distributed Pathways to Impact activities, we request a laptops for Warwick Psychology PDRA who will be in charge with coordinating all partner activities to fulfil project plan, at £1,400.
+Cost of MOOC. We seek resources to develop a “Personality Data Science” MOOC: £10,000.  
+Impact Workshops. We request support for four full one-day workshops, 20 people each at Shard, London.  
+Travel and Subsistence.
+We seek the costs of travel between Warwick and Nottingham (75 trips over 5 investigators and 36 months) for project meetings between UoN and UoW investigators, as well as project partners who are based in Nottingham (Boots, Nutracheck), travel between Warwick and London to meet with project partners and for workshops (55 trips over 3 investigators and 36 months), travel between Nottingham and London to meet with project partners and for the workshops (48 trips, 2 investigators and 4 project partners from Nottingham, over 36 months).
+We also request cost for longer stay of Warwick PDRA in Nottingham to develop ML personality approaches with UoN CI and PDRA, and vice versa: travel and subsistence for 8 trips 2 weeks each Warwick to Nottingham for Warwick PDRA, and travel and subsistence for 8 trips 2 weeks each Nottingham to Warwick for Nottingham PDRA.
+Conferences.
+4 CS conferences (2 UK, 2 europe, 2 overseas); 5 Psychology and Behavioural Science conferences (1 UK, 2 Europe, 3 overseas), 7 business science conference (2 UK, 3 Europe, 3 overseas) between 5 investigators.

### 2019-07-23 pathways_to_impact.tex

@@
 It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.
+
+At the College of Policing (situated just a few miles from Warwick campus) we will work within the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
+(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{framework of the Authorised Professional Practice on domestic abuse}, released in 2015.
+We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
 

### 2019-07-23 pathways_to_impact.tex
pathways to impact

@@
 In addition to workign with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact accross all forces.
-At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the Authorised Professional Practice on domestic abuse, released in 2015.
-(https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
-(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf) We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
+At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
+(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{Authorised Professional Practice} on domestic abuse, released in 2015.
+We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
 
@@
 It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.
-
-At the College of Policing (situated just a few miles from Warwick campus) we will work within the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
-(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{framework of the Authorised Professional Practice on domestic abuse}, released in 2015.
-We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
 
@@
 In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts.
-We will submit these reports to the College of Police What Works database and log them on the Research Map (https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx)
+We will submit these reports to the College of Police What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.
 

### 2019-07-23 JeS_fields.tex
Anna update

@@
 
-Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety.
-We aim to do so by working together other stakeholders, including the police, charities, and the government.
+Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse.
+We aim to do so by expanding the knowledge of other stakeholders, including the police, charities, and the government.
 

### 2019-07-23 pathways_to_impact.tex
Anna update

@@
 The research proposed here has been developed with direct input from officers and experts within WMP.
-This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accellerate the dissemination of findings, and changes in policy.
-To facilitate this, we have a day-to-day contact at West Midlands Police: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office: Alison Spence.
-As aresult of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.
+This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy.
+To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office, Alison Spence.
+As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.
 
-These relationships will enable us to work with West Midlands Police to import the insight from the research into their senior management team and also their day-to-day processes.
+These relationships will enable us to work with WMP to import the insight from the research into their senior management team and also their day-to-day processes.
 This will be possible for each of the objectives and topics within our proposal:
@@
 2.
-The programme on the  ``decision to report'' links with police's design of the inital contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse).
-It will also help the police to develop more efficient and targetted intervention and awareness campaigns.
+The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse).
+It will also help the police to develop more efficient and targeted intervention and awareness campaigns.
 
@@
 4.
-The programme on ``envionmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands.
+The programme on ``environmental factors influencing abuse'' can be used to help predict which local populations are most at risk of abuse in the West Midlands.
 It can also give clues as to likely triggering events, such as economic shocks, or changes to benefits, and large events such as sports championships.
 
-In addition to workign with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact accross all forces.
+In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact across all forces.
 At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
@@
 
-We will meet regularly with our contacts at WMP and the college of policing througout the grant.
+We will meet regularly with our contacts at WMP and the college of policing throughout the grant.
 This will enable us to adapt to current questions that arise during the period of the proposal.
-It also allows us to react quickly to any unaticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes.
+It also allows us to react quickly to any unanticipated issues that arise as a result of our findings, such as following up on unexpected results to identify underlying causes.
 It also ensures that there is an ongoing dialogue about the data being used, and provides an opportunity to alert the police to any data quality issues.
@@
 In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
-This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Accelleration Account.
+This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account.
 We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
 The summit will be a 50/50 academic / practitioner mix.
-We will contact, early in the project, [Insert list of charities in this sector] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+We will contact, early in the project, [Insert list of charities in this sector, Women's Aid, Refuge, Safe Lives, National Centre for Domestic Abuse] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
 
@@
 Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
-Key issues here are work on coercion and control, and having sufficient financial resiliance to escape an abusive relationship and being able to make the decision to report an abuser.
+Key issues here are work on coercion and control, and having sufficient financial resilience to escape an abusive relationship and being able to make the decision to report an abuser.
 Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.

### 2019-07-23 pathways_to_impact.tex
pathways to impact

@@
 \begin{document}
-\title{Understanding domestic abuse}
+\title{Understanding domestic abuse - Pathways to Impact}
 \date{}
@@
 
-\section{Old Accumulating to Choose Pathways to Impact}
-
-Pathways to Impact
-We will target those in industry and public policy with interest in economic decision making.
-While the focus of this programme is on informing micro-level theory of economic choice,
-we will develop the implications for regulation and for the competitiveness of UK financial
-industry. Our strategy will be to translate the laboratory work detailed in the Case for Support
-into the field with a series of randomised control trials, detailed below. To deliver significant
-impact it is essential for us to bridge the divide from the laboratory by working on live
-problems for the regulator and industry using real consumers making real decisions.
-Since their inception in 2012 the Financial Conduct Authority (the UK regulator for all
-financial products, like savings accounts, pensions, mortgages, credit cards, and insurance)
-have placed significant emphasis on behavioural regulation. This includes “...getting a better
-understanding of why consumers act in the way they do, so we can adapt our regulation to
-their [consumers’] common behavioural traits” (Martin Wheatley, outgoing Chief Executive,
-FCA). Indeed, the first publication from the FCA made the case for using behavioural
-economics in regulation (Erta, Hunt, Iscenko, Brambley, 2013). Recently Stewart has worked
-closely with the new Behavioural Economics and Data Science Team at the FCA, led by Dr
-Stefan Hunt, on the psychology of structured deposits (Hunt, Stewart, \& Zaliauskas, 2015).
-The FCA are at the beginning of a project on the complexity of financial products. The
-pathway to impact within the FCA will be via regular meetings between members of the FCA
-Behavioural and Data Science Team, and Stewart and Mullett (most recently in August 2015).
-Ultimately, as the data will drive public policy change regarding presentation and advertising
-of financial products, with the creation of regulations grounded in behavioural science. The
-outcome of this engagement will be the design of randomised control trials in collaboration
-with the FCA and a customer-facing financial services provider using real consumers making
-real decisions. Dissemination via the FCA working paper series will have more significant
-reach than academic publication alone. Please see the letter of support from the Financial
-Conduct Authority.
-Warwick has a formal collaboration with the consumer group Which?, and Stewart has
-worked closely with Alex Chesterfield, Head of Behavioural Insights, and team members
-Sam Himmelweit, Harriet Patterson, and Phillida Cheetham. The formal collaboration covers
-data sharing, exploitation, and publication rights, etc., and we have several existing and
-completed projects (e.g., on credit card repayment behaviour and expectant mums’ birth
-choices). Early insights from this work will feed into Which?’s project on the complexity of
-financial products. They key route will be the monthly joint meetings between Warwick and
-Which? Please see the letter of support from Which? Again, we would seek to implement
-insight from these grants in a practical financial decision domain as part of Which?’s
-consumer testing programme, and thus we will identify a practical application of the drift
-diffusion model to a consumer choice of value to which and implement a field trial. Likely
-candidates are: (a) the development of product information sheets for mortgages, savings
-accounts, pensions, etc., within the context of providing behavioural nudges, and (b)
-information provision for telecoms choices.
-The UK Cards Association is the industry body for all credit card providers in the UK.
-Stewart (and Gathergood, Economist, Nottingham) have a significant existing collaboration,
-with the sharing of millions of credit card statements between about 10 of the largest card
-companies and Warwick and Nottingham Universities. Contacts are Paul McCarron, Head of
-Cards and Fraud Control, and Richard Koch, Head of Policy. Stewart contributed evidence to
-the 2009 White Paper reviewing of the credit industry. Of key interest is (a) consumers’
-
-decisions around credit card repayments, and their integration of information from monthly
-statements and (b) consumers choice of card during switching and how cards are evaluated.
-The former fits well with the evaluation work; the latter fits well with the choice work.
-Dissemination of research findings will be via presentation to the Current Affairs working
-group, with representatives from every UK card provider.
-We will also work closely with the Economic and Social Research Institute, an independent
-research institute funded mainly by the Irish Government. Our key contact is Dr Peter Lunn,
-who has expertise in the application of decision making and consumer psychology research to
-policy and regulation.
-These routes to impact are time consuming. They would be led by the PI, with significant
-involvement from the CI to distribute the load. We anticipate that 15% (i.e., half) of PI time
-will be spent pursuing impact. These contacts will also add value for the PDRA and CI as
-they can be taken to build research collaborations beyond the grant, independently of the PI.
-We have requested funding to develop the field trials over the course of the grant, and in
-previous experience the ability to make modest commitment to a larger programme of
-randomised control trials enhances engagement.
-Beyond these three existing routes to impact, during the course of the grant we will seek to
-extend our contacts and influence to (a) one major UK supermarket, (b) one major UK
-insurance company, and (c) one major bank.
-Table 1. Translational field studies.
-Translational Field Study
-
-Anticipated Design
-
-1. Financial Conduct
-Authority
-
-A representative sample of 2,000 investors in structured
-deposits, payday loans, or other complicated financial
-products.
-
-2. Which?
-
-Presenting multi-attribute choice options to 2,000
-consumers switching broadband and or expectant mums.
-
-3. UK Cards
-
-A representative sample of 2,000 cardholders making (a)
-direct debit setup decisions or (b) monthly repayment
-decisions.
-
-Finally, the opportunity to work with real consumers making real decisions with non-trivial
-economic consequences (maybe tens of pounds with broadband, hundreds of pounds with
-credit cards, and thousands of pounds with structured deposits of mortgages, and hours of
-pain with expectant mums) is of significant academic value. The issue of incentivized choice
-is critical in Experimental Economics (though less so in Psychology), and this impact work
-extends the lab work into high stakes choice.
-
-\section{Old Perfect Cop Pathways to Impact}
-
-1
-
-Pathways to Impact
-This research is likely to deliver impact in recruitment of new officers, identifying outcomes
-associated with the best management, reductions in the rates of sickness, reductions in
-complaints and better responses to complaints, and matching officers to roles. In particular,
-matching responses from our Online Lab to the police data adds value to those data. For
-example, if, as we suspect, conscientiousness does indeed correlate with rates of sickness
-and complaints, this would allow forces to understand sickness and complaints as, at least in
-part, a function of individual differences in personality interacting with the local context in
-which officers and staff are placed. And if well-being is associated with the quality of
-management, this is a first step in developing mechanisms for improving the well-being of
-officers and staff. Below we detail the pathways to these potential impacts.
-The police support this research and have provided their data and access to officers and
-staff without imposing constraints on the academic research programme. We have met with
-and discussed the project with all of the officers and staff named here (and see meeting
-dates on p. 2 of the Case for Support). At the MPS, this research project reports to the Total
-Professionalism Board, which is chaired by our force lead Assistant Commissioner Helen
-King. The Board is responsible workforce development and recruitment strategy. We have
-already made presentations to the Board (April 2015, March 2016) and received their
-backing. By integrating this project with the Board’s remit, we have official and long-term
-support for the project. At Nottinghamshire the project reports to Chief Constable Sue Fish.
-At States of Jersey the project reports to Chief Officer Mike Bowron.
-The findings of this study have relevance to both metropolitan and county forces throughout
-England, Wales and Northern Ireland (whom all operate under a common Doctrine and
-Professional Standard). At the local level we will give at least six monthly feedback. For each
-force, each Chief Constable and Police and Crime Commissioner pairing has independent
-authority over their area (or MPS Commissioner / London Mayor pairing), and we will use
-these meeting to develop interventions and analysis around the five themes below. At the
-national level, the MPS is the largest police force in the UK and is a leader in practice. The
-route to national-level impact is the National Police Chiefs’ Council (business area lead is
-Chief Constable Giles York; Chief Constable Sue Fish is our NPCC sponsor) and through
-the College of Policing who inform the National Approved Professional Practice (Rachel
-Tuffin, Director, Knowledge, Research, and Education). At the international level, the high
-regard of British policing provides a reference point for international standards. We have
-already made links with the Chicago Citizens’ Police Data Project, Harvard Sociology, and
-Chicago Police Department, and with New York Police Department via Warwick’s Institute for
-Sustainable Cities. National and international level feedback will be via Warwick’s Centre for
-Operational Policing Research, co-directed by PI Stewart with CI Hodgson.
-Feedback to forces will be structured against the following themes, which have been
-highlighted in discussions with senior officers, who will lead the implementation within their
-forces. Feedback points are every six months, as agreed with the officers and staff named
-below.
-Public Desire. The research will deliver a list of psychological indicators of good
-performance, reduced complaints and misconduct, and reduced physical and mental ill
-health. These measures will inform the recruitment process and the selection of officers and
-staff for specialist roles in the MPS. But changing recruitment processes represent a shift
-from the implicit objective of police in the image of the public they serve. For example, “We
-can’t have a police force representative of a London which has an ethnic minority population
-of 55% when only 10% of its officers are from an ethnic minority” (Lammey, 13 January
-2014; the 55% is probably a little too high here). Many forces use positive recruitment of
-BME officers, and the MPS used residence requirements in 2013/14. How have recent
-changes in recruitment changes the psychological attributes selected for? There is certainly
-a political imperative for this directive, but little empirical evidence that the public wish this as
-
-2
-a determining factor for officer or staff recruitment. To this end, we will complement the
-behavioural science evidence base with a survey of the public to measure the properties of
-officers they desire (with Chief Constable Sue Fish, Nottinghamshire; Assistant
-Commissioner Martin Hewitt, MPS; and the (London) Mayor’s Office for Police And Crime).
-We will use a market research company to measure, from a representative sample of the UK
-population, their views on the age, sex, race, ethnicity, religious affiliation, psychological
-traits. Our objective is to start and develop a public dialogue.
-Management. What is the impact of performance development review gradings on both
-individual behaviours and those of their subordinates (Deputy Commissioner Craig Mackey
-and Chief Superintendent Robert Jones). That is, what outcomes in are associated with
-better line managers? We have already found that the highest scoring line managers have
-subordinates with a 20% reduction in the incidence of sickness. We have also identified
-significant variability across the Met within the sickness and complaints measures, with
-some boroughs having half the rates of sickness and complaints of others, and some
-boroughs having large changes within the 5-year period of the data. The mechanism for
-impact within the MPS is the HR change programmes (Robin Wilkinson, HR Director).
-Absenteeism and complaints. Using the data we already have, we see a very strong
-association between sickness and complaints. Among officers who have no complaint in the
-5-year period, 63% of officers have one or more episode of sickness. But among officers
-who have a complaint, 84% have one of more sickness. Further, econometric panel data
-analysis shows that there is almost no association between previous complaints and current
-sickness or vice versa: Complaints do not appear to cause sickness, and sickness does not
-put officers at greater risk of a complaint. The logical conclusion from this work is that there
-are strong individual difference predictors of these measures—and we have
-conscientiousness and agreeableness from the online lab as prime candidates. So key
-questions are why are complaints and sickness associated (Chief Constable Sue Fish,
-Nottinghamshire)? Which individual differences predict complaints and sickness (Chief
-Superintendent Robert Jones)?
-Right for the role? Do certain types of behavioural attributes (personality, risk attitudes)
-coalesce in specific police functions, such as specialist operations or investigations (Chief
-Officer Mike Bowron, States of Jersey Police)?
-Bad cops or bad circumstances? Are there career hotspots for misconduct or serious
-substantiated complaints (Deputy Commissioner Craig Mackey). Can we provide early
-intervention warnings for officers at greatest risk of misconduct? The mechanism for impact
-is through Professional Standards (Deputy Assistant Commissioner Fiona Taylor), to help
-design career paths that avoid potentially potent placements or role succession that
-materially increase the risk of misconduct.
-We will also offer a series of four 1-day Behaviour Masterclasses to Senior Officers'
-departments in the final year of the project. Classes will be advertised via the College of
-Policing, the National Police Chief’s Council, and Warwick’s Centre for Operational Policing
-Research. We will target the chief officers responsible for policy and implementation within
-their force, and members of their teams. Classes will be co-led by Stewart or Ritchie, and an
-officer. We will use feedback to shape the further development of the research.
+%
+%
+%
+%
+%\section{Old Accumulating to Choose Pathways to Impact}
+%
+%Pathways to Impact
+%We will target those in industry and public policy with interest in economic decision making.
+%While the focus of this programme is on informing micro-level theory of economic choice,
+%we will develop the implications for regulation and for the competitiveness of UK financial
+%industry. Our strategy will be to translate the laboratory work detailed in the Case for Support
+%into the field with a series of randomised control trials, detailed below. To deliver significant
+%impact it is essential for us to bridge the divide from the laboratory by working on live
+%problems for the regulator and industry using real consumers making real decisions.
+%Since their inception in 2012 the Financial Conduct Authority (the UK regulator for all
+%financial products, like savings accounts, pensions, mortgages, credit cards, and insurance)
+%have placed significant emphasis on behavioural regulation. This includes “...getting a better
+%understanding of why consumers act in the way they do, so we can adapt our regulation to
+%their [consumers’] common behavioural traits” (Martin Wheatley, outgoing Chief Executive,
+%FCA). Indeed, the first publication from the FCA made the case for using behavioural
+%economics in regulation (Erta, Hunt, Iscenko, Brambley, 2013). Recently Stewart has worked
+%closely with the new Behavioural Economics and Data Science Team at the FCA, led by Dr
+%Stefan Hunt, on the psychology of structured deposits (Hunt, Stewart, \& Zaliauskas, 2015).
+%The FCA are at the beginning of a project on the complexity of financial products. The
+%pathway to impact within the FCA will be via regular meetings between members of the FCA
+%Behavioural and Data Science Team, and Stewart and Mullett (most recently in August 2015).
+%Ultimately, as the data will drive public policy change regarding presentation and advertising
+%of financial products, with the creation of regulations grounded in behavioural science. The
+%outcome of this engagement will be the design of randomised control trials in collaboration
+%with the FCA and a customer-facing financial services provider using real consumers making
+%real decisions. Dissemination via the FCA working paper series will have more significant
+%reach than academic publication alone. Please see the letter of support from the Financial
+%Conduct Authority.
+%Warwick has a formal collaboration with the consumer group Which?, and Stewart has
+%worked closely with Alex Chesterfield, Head of Behavioural Insights, and team members
+%Sam Himmelweit, Harriet Patterson, and Phillida Cheetham. The formal collaboration covers
+%data sharing, exploitation, and publication rights, etc., and we have several existing and
+%completed projects (e.g., on credit card repayment behaviour and expectant mums’ birth
+%choices). Early insights from this work will feed into Which?’s project on the complexity of
+%financial products. They key route will be the monthly joint meetings between Warwick and
+%Which? Please see the letter of support from Which? Again, we would seek to implement
+%insight from these grants in a practical financial decision domain as part of Which?’s
+%consumer testing programme, and thus we will identify a practical application of the drift
+%diffusion model to a consumer choice of value to which and implement a field trial. Likely
+%candidates are: (a) the development of product information sheets for mortgages, savings
+%accounts, pensions, etc., within the context of providing behavioural nudges, and (b)
+%information provision for telecoms choices.
+%The UK Cards Association is the industry body for all credit card providers in the UK.
+%Stewart (and Gathergood, Economist, Nottingham) have a significant existing collaboration,
+%with the sharing of millions of credit card statements between about 10 of the largest card
+%companies and Warwick and Nottingham Universities. Contacts are Paul McCarron, Head of
+%Cards and Fraud Control, and Richard Koch, Head of Policy. Stewart contributed evidence to
+%the 2009 White Paper reviewing of the credit industry. Of key interest is (a) consumers’
+%
+%decisions around credit card repayments, and their integration of information from monthly
+%statements and (b) consumers choice of card during switching and how cards are evaluated.
+%The former fits well with the evaluation work; the latter fits well with the choice work.
+%Dissemination of research findings will be via presentation to the Current Affairs working
+%group, with representatives from every UK card provider.
+%We will also work closely with the Economic and Social Research Institute, an independent
+%research institute funded mainly by the Irish Government. Our key contact is Dr Peter Lunn,
+%who has expertise in the application of decision making and consumer psychology research to
+%policy and regulation.
+%These routes to impact are time consuming. They would be led by the PI, with significant
+%involvement from the CI to distribute the load. We anticipate that 15% (i.e., half) of PI time
+%will be spent pursuing impact. These contacts will also add value for the PDRA and CI as
+%they can be taken to build research collaborations beyond the grant, independently of the PI.
+%We have requested funding to develop the field trials over the course of the grant, and in
+%previous experience the ability to make modest commitment to a larger programme of
+%randomised control trials enhances engagement.
+%Beyond these three existing routes to impact, during the course of the grant we will seek to
+%extend our contacts and influence to (a) one major UK supermarket, (b) one major UK
+%insurance company, and (c) one major bank.
+%Table 1. Translational field studies.
+%Translational Field Study
+%
+%Anticipated Design
+%
+%1. Financial Conduct
+%Authority
+%
+%A representative sample of 2,000 investors in structured
+%deposits, payday loans, or other complicated financial
+%products.
+%
+%2. Which?
+%
+%Presenting multi-attribute choice options to 2,000
+%consumers switching broadband and or expectant mums.
+%
+%3. UK Cards
+%
+%A representative sample of 2,000 cardholders making (a)
+%direct debit setup decisions or (b) monthly repayment
+%decisions.
+%
+%Finally, the opportunity to work with real consumers making real decisions with non-trivial
+%economic consequences (maybe tens of pounds with broadband, hundreds of pounds with
+%credit cards, and thousands of pounds with structured deposits of mortgages, and hours of
+%pain with expectant mums) is of significant academic value. The issue of incentivized choice
+%is critical in Experimental Economics (though less so in Psychology), and this impact work
+%extends the lab work into high stakes choice.
+%
+%\section{Old Perfect Cop Pathways to Impact}
+%
+%
+%1
+%
+%Pathways to Impact
+%This research is likely to deliver impact in recruitment of new officers, identifying outcomes
+%associated with the best management, reductions in the rates of sickness, reductions in
+%complaints and better responses to complaints, and matching officers to roles. In particular,
+%matching responses from our Online Lab to the police data adds value to those data. For
+%example, if, as we suspect, conscientiousness does indeed correlate with rates of sickness
+%and complaints, this would allow forces to understand sickness and complaints as, at least in
+%part, a function of individual differences in personality interacting with the local context in
+%which officers and staff are placed. And if well-being is associated with the quality of
+%management, this is a first step in developing mechanisms for improving the well-being of
+%officers and staff. Below we detail the pathways to these potential impacts.
+%The police support this research and have provided their data and access to officers and
+%staff without imposing constraints on the academic research programme. We have met with
+%and discussed the project with all of the officers and staff named here (and see meeting
+%dates on p. 2 of the Case for Support). At the MPS, this research project reports to the Total
+%Professionalism Board, which is chaired by our force lead Assistant Commissioner Helen
+%King. The Board is responsible workforce development and recruitment strategy. We have
+%already made presentations to the Board (April 2015, March 2016) and received their
+%backing. By integrating this project with the Board’s remit, we have official and long-term
+%support for the project. At Nottinghamshire the project reports to Chief Constable Sue Fish.
+%At States of Jersey the project reports to Chief Officer Mike Bowron.
+%The findings of this study have relevance to both metropolitan and county forces throughout
+%England, Wales and Northern Ireland (whom all operate under a common Doctrine and
+%Professional Standard). At the local level we will give at least six monthly feedback. For each
+%force, each Chief Constable and Police and Crime Commissioner pairing has independent
+%authority over their area (or MPS Commissioner / London Mayor pairing), and we will use
+%these meeting to develop interventions and analysis around the five themes below. At the
+%national level, the MPS is the largest police force in the UK and is a leader in practice. The
+%route to national-level impact is the National Police Chiefs’ Council (business area lead is
+%Chief Constable Giles York; Chief Constable Sue Fish is our NPCC sponsor) and through
+%the College of Policing who inform the National Approved Professional Practice (Rachel
+%Tuffin, Director, Knowledge, Research, and Education). At the international level, the high
+%regard of British policing provides a reference point for international standards. We have
+%already made links with the Chicago Citizens’ Police Data Project, Harvard Sociology, and
+%Chicago Police Department, and with New York Police Department via Warwick’s Institute for
+%Sustainable Cities. National and international level feedback will be via Warwick’s Centre for
+%Operational Policing Research, co-directed by PI Stewart with CI Hodgson.
+%Feedback to forces will be structured against the following themes, which have been
+%highlighted in discussions with senior officers, who will lead the implementation within their
+%forces. Feedback points are every six months, as agreed with the officers and staff named
+%below.
+%Public Desire. The research will deliver a list of psychological indicators of good
+%performance, reduced complaints and misconduct, and reduced physical and mental ill
+%health. These measures will inform the recruitment process and the selection of officers and
+%staff for specialist roles in the MPS. But changing recruitment processes represent a shift
+%from the implicit objective of police in the image of the public they serve. For example, “We
+%can’t have a police force representative of a London which has an ethnic minority population
+%of 55% when only 10% of its officers are from an ethnic minority” (Lammey, 13 January
+%2014; the 55% is probably a little too high here). Many forces use positive recruitment of
+%BME officers, and the MPS used residence requirements in 2013/14. How have recent
+%changes in recruitment changes the psychological attributes selected for? There is certainly
+%a political imperative for this directive, but little empirical evidence that the public wish this as
+%
+%2
+%a determining factor for officer or staff recruitment. To this end, we will complement the
+%behavioural science evidence base with a survey of the public to measure the properties of
+%officers they desire (with Chief Constable Sue Fish, Nottinghamshire; Assistant
+%Commissioner Martin Hewitt, MPS; and the (London) Mayor’s Office for Police And Crime).
+%We will use a market research company to measure, from a representative sample of the UK
+%population, their views on the age, sex, race, ethnicity, religious affiliation, psychological
+%traits. Our objective is to start and develop a public dialogue.
+%Management. What is the impact of performance development review gradings on both
+%individual behaviours and those of their subordinates (Deputy Commissioner Craig Mackey
+%and Chief Superintendent Robert Jones). That is, what outcomes in are associated with
+%better line managers? We have already found that the highest scoring line managers have
+%subordinates with a 20% reduction in the incidence of sickness. We have also identified
+%significant variability across the Met within the sickness and complaints measures, with
+%some boroughs having half the rates of sickness and complaints of others, and some
+%boroughs having large changes within the 5-year period of the data. The mechanism for
+%impact within the MPS is the HR change programmes (Robin Wilkinson, HR Director).
+%Absenteeism and complaints. Using the data we already have, we see a very strong
+%association between sickness and complaints. Among officers who have no complaint in the
+%5-year period, 63% of officers have one or more episode of sickness. But among officers
+%who have a complaint, 84% have one of more sickness. Further, econometric panel data
+%analysis shows that there is almost no association between previous complaints and current
+%sickness or vice versa: Complaints do not appear to cause sickness, and sickness does not
+%put officers at greater risk of a complaint. The logical conclusion from this work is that there
+%are strong individual difference predictors of these measures—and we have
+%conscientiousness and agreeableness from the online lab as prime candidates. So key
+%questions are why are complaints and sickness associated (Chief Constable Sue Fish,
+%Nottinghamshire)? Which individual differences predict complaints and sickness (Chief
+%Superintendent Robert Jones)?
+%Right for the role? Do certain types of behavioural attributes (personality, risk attitudes)
+%coalesce in specific police functions, such as specialist operations or investigations (Chief
+%Officer Mike Bowron, States of Jersey Police)?
+%Bad cops or bad circumstances? Are there career hotspots for misconduct or serious
+%substantiated complaints (Deputy Commissioner Craig Mackey). Can we provide early
+%intervention warnings for officers at greatest risk of misconduct? The mechanism for impact
+%is through Professional Standards (Deputy Assistant Commissioner Fiona Taylor), to help
+%design career paths that avoid potentially potent placements or role succession that
+%materially increase the risk of misconduct.
+%We will also offer a series of four 1-day Behaviour Masterclasses to Senior Officers'
+%departments in the final year of the project. Classes will be advertised via the College of
+%Policing, the National Police Chief’s Council, and Warwick’s Centre for Operational Policing
+%Research. We will target the chief officers responsible for policy and implementation within
+%their force, and members of their teams. Classes will be co-led by Stewart or Ritchie, and an
+%officer. We will use feedback to shape the further development of the research.
 \newpage

### 2019-07-23 JeS_fields.tex

@@
 Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach.
-By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights.
+By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights stimulating future research efforts.
 
@@
 
-Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups.
+Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups, and its implications for victim's trust in the CJS.
 

### 2019-07-23 pathways_to_impact.tex
Anna update

@@
 This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account.
-We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at West Midlands Police), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
+We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
 The summit will be a 50/50 academic / practitioner mix.
-We will contact, early in the project, [Insert list of charities in this sector, Women's Aid, Refuge, Safe Lives, National Centre for Domestic Abuse] and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+We will contact, early in the project, domestic abuse charities Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
 
@@
 
-Although a high-profile ``launch'' event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.
+Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.
 
@@
 Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
-Key issues here are work on coercion and control, and having sufficient financial resilience to escape an abusive relationship and being able to make the decision to report an abuser.
+Key issues here are work on coercion and control, and how financial resilience affects the decision to contact the police and escape the cycle of abuse.
 Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.
@@
 CI Stewart will also spend half of his time of the project on the impact activity.
-Stewart has significant experience of impact acitivites in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association.
+Stewart has significant experience of impact activities in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association.
 Postdoc Trendl will be fully involved in the impact programme.

### 2019-07-23 pathways_to_impact.tex
Anna update

@@
 This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy.
-To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the West Midlands Police and Crime Commissioner's Office, Alison Spence.
+To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the WMP and Crime Commissioner's Office, Alison Spence.
 As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.

### 2019-07-23 JeS_fields.tex
Impact summarry Tim

--- 2019-07-23 JeS_fields.tex
@@
 
-Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse.
-We aim to do so by expanding the knowledge of other stakeholders, including the police, charities, and the government.
+In 2018, there were X thousand victims of domestic abuse in England and Wales alone.
+Domestic abuse has a terrible impact upon victims in a variety of ways, and ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support.
+However, the effects of domestic abuse are multi-faceted and far reaching.
+Such abuse often touches the lives of those far beyond the initial victim, such as children, family, neighbours, friends, and colleagues.
+
+This research uses a variety of existing data sets, to help us better understand patterns of domestic abuse.
+The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents such as domestic homicide.
+We will engage with a number of stakeholders, and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.
+
+Many of our primary partners are within the police force.
+The research will help them to identify individuals who are most at risk of being victims of domestic abuse, and improve risk assessment models to identify situations which could escalate into serious acts of violence.
+It will also enable the identification of likely triggers for the onset, or worsening of ongoing abuse allowing police to better direct resources and design risk assessment frameworks.
+The potential triggers that we will investigate include high profile events such as sporting tournaments, and economic shocks, such as changes to the structure of benefit payments.
+Not only will this help the police, but it will also help policy makers estimate the likely impacts of policy change.
+
+rates of gambling and alcohol spending in the local community, financial wellbeing, and
+
+Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support.
+However, domestic abuse is multi-faceted and affects the lives of many individuals who  We aim to do so by working together other stakeholders, including the police, charities, and the government.
 

### 2019-07-23 accumulating_to_choose_interim_report.tex
Accumulating to choose interim report

Progress report for ESRC grant ES/N018192/1 ``Accumulating to choose''

Accumulating to choose is an ESRC grant exploring how evidence is accumulated during decision making. It is a collaboration between psychologist and PI Prof. Neil Stewart, and economists Prof. Colin Camerer and Prof. Chris Starmer.

Named postdoc Dr Tim Mullett began working on the grant on 1 January 2017.Caltech postdoc Devdeepta Bose was hired July 2018, with matched funding from Caltech extending his contract for a second year.  Mullett was hired as an assistant professor in September 2018, but continues to work on the grant. Replacement Dr Charlotte Edmunds joined the project A no-cost extension was granted until 30th June 2020 (in March 2019). Thus the project is now in its third of three funded years.

During the grant over 18 published papers carry the grant number. Core outputs are:

Mullett, T. L., Brown, G. D. A., \& McDonald, R. (2019). Cooperation in public goods games predicts behaviour in incentive-matched binary dilemmas : evidence for stable pro-sociality. Economic Inquiry.

Mullett, T. L., Brown, G. D. A., Fincher, C. L., Kosinski, M. \& Stillwell, D. (2019). Individual-level analyses of the impact of parasite stress on personality: Reduced openness only for older individuals. Personality and Social Psychology Bulletin.

Bhatia, S., \& Mullett, T. L. (2018). Similarity and decision time in preferential choice. Quarterly Journal of Experimental Psychology.

Alempaki, D., Canic, E., Mullett, T. L., Skylark, W. J., Starmer, C., Stewart, N., \& and Tufano, F. (2018). Re-examining how utility and weighting functions get their shapes: A quasi-adversarial collaboration providing a new interpretation. Management Science.

Mullett, T. L., Smart, L., \& Stewart, N. (2018). Blackbird's alarm call or nightingale's lullaby? The effect of tweet risk warnings on attractiveness, search, and understanding. Financial Conduct Authority Occasional Papers in Financial Regulation, 47. https://www.fca.org.uk/publication/occasional-papers/occasional-paper-47.pdf PDF 
Abstract

Mullett, T. L., Smart, L., \& Stewart, N. (2018). The effect of risk warning content for contract for difference products. Available at SSRN: https://ssrn.com/abstract=3231616

Noguchi, T., \& Stewart, N. (2018). Multialternative decision by sampling: A model of decision making constrained by process data. Psychological Review, 125, 512-544. doi: 10.1037/rev0000102

We also have a series of working papers currently under review or in progress. Those most relevant include:

Edmunds, C., Mullett, T. L., \& Stewart, N. No accumulation in value based choice.

Stewart, N., Mullett, T.L., \& Canic, E. On the futility of estimating utility functions: Why the parameters we measure are wrong, and why they do not generalize.

Mullett, T.L., \& McDonald, R. Visual Attention in Health Judgements and Choices.

McDonald, R., Mullett, T.L., \& Tuschia, A. Perceptions of composite attributes in judgements of EQ5D.

Brown, G.D.A., Walasek, L., Mullett, T.L., Fincher, C., Stillwell, D., \& Kosinski, M. Pathogen Stress and Politics: Changing Ecological Origins of Ideology in the USA.

Mullett, T.L., \& Stewart, N. Don’t fixate on interactions, attend to main effects: Attentional models of choice are miss-specified.

Mullett, T.L., \& McDonald, S. How People Choose Universities: The Impact of TEF and Variable Fees.

Walasek, L., Mullett, T.L., \& Stewart, N. A Meta-Analysis of Loss Aversion in Risky Contexts. Available at SSRN: https://ssrn.com/abstract=3189088

Mullett, T.L., \& Stewart, N. No evidence for the payday effect in alcohol related crimes and hospital admissions.

Mullett, T.L. Stewart, N., \& Tunney, R.J. Time course of attention patterns during multi-attribute choice reveals attribute weighting and preference formation in a two stage process.

We have our final round of exchange visits soon, with Bose visiting in August and Mullett visiting Caltech in September.

Data collection is nearly complete. We have one final set of experiments to collect data for in autumn 2019.

### 2019-07-23 JeS_fields.tex

@@
 
-In 2018, there were X thousand victims of domestic abuse in England and Wales alone.
+In 2018, there were almost 2 million victims of domestic abuse in England and Wales alone.
 Domestic abuse has a terrible impact upon victims in a variety of ways, and ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support.
@@
 
-This research uses a variety of existing data sets, to help us better understand patterns of domestic abuse.
-The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents such as domestic homicide.
-We will engage with a number of stakeholders, and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.
+This research uses a variety of existing data sets, to help us better understand the patterns, characteristics, and consequences of domestic abuse victimisation.
+The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents, such as domestic homicide.
+We will engage with a number of stakeholders (police, domestic abuse charities, government), and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.
 
 Many of our primary partners are within the police force.
-The research will help them to identify individuals who are most at risk of being victims of domestic abuse, and improve risk assessment models to identify situations which could escalate into serious acts of violence.
+Our insights about police mis-recording of domestic abuse will help the police improve their recording practices, enhancing victim's trust in the police, and increase willingness to report future incidents.
+
+In addition, the research will help the police to identify individuals who are most at risk of being victims of domestic abuse, and improve risk assessment models to identify situations which could escalate into serious acts of violence.
 It will also enable the identification of likely triggers for the onset, or worsening of ongoing abuse allowing police to better direct resources and design risk assessment frameworks.
@@
 
-rates of gambling and alcohol spending in the local community, financial wellbeing, and
+The police will also benefit from a deeper understanding of the factors governing reporting behaviour, and its temporal characteristics throughout the year, and this knowledge will allow them to improve the allocation of scarce police resources.
 
-Ultimately, the fundamental goal of this research project is to benefit victims of domestic abuse by improving their safety and access to support.
-However, domestic abuse is multi-faceted and affects the lives of many individuals who  We aim to do so by working together other stakeholders, including the police, charities, and the government.
-
-For charities and the government, insights from our research (risk factors of ) will provide useful information for the most effective targeting (geographical and temporal) of domestic abuse awareness campaigns.
-
- will benefit from a comprehensive investigation of a wide range of risk factors of domestic abuse victimisation.
-
-Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase their trust, and willingness to report future incidents.
-The police will also benefit from a deeper understanding of the factors governing reporting behaviour, its temporal characteristics throughout the year, and this knowledge will allow for an improved allocation of scarce police resources.
-Our research on the predictors of serious harm will help design better interventions.
-
-victims of domestic abuse more liekly to report and less likely to be seriously harmed, children, police, policymaker - evidence base, charity
-
-1) characteristics of victims and understanding predictors of serious harm - police can use insights to prevent serious harm, characteristics of victims - expand on previous qualitative research (academics) and help policy-makers better target campaigns
-
-2) reporting behaviour and police mis-recording - police can improve recording practices, understanding reporting behaviour can benefit behavioural scientists who work for the government
-
-3) consequences - helps the government and academics by advancing our knowledge on the consequences of domestic abuse victimisation by improving the methodology of
+For domestic abuse charities and the government, insights from our research regarding the geographical and temporal characteristics of domestic abuse victimisation will provide invaluable information for the most effective targeting of domestic abuse awareness campaigns.
 

### 2019-07-24 pathways_to_impact.tex
Anna Pathways to impact

@@
 
-Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP) , and the college of policing.
+Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP), and the College of Policing (CoP).
 These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.
@@
 The research proposed here has been developed with direct input from officers and experts within WMP.
-This has allowed us to design the research questions that are relevant to current issues within WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and changes in policy.
-To facilitate this, we have a day-to-day contact at WMP: Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and within the WMP and Crime Commissioner's Office, Alison Spence.
-As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe who is the National Police Chiefs Council lead for domestic abuse.
+This has allowed us to design the research questions that are relevant to current issues within the WMP, and that can feed in to existing structures to accelerate the dissemination of findings, and contribute to changes in policy.
+To facilitate this, we have a day-to-day contact at WMP with Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and Alison Spence (Crime Commissioner's Office).
+As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs Council lead for domestic abuse.
 
-These relationships will enable us to work with WMP to import the insight from the research into their senior management team and also their day-to-day processes.
+These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team, and also their day-to-day processes.
 This will be possible for each of the objectives and topics within our proposal:
@@
 
-In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the College of Policing, provide pathways for impact across all forces.
-At the College of Policing (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/) and the revision of the existing DASH risk assessment tool for domestic abuse.
-(https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{Authorised Professional Practice} on domestic abuse, released in 2015.
-We will work initially with David Tucker, Head Crime and Criminal Justice at the College of Policing.
+In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces.
+At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015, and contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse.
+We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.
 
-We will meet regularly with our contacts at WMP and the college of policing throughout the grant.
+We will meet regularly with our contacts at WMP and the CoP throughout the grant.
 This will enable us to adapt to current questions that arise during the period of the proposal.
@@
 
-In the second year of the proposal we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
+In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
 This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account.
 We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
-The summit will be a 50/50 academic / practitioner mix.
-We will contact, early in the project, domestic abuse charities Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+The summit will be a 50/50 academic and practitioner mix.
+We will contact, early in the project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
 
 In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts.
-We will submit these reports to the College of Police What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.
+We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.
 
@@
 Warwick already has a relationship with King's team in CI Stewart's work on the effects of gambling, which was completed using micro-level transaction data from millions of account holders.
-Key issues here are work on coercion and control, and how financial resilience affects the decision to contact the police and escape the cycle of abuse.
+Key issues here are work on coercion and control, and understanding the extent to which financial resilience affects the decision to contact the police and escape the cycle of abuse.
 Our day-to-day contact at Lloyds is Dr David Leake, Head of the Behavioural Insights Team.

### 2019-07-26 JeS_fields.tex
Neil edits to JeS fields

@@
 This will maximise the impact that this research produces.
+Mullett will contribute extensively to the research design and writing academic papers.
 
 As Co-I, Stewart's responsibilities will be to aid in coordinating the research program.
-He will also meet regularly with the early career researcher Anna Trendl, providing insights and support.
+He will also meet regularly with the early career researcher Anna Trendl, providing insights and support---Stewart has extensive experience supervising postdoctoral researchers.
 A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities.
 This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research.
+Stewart will contribute to the research design and writing academic papers.
 
-As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers.
+As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and, as is the norm in psychology, leading the writing of the resulting papers.
 She will also be deeply involved with impact related activity.
 As an early career researcher, it is crucial that she be given the opportunity to expand her network, and attain these new skills.
-The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.
+The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis.
+Trendl already has extensive experience with the WMP records.
 
@@
 The research will help to identify underlying risk factors for potential domestic abuse victims, and indicators for the most violent domestic abuse incidents, such as domestic homicide.
-We will engage with a number of stakeholders (police, domestic abuse charities, government), and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.
+We will engage with a number of stakeholders (police, domestic abuse charities, national and local government), and provide insights relevant to their specific role in reducing the prevalence and harm caused by domestic abuse.
 
@@
 The primary ethical concerns in this project centre around data privacy and data security.
-In particular the data held in the West Midlands Police dataset is highly sensitive, and if it were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers.
+In particular, both the Crime Survey for England and Wales (secure access, low-level geographic data) and  the West Midlands Police datasets are highly sensitive.
+If data were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers.
 For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research.
+We also meet all of the standards for data security for accessing the secure access version of the Crime Survey for England and Wales.
+
 We will never link individuals across datasets, and our lab data plan is fully compliant with GDPR.
@@
 Therefore, we will make very minimal requests on police resources.
-Our primary cost upon staff time will be during feeding back our results to influence policy.
-There are structuers within the police force specifically designed for this, so by presenting our findings to those, we will actually increase WMP efficiency.
+Our primary cost upon staff time will be during feeding back our results to influence police operations and policy.
+There are structures within the police force specifically designed for this, so by presenting our findings to those, we will actually increase WMP efficiency.
 

### 2019-07-26 pathways_to_impact.tex
N minor edits to pathways to impact

@@
 
-Our pathway to impact is built upon the strong existing relationships we have with Wast Midlands Police (WMP), and the College of Policing (CoP).
+Our pathway to impact is built upon the strong existing relationships we have with West Midlands Police (WMP), and the College of Policing (CoP).
 These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.
@@
 To facilitate this, we have a day-to-day contact at WMP with Inspector Jenny Richards (Evidence Based Practice in Risk and Organisational Learning), and Alison Spence (Crime Commissioner's Office).
-As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs Council lead for domestic abuse.
+As a result of this close collaboration, we have received support from senior levels within WMP including from Deputy Chief Constable Louisa Rolfe, who is the National Police Chiefs' Council lead for domestic abuse.
 
-These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team, and also their day-to-day processes.
+These relationships will enable us to work with WMP to import insights generated from our the research into their senior management team and ultimately to influence policy and day-to-day operations.
 This will be possible for each of the objectives and topics within our proposal:
@@
 2.
-The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., https://west-midlands.police.uk/your-options/domestic-abuse).
+The programme on the  ``decision to report'' links with police's design of the initial contact with victims (e.g., \url{https://west-midlands.police.uk/your-options/domestic-abuse}).
 It will also help the police to develop more efficient and targeted intervention and awareness campaigns.
@@
 
+We will contact, in the first three months of project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+
 In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
 This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account.
-We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry.
+We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry, and key contacts from the third sector agencies.
 The summit will be a 50/50 academic and practitioner mix.
-We will contact, early in the project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.
 
@@
 We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.
-
-Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.
 
@@
 
-We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund to continue the impact programme beyond the end of the funded period.
+We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund and continue the impact programme beyond the end of the funded period.
 

### 2019-07-29 case_for_support_TM_hacked.tex
Update case_for_support_TM_hacked.tex

@@
 In the most extreme cases, domestic abuse can culminate in domestic homicide: in the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, and 90\% of these victims were women \cite{homic}.
-Domestic abuse has substantial mental health implications, which are not limited to the the direct target of abuse \cite{ferrari}, but can have a profound effect on the lives of children witnessing domestic abuse at home \cite{callaghan}.
-Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays, health care costs, and the reduced quality fo life for survivors \cite{costs}.
+Domestic abuse has substantial mental health implications, which are not limited to the direct target of abuse \cite{ferrari}, but can have a profound effect on the lives of children witnessing domestic abuse at home \cite{callaghan}.
+Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays, health care costs, and the reduced quality of life for survivors \cite{costs}.
 

### 2019-07-29 JeS_fields.tex
Update JeS_fields.tex

@@
 The primary ethical concerns in this project centre around data privacy and data security.
-In particular, both the Crime Survey for England and Wales (secure access, low-level geographic data) and  the West Midlands Police datasets are highly sensitive.
+In particular, the West Midlands Police datasets are highly sensitive.
 If data were to end up in the wrong hands could be particularly damaging for the individuals present in the data, as well as for the WMP force, and even the researchers.
 For this reason we have developed our data security approach in tandem with WMP to ensure that data is only ever held and transported securely, and that researchers hold only the minimum amount of information in order to perform the research.
-We also meet all of the standards for data security for accessing the secure access version of the Crime Survey for England and Wales.
 

### 2019-07-29 case_for_support_TM_hacked.tex
Anna cfs update

@@
 
-This research programme consists of four research projects that will deliver applicable, policy-relevant insights about domestic abuse.
+This research programme consists of four research topics aiming to deepen our understanding of domestic abuse victimisation, by exploiting the rich information contained in the CSEW, and combine it with insights from other data sources.
 First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, and the predictors of suffering serious harm.
@@
 Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP data, this research complements, extends and deepens our understanding of domestic abuse.
-In outlining the analysis plan for each of these projects, we will specify a set of statistical analyses we plan to conduct.
-We will preregister all of our analysis plans and complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, \textbf{\textit{Trendl Football}}, for an example of this approach in some of our prior work on domestic abuse).
+In outlining the analysis plan for each of these research topics, we will specify a set of statistical analyses we plan to conduct.
+We will preregister all of our analysis plans and complement all analyses with robustness checks, and further exploratory regressions as the data allows (see, for an example of this approach in some of our \href{https://cog.warwick.ac.uk/~pssmar/Trendl_Stewart_Mullett.pdf}{prior work} on domestic abuse).
 
@@
 % \textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
-In this research project, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
-Exploring the risk factors in domestic abuse victimisation is key in designing effectively targeted policy measures.
-Previous research has identified a number of risk factors predicting domestic abuse victimisation (being female, young, unemployed, separated or divorced, living in single parent household, earning in the lowest income bracket, having a long-term disability), based on descriptive statistics derived from the CSEW data \cite{ONS}.
+In this research topic, we will first use the CSEW to investigate the demographic and socio-economic characteristics of survivors of domestic abuse.
+Understanding the risk factors of domestic abuse victimisation is key for designing effectively targeted policy measures.
+Previous research has identified a number of risk factors predicting domestic abuse victimisation (e.g., being female, young, unemployed, separated or divorced, living in single parent household, earning in the lowest income bracket, having a long-term disability), based on descriptive statistics derived from the CSEW data \cite{ONS}.
 However, the CSEW provides a much broader range of information on the characteristics of the respondent, including number of children, ethnicity, education, benefit history, physical and mental health, house and car ownership, self-reported well-being, substance abuse, and frequency of going out.
 
-Investigating the explanatory power of a broader set of victim characteristics within one regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
+Investigating the explanatory power of a broader set of victim characteristics within one (logistic) regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
 We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
 
-However, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (e.g., it is possible that not having stable employment is a more significant risk factor of domestic abuse victimisation for those who have young children).
+In addition, given the complex nature of domestic abuse, it is likely that there are important interactions between various victim characteristics in predicting the risk of domestic abuse victimisation (e.g., it is possible that not having stable employment is a more significant risk factor of domestic abuse victimisation for those with young children).
 To uncover the structure of these interactions without having to a priori specify them -- as is required in a logistic regression model -- we will also use a random forest classification algorithm, a machine learning method that has the ability to detect non-linear relationships between variables in predicting categorical outcomes (e.g., domestic abuse victimisation), allowing us to identify particularly vulnerable subgroups of the population \cite{rforest}.
@@
  We will also explore the victim and offender characteristics that predict serious harm.
-Previous studies investigating risk factors for serious harm mostly relied on police data and focused on identifying high-risk offenders \cite{thornton}.
+Previous studies investigating the risk factors of serious harm in the context of domestic abuse mostly relied on police data, and focused on identifying high-risk offenders \cite{thornton}.
 Using a multinomial logistic approach, we will use the CSEW to investigate how victim characteristics predict the level of harm suffered, including financial independence and resilience (income bracket, employment stability), mental health (self-reported well-being), drug and alcohol dependence (frequency of usage), social isolation (self-reported frequency of going out, living alone or with the perpetrator, family disputes), recent separation, and feeling frightened (increased home security, reporting feeling scared).
@@
 Using a logistic regression approach with perpetrator-victim fixed effects (FE), we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
-Insights from these analyses can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
+Insights from these analyses will help the police to assess the validity of their current risk assessment model, and can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
 
@@
 
-In this project, we will first explore the factors influencing victim's decision to report the abuse.
+In this research topic, we will first explore the factors influencing victim's decision to report the abuse.
 Even though improving willingness to report is key to effectively tackle domestic abuse, we are not aware of previous research exploring this question in depth.
@@
 We are interested in whether these reports are more likely to occur after certain days of the year (e.g., birthday of the victim or perpetrator, Christmas, New Years, Valentine's Day etc.).
-This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to encourage reporting.
+This is particularly important knowledge for police, so that they can efficiently target awareness campaigns to further encourage reporting.
 
@@
 We will also use the CSEW to explore the police's response to reported cases of domestic abuse.
-Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key in improving willingness to report.
+Increasing victim's trust in the Criminal Justice System (CJS) through improving law enforcement response to reported incidents is key for improving willingness to report.
 Mis-recording of domestic abuse is a serious problem across police forces, for example, a recent inspection reported that WMP have failed to record 25\% of reported crimes that were domestic abuse-related \cite{HerMajestysInspectorateofConstabularyandFires&RescueServices2019}.
-In this project, we will explore whether the extent of crime mis-recording depends on victim characteristics.
+In this research topic, we will explore whether the extent of crime mis-recording depends on victim characteristics.
 Using the CSEW, we will be able to tell whether the type of domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
-A multinomial regression approach allows us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), and depends upon the socio-economic characteristics of the victim and the police forces (e.g., funding per police officer, deprivation).
+A multinomial regression approach will allow us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), and depends upon the socio-economic characteristics of the victim and police forces (e.g., funding per police officer, deprivation).
 Complementing this analysis with a random forest approach will reveal the role of interactions between individual and police force characteristics.
@@
  Domestic abuse has long-lasting adverse effects on victims and children witnessing the abuse.
-In this research project, our is aim to explore some of these consequences.
+In this research topic, our is aim to explore some of these consequences.
 The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
 Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
-We will consolidate and extend these findings using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse whilst also controlling for a range of confounds, such as economic deprivation.
+First, we will consolidate and extend these findings using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse, whilst also controlling for a range of confounds, such as economic deprivation.
  %Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
@@
 
-We will complement this analysis using WMP, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
+We will further complement this analysis using WMP data, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
 It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crime they engage in.
@@
 
-In this research project, we will investigate some of the environmental predictors of domestic abuse.
-First, using the CSEW and a logistic regression approach, we will explore the neighbourhood predictors of domestic abuse victimisation and willingness to report, using information on the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), whilst controlling for the socio-economic characteristics of the respondent.
+In this research topic, we will investigate some of the environmental predictors of domestic abuse.
+First, using the CSEW and a logistic regression approach, we will explore the neighbourhood predictors of domestic abuse victimisation and willingness to report, using information on the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), and neighbourhood deprivation (measured by the IMD), whilst controlling for the socio-economic characteristics of the respondent.
 
-Additionally, we will investigate how neighbourhood (LSOA) deprivation (measured by the IMD) affects the prevalence of domestic abuse and willingness to report, using a spatial regression framework.
-This statistical approach will alleviate the problem of spatial dependency in our dataset, and will allow us to derive a precise estimate of the effect.
+These analyses will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first project to provide a comprehensive exploration of the range of factors affecting domestic abuse victimisation and willingness to report.
+
+%Additionally, we will investigate how neighbourhood (LSOA) deprivation (measured by the IMD) affects the prevalence of domestic abuse and willingness to report, using a spatial regression framework.
 
@@
 
-Using the CSEW and the transaction dataset, we will also explore how neighbourhood-level spending on alcohol and gambling predict the prevalence of domestic abuse in the area, whilst controlling for the deprivation of the neighbourhood.
+%Using the CSEW and the transaction dataset, we will also explore how neighbourhood-level spending on alcohol and gambling predict the prevalence of domestic abuse in the area, whilst controlling for the deprivation of the neighbourhood.
 We will do so by estimating a spending profile on alcohol and gambling for each LSOA in a year.
-These analyses will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first project to provide a comprehensive exploration of the factors affecting domestic abuse victimisation and willingness to report.
 
-Finally, we will explore the extent to which changes in alcohol consumption and financial stability on the community level predicts the prevalence of domestic abuse.
-We can identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and investigate how these affect the reported number of domestic abuse incidents in that area in a given time period.
+We will also explore the extent to which changes in alcohol consumption and financial stability on the community level affects the prevalence of domestic abuse.
+To do so, we will use the transaction data to construct an LSOA-level spending profile for a given time period to investigate how temporal changes in this profile affect the number of reported domestic abuse cases in that area, using a spatial panel regression model.
+This statistical estimation approach will alleviate the problem of spatial dependency between neighbourhoods, and will allow us to derive a precise estimate of the effect of temporal changes in community-level alcohol consumption and financial health on the prevalence of domestic abuse in the neighbourhood.
+
+We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and  how these affect the reported number of domestic abuse incidents in that area in a given time period.
 Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.
-Second, drawing on previous findings about the link between financial stress and domestic abuse, we we will explore what effect the roll-out of the Universal Credit (UC) across the West Midlands had on the reported number of domestic abuse cases.
+
+In addition, drawing on previous findings about the link between financial stress and domestic abuse, we will explore what effect the roll-out of the Universal Credit (UC) across the West Midlands had on the reported number of domestic abuse cases.
 These reforms had been criticised widely, due to the temporal financial strain it imposes on the least financially resilient people in society.
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
+This analyses will constitute the first empirical investigation of the direct effect of welfare policy changes on domestic abuse victimisation.
 
@@
 & CSEW & Individual & domestic abuse victimisation/willingness to report & Perception of neighbourhood, socio-economic characteristics & Logistic regression \\
-         \midrule
-          How does neighbourhood deprivation predict domestic abuse?
-& IMD, CSEW & LSOA-level & domestic abuse victimisation/willingness to report & Various measures of deprivation & Spatial Logistic regression \\
-         \midrule
-          How do community-level spending on alcohol and gambling affect domestic abuse?
+%         \midrule
+%          How do community-level spending on alcohol and gambling affect domestic abuse?
 & CSEW, Transaction data, IMD & LSOA-level & domestic abuse victimisation & Spending on alcohol and gambling, deprivation & Spatial Poisson regression \\
@@
     How do community-level temporal changes in alcohol consumption and income affect domestic abuse?
-& WMP, Transaction data & LSOA, day-, week-, month-level & Number of reported domestic abuse cases & Alcohol, gambling spending, benefits & Spatial Poisson regression \\
+& WMP, Transaction data & LSOA, day-, week-, month-level & Number of reported domestic abuse cases & Alcohol, gambling spending, benefits & Spatial panel Poisson/negative binomial regression \\
 
@@
 
-These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK.
 We envisage two articles.
 One will be focussed upon general behavioural theory and the effect of the environment.
-This will be targeted towards Nature Human Behaviour, and Proceedings of the National Acedemy of Sciences.
+This will be targeted towards Nature Human Behaviour, and Proceedings of the National Academy of Sciences.
 The other article will focus upon the implications for criminology and policing.

### 2019-07-29 justification_of_resources.tex
Update justification_of_resources.tex

@@
 Justification of Resources
+
+Staff, Directly Incurred Posts
+
+PDRA Trendl.
+We request 100\% support for PDRA Trendl.
+A postdoctoral appointment is essential here, as the level of technical skill required to run and analyse these large and complex datasets is high.
+Furthermore, Trendl has extensive experience with these datasts, having already completed a project on the effects of Football tournaments on Domestic Abuse during her PhD.
+As outlined in Staff Duties, Trendl will conduct the statistical analyses and lead on the writing of the majority of publications.
+Trendl will also take an active role in impact activities, building upon existing relationships with WMP that were developed during her PhD research, and developing a network of contacts as this project supports her development as an Early Career Researcher.
+
+Staff, Directly Allocated Posts
+
+PI Mullett.
+We request 15% support for Mullett.
+Half of this support will be spent on supporting the empirical work.
+This includes providing support and supervision to PDRA Trendl, as well as data management duties such as data cleaning, outputting from the highly sensitive data of appropriately sanitised/annonymised versions of the dataset for the other researchers.
+The other half of the support will be spent on impact activities.
+Academic faculty support is required to maximise the potential impact of the research.
+Mullett's existing relationships with WMP and membership of the Centre for Operational Policing Research are crucial in gaining the contacts and invitations to collaborate with policy makers and present research to relevant, decision making bodies.
+
+CI Stewart.
+We request 10% support for Stewart.
+Stewart will aid in coordinating the research program.
+He will also meet regularly with the early career researcher Anna Trendl, providing insights and support---Stewart has extensive experience supervising postdoctoral researchers.
+A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities.
+This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research.
+Stewart will contribute to the research design and writing academic papers.
+
+Other Directly Incurred Costs
+
+We request funds for a data processing computer for use by PDRA Trendl.
+A high specification computer is critical for this work.
+The size of the datasets mean that a standard specification desktop computer often cannot even open the large data files, and the complexity of the required analysis means data processing can be prohibitively slow.
+Due to the sensitivity of the data being used, and the necessary security considerations, we cannot make use of other computing solutions as the researchers must maintain absolute control over the storage and access to the data.
+
+Travel and Subsistence
+
+We request support for regular trips to Birmingham, to facilitate ongoing collaboration and communication with partners at West Midlands Police HQ.
+In addition we request funding for travel to London to support the communication of results to national policy makers including contacts within the Metropolitan Police Service.
+We request support to attend academic conferences: we anticipate presenting the results at 2 European conferences, and 1 international conference.
+This will allow us to gain insight and input from other academic experts, and engage a wide range of academic beneficiaries.
+
+Accumulating to Choose
 

### 2019-07-29 case_for_support_TM_hacked.tex
Anna cfs update

@@
 This research programme consists of four research topics aiming to deepen our understanding of domestic abuse victimisation, by exploiting the rich information contained in the CSEW, and combine it with insights from other data sources.
-First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse, and the predictors of suffering serious harm.
-Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and victim's perception of the police after reporting an incident.
-Third, we will attempt to quantify the long-term effects of being a victim of domestic abuse, and witnessing domestic abuse at home as a child.
+First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse and the predictors of suffering serious harm.
+Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases and victim's perception of the police after reporting an incident.
+Third, we will attempt to quantify the long-term effects of being a victim of domestic abuse and witnessing domestic abuse at home as a child.
 Finally, we explore the association between exogenous, time-varying factors, such as changes in alcohol consumption and financial resilience, and the prevalence of domestic abuse.
@@
 The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular.
-Given the serious problem of underreporting, one of the unique characteristic of domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
+Given the serious problem of underreporting, one of the unique characteristics of domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.
 We have access to this dataset via the UK Data Service.
@@
 The CSEW provides us with rich demographic and socio-economic information on the respondent, and to investigate the casual effects of domestic abuse victimisation, we can construct a control group from those individuals who have not experienced domestic abuse.
-However, it does not contain any information on the perpetrators, and has limited longitudinal information.
-In contrast, the WMP dataset has information on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to analyse temporal patterns, and identify high-risk times of the year.
+However, it does not contain any information on the perpetrators and has limited longitudinal information.
+In contrast, the WMP dataset has information on both the victim and the offender, and records all reported incidents for the same victim-offender pair, allowing us to analyse temporal patterns and identify high-risk times of the year.
 We will not link the individuals in these datasets at any time.
@@
 This research programme addresses four overarching topics, exploring different aspects of domestic abuse.
-Drawing on the extensive, rich respondent information in the CSEW, and the unique, temporal nature of the WMP data, this research complements, extends and deepens our understanding of domestic abuse.
+Drawing on the extensive, rich respondent information in the CSEW and the unique, temporal nature of the WMP data, this research complements, extends and deepens our understanding of domestic abuse.
 In outlining the analysis plan for each of these research topics, we will specify a set of statistical analyses we plan to conduct.
@@
 Investigating the explanatory power of a broader set of victim characteristics within one (logistic) regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
-We are also interested in how the predictive power of victim characteristics vary with the type of abuse suffered (physical abuse, threats, sexual abuse).
+We are also interested in how the predictive power of victim characteristics varies with the type of abuse suffered (physical abuse, threats, sexual abuse).
 
@@
 Using the CSEW, we will be able to tell whether the type of domestic abuse reported by the respondent is likely to amount to a crime according to the list of notifiable offences \cite{countingrules}.
-A multinomial regression approach will allow us to examine the extent to which police mis-reporting is different across broad crime types (sexual, physical violence, harassment and stalking), and depends upon the socio-economic characteristics of the victim and police forces (e.g., funding per police officer, deprivation).
+A multinomial regression approach will allow us to examine the extent to which police mis-recording is different across broad crime types (sexual, physical violence, harassment and stalking), and depends upon the socio-economic characteristics of the victim and police forces (e.g., funding per police officer, deprivation).
 Complementing this analysis with a random forest approach will reveal the role of interactions between individual and police force characteristics.
@@
  Domestic abuse has long-lasting adverse effects on victims and children witnessing the abuse.
-In this research topic, our is aim to explore some of these consequences.
+In this research topic, our aim is to explore some of these consequences.
 The 2016 CSEW included a module asking respondents about whether they witnessed domestic abuse at home as a child.
@@
 We will further complement this analysis using WMP data, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
-It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crime they engage in.
+It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crimes they engage in.
 For example, whether, after controlling for the socio-economic characteristics of the neighbourhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
 
- These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
+ These analyses will constitute the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
 The resulting paper will be targeted at The Lancet Public Health, and Social Science and Medicine.
@@
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
-This analyses will constitute the first empirical investigation of the direct effect of welfare policy changes on domestic abuse victimisation.
+These analyses will constitute the first empirical investigation of the direct effect of welfare policy changes on domestic abuse victimisation.
 

### 2019-07-29 case_for_support_TM_hacked.tex
Anna cfs update

@@
 This statistical estimation approach will alleviate the problem of spatial dependency between neighbourhoods, and will allow us to derive a precise estimate of the effect of temporal changes in community-level alcohol consumption and financial health on the prevalence of domestic abuse in the neighbourhood.
-
-We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and  how these affect the reported number of domestic abuse incidents in that area in a given time period.
+We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and explore how these affect the reported number of domestic abuse incidents in that area in a given time period.
 Previously, our research has identified a 60\% increase in alcohol-related domestic abuse when the England national football team won.

### 2019-07-29 case_for_support_TM_hacked.tex
Anna cfs done

@@
 Domestic abuse has substantial mental health implications, which are not limited to the direct target of abuse \cite{ferrari}, but can have a profound effect on the lives of children witnessing domestic abuse at home \cite{callaghan}.
-Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays, health care costs, and the reduced quality of life for survivors \cite{costs}.
+Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays and reduced quality of life for survivors, and costs to the health care system \cite{costs}.
 
@@
 
-This research programme consists of four research topics aiming to deepen our understanding of domestic abuse victimisation, by exploiting the rich information contained in the CSEW, and combine it with insights from other data sources.
-First, we will explore the demographic and socio-economic characteristics of victims of domestic abuse and the predictors of suffering serious harm.
-Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases and victim's perception of the police after reporting an incident.
-Third, we will attempt to quantify the long-term effects of being a victim of domestic abuse and witnessing domestic abuse at home as a child.
-Finally, we explore the association between exogenous, time-varying factors, such as changes in alcohol consumption and financial resilience, and the prevalence of domestic abuse.
+This research programme consists of four research topics aiming to deepen our understanding of various aspects of domestic abuse victimisation, by exploiting the rich information contained in the CSEW, and combining it with insights from other data sources.
+First, we will explore the demographic and socio-economic risk factors of victimisation, and the predictors of suffering serious harm.
+Second, we will examine the reasons behind not just under-reporting from victims, but also police mis-recording of domestic abuse cases, and the predictors of victim's satisfaction of the police after reporting an incident.
+Third, we will quantify the long-term effects of being a victim of domestic abuse and witnessing domestic abuse at home as a child.
+Finally, we will explore the association between exogenous, time-varying community-level factors, such as changes in neighbourhood alcohol consumption and financial resilience, and the prevalence of domestic abuse.
 
@@
 
-The research projects detailed below draw on various data sources.
+The research topics detailed below draw on various data sources.
 All of the projects rely on the CSEW, an annual, cross-sectional representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year \cite{OfficeforNationalStatistics2019}.
@@
 
-Some of the projects also benefit from an anonymised crime dataset provided by the West Midlands Police (WMP; the third largest police force in England, serving a population of 2.9 million; \citeNP{Homeoffice}), which includes all crimes and incidents recorded by the police force between 2010 and 2018, of which about 31\% are domestic abuse-related.
-For each record in this dataset, we know the exact location, time, the gender, age, ethnicity and address of those involved, and the severity of the injury.
+Some of the analyses will also benefit from an anonymised crime dataset provided by the West Midlands Police (WMP; the third largest police force in England, serving a population of 2.9 million; \citeNP{Homeoffice}), which includes all crimes and incidents recorded by the police force between 2010 and 2018, of which about 31\% are domestic abuse-related.
+For each record in this dataset, we know the exact location, time, the gender, age, ethnicity and address of those involved, and the severity of the injury sustained.
 Each person has a person identifier, allowing us to follow people over time.
@@
 
-One proposed project relies on a dataset containing credit card and current account spending of 20 million customers across the UK.
+One proposed analysis relies on a dataset containing credit card and current account spending of 20 million customers across the UK.
 We have access to this data as part of a data sharing agreement with one of the ``Big 4''  UK banks.
@@
 At no point will individual data be used, only geographic, LSOA level, aggregates.
+
 In addition, for analyses that rely on neighbourhood-level characteristics, we will use the Indices of Multiple Deprivation (IMD; \citeNP{IMD}).
@@
 
-Investigating the explanatory power of a broader set of victim characteristics within one (logistic) regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
+Investigating the explanatory power of a broader set of victim characteristics within one logistic regression model will provide us with a deeper understanding of the relative importance of these factors in predicting domestic abuse victimisation, compared to a purely descriptive statistics approach.
 We are also interested in how the predictive power of victim characteristics varies with the type of abuse suffered (physical abuse, threats, sexual abuse).
@@
 The strength of the WMP data is that it has a temporal dimension, and we can follow the same perpetrator-victim pair over time.
-Using a logistic regression approach with perpetrator-victim fixed effects (FE), we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
-Insights from these analyses will help the police to assess the validity of their current risk assessment model, and can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns to protect victims.
+Using a logistic regression approach with perpetrator-victim fixed effects, we will examine whether acts of serous harm can be predicted by previous self-harm and suicide attempts (which required police attendance), previous violent and drug offences, breaches of court orders, co-habitation with, and separation from the victim.
+Insights from these analyses will help the police to assess the validity of their current risk assessment model, and can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns aiming to protect victims.
 
@@
                     What perpetrator characteristics predict serious harm?
-& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, violent and drug offences, breach of court orders, separation &  Logistic regression with perpetrator-victim FE \\
+& WMP & Perpetrator-victim pairs & Violent offences resulting in injury & previous self-harm and suicide attempts, violent and drug offences, breach of court orders, separation &  Logistic regression with perpetrator-victim fixed effects \\
 %    Beznau II & 23.10.1971 & Pressurised water reactor & 365   & 2031 \\
@@
 Descriptive statistics of this dataset revealed that those who reported to have witnessed abuse as a child were significantly more likely to report long-term health problems, and live in a single parent household as an adult \cite{ONSChildhood}.
-First, we will consolidate and extend these findings using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse, whilst also controlling for a range of confounds, such as economic deprivation.
+We will consolidate and extend these findings using propensity score matching, a statistical approach that allows for causal inferences to be drawn about the effect of witnessing abuse, whilst also controlling for a range of confounds, such as economic deprivation.
+The CSEW will allow us to construct relevant control groups for all of these analyses.
  %Gaining a deeper understanding of the tangible, far-reaching consequences of domestic abuse will help to design survivor support programmes and quantify the societal harm caused by it.
@@
 
-Second, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home.
-The CSEW questionnaire for 10-15 year old's records information about experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
-By applying propensity score matching, we will explore the causal effect of living in an abusive household on these outcomes.
-
-We will further complement this analysis using WMP data, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
-It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crimes they engage in.
-For example, whether, after controlling for the socio-economic characteristics of the neighbourhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
-
- These analyses will constitute the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
-The resulting paper will be targeted at The Lancet Public Health, and Social Science and Medicine.
+Using the 2016 CSEW, we will first explore how witnessing domestic abuse as a child affects socio-economic outcomes in adulthood.
+We will also investigate whether past, but not recent (past 12 months) domestic abuse victimisation affects health and employment outcomes in adulthood, to understand the long lasting effects of victimisation.
+In addition, we will explore how children's behavioural problems are affected by witnessing domestic abuse at home, using the rich information recorded by the 10-15 year old's module of the CSEW on experiences with bullying, carrying knives, gang membership, school truancy, learning difficulties and health outcomes, including drug use and drinking behaviour.
 
@@
 
+We will further complement this analysis using WMP data, by identifying whether younger offenders' home addresses can be linked to a past domestic abuse incident.
+It is not possible to predict whether witnessing domestic abuse increases the chance of becoming a young offender, but we can examine whether it predicts the type of crimes they engage in.
+For example, whether, after controlling for the socio-economic characteristics of the neighbourhood (using the IMD), such individuals are more likely to commit similarly violent acts than other young offenders.
+
+ These analyses will constitute the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.
+The resulting paper will be targeted at The Lancet Public Health, and Social Science and Medicine.
+
 %Aim:
@@
 First, using the CSEW and a logistic regression approach, we will explore the neighbourhood predictors of domestic abuse victimisation and willingness to report, using information on the interviewer's perception of the street (signs of rubbish, vandalism, general condition of houses etc.), and neighbourhood deprivation (measured by the IMD), whilst controlling for the socio-economic characteristics of the respondent.
-
-These analyses will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first project to provide a comprehensive exploration of the range of factors affecting domestic abuse victimisation and willingness to report.
+This analysis will extend our understanding of the neighbourhood-level predictors of domestic abuse victimisation, and complement our individual-level approach outlined in the first analysis plan to provide a comprehensive exploration of the range of factors affecting domestic abuse victimisation and willingness to report.
 
@@
 We will also explore the extent to which changes in alcohol consumption and financial stability on the community level affects the prevalence of domestic abuse.
-To do so, we will use the transaction data to construct an LSOA-level spending profile for a given time period to investigate how temporal changes in this profile affect the number of reported domestic abuse cases in that area, using a spatial panel regression model.
+We will use the transaction dataset to construct an LSOA-level spending profile for a given time period to investigate how temporal changes in this profile affect the number of reported domestic abuse cases in a given area, using a spatial panel regression model.
 This statistical estimation approach will alleviate the problem of spatial dependency between neighbourhoods, and will allow us to derive a precise estimate of the effect of temporal changes in community-level alcohol consumption and financial health on the prevalence of domestic abuse in the neighbourhood.
+
 We will identify external events that may affect alcohol consumption  and spending on gambling (e.g., festivals, weather, bank holidays, sport tournaments), and explore how these affect the reported number of domestic abuse incidents in that area in a given time period.
@@
 The fact that the exact date of the roll-out varied across the seven metropolitan boroughs within the county allows for a more precise estimation of the effect of UC on the reported number of domestic abuse incidents in the West Midlands.
-These analyses will constitute the first empirical investigation of the direct effect of welfare policy changes on domestic abuse victimisation.
+These analyses will constitute the first quantitative, large-scale investigation of the effect of welfare policy changes on domestic abuse victimisation.
 

### 2019-07-29 JeS_fields.tex
Anna update

@@
 
-2) To improve our understanding of the costs of domestic abuse, by quantifying the causal effect of victimisation on a variety of socio-economic outcomes.
+2) To improve our understanding of the economic costs of domestic abuse, by quantifying the causal effect of victimisation on a variety of socio-economic outcomes.
 Current cost estimates by the government do not take into account how educational attainment, income and employment status of victims are affected by victimisation and witnessing abuse as a child \cite{costs}.
@@
 3) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
-Our research will provide the police with important information to help the optimal geographical and temporal allocation of resources and improving recording practices.
-In addition, these insights will also help the government to design more effective intervention campaigns, and will be of interest to a wide range of academics.
+Our research will provide the police with important information to facilitate the optimal geographical and temporal allocation of resources and improvement of recording practices.
+In addition, these insights will also help the government to design more effective intervention campaigns to protect victims, and will be of interest to a wide range of academics.
 
-4) To utilise the rich information contained in the Crime Survey for England and Wales (CSEW) to explore the predictors and consequences of domestic abuse victimisation.
-In spite of the detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to explore the predictors and consequences of domestic abuse victimisation in England and Wales.
+4) To exploit the rich information contained in the Crime Survey for England and Wales (CSEW) to explore the predictors and consequences of domestic abuse victimisation.
+Despite the rich, detailed information contained in the CSEW about respondents, we are not aware of any non-exploratory study using the CSEW to understand the predictors and consequences of domestic abuse victimisation in England and Wales.
 We aim to take full advantage of the wealth of information in the CSEW in understanding domestic abuse.
@@
 The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse.
-Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion \cite{costs}.
+Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales was estimated to be as high as \pounds 66 billion in the year ending March, 2017 \cite{costs}.
 
@@
 
-Our project fills this gap in our current understanding of domestic abuse by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
-Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
+Our project fills this gap in our current understanding of domestic abuse, by taking advantage of the wealth of information contained in the CSEW, and drawing on other data sources to complement the findings.
+Applying sophisticated statistical techniques tailored to each analysis (including regression, random forest, and propensity score matching), we will identify the individual and neighbourhood-level predictors of domestic abuse victimisation, and the factors affecting victims' willingness to contact the police.
 We will also explore whether police mis-recording of domestic abuse-related crimes disproportionately affects certain victim groups.

### 2019-07-30 case_for_support_TM_hacked.tex
Anna cfs done

@@
 While anyone can become a victim of domestic abuse, women are disproportionately affected, with more than 25\% of women, and 15\% of men in England and Wales reported to have experienced some form of domestic abuse since the age of 16 \cite{ONS}.
-In the most extreme cases, domestic abuse can culminate in domestic homicide: in the period between April, 2017 and March, 2018, 70 people in England and Wales were killed by their current or former partner, and 90\% of these victims were women \cite{homic}.
+In the most extreme cases, domestic abuse can culminate in domestic homicide: in the year ending March, 2018, 70 people in England and Wales were killed by their current or former partner, and 90\% of these victims were women \cite{homic}.
 Domestic abuse has substantial mental health implications, which are not limited to the direct target of abuse \cite{ferrari}, but can have a profound effect on the lives of children witnessing domestic abuse at home \cite{callaghan}.
-Reflecting the severity of the problem, the economic cost of domestic abuse in England and Wales between April, 2016 and March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays and reduced quality of life for survivors, and costs to the health care system \cite{costs}.
+Reflecting the severity of the problem, the economic cost of domestic abuse in the year ending March, 2017 was estimated to be as high as \pounds 66 billion, which includes the cost of missed workdays and reduced quality of life for survivors, and costs to the health care system \cite{costs}.
 

### 2019-07-30 JeS_fields.tex

@@
 What predicts serious harm and victims' decision to finally report the abuse?
-What is the quantifiable, long-term impact of domestic abuse victimisation, or witnessing domestic abuse as a child on socio-economic and health outcomes in later life?
+What is the quantifiable, long-term impact of domestic abuse victimisation or witnessing domestic abuse as a child on socio-economic and health outcomes in later life?
 How do changes in alcohol consumption and financial stability affect the prevalence of domestic abuse?
@@
 By validating insights from previous, mostly qualitative investigations, we will provide a deeper understanding of the socio-economic factors and their interactions in perpetuating domestic abuse in England and Wales.
-While we will only use UK-specific data, insights from these analyses will likely to be applicable to non-UK contexts.
+While we will only use UK-specific data, insights from these analyses are likely to be applicable to non-UK contexts.
 
@@
 3) To translate our research into impact by delivering applicable insights for the relevant agencies, including the police and policy-makers.
-Our research will provide the police with important information to facilitate the optimal geographical and temporal allocation of resources and improvement of recording practices.
-In addition, these insights will also help the government to design more effective intervention campaigns to protect victims, and will be of interest to a wide range of academics.
+Our research will provide the police with important information to facilitate the optimal geographical and temporal allocation of resources and improvement of crime recording practices.
+In addition, these insights will also help the government to design more effective intervention campaigns to protect victims and will be of interest to a wide range of academics.
 
@@
 However, the true extent of the problem is still often underestimated, and hard to comprehend: 2 million adults in England and Wales (7.9\% of women and 4.2\% of men) reported to have experienced some form of domestic abuse in the year ending 2018 March \cite{ONS}, and 41\% of all women murdered in England and Wales in this period were victims of domestic homicide.
-The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but also has serious developmental implications for children witnessing the abuse.
+The long-lasting, damaging effects of domestic abuse are not limited to the direct target of abuse, but it also has serious developmental implications for children witnessing the abuse.
 Illustrating the extent of the societal harm caused by domestic abuse, the economic cost of domestic abuse in England and Wales was estimated to be as high as \pounds 66 billion in the year ending March, 2017 \cite{costs}.
@@
 While the Office for National Statistics (ONS) regularly publishes findings from the CSEW, these are mostly exploratory and descriptive in nature.
-Despite of the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
+Despite the rich information provided by this survey, only a limited number of studies have utilised the CSEW to explore the predictors of domestic abuse victimisation in England and Wales (e.g., \citeNP{Khalifeh2013a}).
 
@@
 Our work will primarily have implications for the police and policy-makers.
-For example, insights about the predictors of serious harm can inform the police protocol aiming to prevent domestic homicides, while understanding the extent to which crime mis-recording depends on victim characteristics will help the police understanding the causes of mis-recording and improve their practices.
-Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, reporting behaviour, the extent to which gambling and alcohol spending affects it, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood and socio-economic outcomes in later life.
+For example, insights about the predictors of serious harm can inform the police protocol aiming to prevent domestic homicides, while understanding the extent to which crime mis-recording depends on victim characteristics will help the police to understand the causes of mis-recording and improve their practices.
+Policy-makers will be able to design more effective awareness campaigns using information on the geographical and temporal characteristics of domestic abuse victimisation, reporting behaviour, the extent to which gambling and alcohol spending affects it, and better understand its far-reaching societal implications, with particular focus on the effect of domestic abuse victimisation on propensity to violence in young adulthood, and socio-economic outcomes in later life.
 
@@
 
-Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural science, criminology and health economics.
+Owing to the wide variety of questions we aim to answer, and the diverse methodological approaches we plan to employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural science, criminology and health economics.
 

### 2019-07-30 case_for_support_TM_hacked.tex
Update case_for_support_TM_hacked.tex

@@
 Finally, we will explore the association between exogenous, time-varying community-level factors, such as changes in neighbourhood alcohol consumption and financial resilience, and the prevalence of domestic abuse.
+
+The University of Warwick has identified this as an important line of research, and has committed to supporting it, and the Centre for Operational Policing Research, into the future.
+As part of this commitment, Warwick Business School has allocated funding for a 4 year PhD studentship.
+This will begin during the grant period and then run on after the end date.
+This allows for continued impact related work, and provides capacity to build upon initial findings from this project.
 

### 2019-07-30 pathways_to_impact.tex
N minor edits to pathways to impact
Update pathways_to_impact.tex

@@
 These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.
+Our model for impact is to have a senior-level sponsor and a day-to-day contact with each organisation we work with.
+Impact is only delivered by understanding the policy and operational concerns of each organisation and translating the research into direct actions within the organisation.
 
@@
 The programme on ``police mis-recording of abuse'', is of direct interest to their data quality and reporting, as well as identifying any potential shortcomings in the way they deal with reports from particular types of victims.
+It is of particular importance to victims, as mis-reporting can result in them being directed to the wrong support systems, which are not appropriate for their needs.
 
@@
 We will contact, in the first three months of project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.
+We will then follow up with these organisations at the end of the grant to present our overall conclusions and discuss how these can be most useful to the organisations' aims.
 
-In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue.
-This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account.
+In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue, and subsequently publish a summary including policy briefing notes.
+This will be funded by the Warwick Business School Impact Fund.
 We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry, and key contacts from the third sector agencies.
@@
 We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.
+These thought leadership pieces, as well as our other impact pathways will allow us to feed our results into the next Violence Against Women and Girls (VAWG) Strategy.
+The current strategy covers 2016 - 2020 \cite{vawag}, meaning we will be well placed to feed our results into the early stages of the subsequent strategy update.
+A primary goal of the 2016 - 2020 strategy is to identify victims at the earliest possible opportunity to prevent violence and abuse from escalating.
+Our results will be directly applicable to measuring success on this goal, and providing future direction.
 
@@
 
-PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme.
+PI Mullett will spend half of his time on the project leading the impact activity and takes overall responsibility of delivering the impact programme.
 Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority.
@@
 
-We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund and continue the impact programme beyond the end of the funded period.
+Warwick Business School's commitment of a 4 year PhD studentship to run beyond the end of the current project will allow us to continue impact activities into the future.
+To further support this impact activity beyond the end date of the current grant we will also utilize the Warwick Business School Impact Fund, and apply for funds from other sources.
+Future work will allow us to direct research questions towards the areas identified in this project, and in collaboration with our impact partners.
 

### 2019-07-30 pathways_to_impact.tex
Anna update

@@
 In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces.
-At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015, and contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse.
+At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015.
+Insights from our work on the predictors of serious harm will contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse.
+\citeNP{dash} have shown that the DASH framework has poor predictive performance, as only 4 out of 25 risk factors were associated with an increased risk of repeat perpetration.
 We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.

### 2019-07-30 pathways_to_impact.tex
Anna update

@@
 In addition to working with WMP, our links to the National Police Chiefs council, and collaboration with the CoP, provide pathways for impact across all forces.
-At the CoP (situated just a few miles from Warwick campus) we will work within the framework of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} released in 2015.
+Our work will contribute to the ongoing refinement of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} framework in the context of domestic abuse.
+This framework is the primary guidance for police response strategy, there this refinement will result in real change in policing practices and improve victims' experiences.
 Insights from our work on the predictors of serious harm will contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse.

### 2019-07-30 justification_of_resources.tex
Minor edits from Neil

--- 2019-07-23 justification_of_resources.tex
@@
 Justification of Resources
+
+Staff, Directly Incurred Posts
+
+PDRA Trendl.
+We request 100\% support for PDRA Trendl.
+A postdoctoral appointment is essential here, as the level of technical skill required to run the econometric analysis of these large and complex datasets is high.
+Furthermore, Trendl has extensive experience with these datasts, having already completed a project on the effects of Football tournaments on Domestic Abuse during her PhD.
+As outlined in Staff Duties, Trendl will conduct the statistical analyses and act as first author on the majority of publications.
+Trendl will also take an active role in impact activities, building upon existing relationships with West Midlands Police (WMP) that were developed during her PhD research, and developing a network of contacts as this project supports her development as an Early Career Researcher.
+
+Staff, Directly Allocated Posts
+
+PI Mullett.
+We request 15\% support for Mullett.
+Half of this support will be spent on supporting the empirical work.
+This includes providing support and supervision to PDRA Trendl, as well as data management duties requiring level 3 police vetting, such as data cleaning, outputting from the highly sensitive data of appropriately sanitised/annonymised versions of the dataset for the other researchers.
+The other half of the support will be spent on impact activities.
+Academic faculty support is required to maximise the potential impact of the research.
+Mullett's existing relationship with WMP is strong.
+A PI level contribution is required for gaining the contacts and invitations to collaborate with policy makers, which will be assisted by Mullett's Membership of the Centre for Operational Policing Research.
+
+CI Stewart.
+We request 10\% support for Stewart.
+Stewart will split time between assisting with the research design and implementation and the impact programme.
+He will meet regularly with PI Mullett and PDRA Trendl, providing insights and support---Stewart has extensive experience supervising postdoctoral researchers.
+Stewart will exploit close links with WMP, the College of Policing, and the Metropolitan Police, and membership of the Centre for Operational Policing.
+Stewart will contribute to writing academic papers and policy / thought leadership pieces.
+
+Other Directly Incurred Costs
+
+We request funds for a data processing computer for use by PDRA Trendl.
+A high specification computer is critical for this work.
+The size of the datasets mean that a standard specification desktop computer often cannot even open the large data files, and the complexity of the required analysis means data processing can be prohibitively slow.
+Due to the sensitivity of the data being used, and the necessary security considerations, we cannot make use of other computing solutions as the researchers must maintain absolute control over the storage and access to the data.
+
+Travel and Subsistence
+
+We request support for regular trips to Birmingham, to facilitate ongoing collaboration and communication with partners at West Midlands Police HQ.
+In addition we request funding for travel to London to support the communication of results to national policy makers including contacts within the Metropolitan Police Service.
+We request support to attend academic conferences: we anticipate presenting the results at 2 European conferences, and 1 international conference.
+This will allow us to gain insight and input from other academic experts, and engage a wide range of academic beneficiaries.
+
+Accumulating to Choose
 

### 2019-07-30 pathways_to_impact.tex
Anna update

@@
 Our work will contribute to the ongoing refinement of the \href{https://www.app.college.police.uk/app-content/major-investigation-and-public-protection/domestic-abuse/introduction/)}{Authorised Professional Practice} framework in the context of domestic abuse.
-This framework is the primary guidance for police response strategy, there this refinement will result in real change in policing practices and improve victims' experiences.
+This framework is the primary guidance for police response strategy, therefore it has real impact on policing practices and victims' experiences.
 Insights from our work on the predictors of serious harm will contribute to the \href{https://whatworks.college.police.uk/Research/Documents/DA_risk_assessment_pilot.pdf}{revision of the existing DASH risk assessment tool} for domestic abuse.
-\citeNP{dash} have shown that the DASH framework has poor predictive performance, as only 4 out of 25 risk factors were associated with an increased risk of repeat perpetration.
+\citeA{dash} have shown that the DASH framework has poor predictive performance, as only 4 out of 25 risk factors were associated with an increased risk of repeat perpetration.
 We will work initially with David Tucker, Head Crime and Criminal Justice at the CoP.

### 2019-07-31 Data_Management_Plan.tex
Files and stuff

\documentclass[doc]{apa6}
\captionsetup{singlelinecheck=on}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage{hyperref}
\bibliographystyle{apacite}
\usepackage{apacite}
\usepackage{color}
\usepackage{tabularx,colortbl}
\usepackage{textcomp}
\usepackage{eurosym}
\usepackage{pdflscape}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{afterpage}
\usepackage{adjustbox}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{setspace}
\usepackage{rotating}
%\DeclareDelayedFloatFlavor{sidewaystable}{table}
%\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\usepackage{siunitx}
\usepackage{xfrac}
\singlespacing
\newcommand{\todo}[1] {{\textcolor{red}{#1}}}

\title{Data Management Plan}

\shorttitle{Data Management Plan}

%\abstract{%\doublespacing}

%\keywords{data mangement plan}

\begin{document}
\maketitle

\section{Personally Identifying Information}

Where possible, our strong preference is not to collect or receive personally identifiable information (PII) such as name, photographs of faces, home addresses, credit card numbers, date of birth, email addresses, etc. Where such information is held, it is classified as \emph{restricted} or more likely \emph{reserved} under the University's information security procedures. The procedures below are designed to meet the higher \emph{reserved} standard.

We appreciate that the anonymity of data is not limited to consideration of personally identifying information (e.g., name, date of birth, address). Instead we take the view of considering what data a potential adversary might hold and be able to match against our data \cite{LeaseHullmanBighamBernsteinKimLaseckiBakhshiMitraMiller13,deMontjoyeRadaelliSinghPentland15}.

\section{Quality Assurance of Data}

The lead author for a paper is responsible for the QA process for the data in that paper, and the data manager for the overall project/dataset is responsible for collating QA information and communicating it to the relevant researchers, or external partners. We will conduct a set of independent replications of key results (e.g., with a simple linear regression in place of a more complicated econometric specification). We will also assess the match between our analysis and publicly available industry or regulator aggregate and summary statistics (e.g., the fraction of people defaulting on their card in any month, etc.). Finally, by linking data sets with public data, we can assess the data quality. For example the prevalence of cash advance charges on credit cards correlates with the fraction of children receiving free school meals in the public domain School Census data, at the level outbound postcode sectors (all but the last two letters).

In addition, we describe specific QA for specific datasets. Financial services in the UK have statutory duties with regard to the collation and maintenance of accurate records under the European Credit Directive and as part of their broader obligations under the Data Protection Act. Thus Barclays and Lloyds have their own internal quality assurance process, as do the credit card providers who have shared data with us in collaboration with the UK Cards Association and the data aggregator Argus. The police has a statutory duty to report statistics (e.g., recorded crime, stop and search) to the Home Office.

\section{Backup and Security of Data}

\subsection{Storage}

Data for the majority of datasets are held on servers physically at Warwick. These servers are fully encrypted at rest, rendering data inaccessible in the event of physical theft. These are further backed up to University of Warwick file stores. All data transferred off-site for backup are encrypted beforehand, preventing data access within the backup system. Backups are maintained under standard University of Warwick information services policies. Storage on removable media (e.g., USB sticks, external hard drives) or laptops is not permitted.

For police data that includes identifying information and that requires level 3 vetting to access, the data will not be stored on a server, but on a single machine. Hard drives on this machine are at rest encrypted, with the sensitive data held on virtual drives with an additional layer of encryption. These virtual drives are only mounted and made accessible when a level three vetted researcher is working on the data. The machine is stored in a physically secure room, and only level 3 vetted individuals have login credentials or encryption passwords.

\subsection{Transfer}

To protect against data interception during transfer, data are only ever transferred over encrypted channels, or, data are encrypted before being placed on an unencrypted channel or device, with PGP keys or separately communicated symmetric keys. Where possible, we prefer to use secure FTP to transfer data. Alternatively, encrypted data can be shared by the warwick.files service. Where use of a physical device is absolutely necessary, data must be encrypted. Sharing of data unencrypted data by email attachment is forbidden. Use of Google Drive, Dropbox, etc., is forbidden.

\subsection{Access}

Data are only accessed by a limited, named set of researchers. Strong passwords are enforced and two factor authentication used. Physical access is restricted by locked office or server room doors. Logins are logged. Password protected lock screens are used on all data access computers, protecting the data while machines are on but the operator is away.

\subsection{Data Provided by Industry Partners}

ESRC Research Data Policy does not specify requirements for handling data provided by 3rd parties (i.e., industry partners). Here we follow the Engineering and Physical Sciences Research Council (EPSRC) policy framework on research data. Ethical and legal responsibilities are undertaken by the company collecting the data. Data are held under conditions of the specific company agreements. Company specific legal and ethical procedures will be undertaken and conformed to on a case-by-case basis. Additional ethical and legal considerations, that may extend past 3rd party responsibilities, are undertaken on a per dataset basis within the University of Warwick. This is compliant with EPSRC guidelines, specifically: ``Research Organisations are not expected to assume responsibility for the preservation and management of third party research data not generated within their own organisation'' [clarification of Expectation VII]. When data are used to support research findings (becoming research data under EPSRC definitions) then metadata, as defined by the EPSRC, will be published alongside journal articles in order to support research replicability. Additionally, meeting EPSRC Expectation II, published research papers will include a short statement describing ``how and on what terms any supporting research data may be accessed'' noting that this data are covered by the clause in the provided clarification document stating that access is restricted due to ``compelling legal or ethical reasons [that] exist to protect access to the data''. For confidential and/or sensitive data, metadata will be limited to a researcher contact and a statement indicating that data access was under legal agreement and that ``compelling legal or ethical reasons exist to protect access to the data''. UK Data Protection Act compliance responsibilities are undertaken by the company collecting the data.

\subsection{Data Collected by Us}

Any personal data collection will require and be governed by University of Warwick Humanities and Social Sciences Research Ethics Committee, in addition to any other funder requirements. Data will be held for 10 years from date of last use/access by a third party [EPSRC Expectation VII]. Data will not publicly accessible [EPSRC Expectation II, Expectation VI]. Meta-data will be publicly published, including access statement detailing the route to access [EPSRC Expectation V, Expectation VI]. UK Data Protection Act compliance responsibilities are undertaken by University of Warwick.

\section{Expected Difficulties in Data Sharing}

We will provide full contact details for data collected by third parties as part of the meta data [EPSRC Expectation V, Expectation VI]. Thus other researchers will be able to request the same or additional extracts. For data collected by us, data will be freely available and will be deposited at the UK Data Archive. We will use standard CSV file formats with accompanying README files detailing the column headings. For confidential and/or sensitive data collected by us, sharing is limited to metadata and a statement indicating that data access was under legal agreement and that ``compelling legal or ethical reasons exist to protect access to the data''. Confidential or sensitive data will not be publicly available [EPSRC Expectation II, Expectation VI].

\section{Copyright/Intellectual Property Right}

The data provided by third parties remains the property of the industry partners and these rights are not transferable.

\section{Responsibilities}

All researchers on the project will share responsibility for the data. Mullett is the data license holder. Mullett is responsible for data security, processing, quality assurance, archiving, and for providing researchers with the appropriate level of data access given their vetting and research projects.

\section{University and Other Relevant Bounding Policies}

Warwick works with confidential and sensitive data every day from a wide range of sources (e.g., credit card records, medical records, police and security services data). As employees of Warwick all researchers are bound by:

\begin{itemize}
	\item The University's obligations under UK Data Protection Legislation
	\item Locally by University data protection policies
	\item The University research ethics committees specialising in the use of human data in the social sciences
	\item The professional bodies for Psychology and Economics in the UK
	\item The ethical requirements of the scientific journals in which they publish
\end{itemize}

Relevant links are:

\begin{itemize}
	\item All lab members should be aware of \href{https://warwick.ac.uk/services/idc/}{University policies} and their obligations under those policies
	\item British Psychological Society \href{https://www.bps.org.uk/news-and-policy/bps-code-ethics-and-conduct}{Code of Conduct}
	\item University \href{http://www2.warwick.ac.uk/services/ris/research\_integrity/researchethicscommittees/hssrec/}{HSSREC}
	\item \href{https://epsrc.ukri.org/files/aboutus/standards/clarificationsofexpectationsresearchdatamanagement/}{EPSRC standards}
\end{itemize}

%\bibliography{refs}
\bibliography{local_refs}

\end{document}

### 2019-07-31 Data_Management_Plan.tex
fiel changes

@@
 \newcommand{\todo}[1] {{\textcolor{red}{#1}}}
+\usepackage[margin=0.2in]{geometry}
 
@@
 
-The lead author for a paper is responsible for the QA process for the data in that paper, and the data manager for the overall project/dataset is responsible for collating QA information and communicating it to the relevant researchers, or external partners.
+The lead author for a paper is responsible for the QA process for the data in that paper, and the data manager for the overall project/dataset.
+The data manager is also responsible for collating QA information and communicating it to the relevant researchers, or external partners.
 We will conduct a set of independent replications of key results (e.g., with a simple linear regression in place of a more complicated econometric specification).
@@
 For example the prevalence of cash advance charges on credit cards correlates with the fraction of children receiving free school meals in the public domain School Census data, at the level outbound postcode sectors (all but the last two letters).
-
-In addition, we describe specific QA for specific datasets.
-Financial services in the UK have statutory duties with regard to the collation and maintenance of accurate records under the European Credit Directive and as part of their broader obligations under the Data Protection Act.
-Thus Barclays and Lloyds have their own internal quality assurance process, as do the credit card providers who have shared data with us in collaboration with the UK Cards Association and the data aggregator Argus.
-The police has a statutory duty to report statistics (e.g., recorded crime, stop and search) to the Home Office.
 
@@
 
-\subsection{Data Collected by Us}
-
-Any personal data collection will require and be governed by University of Warwick Humanities and Social Sciences Research Ethics Committee, in addition to any other funder requirements.
-Data will be held for 10 years from date of last use/access by a third party [EPSRC Expectation VII].
-Data will not publicly accessible [EPSRC Expectation II, Expectation VI].
-Meta-data will be publicly published, including access statement detailing the route to access [EPSRC Expectation V, Expectation VI].
-UK Data Protection Act compliance responsibilities are undertaken by University of Warwick.
-
-\section{Expected Difficulties in Data Sharing}
-
-We will provide full contact details for data collected by third parties as part of the meta data [EPSRC Expectation V, Expectation VI].
-Thus other researchers will be able to request the same or additional extracts.
-For data collected by us, data will be freely available and will be deposited at the UK Data Archive.
-We will use standard CSV file formats with accompanying README files detailing the column headings.
-For confidential and/or sensitive data collected by us, sharing is limited to metadata and a statement indicating that data access was under legal agreement and that ``compelling legal or ethical reasons exist to protect access to the data''.
-Confidential or sensitive data will not be publicly available [EPSRC Expectation II, Expectation VI].
-
-\section{Copyright/Intellectual Property Right}
-
-The data provided by third parties remains the property of the industry partners and these rights are not transferable.
-
 \section{Responsibilities}
@@
 
-\section{University and Other Relevant Bounding Policies}
-
-Warwick works with confidential and sensitive data every day from a wide range of sources (e.g., credit card records, medical records, police and security services data).
-As employees of Warwick all researchers are bound by:
-
-\begin{itemize}
-	\item The University's obligations under UK Data Protection Legislation
-	\item Locally by University data protection policies
-	\item The University research ethics committees specialising in the use of human data in the social sciences
-	\item The professional bodies for Psychology and Economics in the UK
-	\item The ethical requirements of the scientific journals in which they publish
-\end{itemize}
-
-Relevant links are:
-
-\begin{itemize}
-	\item All lab members should be aware of \href{https://warwick.ac.uk/services/idc/}{University policies} and their obligations under those policies
-	\item British Psychological Society \href{https://www.bps.org.uk/news-and-policy/bps-code-ethics-and-conduct}{Code of Conduct}
-	\item University \href{http://www2.warwick.ac.uk/services/ris/research\_integrity/researchethicscommittees/hssrec/}{HSSREC}
-	\item \href{https://epsrc.ukri.org/files/aboutus/standards/clarificationsofexpectationsresearchdatamanagement/}{EPSRC standards}
-\end{itemize}
-
 %\bibliography{refs}

### 2019-07-31 justification_of_resources.tex
fiel changes

@@
 This will allow us to gain insight and input from other academic experts, and engage a wide range of academic beneficiaries.
-
-Accumulating to Choose
-
-Staff, Directly Incurred Posts
-
-PDRA Mullett. We request 100\% support for PDRA Mullett. A postdoctoral appointment is
-essential here, as the level of technical skill required to run and analyse eye movement data is
-high. As outlined in Staff Duties, Mullett will design the studies with the PI and lead on the
-writing of the majority. Mullett will program the eye movement system and implement the
-statistical analysis designed with the PI using the R and Matlab programming languages.
-Mullett will also take a secondary role in the impact programme, and lead on the supermarket
-collaboration.
-
-PDRA at Caltech. We seek 100\% support for a 1-year PDRA at Caltech. The experimental
-games eye tracking from Series 1, 3, 5, and 6 will be conducted at Caltech, together with a
-subset of cross-lab replications.
-
-RA. We request 25\% support for an RA. BSc or MSc level training in Psychology or
-Behavioural Science will be sufficient. As outlined in Staff Duties, testing of participants one-
-by-one, and testing 100 people is about 3 weeks of full time work. RA support will free
-PDRA time for the more skilled writing and analysis.
-
-Staff, Directly Allocated Posts
-
-PI Stewart. We request 30\% support for Stewart. 15\%, half of this support, will be spent on
-the laboratory programme, designing experiments and analysing data with the PDRA.
-Stewart has developed a new statistical analysis for eye movement data (see two papers
-forthcoming in Journal of Behavioural Decision Making) and this work will continue here.
-The other 15\% is required for the ambitious impact work, which requires professorial level
-and extensive liaison with the three current industry partners to negotiate access to data and
-field trials, to set up access to three new partners, and to disseminate results back into
-industry.
-
-CI Chris Starmer. We will seek 10\% support for significant input from Experimental
-Economist Prof. Starmer. Because of the interdisciplinary nature of the research, this
-contribution is important for maximising the academic impact of the work beyond
-Psychology.
-
-Other Directly Incurred Costs
-
-Computer resources. The computations required to estimate drift diffusion models and assess
-model flexibility (e.g., with parameter space partitioning, Mullett & Stewart, 2015; Pitt,
-Woojae, Navarro, & Myung, 2006) require serial search of model parameter spaces.
-Compared to typical regressions which take fractions of a second, these methods take of the
-order of days or weeks on, for example, a typical Intel 8-core i7-4770 CPU. We request
-£2,000 for this dedicated computer machine.
-
-Travel and Subsistence
-
-We seek the costs of day visits to impact partners, all London based. We anticipate 6 visits per year x 2 people x 3 years. We will attend the SJDM conferences in 2016 and 2017. 2
-people x 2 years (Vancouver and New Orleans) and the SPUDM conference (European city)
-in 2017. These conferences are the most significant in the domain, giving coverage of
-America and Europe. We seek the cost of a postdoc exchange with Prof. Colin Camerer at
-Caltech. Caltech is the home of Camerer and Rangel labs, leaders in eye tracking economics.
-
-From machine learned personality grant:
-
-Justification of Resources
-Staff, Directly Incurred Posts
-Personality Psychology PDRA Skatova.
-We request 100% 36 months support for PDRA Skatova.
-A postdoctoral appointment is essential because the position requires high level of technical skills with psychometric approaches, as well as an advanced knowledge of the personality literature.
-The project is on the intersection of psychology and computer science, and thus experience across economics, computer science, and psychology that Skatova has will be essential.
-Further, experience translating output to industry, and experience of working with industry partners is essential.
-As outlined in Staff Duties, Skatova will design analyses with the investigators, and lead on the writing of publications.
-Skatova will implement the statistical analysis using the R programming language.
-Skatova will lead on contacts with industry partners (particularly Boots, Tesco and Barclays) and public policy collaborators (particularly the BIT and Which?).
-PDRA Computer Scientist.
-We request 100% 36 months support for a PDRA in the domains of data science, computer science, or machine learning.
-Postdoctoral experience of advanced algorithms and management of very large data sets is essential.
-The PDRA will lead on the writing of publications.
-The PDRA will supervise the management of data.
-The PDRA will develop the ML Personality Toolbox.
-Both PDRAs will be involved in the Pathways to Impact demonstrators and workshops.
-Lab manager.
-We request 10% 36 months support for a lab manager to support communication between the project team and project partners, implementing Data Management Plan as well as organization of Pathway to Impacts events including the workshops, MOOC and other public dissemination.
-Staff, Directly Allocated Posts
-PI Stewart.
-We request 20% 36 months support for psychologist Stewart.
-10%, half of this support, will be spent on the scientific programme, designing analyses of the data with the PDRA.
-Stewart has significant experience working with very large data sets, including financial transactions and police records.
-The other 10% is required for the ambitious impact work, which requires professorial level standing and extensive liaisons with the collaborators.
-Stewart will lead on contacts with the credit card industry and UBS.
-Stewart will oversee the second and third impact demonstrator.
-CI Goulding.
-We request 15% 36 months support for Goulding.
-10% of this support will be spent integrating personality concepts with the development of machine learning algorithms for very sparse transaction data.
-The other 5% support is required for the impact work.
-Goulding will oversee the first impact demonstrator.
-CI Chater.
-We request 10% 36 months support for Chater.
-Chater has extensive experience in mathematical psychology and the application to broad, domain-general principles of cognition.
-Chater also has significant experience in applying behavioural science to consumer behaviour as a director of Decision Technology.
-Finally Chater has led the “Mind is Flat” MOOC, one of Europe’s largest online courses, now in its fifth year and will supervise setting the MOOC for this project (see Pathways to Impact).
-Other Directly Incurred Costs
-Computer resources.
-We request support for (University non-standard) PCs.
-These require encrypted 6 TB HDDs to store the retail data, and enough RAM (64 GB) to run analyses without swapping to the HDD.
-The OS will be hosted on modest SSDs.
-Only typical desktop CPUs are required (e.g., Intel 8-core i7-4770), with only standard graphics.
-A non-standard PC is required for Psychology PDRA at £1,600; and a specialist PC is required for CS PDRA at £2,484 with a larger SSD and a second processor to deliver enough threads for the machine learning algorithms.
-Since the project requires coordinating collaborators and project partners in various places across the country and well as geographically distributed Pathways to Impact activities, we request a laptops for Warwick Psychology PDRA who will be in charge with coordinating all partner activities to fulfil project plan, at £1,400.
-Cost of MOOC. We seek resources to develop a “Personality Data Science” MOOC: £10,000.  
-Impact Workshops. We request support for four full one-day workshops, 20 people each at Shard, London.  
-Travel and Subsistence.
-We seek the costs of travel between Warwick and Nottingham (75 trips over 5 investigators and 36 months) for project meetings between UoN and UoW investigators, as well as project partners who are based in Nottingham (Boots, Nutracheck), travel between Warwick and London to meet with project partners and for workshops (55 trips over 3 investigators and 36 months), travel between Nottingham and London to meet with project partners and for the workshops (48 trips, 2 investigators and 4 project partners from Nottingham, over 36 months).
-We also request cost for longer stay of Warwick PDRA in Nottingham to develop ML personality approaches with UoN CI and PDRA, and vice versa: travel and subsistence for 8 trips 2 weeks each Warwick to Nottingham for Warwick PDRA, and travel and subsistence for 8 trips 2 weeks each Nottingham to Warwick for Nottingham PDRA.
-Conferences.
-4 CS conferences (2 UK, 2 europe, 2 overseas); 5 Psychology and Behavioural Science conferences (1 UK, 2 Europe, 3 overseas), 7 business science conference (2 UK, 3 Europe, 3 overseas) between 5 investigators.

### 2019-12-03 reviews/reply_to_reviews.md
Crappy first draft

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

No one else has or is currently proposing to take a data science view of domestic abuse. We will be the first to demonstrate how mass administrative data can be used to address domestic abuse. We have a track record in using such data for social science (see

Quispe-Torreblanca, E., & Stewart, N. (2019). Causal peer effects in police misconduct. Nature Human Behaviour. doi: 10.1038/s41562-019-0612-8 Available at https://rdcu.be/bEAue

Adams, P., Guttman-Kenney, B., Hayes, L., Hunt, S., Laibson, D., & Stewart, N. (2018). The semblance of success in nudging consumers to pay down credit card debt. Financial Conduct Authority Occasional Papers in Financial Regulation, 45. https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf

Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployement and disability, and higher mortality rates. This view is unique and the first ever to demonstate such associations---again complementing the traditional qualitative case-study and small survey based approach. I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitiage the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed in place.

## There are factual errors in the reviews:

## There are also unreasonable suggestions:

1. Having Lloyds Banking Group as a partner in the research is a huge asset. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any every used to study domestic abuse.

2. We are aware of the issues when using police data. We are extremely familiar with the West Midlands Police data, and have worked on project is stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources. We are mitigating the issues with police data by working with bank data and with CSEW data.

3. It is not possible to provide a complete review of the literature in a six page proposal. Not is it reasonable to cite studies that are not directly relevant. We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX.

4. We already have access to all relevant data. Concerns raised by reviews XXXXXX are not relevant. We hold te police data here on servers at Warwick. The CSEW is held by XXXX and academic access is straightforward. The Lloyds data are available as postdoc Trendl works inside and is employed by Lloyds Banking Group as well as Warwick. Approvals and data sharing agreements are already signed. We stated this in the proposal.

5. As the application of very large data to research in domestic abuse is novel, there is no one with a track record in domestic abuse research with the required skills in econometrics and data science to conduct this research. Requiring such a background would make it impossible to complete the research, because there is no one with such a background. See below on advisory panel.

We adopt the following adjustments in response to the reviewers:

We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse. The user reviewer has made clear their views of the language used to describe such circumstances. The reviewer is clearly reluctant for this component of the research to be completed. We take an empirical perspective: It is an empirical question whether these children are at risk of future XXXXXXX, one which this proposal will answer.

We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).

We are familiar with the Walby papers on the cost of domestic abuse

We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.

### 2019-12-03 reviews/reply_to_reviews.md
Initial changes to response

@@
 Lloyds are the largest retail bank with 22 million customers.
-It is unnecessary to have data from a second retail bank.
+It is unnecessary to have data from a second retail bank and would be logistically impossible for any researchers.
 By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any every used to study domestic abuse.
@@
 We are aware of the issues when using police data.
-We are extremely familiar with the West Midlands Police data, and have worked on project is stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources.
+We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources.
 We are mitigating the issues with police data by working with bank data and with CSEW data.
@@
 We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX.
+The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals.
+Hence our proposed research to identify reliable indicative patterns in a data scientific approach and build upon the existing work.
 
@@
 Concerns raised by reviews XXXXXX are not relevant.
-We hold te police data here on servers at Warwick.
-The CSEW is held by XXXX and academic access is straightforward.
-The Lloyds data are available as postdoc Trendl works inside and is employed by Lloyds Banking Group as well as Warwick.
+We hold the police data and CSEW data here on servers at Warwick.
+The Lloyds data are immediately available, as postdoc Trendl is currently working with this data, being employed by Lloyds Banking Group as well as Warwick.
 Approvals and data sharing agreements are already signed.
@@
 5.
-As the application of very large data to research in domestic abuse is novel, there is no one with a track record in domestic abuse research with the required skills in econometrics and data science to conduct this research.
-Requiring such a background would make it impossible to complete the research, because there is no one with such a background.
-See below on advisory panel.
+As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
+Requiring such a background would make it impossible to complete the research, because no such individuals exist.
+We have acknowledged this from the start, hence our working closely with policing leads, and why we propose including an advisory panel.
 
@@
 
-We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse.
+We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse, noting that the act of witnessing such events is what makes them victims.
 The user reviewer has made clear their views of the language used to describe such circumstances.
 The reviewer is clearly reluctant for this component of the research to be completed.
-We take an empirical perspective: It is an empirical question whether these children are at risk of future XXXXXXX, one which this proposal will answer.
+We believe this arises from a difference of perspectives: we aim to identify the risk factors for later criminal behaviour, not out of a desire to stereotype or assign blame, but to better identify vulnerable individuals.
+It is an empirical question, whether such individuals are more likely to commit crime later.
+If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.
+
+The reviewer is also reluctant about the investigation of certain socio-economic factors such as the effect of benefit payment systems, expressing concern about potential working class stereotypes.
+Their assertion is absolutely correct that domestic abuse exists in all sections of society.
+However, prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
 
@@
 
-We are familiar with the Walby papers on the cost of domestic abuse
+We are familiar with the Walby papers on the cost of domestic abuse.
+We agree they are important seminal works.
+Our proposal builds upon their results from qualitative works and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 
-We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.
+%We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

@@
 Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
-We have director support from Lloyds Banking Group for the project.
+We have director level support from Lloyds Banking Group for the project.
 Applying data at this scale to the study of domestic abuse has never been done before.
 
-No one else has or is currently proposing to take a data science view of domestic abuse.
-We will be the first to demonstrate how mass administrative data can be used to address domestic abuse.
+No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets.
+Other work focusses on a qualitative approach of case studies and interviews.
+Quantitative work in the area (such as that by Sylvia Walby which was raised by reviewers) has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
+We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse.
 We have a track record in using such data for social science (see
+
+Mullett, T.
+L., Brown, G.
+D.
+A., Fincher, C.
+L., Kosinski, M., & Stillwell, D.
+(2019).
+Individual-Level Analyses of the Impact of Parasite Stress on Personality: Reduced Openness Only for Older Individuals.
+Personality and Social Psychology Bulletin.
+THIS IS THE FACEBOOK DATA PAPER, SHOULD WE WORRY THAT ALL PAPERS ARE NEIL'S?
 
@@
 
-Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployement and disability, and higher mortality rates.
-This view is unique and the first ever to demonstate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
+This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
 I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)
@@
 We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
-We mitiage the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed in place.
+We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
 
@@
 It is unnecessary to have data from a second retail bank and would be logistically impossible for any researchers.
-By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any every used to study domestic abuse.
+By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
 
@@
 The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals.
-Hence our proposed research to identify reliable indicative patterns in a data scientific approach and build upon the existing work.
+Hence our proposed research to build upon this by identifying reliable indicative patterns in a data science approach.
 
@@
 We already have access to all relevant data.
-Concerns raised by reviews XXXXXX are not relevant.
+Concerns raised are not relevant.
 We hold the police data and CSEW data here on servers at Warwick.
-The Lloyds data are immediately available, as postdoc Trendl is currently working with this data, being employed by Lloyds Banking Group as well as Warwick.
+Postdoc Trendl is already working with Lloyds data, being employed by Lloyds Banking Group as well as Warwick.
 Approvals and data sharing agreements are already signed.
@@
 Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with policing leads, and why we propose including an advisory panel.
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

--- 2019-12-03 reviews/reply_to_reviews.md
@@
 %We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.
+
+##Anna comments
+
+###no previous experience in domestic abuse research/no collaboration with experts
+not sure what's the appropriate response to this
+
+###too data-driven/no clear theoretical framework or mention or previous studies/issues about originality as some of the questions have either been examined in the context of other countries or with a qualitative approach
+we are combining data from various sources to address key questions that either have never been examined or have only been examined using one approach - fresh perspectice argument, and emphasize the importance of data driven research.
+The mentioned {r} [ESRC grant] (https://gtr.ukri.org/projects?ref=ES/M01178X/1) looks at improving the DASH using "more sophisticated algorithms than a traditional logistic regression framework." -- I can't find more details on this, but they seem to be only using police data, whereas we are taking a broader view by relying on the very detailed information in the CSEW as well.
+We are also aware of the US literature on domestic abuse victimisation risk factors (which informed our selection of explanatory variables in the proposed analyses), however, we believe that we still lack the proper evidence base for understanding domestic abuse victimisation in the Uk.
+Despite of the documented issues with the CSEW, it is an incredibly rich and useful source of information on domestic abuse victimisation, which has not been exploited.
+Combining insights from the CSEW and police data will complement and validate existing knowledge from qualitative invetsigations.
+
+###issues with the CSEW
+Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repated).
+We are aware of this and plan to combine CSEW data with data from other sources.
+
+####data quality/data access issues/timescales
+
+####"worrying" assumptions
+
+###specific points: 
+young person living at the address -- we'll know this from police records
+police mis-reporting -- comparison of csew and police reports
+reliability of data, ethnicity -- 
+children, only a year of data //
+different explanatory variables for question 1--
+random forest not explaiend--
+causal effects --
+no domestic abuse journals--
+no mention of cost--

### 2019-12-05 reviews/reply_to_reviews.md
Big reshape

@@
 
+We were dismayed by the reviews.
+Only reviewer XXX appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research.
+Reviewers XXX, XXX, and XXX raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
+Our approach contrasts with the qualitative approach using case studies and interviews.
+Our findings will complement this qualitative literature.
+It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics.
+Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work.
+We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
+We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
+
+# Research team experience
+
 No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets.
-Other work focusses on a qualitative approach of case studies and interviews.
-Quantitative work in the area (such as that by Sylvia Walby which was raised by reviewers) has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
+As 199347314 describes, "most research on domestic abuse in the UK context is qualitative in nature".
+Quantitative work in the area has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
 We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse.
 We have a track record in using such data for social science (see
-
 Mullett, T.
@@
 
-Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
+Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
 This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
@@
 
-Our approach contrasts with the qualitative approach using case studies and interviews.
-Our findings will complement this qualitative literature.
-It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics.
-Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work.
-We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
-We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
+We are familiar with the Walby papers described by XXX on the cost of domestic abuse.
+We agree they are important seminal works.
+Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 
-## There are factual errors in the reviews:
+5.
+As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
+Requiring such a background would make it impossible to complete the research, because no such individuals exist.
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
 
-## There are also unreasonable suggestions:
+We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 
-1.
-Having Lloyds Banking Group as a partner in the research is a huge asset.
-Lloyds are the largest retail bank with 22 million customers.
-It is unnecessary to have data from a second retail bank and would be logistically impossible for any researchers.
-By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
-
-2.
-We are aware of the issues when using police data.
-We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources.
-We are mitigating the issues with police data by working with bank data and with CSEW data.
+# Theory
 
@@
 
+# Feasibility of the work
+
 4.
-We already have access to all relevant data.
-Concerns raised are not relevant.
+We already have access to all relevant data, as we stated in the proposal.
 We hold the police data and CSEW data here on servers at Warwick.
-Postdoc Trendl is already working with Lloyds data, being employed by Lloyds Banking Group as well as Warwick.
+Postdoc Trendl is already working with Lloyds data and is an employee of Lloyds Banking Group as well as Warwick University.
 Approvals and data sharing agreements are already signed.
-We stated this in the proposal.
+We stated that access to data is in place and so were dismayed to see the issue raised by reviewers XXX, XXX.
 
-5.
-As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
-Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
+1.
+Having Lloyds Banking Group as a partner in the research is a huge asset.
+Lloyds are the largest retail bank with 22 million customers.
+It is unnecessary to have data from a second retail bank and would be logistically difficult.
+By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
 
-We adopt the following adjustments in response to the reviewers:
+2.
+We are aware of the issues when using police data and CSEW data.
+For example, Walby and Towers have found that the CSEW underestimates the true extent of domestic abuse as it caps the maximum number of incidents (whereas domestic abuse is often repeated).
+We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources.
+We are mitigating the issues with each data set by using multiple data sets .
+
+Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repeated).
+We are aware of this and plan to combine CSEW data with data from other sources.
+
+## There are factual errors in the reviews:
+
+# The sensitive nature of the research topic
 
@@
 Their assertion is absolutely correct that domestic abuse exists in all sections of society.
-However, prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
+But note, the word class appears nowhere in the proposal---our proposed research is not about class.
+Prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
+This is an uncomfortable fact, but ignoring it does not make it false.
 
-We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
-
-We are familiar with the Walby papers on the cost of domestic abuse.
-We agree they are important seminal works.
-Our proposal builds upon their results from qualitative works and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+# ################## Unused Text Below Here #################
 
@@
 ###issues with the CSEW
-Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repated).
-We are aware of this and plan to combine CSEW data with data from other sources.
-
 ####data quality/data access issues/timescales
@@
 ###specific points:
+
 young person living at the address -- we'll know this from police records

### 2019-12-05 reviews/reply_to_reviews.md
Big reshape
Push

@@
 Only reviewer XXX appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research.
-Reviewers XXX, XXX, and XXX raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
+Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
 Our approach contrasts with the qualitative approach using case studies and interviews.
@@
 
-# Research team experience
+## Research team experience
 
@@
 
-We are familiar with the Walby papers described by XXX on the cost of domestic abuse.
-We agree they are important seminal works.
-Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 
@@
 
-We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
-
-# Theory
+## Theory
 
@@
 
-# Feasibility of the work
+We are familiar with the Walby papers described by XXX on the cost of domestic abuse.
+We agree they are important seminal works.
+Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+
+## With Data Access Secured Already, the Project is Viable
 
@@
 Approvals and data sharing agreements are already signed.
-We stated that access to data is in place and so were dismayed to see the issue raised by reviewers XXX, XXX.
+We stated in the proposal that access to data is already in place and so were dismayed to see the issue raised by Reviewer 158241287.
 
@@
 Having Lloyds Banking Group as a partner in the research is a huge asset.
+130837269 was concerned that we are only using data from one retail bank, but this criticism is a misunderstanding.
 Lloyds are the largest retail bank with 22 million customers.
@@
 
-## There are factual errors in the reviews:
-
-# The sensitive nature of the research topic
+## The sensitive nature of the research topic
 
@@
 This is an uncomfortable fact, but ignoring it does not make it false.
+
+##Specific points
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
+---
+output:
+  word_document: default
+  html_document: default
+---
 # The behavioural economics of domestic abuse
 
-## Unique and new big-data perspective
+## A data-driven approach
 
-We bring a data science approach to the study of domestic abuse data.
-We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
-Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data.
+Our proposal offers a novel, data-driven approach to deepen our existing knowledge of domestic abuse in the UK.
+We use data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW; the most extensive national-level survey about domestic abuse victimisation in the UK).
+Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews.
+It is from this qualitative background that the reviewers appear to have come, and we believe that --very carefully putting that they dont have experiences in analysis of big data ---.
+
+For example, the reviewers pointed out that we do not discuss previous literature in detail and that our proposed research programme does not seem to be embedded in an established theoretical framework.
+We are familiar with the research papers mentioned by the reviewers, and these heavily influenced our proposed analyses (as our primary aim was to address gaps in the literature and complement existing knowledge using novel data sources).
+However, it should be recognised that it is simply not possible to provide a literature review and detailed analysis plan within the given page limits, especially given the scale of our project.
+We do not have a explicit theoretical framework, as our research programme is guided by data.
+
+Our proposal focuses on
+
+Our approach is new and ambitious,
+
+yet eminently feasible, as we already hold the necessary data.
 We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
@@
 
-We were dismayed by the reviews.
-Only reviewer XXX appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research.
+We were dismayed by the lack of recognition regarding the unique potential of utilising these extensive datasets and derive novel, policy-relevant insights about domestic abuse.
+
+Only reviewer appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research.
 Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews.
-It is from this qualitative background that the reviewers appear to have come, and we believe that --very carefully putting that they dont have experiences in analysis of big data ---.
+It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers have emphasized .
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews.
-It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers have emphasized .
+It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers mention the importance of using a quantitative approach to study domestic abuse and exploiting the rich information in the CSEW, they do not appear to fully recognise the .
+Secondary data analysis
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 
+Several reviewers made the point that our research team do not have previous experience in domestic abuse research.
+While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we unfortunately could not detail), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+In particular, in the gambling paper we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
+This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+
 No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets.
@@
 We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse.
-We have a track record in using such data for social science (see
-Mullett, T.
-L., Brown, G.
-D.
-A., Fincher, C.
-L., Kosinski, M., & Stillwell, D.
-(2019).
-Individual-Level Analyses of the Impact of Parasite Stress on Personality: Reduced Openness Only for Older Individuals.
-Personality and Social Psychology Bulletin.
-THIS IS THE FACEBOOK DATA PAPER, SHOULD WE WORRY THAT ALL PAPERS ARE NEIL'S?
-
-Quispe-Torreblanca, E., & Stewart, N. (2019). Causal peer effects in police misconduct. Nature Human Behaviour. doi: 10.1038/s41562-019-0612-8 Available at https://rdcu.be/bEAue
-
-Adams, P., Guttman-Kenney, B., Hayes, L., Hunt, S., Laibson, D., & Stewart, N.
-(2018).
-The semblance of success in nudging consumers to pay down credit card debt.
-Financial Conduct Authority Occasional Papers in Financial Regulation, 45.
-https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf
-
-Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
-This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+We have a track record in using such data for social science
  I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

--- 2019-12-05 reviews/reply_to_reviews.md
@@
----
-output:
-  word_document: default
-  html_document: default
----
 # The behavioural economics of domestic abuse
 
-## A data-driven approach
+## Unique and new big-data perspective
 
-Our proposal offers a novel, data-driven approach to deepen our existing knowledge of domestic abuse in the UK.
-We use data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW; the most extensive national-level survey about domestic abuse victimisation in the UK).
-Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews.
-It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers have emphasized .
-
-For example, the reviewers pointed out that we do not discuss previous literature in detail and that our proposed research programme does not seem to be embedded in an established theoretical framework.
-We are familiar with the research papers mentioned by the reviewers, and these heavily influenced our proposed analyses (as our primary aim was to address gaps in the literature and complement existing knowledge using novel data sources).
-However, it should be recognised that it is simply not possible to provide a literature review and detailed analysis plan within the given page limits, especially given the scale of our project.
-We do not have a explicit theoretical framework, as our research programme is guided by data.
-
-Our proposal focuses on
-
-Our approach is new and ambitious,
-
-yet eminently feasible, as we already hold the necessary data.
+We bring a data science approach to the study of domestic abuse data.
+We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
+Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data.
 We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
@@
 
-We were dismayed by the lack of recognition regarding the unique potential of utilising these extensive datasets and derive novel, policy-relevant insights about domestic abuse.
+We were dismayed by the reviews.
+Our approach contrasts with the qualitative approach using case studies and interviews.
+It is from this qualitative background that the reviewers appear to have come.
+Although the reviewers identified that there is a need for quantitative research, in a field dominated by qualitative work, they subsequently focused their reviews on qualitative models and theory.
+Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal.
+Something we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative.
+Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven
 
-Only reviewer appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research.
-Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
-Our approach contrasts with the qualitative approach using case studies and interviews.
-Our findings will complement this qualitative literature.
-It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics.
-Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work.
+The reviewers' criticism is focused on us as new researchers in their domain and on the feasibility of the work.
 We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
 We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
+
+% Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Several reviewers made the point that our research team do not have previous experience in domestic abuse research.
-While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we unfortunately could not detail), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
-In particular, in the gambling paper we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
+While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we chose not to detail to have enough space to outline our empirical strategy), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
 This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+
+## Feasibility
+
+One reviewer raised concerns about the feasibility of the project regarding access to the data.
+We would like to clarify that we already hold the necessary data (with the exception of the CSEW, which is accessible for academic research).
+In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
+Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
+We have director level support from Lloyds Banking Group for the project.
+Applying data at this scale to the study of domestic abuse has never been done before.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
+---
+output:
+  word_document: default
+  html_document: default
+---
 # The behavioural economics of domestic abuse
@@
 
-We bring a data science approach to the study of domestic abuse data.
-We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
+Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
 Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data.
-We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
-Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
-We have director level support from Lloyds Banking Group for the project.
-Applying data at this scale to the study of domestic abuse has never been done before.
 
@@
 
-Several reviewers made the point that our research team do not have previous experience in domestic abuse research.
+Several reviewers made the point that our research team does not have previous experience in domestic abuse research.
 While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we chose not to detail to have enough space to outline our empirical strategy), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
-Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data.
+Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and inetrviews.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Something we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative.
-Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven
-
-The reviewers' criticism is focused on us as new researchers in their domain and on the feasibility of the work.
-We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
-We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
-
-% Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
+Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.
 
@@
 
+We will also establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
+
 ## Feasibility
+
+% Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
 
@@
 
+-------------
+
 No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets.
@@
  I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)
-
-We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
-Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data.
+Our approach is new and ambitious, and has the potential to derive new insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
 
 We were dismayed by the reviews.
-Our approach contrasts with the qualitative approach using case studies and interviews.
-It is from this qualitative background that the reviewers appear to have come.
+Our approach contrasts with the qualitative approach and it is from this background that the reviewers appear to have come.
 Although the reviewers identified that there is a need for quantitative research, in a field dominated by qualitative work, they subsequently focused their reviews on qualitative models and theory.
@@
 
-Several reviewers made the point that our research team does not have previous experience in domestic abuse research.
-While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we chose not to detail to have enough space to outline our empirical strategy), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+Several reviewers made the point that our research team does not have extensive experience in domestic abuse research.
+While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we chose not to detail so there was sufficient space to outline our empirical strategy).
+Our research team is fully qualified to carry out the proposed research programme, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
 In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
@@
 One reviewer raised concerns about the feasibility of the project regarding access to the data.
-We would like to clarify that we already hold the necessary data (with the exception of the CSEW, which is accessible for academic research).
+We would like to clarify that we already hold the necessary data.
 In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
-Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
+Named postdoc Trendl works here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
 We have director level support from Lloyds Banking Group for the project.
@@
 As 199347314 describes, "most research on domestic abuse in the UK context is qualitative in nature".
-Quantitative work in the area has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
-We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse.
-We have a track record in using such data for social science
- I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)
+Quantitative work in the area has only incorporated a single data source (such as the CSEW, _or_ data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 
-Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
+Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW).
 Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and inetrviews.
@@
 Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.
+
+It is not possible to provide a complete review of the literature in a six page proposal whilst also clearly outlining our analysis strategy, especially given the scale of the project.
+We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
+However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 
@@
 3.
-It is not possible to provide a complete review of the literature in a six page proposal.
-Not is it reasonable to cite studies that are not directly relevant.
-We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX.
-The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals.
-Hence our proposed research to build upon this by identifying reliable indicative patterns in a data science approach.
-
-We are familiar with the Walby papers described by XXX on the cost of domestic abuse.
-We agree they are important seminal works.
-Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 
-The reviewers' criticism is focused on us as new researchers in their domain and on the feasibility of the work.
-We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background.
-We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.
-
-% Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
-
 ## Research team experience
@@
 This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+
+We will also establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 
@@
 
+One reviewer raised concerns about the feasibility of the project regarding access to the data.
+We would like to clarify that we already hold the necessary data (with the exception of the CSEW, which is accessible for academic research).
+In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
+Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
+We have director level support from Lloyds Banking Group for the project.
+Applying data at this scale to the study of domestic abuse has never been done before.
+
+-------------
+
 No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets.
@@
 Quantitative work in the area has only incorporated a single data source (such as the CSEW, _or_ data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
-
-We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 ---
-# The behavioural economics of domestic abuse
-
 ## Unique and new big-data perspective
@@
 Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW).
-Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and inetrviews.
+Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
 
@@
 One reviewer raised concerns about the feasibility of the project regarding access to the data.
-We would like to clarify that we already hold the necessary data (with the exception of the CSEW, which is accessible for academic research).
+We would like to clarify that we already hold the necessary data on our servers here at Warwick.
 In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.

### 2019-12-05 reviews/reply_to_reviews.md

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven
+
+It is not possible to provide a complete review of the literature in a six page proposal whilst also clearly outlining our analysis strategy, especially given the scale of the project.
+We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
+However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 

### 2019-12-05 reviews/reply_to_reviews.md

@@
 ---
-# The behavioural economics of domestic abuse
-
 ## Unique and new big-data perspective
 
-Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales.
-Our approach is new and ambitious, and has the potential to derive new insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
+Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW).
+Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
 

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

@@
 As 199347314 describes, "most research on domestic abuse in the UK context is qualitative in nature".
-Quantitative work in the area has only incorporated a single data source (such as the CSEW, _or_ data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors.
+Previous quantitative work in the area has generally been structured around a single data source (such as the CSEW, _or_ data from a police force), and does not incorporate external sources which can provide additional data on potential causes and environmental risk factors.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 Applying data at this scale to the study of domestic abuse has never been done before.
+
+Having Lloyds Banking Group as a partner in the research is a huge asset.
+Reviewer 130837269 was concerned that we are only using data from one retail bank, but this criticism is a misunderstanding.
+Lloyds are the largest retail bank with 22 million customers.
+It is unnecessary to have data from a second retail bank and would be logistically difficult.
+By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
+
+As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
+Requiring such a background would make it impossible to complete the research, because no such individuals exist.
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
 
@@
 # ################## Unused Text Below Here #################
-
-%We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.
-
-##Anna comments
-
-###no previous experience in domestic abuse research/no collaboration with experts
-not sure what's the appropriate response to this
-
-###too data-driven/no clear theoretical framework or mention or previous studies/issues about originality as some of the questions have either been examined in the context of other countries or with a qualitative approach
-we are combining data from various sources to address key questions that either have never been examined or have only been examined using one approach - fresh perspectice argument, and emphasize the importance of data driven research.
-The mentioned {r} [ESRC grant] (https://gtr.ukri.org/projects?ref=ES/M01178X/1) looks at improving the DASH using "more sophisticated algorithms than a traditional logistic regression framework." -- I can't find more details on this, but they seem to be only using police data, whereas we are taking a broader view by relying on the very detailed information in the CSEW as well.
-We are also aware of the US literature on domestic abuse victimisation risk factors (which informed our selection of explanatory variables in the proposed analyses), however, we believe that we still lack the proper evidence base for understanding domestic abuse victimisation in the Uk.
-Despite of the documented issues with the CSEW, it is an incredibly rich and useful source of information on domestic abuse victimisation, which has not been exploited.
-Combining insights from the CSEW and police data will complement and validate existing knowledge from qualitative invetsigations.
-
-###issues with the CSEW
-####data quality/data access issues/timescales
-
-####"worrying" assumptions
-
-###specific points:
-
-young person living at the address -- we'll know this from police records
-police mis-reporting -- comparison of csew and police reports
-reliability of data, ethnicity -- 
-children, only a year of data //
-different explanatory variables for question 1--
-random forest not explaiend--
-causal effects --
-no domestic abuse journals--
-no mention of cost--

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 
-Our proposal aims to bring a data science approach to the study of domestic abuss, by using large-scale data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW).
-Our approach is new and ambitious, and has the potential to derive new insights bout domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
+Our proposal aims to bring a data science approach to the study of domestic abuse, by using multiple large-scale datasets including crime data from the West Midlands Police (serving a population of 2.9 million people), financial transactions data from Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and a national-level victimisation survey (Crime survey for England and Wales; CSEW).
+Our approach is new and ambitious, and has the potential to derive new insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
+In addition, our research team is uniquely placed to deliver this research project, both via the simulatenous access to these datasets that have never been linked to investigate domestic abuse, and in terms of research skills.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our approach is new and ambitious, and has the potential to derive new insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
-In addition, our research team is uniquely placed to deliver this research project, both via the simulatenous access to these datasets that have never been linked to investigate domestic abuse, and in terms of research skills.
+Our research team is uniquely placed to deliver this research project, both in terms of research skills required and access to these datasets that have never been linked to investigate domestic abuse.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our proposal aims to bring a data science approach to the study of domestic abuse, by using multiple large-scale datasets including crime data from the West Midlands Police (serving a population of 2.9 million people), financial transactions data from Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and a national-level victimisation survey (Crime survey for England and Wales; CSEW).
-Our approach is new and ambitious, and has the potential to derive new insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
-Our research team is uniquely placed to deliver this research project, both in terms of research skills required and access to these datasets that have never been linked to investigate domestic abuse.
+Our approach is new and ambitious, and has significant potential to derive novel, policy-relevant insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
+Our research team is uniquely placed to deliver this research project, both in terms of the research skills required to carry out the proposed analyses, and access to these datasets that have never been linked before to investigate domestic abuse.
 
 We were dismayed by the reviews.
-Our approach contrasts with the qualitative approach and it is from this background that the reviewers appear to have come.
-Although the reviewers identified that there is a need for quantitative research, in a field dominated by qualitative work, they subsequently focused their reviews on qualitative models and theory.
-Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal.
-Something we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative.
-Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven
-
-It is not possible to provide a complete review of the literature in a six page proposal whilst also clearly outlining our analysis strategy, especially given the scale of the project.
-We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
-However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+Our approach contrasts with the qualitative approach, and it is from this background that the reviewers appear to have come.
+Although the reviewers seem to have acknowledged that there is a need for quantitative research in a field dominated by qualitative work and that there is scope for the CSEW to be exploited better, they subsequently focused their reviews on qualitative models and theory (or lack thereof).
+Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal, which we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative.
+Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.
 
@@
 
-Several reviewers made the point that our research team does not have extensive experience in domestic abuse research.
-While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we chose not to detail so there was sufficient space to outline our empirical strategy).
+All reviwers made the point that our research team does not have extensive experience in domestic abuse research.
+While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature, and the lack of references in the proposal is merely due to space limitations.
+Indeed, it is not possible to provide a complete (or even a short) review of the literature in a six page proposal, whilst also clearly outlining our analysis strategy, especially given the scale of the project.
+We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
+However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+We are also aware of the ESRC grant ES/M01178X/1 aiming to improve DASH, but our proposal substantially differs from it in its research questions, analysis techniques, and data sources.
+
+As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
+Requiring such a background would make it impossible to complete the research, because no such individuals exist.
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
+
 Our research team is fully qualified to carry out the proposed research programme, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
@@
 
-We will also establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
-
 ## Feasibility
 
-One reviewer raised concerns about the feasibility of the project regarding access to the data.
-We would like to clarify that we already hold the necessary data.
+Reviewer 158241287 raises concerns about the feasibility of the project regarding access to the data.
+We would like to clarify that we already hold the necessary data on our servers here at Warwick.
 In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
@@
 
-One reviewer raised concerns about the feasibility of the project regarding access to the data.
-We would like to clarify that we already hold the necessary data on our servers here at Warwick.
-In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
-Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
-We have director level support from Lloyds Banking Group for the project.
-Applying data at this scale to the study of domestic abuse has never been done before.
-
 Having Lloyds Banking Group as a partner in the research is a huge asset.
-Reviewer 130837269 was concerned that we are only using data from one retail bank, but this criticism is a misunderstanding.
-Lloyds are the largest retail bank with 22 million customers.
+Reviewer 130837269 was concerned that we are only using data from one retail bank (the largest in the UK).
 It is unnecessary to have data from a second retail bank and would be logistically difficult.
-By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
-
-As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
-Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
+By using weighted sampling of the 22 million customers, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Our approach contrasts with the qualitative approach, and it is from this background that the reviewers appear to have come.
-Although the reviewers seem to have acknowledged that there is a need for quantitative research in a field dominated by qualitative work and that there is scope for the CSEW to be exploited better, they subsequently focused their reviews on qualitative models and theory (or lack thereof).
-Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal, which we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative.
+Although the reviewers seem to have acknowledged that there is a need for quantitative research in a field dominated by qualitative work and that there is scope for the CSEW to be exploited to understand domestic abuse, they subsequently focused their reviews on qualitative models and theory (or lack thereof).
+Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal, which we found particularly incongruous, given that this is a proposal for the Secondary Data Analysis Initiative.
 Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 All reviwers made the point that our research team does not have extensive experience in domestic abuse research.
-While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature, and the lack of references in the proposal is merely due to space limitations.
-Indeed, it is not possible to provide a complete (or even a short) review of the literature in a six page proposal, whilst also clearly outlining our analysis strategy, especially given the scale of the project.
+While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature, and the lack of references in the proposal is merely a result of space limitations.
+Indeed, it is not possible to provide a complete (or even a short) review of the literature in a six page proposal, whilst also clearly outlining our analysis strategy, especially given the scale of the proposed project.
 We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
 However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
-We are also aware of the ESRC grant ES/M01178X/1 aiming to improve DASH, but our proposal substantially differs from it in its research questions, analysis techniques, and data sources.
+We are also aware of the ESRC grant ES/M01178X/1 aiming to improve DASH, but our proposal substantially differs from it in terms of research questions, analysis techniques, and data sources.
 
@@
 Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse research, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
 
-Our research team is fully qualified to carry out the proposed research programme, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+There is a vast scope for a data-driven approach to generate novel insights to complement qualitative approaches, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
 In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 
-There is a vast scope for a data-driven approach to generate novel insights to complement qualitative approaches, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+There is a vast scope for a data-driven approach to generate novel insights to complement existing qualitative research, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
 In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
@@
 
+## The sensitive nature of the research topic
+
+We acknowledge that domestic abuse is an extremely sensitive topic, and any research should be done with the lived experiences of victims in mind.
+We take the semantic point raised by Reviewer 185645305 about describing children who witness domestic abuse as victims of domestic abuse, noting that the act of witnessing such events is what makes them victims.
+The reviewer  expressed concern about our proposed analysis investigating criminal behaviour in later life.
+We believe this arises from a difference of perspectives: we aim to identify the risk factors for later criminal behaviour, not out of a desire to stereotype or assign blame (nor we would allow our findings to be used for such purposes), but to better identify vulnerable individuals.
+It is an empirical question, whether such individuals are more likely to commit crime later.
+If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.
+We would also like to note that our data-driven approach will also be able to identify potential protective factors (as suggested by the reviewer).
+
+Reviewer 130837269 is also reluctant about the investigation of certain socio-economic factors, such as the effect of benefit payment systems, expressing concern about potential working class stereotypes.
+Their assertion is absolutely correct that domestic abuse exists in all sections of society.
+But note, the word class appears nowhere in the proposal---our proposed research is not about class.
+Prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
+This is an uncomfortable fact, but ignoring it does not make it false.
+
 -------------
@@
 Previous quantitative work in the area has generally been structured around a single data source (such as the CSEW, _or_ data from a police force), and does not incorporate external sources which can provide additional data on potential causes and environmental risk factors.
-
-5.
-As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
-Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.
-
-## Theory
-
-3.
-
-## With Data Access Secured Already, the Project is Viable
-
-4.
-We already have access to all relevant data, as we stated in the proposal.
-We hold the police data and CSEW data here on servers at Warwick.
-Postdoc Trendl is already working with Lloyds data and is an employee of Lloyds Banking Group as well as Warwick University.
-Approvals and data sharing agreements are already signed.
-We stated in the proposal that access to data is already in place and so were dismayed to see the issue raised by Reviewer 158241287.
-
-1.
-Having Lloyds Banking Group as a partner in the research is a huge asset.
-130837269 was concerned that we are only using data from one retail bank, but this criticism is a misunderstanding.
-Lloyds are the largest retail bank with 22 million customers.
-It is unnecessary to have data from a second retail bank and would be logistically difficult.
-By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
-
-2.
-We are aware of the issues when using police data and CSEW data.
-For example, Walby and Towers have found that the CSEW underestimates the true extent of domestic abuse as it caps the maximum number of incidents (whereas domestic abuse is often repeated).
-We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources.
-We are mitigating the issues with each data set by using multiple data sets .
-
-Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repeated).
-We are aware of this and plan to combine CSEW data with data from other sources.
-
-## The sensitive nature of the research topic
-
-We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse, noting that the act of witnessing such events is what makes them victims.
-The user reviewer has made clear their views of the language used to describe such circumstances.
-The reviewer is clearly reluctant for this component of the research to be completed.
-We believe this arises from a difference of perspectives: we aim to identify the risk factors for later criminal behaviour, not out of a desire to stereotype or assign blame, but to better identify vulnerable individuals.
-It is an empirical question, whether such individuals are more likely to commit crime later.
-If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.
-
-The reviewer is also reluctant about the investigation of certain socio-economic factors such as the effect of benefit payment systems, expressing concern about potential working class stereotypes.
-Their assertion is absolutely correct that domestic abuse exists in all sections of society.
-But note, the word class appears nowhere in the proposal---our proposed research is not about class.
-Prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
-This is an uncomfortable fact, but ignoring it does not make it false.
-
-##Specific points
-
-# ################## Unused Text Below Here #################

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse research, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse research, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (\textcolor{red}{nominated by the charity}).
 
@@
 In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
-This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.
+This view is unique and the first ever to demonstrate such associations -- again complementing the traditional qualitative case-study and small survey based approach.
 

### 2019-12-05 reviews/reply_to_reviews.md
Anna update

@@
 Requiring such a background would make it impossible to complete the research, because no such individuals exist.
-We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse research, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (\textcolor{red}{nominated by the charity}).
+We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse research, and a member of the charity sector (!!!!!!NAME CHARITY!!!!!!!!) and a survivor of domestic abuse (nominated by the charity).
 

### 2019-12-05 reviews/reply_to_reviews.md
needs to be cut down by half a page and add DA charity

@@
 
-All reviwers made the point that our research team does not have extensive experience in domestic abuse research.
+All reviewers made the point that our research team does not have extensive experience in domestic abuse research.
 While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature, and the lack of references in the proposal is merely a result of space limitations.
@@
 
-Reviewer 130837269 is also reluctant about the investigation of certain socio-economic factors, such as the effect of benefit payment systems, expressing concern about potential working class stereotypes.
+Reviewer 130837269 is reluctant about the investigation of certain socio-economic factors, such as the effect of benefit payment systems, expressing concern about potential working class stereotypes.
 Their assertion is absolutely correct that domestic abuse exists in all sections of society.

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

@@
 
-Our proposal aims to bring a data science approach to the study of domestic abuse, by using multiple large-scale datasets including crime data from the West Midlands Police (serving a population of 2.9 million people), financial transactions data from Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and a national-level victimisation survey (Crime survey for England and Wales; CSEW).
+Our proposal brings a data science approach to the study of domestic abuse, by using multiple large-scale datasets including crime data from the West Midlands Police (serving a population of 2.9 million people), financial transactions data from Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and a national-level victimisation survey (Crime survey for England and Wales; CSEW).
 Our approach is new and ambitious, and has significant potential to derive novel, policy-relevant insights about domestic abuse in the UK and complement the existing body of knowledge on the topic, which has been predominantly generated via qualitative research methods, such as case studies and interviews.
 Our research team is uniquely placed to deliver this research project, both in terms of the research skills required to carry out the proposed analyses, and access to these datasets that have never been linked before to investigate domestic abuse.
+We can envisage no better alternative.
+We are well aware of the issues in the datasets, and know from long experience that there is no other collection of datasets available for research that is better, or equal to what we propose.
+This is unique.
+***I SUSPECT NEIL WILL JAZZ THESE FEW SENTENCES UP A BIT***
 
@@
 Our approach contrasts with the qualitative approach, and it is from this background that the reviewers appear to have come.
-Although the reviewers seem to have acknowledged that there is a need for quantitative research in a field dominated by qualitative work and that there is scope for the CSEW to be exploited to understand domestic abuse, they subsequently focused their reviews on qualitative models and theory (or lack thereof).
+Although the reviewers acknowledged that there is a need for quantitative research in a field dominated by qualitative work, they subsequently focused their reviews on qualitative models and theory.
 Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal, which we found particularly incongruous, given that this is a proposal for the Secondary Data Analysis Initiative.
-Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.
+Furthermore, recent results from a related ESRC grant (ES/M01178X/1) have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven.
 
@@
 All reviewers made the point that our research team does not have extensive experience in domestic abuse research.
-While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature, and the lack of references in the proposal is merely a result of space limitations.
-Indeed, it is not possible to provide a complete (or even a short) review of the literature in a six page proposal, whilst also clearly outlining our analysis strategy, especially given the scale of the proposed project.
-We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the limitations of the CSEW.
-However, our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
+While we do not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature cited by reviewers, and the lack of references in the proposal is merely a result of space limitations.
+Indeed, it is not possible to provide a complete review of the literature in a six page proposal whilst also clearly outlining our analysis strategy, and given the complexity of the data and proposed analyses, we focused upon the proposed methods.
+We are fully aware of the studies by Walby and Towers, and we agree they are important seminal works highlighting the benefits and limitations of the CSEW.
+However, our proposal builds upon the qualitative findings and prior analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.
 We are also aware of the ESRC grant ES/M01178X/1 aiming to improve DASH, but our proposal substantially differs from it in terms of research questions, analysis techniques, and data sources.
 
-As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research.
+As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research.
 Requiring such a background would make it impossible to complete the research, because no such individuals exist.
@@
 In addition, we have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse.
-Named postdoc Trendl works here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team.
-We have director level support from Lloyds Banking Group for the project.
-Applying data at this scale to the study of domestic abuse has never been done before.
+We have director level support from Lloyds Banking Group for the project, where named postdoc Trendl is an employee in their behavioural and data science team, as well as being at Warwick.
+Applying data at this scale to the study of domestic abuse has never been done before but we, uniquely, have the agreements and infrastructure in place to begin immediately.
 
@@
 Reviewer 130837269 was concerned that we are only using data from one retail bank (the largest in the UK).
-It is unnecessary to have data from a second retail bank and would be logistically difficult.
+It is unnecessary to have data from a second retail bank and logistically would be virtually impossible for any researcher given it's secure and proprietary nature.
 By using weighted sampling of the 22 million customers, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.
@@
 If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.
-We would also like to note that our data-driven approach will also be able to identify potential protective factors (as suggested by the reviewer).
+We also note that our data-driven approach will identify potential protective factors (as suggested by the reviewer).
 
@@
 Prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.
-This is an uncomfortable fact, but ignoring it does not make it false.
+This is an uncomfortable fact, but ignoring it does not make it false, and again allows us to identify protective changes that could be made, such as changes to benefit payment schedules.
 

### 2019-12-05 reviews/reply_to_reviews.md
First paragraph

@@
 Our research team is uniquely placed to deliver this research project, both in terms of the research skills required to carry out the proposed analyses, and access to these datasets that have never been linked before to investigate domestic abuse.
-We can envisage no better alternative.
-We are well aware of the issues in the datasets, and know from long experience that there is no other collection of datasets available for research that is better, or equal to what we propose.
-This is unique.
-***I SUSPECT NEIL WILL JAZZ THESE FEW SENTENCES UP A BIT***
+Without funding, this unique opportunity to link datasets will be missed.
+With domestic abuse at this scale, even marginal gains will help thousands of women.
 

### 2019-12-05 reviews/reply_to_reviews.md
Update reply_to_reviews.md

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 Reviewer 130837269 was concerned that we are only using data from one retail bank (the largest in the UK).
-It is unnecessary to have data from a second retail bank and logistically would be virtually impossible for any researcher given it's secure and proprietary nature.
+It is unnecessary to have data from a second retail bank and logistically would be virtually impossible for any researcher given its secure and proprietary nature.
 By using weighted sampling of the 22 million customers, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.

### 2019-12-05 reviews/reply_to_reviews.md
Typo

--- 2019-12-05 reviews/reply_to_reviews.md
@@
 
-There is a vast scope for a data-driven approach to generate novel insights to complement existing qualitative research, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
+There is a vast scope for a data-driven approach to generate novel insights to complement existing qualitative research, as is demonstrated by numerous, high-impact publications in other, policy-relevant research topics.
+Our team has recently written papers estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test environmental effects on behaviour and personality](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).
 In particular, in the gambling paper, we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates.
